### 2015-10-11 paper2.tex
set up template

% mnras_template.tex
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[a4paper,fleqn,usenatbib]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
%\usepackage{newtxtext,newtxmath} % not yet supported on arxiv and uni computer
%\usepackage{txfonts}

% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Short title, max. 45 characters]{MNRAS \LaTeXe\ template -- title goes here}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[R. Kueng et al.]{
Rafael Kueng,$^{1}$\thanks{E-mail: rafael.kueng@uzh.ch}
Presenjit Saha,$^{1}$
Third Author$^{2,3}$
and Fourth Author$^{3}$
\\
% List of institutions
$^{1}$Physik Institut, University of Zurich, Winterthurerstrasse XXX, Zurich 8057, Switzerland\\
$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2015}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}

%This is a simple template for authors to write new MNRAS papers.
%The abstract should briefly describe the aims, methods, and main results of the paper.
%It should be a single paragraph not more than 250 words (200 words for Letters).
%No references should appear in the abstract.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
keyword1 -- keyword2 -- keyword3
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:
\bibliographystyle{mnras}
\bibliography{bib/bibli} % if your bibtex file is called example.bib

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendix

\section{Some extra material}

If you want to present additional material which would interrupt the flow of the main paper,
it can be placed in an Appendix which appears after the list of references.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%% END %%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% 
% \section{Introduction}
% 
% This is a simple template for authors to write new MNRAS papers.
% See \texttt{mnras\_sample.tex} for a more complex example, and \texttt{mnras\_guide.tex}
% for a full user guide.
% 
% All papers should start with an Introduction section, which sets the work
% in context, cites relevant earlier studies in the field by \citet{Others2013},
% and describes the problem the authors aim to solve \citep[e.g.][]{Author2012}.
% 
% \section{Methods, Observations, Simulations etc.}
% 
% Normally the next section describes the techniques the authors used.
% It is frequently split into subsections, such as Section~\ref{sec:maths} below.
% 
% \subsection{Maths}
% \label{sec:maths} % used for referring to this section from elsewhere
% 
% Simple mathematics can be inserted into the flow of the text e.g. $2\times3=6$
% or $v=220$\,km\,s$^{-1}$, but more complicated expressions should be entered
% as a numbered equation:
% 
% \begin{equation}
%     x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}.
% 	\label{eq:quadratic}
% \end{equation}
% 
% Refer back to them as e.g. equation~(\ref{eq:quadratic}).
% 
% \subsection{Figures and tables}
% 
% Figures and tables should be placed at logical positions in the text. Don't
% worry about the exact layout, which will be handled by the publishers.
% 
% Figures are referred to as e.g. Fig.~\ref{fig:example_figure}, and tables as
% e.g. Table~\ref{tab:example_table}.
% 
% % Example figure
% \begin{figure}
% 	% To include a figure from a file named example.*
% 	% Allowable file formats are eps or ps if compiling using latex
% 	% or pdf, png, jpg if compiling using pdflatex
% 	\includegraphics[width=\columnwidth]{example}
%     \caption{This is an example figure. Captions appear below each figure.
% 	Give enough detail for the reader to understand what they're looking at,
% 	but leave detailed discussion to the main body of the text.}
%     \label{fig:example_figure}
% \end{figure}
% 
% % Example table
% \begin{table}
% 	\centering
% 	\caption{This is an example table. Captions appear above each table.
% 	Remember to define the quantities, symbols and units used.}
% 	\label{tab:example_table}
% 	\begin{tabular}{lccr} % four columns, alignment for each
% 		\hline
% 		A & B & C & D\\
% 		\hline
% 		1 & 2 & 3 & 4\\
% 		2 & 4 & 6 & 8\\
% 		3 & 5 & 7 & 9\\
% 		\hline
% 	\end{tabular}
% \end{table}
% 
% 
% \section{Conclusions}
% 
% The last numbered section should briefly summarise what has been done, and describe
% the final conclusions which the authors draw from their work.
% 
% \section*{Acknowledgements}
% 
% The Acknowledgements section is not numbered. Here you can thank helpful
% colleagues, acknowledge funding agencies, telescopes and facilities used etc.
% Try to keep it short.
% 
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% %%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
% 
% % The best way to enter references is to use BibTeX:
% 
% %\bibliographystyle{mnras}
% %\bibliography{example} % if your bibtex file is called example.bib
% 
% 
% % Alternatively you could enter them by hand, like this:
% % This method is tedious and prone to error if you have lots of references
% \begin{thebibliography}{99}
% \bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
% Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
% \bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
% Others S., 2012, Journal of Interesting Stuff, 17, 198
% \end{thebibliography}
% 
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% %%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
% 
% \appendix
% 
% \section{Some extra material}
% 
% If you want to present additional material which would interrupt the flow of the main paper,
% it can be placed in an Appendix which appears after the list of references.
% 
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% 
% % Don't change these lines
% \bsp	% typesetting comment
% \label{lastpage}
% \end{document}
% 
% % End of mnras_template.tex

### 2015-12-18 paper2.tex
comments on lenses

@@
 % Keep the title short and informative.
-\title[Short title, max. 45 characters]{MNRAS \LaTeXe\ template -- title goes here}
+\title[Short title, max. 45 characters]{Preliminary categorisation of SpaceWarps candidates}
 
@@
 \pubyear{2015}
+
+\newcommand{\inclfig}[2]{
+	\includegraphics[width=0.49\linewidth]{spaghetti/#2_input.png}
+	\includegraphics[width=0.49\linewidth]{spaghetti/#2_img1.png}
+	\includegraphics[width=0.49\linewidth]{spaghetti/#2_img3_ipol.png}
+	\includegraphics[width=0.49\linewidth]{spaghetti/#2_img2.png}
+	\includegraphics[width=1\linewidth]{masses/#1_#2_mstel_vs_mtot.png}
+}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Introduction}
+
+\section{Methods}
+
+\section{Results}
+We came up with four kind of candidates.
+
+\subsection{HiRes image}
+Almost certain candidates, that qualify for follow up hires observations
+
+\subsection{Spectra}
+Candidates to follow up with a spectral analysis.
+
+\subsection{Bad models}
+Candidates that need more work to be modelled.
+Or that have features that are hard / impossible to model with the current SpaghettiLens version.
+Examples are group lenses
+
+\subsection{Non Lenses}
+Those are most probly non lenses,
+
+\subsection{plausible}
+\begin{itemize}
+  \item SW01 (ASW0004dv8) \\
+
+  \item SW08 (ASW00099ed) \\
+  Simple lens with two images;
+  model has minor arthefacts
+
+  \item SW11 (ASW0002qtn) \\
+  Simple small arc;
+  model nedes minor refinement;
+  quite low mass ratio
+
+  \item SW12 (ASW0003wsu) \\
+  faint arc, bright overall situation, no counter image;
+  has good model;
+  low Mstel and low Mlens
+
+  \item SW21 (ASW0004m3x) \\
+  clear arc, no counter image; inbetween two external sources;
+  model needs work, predicts additional images. play with external mass / sheer?
+  Mass ratio low.
+
+  \item SW27 (ASW0006jh5) \\
+  (really plausible?)
+  unclear situation, but arc is visible;
+  model shows extended arc not there in org image;
+  mass ratio ok
+
+  \item SW31 (ASW00021r0) \\
+  (really plausible?)
+  noisy situation, unclear images, potential external mass interfering;
+  model ok'ish, hard to say;
+  high mass ratio
+
+  \item SW33 (ASW0003s0m)\\
+  clear picture, two image situation;
+  model simple, but ok. arc too much extended;
+  masses in the middle, but rather high ratio
+
+  \item SW36 (ASW000096t) \\
+  noisy picture, many possible external masses, faint images;
+  model predicts additional images, needs more work, arc too extended;
+  masses look ok
+
+  \item SW38 (ASW0009cp0) \\
+  quite clean picture, two bright minima, counter image hidden;
+  model fine
+  really hi stellar mass
+
+  \item SW43 (ASW0001c3j) \\
+  clean situation, faint arc'ish images;
+  model needs work, shows additional images, strange arc (LHD);
+  very high Mstel
+
+  \item SW45 (ASW00024id)\\
+  ring like structure, very clean \\
+  usual problems with rings, otherwise model quite ok actually;
+  very high Mstel
+
+  \item SW46 (ASW00024q6) \\
+  yellow'ish arc, two image configuration;
+  model ok;
+  masses ok
+
+  \item SW52 (ASW0006a07) \\
+  (no imgs)
+
+  \item SW54 (ASW0007sez) \\
+  white lens, fuzzy ring like structure;
+  model really good, given ring like;
+  masses ok
+
+  \item SW58 (ASW0007iwp) \\
+  nice arc, no counter image;
+  model prediction really good;
+  masses ok
+
+\end{itemize}
+
+good example of plausible
+
+% \begin{figure}
+% 	\inclfig{SW45}{ASW000024id_TSKKYHD3CB}
+% \end{figure}
+
+\begin{figure}
+	\inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
+\end{figure}
+
+\subsubsection{grouplens}
+
+\begin{figure}
+	\inclfig{SW36}{ASW000096t_7IPP7LWVOF}
+\end{figure}
+
+(like 4dv8 collective modelling)
+
+\subsection{unclear}
+\begin{itemize}
+  \item SW04 (ASW0009cjs) \\
+  noisy field, possible group lens, but images not typical? (no arclike structure);
+  model fail (input errors);
+  Mlens too high (10e13)
+
+  \item SW06 (ASW0008swn)\\
+  green images, elongated lens, images on strange positions?;
+  model ok'ish, but mass distr. doesn't reflect visuals;
+  masses ok
+
+  \item SW07 (ASW0007e08) \\
+  (no img)
+
+  \item SW13 (ASW00047ae) \\
+  croweded situation unclear setup;
+  model failed, predicts additional images;
+  masses ok
+
+  \item SW15 (ASW0004nan) \\
+  no counter image (should be visible)?
+  model ok'ish;
+  Mlens on the lower end
+
+  \item SW17 (ASW0005rnb) \\
+  two image setup, but arcish structure of images missing;
+  model failed, predicts additional images, rednering failed;
+
+  \item SW19 (ASW0001ld7) \\
+  asymmetry / really extended arc and no counter image rather no lensing configuration;
+  rendering ok'ish, model predicts additionla images;
+  Mstel and Mlens way too low (e10 / e11)
+
+  \item SW24 (ASW00050sk) \\
+  unclear / noisy situation, shape of arc strange;
+  model ok;
+  mass ration close to unity
+
+  \item SW32 (ASW0004iye) \\
+  (no img)
+
+  \item SW35 (ASW0004wgd) \\
+  hard to say, doesn't look convincing, but neither totally off
+  modell ok;
+  masses as well;
+
+  \item SW44 (ASW0002k40) \\
+  (no img);
+  very old model;
+  hi mass ratio
+
+  \item SW47 (ASW0003r6c) \\
+  two images, no arcish structre.. too far away from lens?;
+  model predicts additional images;
+  quite high mass ratio
+
+  \item SW51 (ASW0006e0o) \\
+  (no img)
+
+  \item SW56 (ASW0007pga) \\
+  very ellyptical lens, images not really arcish;
+  model failed, predicts additional images;
+  masses ok
+
+  \item SW57 (ASW0008pag) \\
+  point mass / group lens interfering? symertry of arc off;
+  model failed completly;
+  Mlens too high
+
+\end{itemize}
+
+\begin{figure}
+	\inclfig{SW19}{ASW0001ld7_OS3CYAKLRT}
+\end{figure}
+
+\begin{figure}
+	\inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
+\end{figure}
+
+\subsection{convincing}
+\begin{itemize}
+  \item SW02 (ASW000619d) \\
+
+  \item SW05 (ASW0007k4r) \\
+
+  \item SW09 (ASW0002asp) \\
+
+  \item SW28 (ASW0007xrs) \\
+
+  \item SW29 (ASW0008qsm) \\
+
+\end{itemize}
+
+\begin{figure}
+	\inclfig{SW02}{ASW000619d_011489}
+\end{figure}
+
+\begin{figure}
+	\inclfig{SW05}{ASW0007k4r_AJIBCHQ6EM}
+\end{figure}
+
+\begin{figure}
+	\inclfig{SW09}{ASW0002asp_5EKMWWVJHL}
+\end{figure}
+
+\begin{figure}
+	\inclfig{SW28}{ASW0007xrs_JHC3J2HYV7}
+\end{figure}
+
+\begin{figure}
+	\inclfig{SW29}{ASW0008qsm_TOFS7JNGEK}
+\end{figure}
+
+\subsection{doubtful}
+\begin{itemize}
+  \item SW10 (ASW0002bmc) \\
+  very elliptical setup, unlikley to be a lens;
+  model failed totally
+
+  \item SW16 (ASW0009bp2) \\
+  very faint images
+
+  \item SW18 (ASW0007hu2) \\
+  model failed completly
+
+  \item SW20 (ASW0002dx7) \\
+  faint white images, rather substuctre of ``lens'' ??
+
+  \item SW22 (ASW0009ab8) \\
+  very faint images, group configuration;
+  model predicts additional images;
+  mass ration close to unity
+
+  \item SW23 (ASW0003r61) \\
+  (no img)
+
+  \item SW26 (ASW0005ma2) \\
+  similar to SW10
+
+  \item SW34 (ASW00051ld) \\
+  (no img)
+
+  \item SW41 (ASW0008xbu) \\
+  similar to SW10. very ellyptical lens
+
+  \item SW42 (ASW00096rm) \\
+  ring like structure, but very strange distribution;
+  model not too bad, brightnesses off;
+  stellar mass way too lower
+
+  \item SW53 (ASW00070vl) \\
+  images don't look liked lensed;
+  model predicts additional images
+
+\end{itemize}
+
+outlier because very odd mass ratio
+\begin{figure}
+	\inclfig{SW42}{ASW00096rm_4Q3YCEWGLN}
+\end{figure}
+
+\subsection{missing}
+\begin{itemize}
+  \item SW03 (ASW0006mea)
+  \item SW14 (ASW0004xjk)
+  \item SW25 (ASW00007mq)
+  \item SW30 (ASW0002p8y)
+  \item SW37 (ASW00086xq)
+  \item SW39 (ASW0005qiz)
+  \item SW40 (ASW0008wmr)
+  \item SW48 (ASW0000g95)
+  \item SW49 (ASW00007ls)
+  \item SW50 (ASW00008a0)
+  \item SW55 (ASW0007t5y)
+  \item SW59 (ASW00085cp)
+\end{itemize}
 

### 2016-03-23 paper2.tex
added lucys text

@@
 
+\newcommand{\inclfig}[2]{
+  \includegraphics[width=0.49\linewidth]{spaghetti/#2_input.png}
+  \includegraphics[width=0.49\linewidth]{spaghetti/#2_img1.png}
+  \includegraphics[width=0.49\linewidth]{spaghetti/#2_img3_ipol.png}
+  \includegraphics[width=0.49\linewidth]{spaghetti/#2_img2.png}
+  \includegraphics[width=1\linewidth]{masses/#1_#2_mstel_vs_mtot.png}
+}
+
+\newcommand{\lenstitle}[1]{\noindent\textit{#1}\quad}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Presenjit Saha,$^{1}$
-Third Author$^{2,3}$
-and Fourth Author$^{3}$
+Lucy Oswald$^{3}$
+%and Fourth Author$^{4}$
 \\
@@
 $^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
+%$^{4}$Another Department, Different Institution, Street Address, City Postal Code, Country
 }
@@
 % Enter the current year, for the copyright statements etc.
-\pubyear{2015}
-
-\newcommand{\inclfig}[2]{
-	\includegraphics[width=0.49\linewidth]{spaghetti/#2_input.png}
-	\includegraphics[width=0.49\linewidth]{spaghetti/#2_img1.png}
-	\includegraphics[width=0.49\linewidth]{spaghetti/#2_img3_ipol.png}
-	\includegraphics[width=0.49\linewidth]{spaghetti/#2_img2.png}
-	\includegraphics[width=1\linewidth]{masses/#1_#2_mstel_vs_mtot.png}
-}
+\pubyear{2016}
 
@@
 
+\subsection{Parameterisation of pixel models}
+In order to fit the set of pixelated models to a single parameterised model, a program was written that took a parameterised function and subtracted from it the mean and the principle components of the data, which were calculated using classical Principle Component Analysis.
+This created the residuals function.
+The number of components defined as principle was varied to test how this affected the output, and it was found that using 5 principle components tended to give a reasonable approximation.
+A masking function was added which selected only the data points that fell inside the image of the lens, and the principal components were clipped in order to keep the values inside the region of the ensemble of models.
+Any value higher than the clip was set to be the clip value.
+This was chosen to be 2.5 as, assuming that the data follows a Gaussian error distribution, almost all the values for the variance should lie between 2 and 3 standard deviations from the mean.
+Minimising the residuals function produces the set of parameters that fit the parameterised function to the original pixelated ensemble most closely.
+A least squares fit was used to perform this minimisation.
+
+The parameterised model function was obtained from the gravitational potential of an isothermal ellipsoid mass distribution (Keeton, 2002).
+This model is frequently used to describe gravitational lenses as it tends to fit well with observations.
+The isothermal ellipsoid model outputs three useful parameters: the radius of the Einstein ring, the ellipticity of the model and the angle of the ellipticity from the vertical, giving the orientation of the galaxy.
+By applying this model to simulated lenses for which the values of these parameters were already known, it was possible to gain an estimate of the projected accuracy of the results, before applying the model to the candidate lensing galaxies.
+
+%TODO append this to the bibliography file (bibli.bib)
+% References
+% Keeton C.
+% R., 2002, “A Catalog of Mass Models for Gravitational Lensing”, arXiv:astro-ph/0102341v2
+
 \section{Results}
@@
 \subsection{plausible}
-\begin{itemize}
-  \item SW01 (ASW0004dv8) \\
 
-  \item SW08 (ASW00099ed) \\
+\lenstitle{SW01 (ASW0004dv8)}
+	This is some text that says somwthing more than this line.
+
+\lenstitle{SW08 (ASW00099ed)}
   Simple lens with two images;
-  model has minor arthefacts
+  model has minor arthefacts.
 
-  \item SW11 (ASW0002qtn) \\
+\lenstitle{SW11 (ASW0002qtn)}
   Simple small arc;
@@
 
+\begin{itemize}
   \item SW12 (ASW0003wsu) \\

### 2016-04-08 paper2.tex
more refs
compile without errors

@@
 % Basic setup. Most papers should leave these options alone.
-\documentclass[a4paper,fleqn,usenatbib]{mnras}
+\documentclass[fleqn,usenatbib]{mnras}
 
@@
 \usepackage[T1]{fontenc}
-\usepackage{ae,aecompl}
+%\usepackage{ae,aecompl}
 
@@
 % Only include extra packages if you really need them. Common packages are:
-\usepackage{graphicx}	% Including figure files
+\usepackage[dvipdfmx]{graphicx}	% Including figure files
 \usepackage{amsmath}	% Advanced maths commands
 \usepackage{amssymb}	% Extra maths symbols
+\usepackage{bmpsize}
 
@@
 \newcommand{\inclfig}[2]{
-  \includegraphics[width=0.49\linewidth]{spaghetti/#2_input.png}
-  \includegraphics[width=0.49\linewidth]{spaghetti/#2_img1.png}
-  \includegraphics[width=0.49\linewidth]{spaghetti/#2_img3_ipol.png}
-  \includegraphics[width=0.49\linewidth]{spaghetti/#2_img2.png}
-  \includegraphics[width=1\linewidth]{masses/#1_#2_mstel_vs_mtot.png}
+  \centering
+  \includegraphics[width=0.49\linewidth]{spaghetti/#2_input} %
+  \includegraphics[width=0.49\linewidth]{spaghetti/#2_img1} \\
+  \includegraphics[width=0.49\linewidth]{spaghetti/#2_img3_ipol} %
+  \includegraphics[width=0.49\linewidth]{spaghetti/#2_img2} \\
+  \includegraphics[width=1\linewidth]{masses/#1_#2_mstel_vs_mtot}
 }
 
-\newcommand{\lenstitle}[1]{\noindent\textit{#1}\quad}
+\newcommand{\lenstitle}[1]{\noindent\textit{#1} --}
 
@@
 \begin{abstract}
-
-%This is a simple template for authors to write new MNRAS papers.
-%The abstract should briefly describe the aims, methods, and main results of the paper.
-%It should be a single paragraph not more than 250 words (200 words for Letters).
-%No references should appear in the abstract.
+This is a simple template for authors to write new MNRAS papers.
+The abstract should briefly describe the aims, methods, and main results of the paper.
+It should be a single paragraph not more than 250 words (200 words for Letters).
+No references should appear in the abstract.
 \end{abstract}
@@
 
+Here we cite \cite{2015MNRAS.447.2170K}.
+
 \section{Methods}
@@
 
-The parameterised model function was obtained from the gravitational potential of an isothermal ellipsoid mass distribution (Keeton, 2002).
+The parameterised model function was obtained from the gravitational potential of an isothermal ellipsoid mass distribution \cite{2001astro.ph..2340K}.
 This model is frequently used to describe gravitational lenses as it tends to fit well with observations.
@@
   \inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
+  \caption{}
 \end{figure}

### 2016-04-08 paper2.tex
clean up images

@@
 \usepackage{amssymb}	% Extra maths symbols
-\usepackage{bmpsize}
+%\usepackage{bmpsize}
+
+% I disabled hyperlink in the cls und included it here because of bugs
+\usepackage{hyperref}   % Hyperlinks
+\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,filecolor=blue,urlcolor=blue}
 
@@
 \lenstitle{SW01 (ASW0004dv8)}
-  This is some text that says somwthing more than this line.
+  This is some text that says something more than this line.
 
@@
 \begin{itemize}
-  \item SW02 (ASW000619d) \\
+  \item SW02 (ASW000619d)
 
-  \item SW05 (ASW0007k4r) \\
+  \item SW05 (ASW0007k4r)
 
-  \item SW09 (ASW0002asp) \\
+  \item SW09 (ASW0002asp)
 
-  \item SW28 (ASW0007xrs) \\
+  \item SW28 (ASW0007xrs)
 
-  \item SW29 (ASW0008qsm) \\
+  \item SW29 (ASW0008qsm)
 
@@
 \bibliographystyle{mnras}
-\bibliography{bib/bibli} % if your bibtex file is called example.bib
+\bibliography{bib/bibli.bib} % if your bibtex file is called example.bib
 

### 2016-04-13 paper2.tex
compiling without error

@@
 
+\usepackage{silence} % silence error warinings
+\WarningFilter{caption}{Unsupported document class} % caption doesn't know mnras..
+
 % MNRAS is set in Times font. If you don't have this installed (most LaTeX
@@
 % Don't change these lines unless you know what you are doing
-\usepackage[T1]{fontenc}
-%\usepackage{ae,aecompl}
+\usepackage[T1]{fontenc} % make sure font is supported
+% \usepackage{ae,aecompl} %obsolete when using modern fonts
+\usepackage[final]{microtype} % make sure font is supported
+% and a suitable font
+\usepackage{lmodern} % use a modern font with T1 support
+%\usepackage{cm-super} % use a modern font with T1 support
 
@@
 % Only include extra packages if you really need them. Common packages are:
-\usepackage[dvipdfmx]{graphicx}	% Including figure files
+%\usepackage[dvipdfmx]{graphicx}	% Including figure files
+\usepackage{graphicx} % Including figure files
+\usepackage[skip=0pt]{subcaption}
 \usepackage{amsmath}	% Advanced maths commands
 \usepackage{amssymb}	% Extra maths symbols
-%\usepackage{bmpsize}
+%\usepackage{bmpsize}  % PS still needs this for correct bounding boxes?
+
+% TODO stuff, comment out for final submit
+\usepackage{todonotes} % as long as we are editing...
+\usepackage{showframe} % for debug
+\overfullrule=5pt      % show overfull boxes
 
@@
   \centering
-  \includegraphics[width=0.49\linewidth]{spaghetti/#2_input} %
-  \includegraphics[width=0.49\linewidth]{spaghetti/#2_img1} \\
-  \includegraphics[width=0.49\linewidth]{spaghetti/#2_img3_ipol} %
-  \includegraphics[width=0.49\linewidth]{spaghetti/#2_img2} \\
-  \includegraphics[width=1\linewidth]{masses/#1_#2_mstel_vs_mtot}
+  \begin{subfigure}{0.5\linewidth}
+    \includegraphics[width=\linewidth]{spaghetti/#2_input}
+  \end{subfigure}%
+  \begin{subfigure}{0.5\linewidth}
+    \includegraphics[width=\linewidth]{spaghetti/#2_img1}
+  \end{subfigure}%
+  \\[-1px]%
+  \begin{subfigure}{0.5\linewidth}
+    \includegraphics[width=\linewidth]{spaghetti/#2_img3_ipol}
+  \end{subfigure}%
+  \begin{subfigure}{0.5\linewidth}
+    \includegraphics[width=\linewidth]{spaghetti/#2_img2}
+  \end{subfigure}%
+  \\[-1px]%
+  \begin{subfigure}[b]{\linewidth}
+    \includegraphics[width=\linewidth]{masses/#1_#2_mstel_vs_mtot}
+  \end{subfigure}
 }
 
-\newcommand{\lenstitle}[1]{\noindent\textit{#1} --}
+\newcommand{\lenstitle}[1]{\noindent\textbf{#1} --}
 
@@
 
-%TODO append this to the bibliography file (bibli.bib)
-% References
-% Keeton C.
-% R., 2002, “A Catalog of Mass Models for Gravitational Lensing”, arXiv:astro-ph/0102341v2
+\subsection{HiRes image}
+Almost certain candidates, that qualify for follow up hires observations
 
@@
 We came up with four kind of candidates.
-
-\subsection{HiRes image}
-Almost certain candidates, that qualify for follow up hires observations
 
@@
 \subsection{plausible}
+  The plausible candidates fail in one category, but are quite convincing in all the others.
+  Thats why we recomend them for a following up study for ...
 
@@
 
+\newpage
+
+\section{TODO}
+\listoftodos
+
+\todo{REMOVE TODOS at the end}
+
 % Don't change these lines

### 2016-04-18 paper2.tex
added imgs

@@
 
+%%% DEBUG SETTINGS - remove at the end %%%%%%%%%%%%%%%
 \usepackage{silence} % silence error warinings
 \WarningFilter{caption}{Unsupported document class} % caption doesn't know mnras..
+\hbadness = 5000
+\vbadness = 10000
+\usepackage{}
 
@@
 \newcommand{\lenstitle}[1]{\noindent\textbf{#1} --}
+\newcommand{\params}[3]{(\(\Theta_\text{E}:#1\), $\varepsilon:#2$, $\alpha_\varepsilon:#3$ )}
+
+\newcommand{\asw}[1]{ASW000#1}
+\newcommand{\sw}[1]{SW~#1}
+\newcommand{\model}[1]{SL model~#1}
+
+\newcommand{\figref}[1]{Figure \ref{fig:#1}}
+\newcommand{\Figref}[1]{Figure \ref{fig:#1}}
 
@@
 
-\subsection{Parameterisation of pixel models}
+\subsection{Parameterisation of pixel models} \label{sec:parameter}
 In order to fit the set of pixelated models to a single parameterised model, a program was written that took a parameterised function and subtracted from it the mean and the principle components of the data, which were calculated using classical Principle Component Analysis.
@@
 
-\subsection{HiRes image}
-Almost certain candidates, that qualify for follow up hires observations
+\subsection{HiRes / Subsampling of central region}
+In a previous paper \cite{2015MNRAS.447.2170K} we identified the problem of the tendency of the models to be too shallow.
+We pinned down the problem to the central region and are confident to have it fixed with enabling sub pixel sampling in the central area.
+The software allows for subsampling parameters of radius of pixels $r_\text{subs}$ and amount of subpixels per pixel $n_\text{subs}$.
+\Figref{subsampling} shows the results of different settings for $r_\text{subs}$ and $n_\text{subs}$.
+We can see that even the computationally least expensive settings of $r_\text{subs}=1$ and $n_\text{subs}=3$ leads to drastically improved profiles.
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{hires/007022_kappa_encl}
+  \caption{
+    Circularly averaged mass profile for different subsampling of central region.
+    Red line without subsampling, blue lines show subsampling with dash-dot pattern showing the mode.
+    $\cdot / \cdot \cdot \cdot$: $r_\text{subs}=1$ inner pixels, each subdivided into $n_\text{subs}=3$ sub pixels.
+    $\cdot / \cdot \cdot \cdot \cdot \cdot$: $r_\text{subs}=1$, $n_\text{subs}=5$.
+    $\cdot \cdot / \cdot \cdot \cdot $: $r_\text{subs}=2$, $n_\text{subs}=3$.
+    $\cdot \cdot \cdot / \cdot \cdot \cdot $: $r_\text{subs}=3$, $n_\text{subs}=3$.
+    }
+  \label{fig:subsampling}
+\end{figure}
+
+\subsection{Additional / Improved Synthetic Image}
+
+Volunteers often ask about better indicators to identify wether the modelling resulted in a ``good'' or ``bad'' model.
+We developped a prototype of a better syntetic image than just the rendering of a \todo{insert currently used source profile} profile.
+It operates on the composite input image.
+The user has to mask the supposed lensed images.
+The algorith then establishes a grid on the source plane and projects the masked pixels of the lense plane back to the source plane.
+Multiple lens plane pixels fall onto one source plane pixel and get averaged.
+The new synthetic image then reverses the mapping, coloring each pixel in the lens plane with the corresponding values of the source plane pixel.
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{img/new_synth_img_detailed}
+  \caption{
+      Top-left: Orginal image, top-right: improved synthetic image for candidate \sw{5} (\asw{7k4r}) and model \model{12402};
+      bottom from left to right:
+        reconstructed source in color,
+        intensity (grayscale),
+        count of lens plane pixels per source plane pixel,
+        residual of orginal image to improved syntetic image in grayscale
+    }
+  \label{fig:synthimg}
+\end{figure}
 
 \section{Results}
-We came up with four kind of candidates.
+Throu visual inspection of the most popular models generated for each candidate and data generated by those models we classified the candidates in four categories.
+The data available is shown in \figref{SW58}.
+\todo{better explain criterias?}
+The following sections list all the models for all the categories, each with a short explanation of the reasons.
+Additionally, selected models are presented in figures for demonstration.
 
-\subsection{Spectra}
-Candidates to follow up with a spectral analysis.
-
-\subsection{Bad models}
-Candidates that need more work to be modelled.
-Or that have features that are hard / impossible to model with the current SpaghettiLens version.
-Examples are group lenses
-
-\subsection{Non Lenses}
-Those are most probly non lenses,
+% 
+% \subsection{Spectra}
+% Candidates to follow up with a spectral analysis. 
+% 
+% 
+% \subsection{Bad models}
+% Candidates that need more work to be modelled.
+% Or that have features that are hard / impossible to model with the current SpaghettiLens version.
+% Examples are group lenses
+% 
+% 
+% 
+% \subsection{Non Lenses}
+% Those are most probly non lenses,
 
 \subsection{plausible}
+
 The plausible candidates fail in one category, but are quite convincing in all the others.
-  Thats why we recomend them for a following up study for ...
+One particular reason for a candidate to end up in this category is that is has extended arcs, what is hard to modell with the current version of the program.
+Thats why we recomend them for a following up study, for example for taking spectras or other follow up obersatories and for other modelling programs for a try.
 
@@
 
-\begin{itemize}
-  \item SW12 (ASW0003wsu) \\
+\lenstitle{SW12 (ASW0003wsu)} 
   faint arc, bright overall situation, no counter image;
@@
 
-  \item SW21 (ASW0004m3x) \\
+\lenstitle{SW21 (ASW0004m3x)} 
   clear arc, no counter image; inbetween two external sources;
@@
 
-  \item SW27 (ASW0006jh5) \\
+\lenstitle{SW27 (ASW0006jh5)} 
   (really plausible?)
@@
 
-  \item SW31 (ASW00021r0) \\
+\lenstitle{SW31 (ASW00021r0)} 
   (really plausible?)
@@
 
-  \item SW33 (ASW0003s0m)\\
+\lenstitle{SW33 (ASW0003s0m)}
   clear picture, two image situation;
@@
 
-  \item SW36 (ASW000096t) \\
+\lenstitle{SW36 (ASW000096t)} 
   noisy picture, many possible external masses, faint images;
@@
 
-  \item SW38 (ASW0009cp0) \\
+\lenstitle{SW38 (ASW0009cp0)} 
   quite clean picture, two bright minima, counter image hidden;
@@
 
-  \item SW43 (ASW0001c3j) \\
+\lenstitle{SW43 (ASW0001c3j)} 
   clean situation, faint arc'ish images;
@@
 
-  \item SW45 (ASW00024id)\\
-  ring like structure, very clean \\
+\lenstitle{SW45 (ASW00024id)}
+  ring like structure, very clean
   usual problems with rings, otherwise model quite ok actually;
@@
 
-  \item SW46 (ASW00024q6) \\
+\lenstitle{SW46 (ASW00024q6)} 
   yellow'ish arc, two image configuration;
@@
 
-  \item SW52 (ASW0006a07) \\
+\lenstitle{SW52 (ASW0006a07)} 
   (no imgs)
 
-  \item SW54 (ASW0007sez) \\
+\lenstitle{SW54 (ASW0007sez)} 
   white lens, fuzzy ring like structure;
@@
 
-  \item SW58 (ASW0007iwp) \\
+\lenstitle{SW58 (ASW0007iwp)} 
   nice arc, no counter image;
@@
   masses ok
-
-\end{itemize}
 
@@
   \inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
-  \caption{}
+  \caption{SW58.
+topleft: user input; top right: resulting contour map of arrival time surface; mid left: synthetic image, renering a TODO{profile} source behind the modelled lens; mid right: mass profile; bottom: lensing mass, obtained from the model against estimate of stellar mass, obtained using photometric redshift assuming TODO(which population model?).}
+  \label{fig:SW58}
 \end{figure}
@@
 \subsection{unclear}
-\begin{itemize}
-  \item SW04 (ASW0009cjs) \\
+
+This categy contains the ones that are hard to say.
+They might look like lenses visually, but the modelling failed or prediced additional images.
+
+\lenstitle{SW04 (ASW0009cjs)} 
   noisy field, possible group lens, but images not typical? (no arclike structure);
@@
 
-  \item SW06 (ASW0008swn)\\
+\lenstitle{SW06 (ASW0008swn)}
   green images, elongated lens, images on strange positions?;
@@
 
-  \item SW07 (ASW0007e08) \\
+\lenstitle{SW07 (ASW0007e08)} 
   (no img)
 
-  \item SW13 (ASW00047ae) \\
+\lenstitle{SW13 (ASW00047ae)} 
   croweded situation unclear setup;
@@
 
-  \item SW15 (ASW0004nan) \\
+\lenstitle{SW15 (ASW0004nan)} 
   no counter image (should be visible)?
@@
 
-  \item SW17 (ASW0005rnb) \\
+\lenstitle{SW17 (ASW0005rnb)} 
   two image setup, but arcish structure of images missing;
@@
 
-  \item SW19 (ASW0001ld7) \\
+\lenstitle{SW19 (ASW0001ld7)} 
   asymmetry / really extended arc and no counter image rather no lensing configuration;
@@
 
-  \item SW24 (ASW00050sk) \\
+\lenstitle{SW24 (ASW00050sk)} 
   unclear / noisy situation, shape of arc strange;
@@
 
-  \item SW32 (ASW0004iye) \\
+\lenstitle{SW32 (ASW0004iye)} 
   (no img)
 
-  \item SW35 (ASW0004wgd) \\
+\lenstitle{SW35 (ASW0004wgd)} 
   hard to say, doesn't look convincing, but neither totally off
@@
 
-  \item SW44 (ASW0002k40) \\
+\lenstitle{SW44 (ASW0002k40)} 
   (no img);
@@
 
-  \item SW47 (ASW0003r6c) \\
+\lenstitle{SW47 (ASW0003r6c)} 
   two images, no arcish structre.. too far away from lens?;
@@
 
-  \item SW51 (ASW0006e0o) \\
+\lenstitle{SW51 (ASW0006e0o)} 
   (no img)
 
-  \item SW56 (ASW0007pga) \\
+\lenstitle{SW56 (ASW0007pga)} 
   very ellyptical lens, images not really arcish;
@@
 
-  \item SW57 (ASW0008pag) \\
+\lenstitle{SW57 (ASW0008pag)} 
   point mass / group lens interfering? symertry of arc off;
@@
   Mlens too high
-
-\end{itemize}
 
@@
 \subsection{convincing}
-\begin{itemize}
-  \item SW02 (ASW000619d)
 
-  \item SW05 (ASW0007k4r)
+The canidates that looked the most promising and left little doubt about being lenses were grouped into the category ``convincing''.
+In Figures \ref{fig:SW02} to \ref{fig:SW29} we show all the convincing candidates.
+Following we list the parameters, obtained applying the technique described in section~\ref{sec:parameter}
 
-  \item SW09 (ASW0002asp)
+\lenstitle{SW02 (ASW000619d)}
+Nice arc with counter image;
+additional mass at 12 o'clock doesn't seem to influence the image.
+\params{1.04}{0.32}{-5.18}
 
-  \item SW28 (ASW0007xrs)
+\lenstitle{SW05 (ASW0007k4r)}
+The model predicts very steep central mass profile, and thus a very high lensing mass;
+looks otherwise very convincing.
+\params{3.80}{0.15}{52.50}
 
-  \item SW29 (ASW0008qsm)
+\lenstitle{SW09 (ASW0002asp)}
+\params{1.12}{0.00}{88.39}
 
-\end{itemize}
+\lenstitle{SW28 (ASW0007xrs)}
+Faint, but clearly visible arc and counter image;
+but model sfits nicely
+\params{1.04}{0.33}{66.63}
+
+\lenstitle{SW29 (ASW0008qsm)}
+Faint close arc, but reconstruion works very well;
+parameterisation of ellypticity fails.
+\params{0.73}{0.00}{249.80}
 
@@
   \inclfig{SW02}{ASW000619d_011489}
+  \caption{SW02}
+  \label{fig:SW02}
 \end{figure}
@@
   \inclfig{SW05}{ASW0007k4r_AJIBCHQ6EM}
+  \caption{SW05}
+  \label{fig:SW05}
 \end{figure}
@@
   \inclfig{SW09}{ASW0002asp_5EKMWWVJHL}
+  \caption{SW09}
+  \label{fig:SW09}
 \end{figure}
@@
   \inclfig{SW28}{ASW0007xrs_JHC3J2HYV7}
+  \caption{SW28}
+  \label{fig:SW28}
 \end{figure}
@@
   \inclfig{SW29}{ASW0008qsm_TOFS7JNGEK}
+  \caption{SW29}
+  \label{fig:SW29}
 \end{figure}
@@
 \subsection{doubtful}
-\begin{itemize}
-  \item SW10 (ASW0002bmc) \\
+
+\lenstitle{SW10 (ASW0002bmc)} 
   very elliptical setup, unlikley to be a lens;
@@
 
-  \item SW16 (ASW0009bp2) \\
+\lenstitle{SW16 (ASW0009bp2)} 
   very faint images
 
-  \item SW18 (ASW0007hu2) \\
+\lenstitle{SW18 (ASW0007hu2)} 
   model failed completly
 
-  \item SW20 (ASW0002dx7) \\
+\lenstitle{SW20 (ASW0002dx7)} 
   faint white images, rather substuctre of ``lens'' ??
 
-  \item SW22 (ASW0009ab8) \\
+\lenstitle{SW22 (ASW0009ab8)} 
   very faint images, group configuration;
@@
 
-  \item SW23 (ASW0003r61) \\
+\lenstitle{SW23 (ASW0003r61)} 
   (no img)
 
-  \item SW26 (ASW0005ma2) \\
+\lenstitle{SW26 (ASW0005ma2)} 
   similar to SW10
 
-  \item SW34 (ASW00051ld) \\
+\lenstitle{SW34 (ASW00051ld)} 
   (no img)
 
-  \item SW41 (ASW0008xbu) \\
+\lenstitle{SW41 (ASW0008xbu)} 
   similar to SW10. very ellyptical lens
 
-  \item SW42 (ASW00096rm) \\
+\lenstitle{SW42 (ASW00096rm)} 
   ring like structure, but very strange distribution;
@@
 
-  \item SW53 (ASW00070vl) \\
+\lenstitle{SW53 (ASW00070vl)} 
   images don't look liked lensed;
@@
 
-\end{itemize}
-
-outlier because very odd mass ratio
 \begin{figure}
   \inclfig{SW42}{ASW00096rm_4Q3YCEWGLN}
+  \caption{outlier because very odd mass ratio}
+  \label{fig:SW42}
 \end{figure}
@@
 \subsection{missing}
-\begin{itemize}
-  \item SW03 (ASW0006mea)
-  \item SW14 (ASW0004xjk)
-  \item SW25 (ASW00007mq)
-  \item SW30 (ASW0002p8y)
-  \item SW37 (ASW00086xq)
-  \item SW39 (ASW0005qiz)
-  \item SW40 (ASW0008wmr)
-  \item SW48 (ASW0000g95)
-  \item SW49 (ASW00007ls)
-  \item SW50 (ASW00008a0)
-  \item SW55 (ASW0007t5y)
-  \item SW59 (ASW00085cp)
-\end{itemize}
+
+Finally this category lists all the candidates, that miss redshift measurements of the lens and thus further analysis is difficult.
+
+\lenstitle{SW03 (ASW0006mea)}
+
+\lenstitle{SW14 (ASW0004xjk)}
+
+\lenstitle{SW25 (ASW00007mq)}
+
+\lenstitle{SW30 (ASW0002p8y)}
+
+\lenstitle{SW37 (ASW00086xq)}
+
+\lenstitle{SW39 (ASW0005qiz)}
+
+\lenstitle{SW40 (ASW0008wmr)}
+
+\lenstitle{SW48 (ASW0000g95)}
+
+\lenstitle{SW49 (ASW00007ls)}
+
+\lenstitle{SW50 (ASW00008a0)}
+
+\lenstitle{SW55 (ASW0007t5y)}
+
+\lenstitle{SW59 (ASW00085cp)}
 
@@
 
-\newpage
+\clearpage
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% 
-% \section{Introduction}
-% 
-% This is a simple template for authors to write new MNRAS papers.
-% See \texttt{mnras\_sample.tex} for a more complex example, and \texttt{mnras\_guide.tex}
-% for a full user guide.
-% 
-% All papers should start with an Introduction section, which sets the work
-% in context, cites relevant earlier studies in the field by \citet{Others2013},
-% and describes the problem the authors aim to solve \citep[e.g.][]{Author2012}.
-% 
-% \section{Methods, Observations, Simulations etc.}
-% 
-% Normally the next section describes the techniques the authors used.
-% It is frequently split into subsections, such as Section~\ref{sec:maths} below.
-% 
-% \subsection{Maths}
-% \label{sec:maths} % used for referring to this section from elsewhere
-% 
-% Simple mathematics can be inserted into the flow of the text e.g. $2\times3=6$
-% or $v=220$\,km\,s$^{-1}$, but more complicated expressions should be entered
-% as a numbered equation:
-% 
-% \begin{equation}
-%     x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}.
-% 	\label{eq:quadratic}
-% \end{equation}
-% 
-% Refer back to them as e.g. equation~(\ref{eq:quadratic}).
-% 
-% \subsection{Figures and tables}
-% 
-% Figures and tables should be placed at logical positions in the text. Don't
-% worry about the exact layout, which will be handled by the publishers.
-% 
-% Figures are referred to as e.g. Fig.~\ref{fig:example_figure}, and tables as
-% e.g. Table~\ref{tab:example_table}.
-% 
-% % Example figure
-% \begin{figure}
-% 	% To include a figure from a file named example.*
-% 	% Allowable file formats are eps or ps if compiling using latex
-% 	% or pdf, png, jpg if compiling using pdflatex
-% 	\includegraphics[width=\columnwidth]{example}
-%     \caption{This is an example figure. Captions appear below each figure.
-% 	Give enough detail for the reader to understand what they're looking at,
-% 	but leave detailed discussion to the main body of the text.}
-%     \label{fig:example_figure}
-% \end{figure}
-% 
-% % Example table
-% \begin{table}
-% 	\centering
-% 	\caption{This is an example table. Captions appear above each table.
-% 	Remember to define the quantities, symbols and units used.}
-% 	\label{tab:example_table}
-% 	\begin{tabular}{lccr} % four columns, alignment for each
-% 		\hline
-% 		A & B & C & D\\
-% 		\hline
-% 		1 & 2 & 3 & 4\\
-% 		2 & 4 & 6 & 8\\
-% 		3 & 5 & 7 & 9\\
-% 		\hline
-% 	\end{tabular}
-% \end{table}
-% 
-% 
-% \section{Conclusions}
-% 
-% The last numbered section should briefly summarise what has been done, and describe
-% the final conclusions which the authors draw from their work.
-% 
-% \section*{Acknowledgements}
-% 
-% The Acknowledgements section is not numbered. Here you can thank helpful
-% colleagues, acknowledge funding agencies, telescopes and facilities used etc.
-% Try to keep it short.
-% 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% %%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-% 
-% % The best way to enter references is to use BibTeX:
-% 
-% %\bibliographystyle{mnras}
-% %\bibliography{example} % if your bibtex file is called example.bib
-% 
-% 
-% % Alternatively you could enter them by hand, like this:
-% % This method is tedious and prone to error if you have lots of references
-% \begin{thebibliography}{99}
-% \bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
-% Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
-% \bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
-% Others S., 2012, Journal of Interesting Stuff, 17, 198
-% \end{thebibliography}
-% 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% %%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-% 
-% \appendix
-% 
-% \section{Some extra material}
-% 
-% If you want to present additional material which would interrupt the flow of the main paper,
-% it can be placed in an Appendix which appears after the list of references.
-% 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% 
-% 
-% % Don't change these lines
-% \bsp	% typesetting comment
-% \label{lastpage}
-% \end{document}
-% 
-% % End of mnras_template.tex

### 2016-05-12 paper2.tex
removing subcaption
added table
tick/cross ding
working on text

@@
-% mnras_template.tex
-%
-% LaTeX template for creating an MNRAS paper
-%
-% v3.0 released 14 May 2015
-% (version numbers match those of mnras.cls)
-%
-% Copyright (C) Royal Astronomical Society 2015
-% Authors:
-% Keith T. Smith (Royal Astronomical Society)
-
-% Change log
-%
-% v3.0 May 2015
-%    Renamed to match the new package name
-%    Version number matches mnras.cls
-%    A few minor tweaks to wording
-% v1.0 September 2013
-%    Beta testing only - never publicly released
-%    First version: a simple (ish) template for creating an MNRAS paper
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Basic setup. Most papers should leave these options alone.
 \documentclass[fleqn,usenatbib]{mnras}
@@
 \vbadness = 10000
-\usepackage{}
+% \usepackage{}
 
@@
 \usepackage{graphicx} % Including figure files
-\usepackage[skip=0pt]{subcaption}
+%\usepackage[skip=0pt]{subcaption}
 \usepackage{amsmath}	% Advanced maths commands
 \usepackage{amssymb}	% Extra maths symbols
+\usepackage{pifont}	% Extra maths symbols
 %\usepackage{bmpsize}  % PS still needs this for correct bounding boxes?
@@
 \usepackage{todonotes} % as long as we are editing...
-\usepackage{showframe} % for debug
-\overfullrule=5pt      % show overfull boxes
+%\usepackage{showframe} % for debug
+%\overfullrule=5pt      % show overfull boxes
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
-
-% Please keep new commands to a minimum, and use \newcommand not \def to avoid
-% overwriting existing commands. Example:
-%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
-
 \newcommand{\inclfig}[2]{
   \centering
-  \begin{subfigure}{0.5\linewidth}
-    \includegraphics[width=\linewidth]{spaghetti/#2_input}
-  \end{subfigure}%
-  \begin{subfigure}{0.5\linewidth}
-    \includegraphics[width=\linewidth]{spaghetti/#2_img1}
-  \end{subfigure}%
-  \\[-1px]%
-  \begin{subfigure}{0.5\linewidth}
-    \includegraphics[width=\linewidth]{spaghetti/#2_img3_ipol}
-  \end{subfigure}%
-  \begin{subfigure}{0.5\linewidth}
-    \includegraphics[width=\linewidth]{spaghetti/#2_img2}
-  \end{subfigure}%
-  \\[-1px]%
-  \begin{subfigure}[b]{\linewidth}
+	\includegraphics[width=0.5\linewidth]{spaghetti/#2_input}%
+	\includegraphics[width=0.5\linewidth]{spaghetti/#2_img1}
+	\includegraphics[width=0.5\linewidth]{spaghetti/#2_img3_ipol}%
+	\includegraphics[width=0.5\linewidth]{spaghetti/#2_img2}
 	\includegraphics[width=\linewidth]{masses/#1_#2_mstel_vs_mtot}
-  \end{subfigure}
 }
+
+\newcommand*{\rot}{\rotatebox{90}}
+\newcommand*{\OK}{\ding{51}}
+\newcommand*{\NO}{\ding{55}}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
-
-% Title of the paper, and the short title which is used in the headers.
-% Keep the title short and informative.
-\title[Short title, max. 45 characters]{Preliminary categorisation of SpaceWarps candidates}
+\title[Short title, max. 45 characters]{Model of lens candidates from
+  Space Warps CFHTLS}
 
@@
 % These dates will be filled out by the publisher
-\date{Accepted XXX. Received YYY; in original form ZZZ}
+% \date{Accepted XXX. Received YYY; in original form ZZZ}
 
@@
 
-% Abstract of the paper
 \begin{abstract}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Introduction}
 
-Here we cite \cite{2015MNRAS.447.2170K}.
+Space Warps \citep{2016MNRAS.455.1171M} found lens candidates
+\citep{2016MNRAS.455.1191M}.
+
+Modelling method \citep{2015MNRAS.447.2170K}.
 
 \section{Methods}
+
+\subsection{Stellar mass}
 
@@
 
-The parameterised model function was obtained from the gravitational potential of an isothermal ellipsoid mass distribution \cite{2001astro.ph..2340K}.
+The parameterised model function was obtained from the gravitational potential of an isothermal ellipsoid mass distribution \cite{2001astro.ph..2341K}.
 This model is frequently used to describe gravitational lenses as it tends to fit well with observations.
@@
 By applying this model to simulated lenses for which the values of these parameters were already known, it was possible to gain an estimate of the projected accuracy of the results, before applying the model to the candidate lensing galaxies.
-
-\subsection{HiRes / Subsampling of central region}
-In a previous paper \cite{2015MNRAS.447.2170K} we identified the problem of the tendency of the models to be too shallow.
-We pinned down the problem to the central region and are confident to have it fixed with enabling sub pixel sampling in the central area.
-The software allows for subsampling parameters of radius of pixels $r_\text{subs}$ and amount of subpixels per pixel $n_\text{subs}$.
-\Figref{subsampling} shows the results of different settings for $r_\text{subs}$ and $n_\text{subs}$.
-We can see that even the computationally least expensive settings of $r_\text{subs}=1$ and $n_\text{subs}=3$ leads to drastically improved profiles.
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{hires/007022_kappa_encl}
-  \caption{
-    Circularly averaged mass profile for different subsampling of central region.
-    Red line without subsampling, blue lines show subsampling with dash-dot pattern showing the mode.
-    $\cdot / \cdot \cdot \cdot$: $r_\text{subs}=1$ inner pixels, each subdivided into $n_\text{subs}=3$ sub pixels.
-    $\cdot / \cdot \cdot \cdot \cdot \cdot$: $r_\text{subs}=1$, $n_\text{subs}=5$.
-    $\cdot \cdot / \cdot \cdot \cdot $: $r_\text{subs}=2$, $n_\text{subs}=3$.
-    $\cdot \cdot \cdot / \cdot \cdot \cdot $: $r_\text{subs}=3$, $n_\text{subs}=3$.
-    }
-  \label{fig:subsampling}
-\end{figure}
 
@@
 
-\section{Results}
+\subsection{HiRes / Subsampling of central region}
+In a previous paper \cite{2015MNRAS.447.2170K} we identified the problem of the tendency of the models to be too shallow.
+We pinned down the problem to the central region and are confident to have it fixed with enabling sub pixel sampling in the central area.
+The software allows for subsampling parameters of radius of pixels $r_\text{subs}$ and amount of subpixels per pixel $n_\text{subs}$.
+\Figref{subsampling} shows the results of different settings for $r_\text{subs}$ and $n_\text{subs}$.
+We can see that even the computationally least expensive settings of $r_\text{subs}=1$ and $n_\text{subs}=3$ leads to drastically improved profiles.
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{hires/007022_kappa_encl}
+  \caption{
+    Circularly averaged mass profile for different subsampling of central region.
+    Red line without subsampling, blue lines show subsampling with dash-dot pattern showing the mode.
+    $\cdot / \cdot \cdot \cdot$: $r_\text{subs}=1$ inner pixels, each subdivided into $n_\text{subs}=3$ sub pixels.
+    $\cdot / \cdot \cdot \cdot \cdot \cdot$: $r_\text{subs}=1$, $n_\text{subs}=5$.
+    $\cdot \cdot / \cdot \cdot \cdot $: $r_\text{subs}=2$, $n_\text{subs}=3$.
+    $\cdot \cdot \cdot / \cdot \cdot \cdot $: $r_\text{subs}=3$, $n_\text{subs}=3$.
+    }
+  \label{fig:subsampling}
+\end{figure}
+
+\section{Example systems}
+
+\begin{figure}
+  \inclfig{SW02}{ASW000619d_011489}
+  \caption{SW02}
+  \label{fig:SW02}
+\end{figure}
+
+\begin{figure}
+  \inclfig{SW05}{ASW0007k4r_AJIBCHQ6EM}
+  \caption{SW05}
+  \label{fig:SW05}
+\end{figure}
+
+\begin{figure}
+  \inclfig{SW09}{ASW0002asp_5EKMWWVJHL}
+  \caption{SW09}
+  \label{fig:SW09}
+\end{figure}
+
+\begin{figure}
+  \inclfig{SW28}{ASW0007xrs_JHC3J2HYV7}
+  \caption{SW28}
+  \label{fig:SW28}
+\end{figure}
+
+\begin{figure}
+  \inclfig{SW29}{ASW0008qsm_TOFS7JNGEK}
+  \caption{SW29}
+  \label{fig:SW29}
+\end{figure}
+
+Plausible
+
+\begin{figure}
+  \inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
+  \caption{SW58.
+topleft: user input; top right: resulting contour map of arrival time surface; mid left: synthetic image, renering a TODO{profile} source behind the modelled lens; mid right: mass profile; bottom: lensing mass, obtained from the model against estimate of stellar mass, obtained using photometric redshift assuming TODO(which population model?).}
+  \label{fig:SW58}
+\end{figure}
+
+Uncertain
+
+\begin{figure}
+  \inclfig{SW36}{ASW000096t_7IPP7LWVOF}
+\end{figure}
+
+\begin{figure}
+	\inclfig{SW19}{ASW0001ld7_OS3CYAKLRT}
+\end{figure}
+
+\begin{figure}
+	\inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
+\end{figure}
+
+\section{Summary of models}
+
 Throu visual inspection of the most popular models generated for each candidate and data generated by those models we classified the candidates in four categories.
@@
 Additionally, selected models are presented in figures for demonstration.
-
-% 
-% \subsection{Spectra}
-% Candidates to follow up with a spectral analysis. 
-% 
-% 
-% \subsection{Bad models}
-% Candidates that need more work to be modelled.
-% Or that have features that are hard / impossible to model with the current SpaghettiLens version.
-% Examples are group lenses
-% 
-% 
-% 
-% \subsection{Non Lenses}
-% Those are most probly non lenses,
 
@@
   masses ok
-
   good example of plausible
-
-% \begin{figure}
-% 	\inclfig{SW45}{ASW000024id_TSKKYHD3CB}
-% \end{figure}
-
-\begin{figure}
-  \inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
-  \caption{SW58.
-topleft: user input; top right: resulting contour map of arrival time surface; mid left: synthetic image, renering a TODO{profile} source behind the modelled lens; mid right: mass profile; bottom: lensing mass, obtained from the model against estimate of stellar mass, obtained using photometric redshift assuming TODO(which population model?).}
-  \label{fig:SW58}
-\end{figure}
 
@@
 
-\begin{figure}
-  \inclfig{SW36}{ASW000096t_7IPP7LWVOF}
-\end{figure}
-
+\lenstitle{SW36 (ASW000096t)}
 (like 4dv8 collective modelling)
@@
 
-\begin{figure}
-	\inclfig{SW19}{ASW0001ld7_OS3CYAKLRT}
-\end{figure}
-
-\begin{figure}
-	\inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
-\end{figure}
-
 \subsection{convincing}
@@
 \params{0.73}{0.00}{249.80}
-
-\begin{figure}
-  \inclfig{SW02}{ASW000619d_011489}
-  \caption{SW02}
-  \label{fig:SW02}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW05}{ASW0007k4r_AJIBCHQ6EM}
-  \caption{SW05}
-  \label{fig:SW05}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW09}{ASW0002asp_5EKMWWVJHL}
-  \caption{SW09}
-  \label{fig:SW09}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW28}{ASW0007xrs_JHC3J2HYV7}
-  \caption{SW28}
-  \label{fig:SW28}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW29}{ASW0008qsm_TOFS7JNGEK}
-  \caption{SW29}
-  \label{fig:SW29}
-\end{figure}
 
@@
 
+\subsection{Table}
+
+\begin{table*}
+  \caption{Categorisation of SW models}
+  \label{tab:models}
+\include{table}
+\end{table*}
+
+\section{Discussions}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \bibliographystyle{mnras}
-\bibliography{bib/bibli.bib} % if your bibtex file is called example.bib
+\bibliography{bib/bibli} % if your bibtex file is called example.bib
 
@@
 \end{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%% END %%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-05-12 bib/getbibs.py

@@ -1,0 +1,22 @@
+from urllib.request import urlopen
+from sys import argv
+
+bfil = open('bibli.bib','a')
+
+def getbib(code):
+    url = 'http://adsabs.harvard.edu/cgi-bin/nph-bib_query?bibcode=' + \
+          code + '&data_type=BIBTEX'
+    page = urlopen(url)
+    s = 0
+    for l in page:
+        line = str(l,encoding='utf-8')
+        if s < 5:
+            s += 1
+        else:
+            bfil.write(line)
+    print ('Read',code)
+
+if len(argv) > 1:
+    code = argv[1]
+    getbib(code)
+

### 2016-05-20 old_classification.tex
update table (autogenerated)

--- 2016-05-12 paper2.tex
@@
-\documentclass[fleqn,usenatbib]{mnras}
-
-%%% DEBUG SETTINGS - remove at the end %%%%%%%%%%%%%%%
-\usepackage{silence} % silence error warinings
-\WarningFilter{caption}{Unsupported document class} % caption doesn't know mnras..
-\hbadness = 5000
-\vbadness = 10000
-% \usepackage{}
-
-% MNRAS is set in Times font. If you don't have this installed (most LaTeX
-% installations will be fine) or prefer the old Computer Modern fonts, comment
-% out the following line
-%\usepackage{newtxtext,newtxmath} % not yet supported on arxiv and uni computer
-%\usepackage{txfonts}
-
-% Depending on your LaTeX fonts installation, you might get better results with one of these:
-%\usepackage{mathptmx}
-%\usepackage{txfonts}
-
-% Use vector fonts, so it zooms properly in on-screen viewing software
-% Don't change these lines unless you know what you are doing
-\usepackage[T1]{fontenc} % make sure font is supported
-% \usepackage{ae,aecompl} %obsolete when using modern fonts
-\usepackage[final]{microtype} % make sure font is supported
-% and a suitable font
-\usepackage{lmodern} % use a modern font with T1 support
-%\usepackage{cm-super} % use a modern font with T1 support
-
-%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
-
-% Only include extra packages if you really need them. Common packages are:
-%\usepackage[dvipdfmx]{graphicx}	% Including figure files
-\usepackage{graphicx} % Including figure files
-%\usepackage[skip=0pt]{subcaption}
-\usepackage{amsmath}	% Advanced maths commands
-\usepackage{amssymb}	% Extra maths symbols
-\usepackage{pifont}	% Extra maths symbols
-%\usepackage{bmpsize}  % PS still needs this for correct bounding boxes?
-
-% TODO stuff, comment out for final submit
-\usepackage{todonotes} % as long as we are editing...
-%\usepackage{showframe} % for debug
-%\overfullrule=5pt      % show overfull boxes
-
-% I disabled hyperlink in the cls und included it here because of bugs
-\usepackage{hyperref}   % Hyperlinks
-\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,filecolor=blue,urlcolor=blue}
-
-\newcommand{\inclfig}[2]{
-  \centering
-	\includegraphics[width=0.5\linewidth]{spaghetti/#2_input}%
-	\includegraphics[width=0.5\linewidth]{spaghetti/#2_img1}
-	\includegraphics[width=0.5\linewidth]{spaghetti/#2_img3_ipol}%
-	\includegraphics[width=0.5\linewidth]{spaghetti/#2_img2}
-	\includegraphics[width=\linewidth]{masses/#1_#2_mstel_vs_mtot}
-}
-
-\newcommand*{\rot}{\rotatebox{90}}
-\newcommand*{\OK}{\ding{51}}
-\newcommand*{\NO}{\ding{55}}
-
-\newcommand{\lenstitle}[1]{\noindent\textbf{#1} --}
-\newcommand{\params}[3]{(\(\Theta_\text{E}:#1\), $\varepsilon:#2$, $\alpha_\varepsilon:#3$ )}
-
-\newcommand{\asw}[1]{ASW000#1}
-\newcommand{\sw}[1]{SW~#1}
-\newcommand{\model}[1]{SL model~#1}
-
-\newcommand{\figref}[1]{Figure \ref{fig:#1}}
-\newcommand{\Figref}[1]{Figure \ref{fig:#1}}
-
-\title[Short title, max. 45 characters]{Model of lens candidates from
-  Space Warps CFHTLS}
-
-% The list of authors, and the short list which is used in the headers.
-% If you need two or more lines of authors, add an extra line using \newauthor
-\author[R. Kueng et al.]{
-Rafael Kueng,$^{1}$\thanks{E-mail: rafael.kueng@uzh.ch}
-Presenjit Saha,$^{1}$
-Lucy Oswald$^{3}$
-%and Fourth Author$^{4}$
-\\
-% List of institutions
-$^{1}$Physik Institut, University of Zurich, Winterthurerstrasse XXX, Zurich 8057, Switzerland\\
-$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
-$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
-%$^{4}$Another Department, Different Institution, Street Address, City Postal Code, Country
-}
-
-% These dates will be filled out by the publisher
-% \date{Accepted XXX. Received YYY; in original form ZZZ}
-
-% Enter the current year, for the copyright statements etc.
-\pubyear{2016}
-
-% Don't change these lines
-\begin{document}
-\label{firstpage}
-\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\maketitle
-
-\begin{abstract}
-This is a simple template for authors to write new MNRAS papers.
-The abstract should briefly describe the aims, methods, and main results of the paper.
-It should be a single paragraph not more than 250 words (200 words for Letters).
-No references should appear in the abstract.
-\end{abstract}
-
-% Select between one and six entries from the list of approved keywords.
-% Don't make up new ones.
-\begin{keywords}
-keyword1 -- keyword2 -- keyword3
-\end{keywords}
-
-\section{Introduction}
-
-Space Warps \citep{2016MNRAS.455.1171M} found lens candidates
-\citep{2016MNRAS.455.1191M}.
-
-Modelling method \citep{2015MNRAS.447.2170K}.
-
-\section{Methods}
-
-\subsection{Stellar mass}
-
-\subsection{Parameterisation of pixel models} \label{sec:parameter}
-In order to fit the set of pixelated models to a single parameterised model, a program was written that took a parameterised function and subtracted from it the mean and the principle components of the data, which were calculated using classical Principle Component Analysis.
-This created the residuals function.
-The number of components defined as principle was varied to test how this affected the output, and it was found that using 5 principle components tended to give a reasonable approximation.
-A masking function was added which selected only the data points that fell inside the image of the lens, and the principal components were clipped in order to keep the values inside the region of the ensemble of models.
-Any value higher than the clip was set to be the clip value.
-This was chosen to be 2.5 as, assuming that the data follows a Gaussian error distribution, almost all the values for the variance should lie between 2 and 3 standard deviations from the mean.
-Minimising the residuals function produces the set of parameters that fit the parameterised function to the original pixelated ensemble most closely.
-A least squares fit was used to perform this minimisation.
-
-The parameterised model function was obtained from the gravitational potential of an isothermal ellipsoid mass distribution \cite{2001astro.ph..2341K}.
-This model is frequently used to describe gravitational lenses as it tends to fit well with observations.
-The isothermal ellipsoid model outputs three useful parameters: the radius of the Einstein ring, the ellipticity of the model and the angle of the ellipticity from the vertical, giving the orientation of the galaxy.
-By applying this model to simulated lenses for which the values of these parameters were already known, it was possible to gain an estimate of the projected accuracy of the results, before applying the model to the candidate lensing galaxies.
-
-\subsection{Additional / Improved Synthetic Image}
-
-Volunteers often ask about better indicators to identify wether the modelling resulted in a ``good'' or ``bad'' model.
-We developped a prototype of a better syntetic image than just the rendering of a \todo{insert currently used source profile} profile.
-It operates on the composite input image.
-The user has to mask the supposed lensed images.
-The algorith then establishes a grid on the source plane and projects the masked pixels of the lense plane back to the source plane.
-Multiple lens plane pixels fall onto one source plane pixel and get averaged.
-The new synthetic image then reverses the mapping, coloring each pixel in the lens plane with the corresponding values of the source plane pixel.
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{img/new_synth_img_detailed}
-  \caption{
-      Top-left: Orginal image, top-right: improved synthetic image for candidate \sw{5} (\asw{7k4r}) and model \model{12402};
-      bottom from left to right:
-        reconstructed source in color,
-        intensity (grayscale),
-        count of lens plane pixels per source plane pixel,
-        residual of orginal image to improved syntetic image in grayscale
-    }
-  \label{fig:synthimg}
-\end{figure}
-
-\subsection{HiRes / Subsampling of central region}
-In a previous paper \cite{2015MNRAS.447.2170K} we identified the problem of the tendency of the models to be too shallow.
-We pinned down the problem to the central region and are confident to have it fixed with enabling sub pixel sampling in the central area.
-The software allows for subsampling parameters of radius of pixels $r_\text{subs}$ and amount of subpixels per pixel $n_\text{subs}$.
-\Figref{subsampling} shows the results of different settings for $r_\text{subs}$ and $n_\text{subs}$.
-We can see that even the computationally least expensive settings of $r_\text{subs}=1$ and $n_\text{subs}=3$ leads to drastically improved profiles.
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{hires/007022_kappa_encl}
-  \caption{
-    Circularly averaged mass profile for different subsampling of central region.
-    Red line without subsampling, blue lines show subsampling with dash-dot pattern showing the mode.
-    $\cdot / \cdot \cdot \cdot$: $r_\text{subs}=1$ inner pixels, each subdivided into $n_\text{subs}=3$ sub pixels.
-    $\cdot / \cdot \cdot \cdot \cdot \cdot$: $r_\text{subs}=1$, $n_\text{subs}=5$.
-    $\cdot \cdot / \cdot \cdot \cdot $: $r_\text{subs}=2$, $n_\text{subs}=3$.
-    $\cdot \cdot \cdot / \cdot \cdot \cdot $: $r_\text{subs}=3$, $n_\text{subs}=3$.
-    }
-  \label{fig:subsampling}
-\end{figure}
-
-\section{Example systems}
-
-\begin{figure}
-  \inclfig{SW02}{ASW000619d_011489}
-  \caption{SW02}
-  \label{fig:SW02}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW05}{ASW0007k4r_AJIBCHQ6EM}
-  \caption{SW05}
-  \label{fig:SW05}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW09}{ASW0002asp_5EKMWWVJHL}
-  \caption{SW09}
-  \label{fig:SW09}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW28}{ASW0007xrs_JHC3J2HYV7}
-  \caption{SW28}
-  \label{fig:SW28}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW29}{ASW0008qsm_TOFS7JNGEK}
-  \caption{SW29}
-  \label{fig:SW29}
-\end{figure}
-
-Plausible
-
-\begin{figure}
-  \inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
-  \caption{SW58.
-topleft: user input; top right: resulting contour map of arrival time surface; mid left: synthetic image, renering a TODO{profile} source behind the modelled lens; mid right: mass profile; bottom: lensing mass, obtained from the model against estimate of stellar mass, obtained using photometric redshift assuming TODO(which population model?).}
-  \label{fig:SW58}
-\end{figure}
-
-Uncertain
-
-\begin{figure}
-  \inclfig{SW36}{ASW000096t_7IPP7LWVOF}
-\end{figure}
-
-\begin{figure}
-	\inclfig{SW19}{ASW0001ld7_OS3CYAKLRT}
-\end{figure}
-
-\begin{figure}
-	\inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
-\end{figure}
-
 \section{Summary of models}
@@
 \lenstitle{SW59 (ASW00085cp)}
-
-\subsection{Table}
-
-\begin{table*}
-  \caption{Categorisation of SW models}
-  \label{tab:models}
-\include{table}
-\end{table*}
-
-\section{Discussions}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% The best way to enter references is to use BibTeX:
-\bibliographystyle{mnras}
-\bibliography{bib/bibli} % if your bibtex file is called example.bib
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-
-\section{Some extra material}
-
-If you want to present additional material which would interrupt the flow of the main paper,
-it can be placed in an Appendix which appears after the list of references.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\clearpage
-
-\section{TODO}
-\listoftodos
-
-\todo{REMOVE TODOS at the end}
-
-% Don't change these lines
-\bsp	% typesetting comment
-\label{lastpage}
-\end{document}

### 2016-05-20 paper2.tex
update table (autogenerated)

@@
 
-\lenstitle{SW01 (ASW0004dv8)}
-  This is some text that says something more than this line.
-
-\lenstitle{SW08 (ASW00099ed)}
-  Simple lens with two images;
-  model has minor arthefacts.
-
-\lenstitle{SW11 (ASW0002qtn)}
-  Simple small arc;
-  model nedes minor refinement;
-  quite low mass ratio
-
-\lenstitle{SW12 (ASW0003wsu)} 
-  faint arc, bright overall situation, no counter image;
-  has good model;
-  low Mstel and low Mlens
-
-\lenstitle{SW21 (ASW0004m3x)} 
-  clear arc, no counter image; inbetween two external sources;
-  model needs work, predicts additional images. play with external mass / sheer?
-  Mass ratio low.
-
-\lenstitle{SW27 (ASW0006jh5)} 
-  (really plausible?)
-  unclear situation, but arc is visible;
-  model shows extended arc not there in org image;
-  mass ratio ok
-
-\lenstitle{SW31 (ASW00021r0)} 
-  (really plausible?)
-  noisy situation, unclear images, potential external mass interfering;
-  model ok'ish, hard to say;
-  high mass ratio
-
-\lenstitle{SW33 (ASW0003s0m)}
-  clear picture, two image situation;
-  model simple, but ok. arc too much extended;
-  masses in the middle, but rather high ratio
-
-\lenstitle{SW36 (ASW000096t)} 
-  noisy picture, many possible external masses, faint images;
-  model predicts additional images, needs more work, arc too extended;
-  masses look ok
-
-\lenstitle{SW38 (ASW0009cp0)} 
-  quite clean picture, two bright minima, counter image hidden;
-  model fine
-  really hi stellar mass
-
-\lenstitle{SW43 (ASW0001c3j)} 
-  clean situation, faint arc'ish images;
-  model needs work, shows additional images, strange arc (LHD);
-  very high Mstel
-
-\lenstitle{SW45 (ASW00024id)}
-  ring like structure, very clean
-  usual problems with rings, otherwise model quite ok actually;
-  very high Mstel
-
-\lenstitle{SW46 (ASW00024q6)} 
-  yellow'ish arc, two image configuration;
-  model ok;
-  masses ok
-
-\lenstitle{SW52 (ASW0006a07)} 
-  (no imgs)
-
-\lenstitle{SW54 (ASW0007sez)} 
-  white lens, fuzzy ring like structure;
-  model really good, given ring like;
-  masses ok
-
-\lenstitle{SW58 (ASW0007iwp)} 
-  nice arc, no counter image;
-  model prediction really good;
-  masses ok
-  good example of plausible
-
-\subsubsection{grouplens}
-
-\lenstitle{SW36 (ASW000096t)}
-(like 4dv8 collective modelling)
-
 \subsection{unclear}
@@
 They might look like lenses visually, but the modelling failed or prediced additional images.
-
-\lenstitle{SW04 (ASW0009cjs)} 
-  noisy field, possible group lens, but images not typical? (no arclike structure);
-  model fail (input errors);
-  Mlens too high (10e13)
-
-\lenstitle{SW06 (ASW0008swn)}
-  green images, elongated lens, images on strange positions?;
-  model ok'ish, but mass distr. doesn't reflect visuals;
-  masses ok
-
-\lenstitle{SW07 (ASW0007e08)} 
-  (no img)
-
-\lenstitle{SW13 (ASW00047ae)} 
-  croweded situation unclear setup;
-  model failed, predicts additional images;
-  masses ok
-
-\lenstitle{SW15 (ASW0004nan)} 
-  no counter image (should be visible)?
-  model ok'ish;
-  Mlens on the lower end
-
-\lenstitle{SW17 (ASW0005rnb)} 
-  two image setup, but arcish structure of images missing;
-  model failed, predicts additional images, rednering failed;
-
-\lenstitle{SW19 (ASW0001ld7)} 
-  asymmetry / really extended arc and no counter image rather no lensing configuration;
-  rendering ok'ish, model predicts additionla images;
-  Mstel and Mlens way too low (e10 / e11)
-
-\lenstitle{SW24 (ASW00050sk)} 
-  unclear / noisy situation, shape of arc strange;
-  model ok;
-  mass ration close to unity
-
-\lenstitle{SW32 (ASW0004iye)} 
-  (no img)
-
-\lenstitle{SW35 (ASW0004wgd)} 
-  hard to say, doesn't look convincing, but neither totally off
-  modell ok;
-  masses as well;
-
-\lenstitle{SW44 (ASW0002k40)} 
-  (no img);
-  very old model;
-  hi mass ratio
-
-\lenstitle{SW47 (ASW0003r6c)} 
-  two images, no arcish structre.. too far away from lens?;
-  model predicts additional images;
-  quite high mass ratio
-
-\lenstitle{SW51 (ASW0006e0o)} 
-  (no img)
-
-\lenstitle{SW56 (ASW0007pga)} 
-  very ellyptical lens, images not really arcish;
-  model failed, predicts additional images;
-  masses ok
-
-\lenstitle{SW57 (ASW0008pag)} 
-  point mass / group lens interfering? symertry of arc off;
-  model failed completly;
-  Mlens too high
 
@@
 
-\lenstitle{SW10 (ASW0002bmc)} 
-  very elliptical setup, unlikley to be a lens;
-  model failed totally
-
-\lenstitle{SW16 (ASW0009bp2)} 
-  very faint images
-
-\lenstitle{SW18 (ASW0007hu2)} 
-  model failed completly
-
-\lenstitle{SW20 (ASW0002dx7)} 
-  faint white images, rather substuctre of ``lens'' ??
-
-\lenstitle{SW22 (ASW0009ab8)} 
-  very faint images, group configuration;
-  model predicts additional images;
-  mass ration close to unity
-
-\lenstitle{SW23 (ASW0003r61)} 
-  (no img)
-
-\lenstitle{SW26 (ASW0005ma2)} 
-  similar to SW10
-
-\lenstitle{SW34 (ASW00051ld)} 
-  (no img)
-
-\lenstitle{SW41 (ASW0008xbu)} 
-  similar to SW10. very ellyptical lens
-
-\lenstitle{SW42 (ASW00096rm)} 
-  ring like structure, but very strange distribution;
-  model not too bad, brightnesses off;
-  stellar mass way too lower
-
-\lenstitle{SW53 (ASW00070vl)} 
-  images don't look liked lensed;
-  model predicts additional images
-
 \begin{figure}
@@
 \lenstitle{SW03 (ASW0006mea)}
-
 \lenstitle{SW14 (ASW0004xjk)}
-
 \lenstitle{SW25 (ASW00007mq)}
-
 \lenstitle{SW30 (ASW0002p8y)}
-
 \lenstitle{SW37 (ASW00086xq)}
-
 \lenstitle{SW39 (ASW0005qiz)}
-
 \lenstitle{SW40 (ASW0008wmr)}
-
 \lenstitle{SW48 (ASW0000g95)}
-
 \lenstitle{SW49 (ASW00007ls)}
-
 \lenstitle{SW50 (ASW00008a0)}
-
 \lenstitle{SW55 (ASW0007t5y)}
-
 \lenstitle{SW59 (ASW00085cp)}

### 2016-06-24 paper2.tex
included new plots
editing examples section

@@
 
+\edef\smallwidth{0.4\linewidth}
+
 \newcommand{\inclfig}[2]{
   \centering
-	\includegraphics[width=0.5\linewidth]{spaghetti/#2_input}%
-	\includegraphics[width=0.5\linewidth]{spaghetti/#2_img1}
-	\includegraphics[width=0.5\linewidth]{spaghetti/#2_img3_ipol}%
-	\includegraphics[width=0.5\linewidth]{spaghetti/#2_img2}
-	\includegraphics[width=\linewidth]{masses/#1_#2_mstel_vs_mtot}
+	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
+	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
+	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
+	\includegraphics[width=\smallwidth]{img/M_encl/#2_M_encl}
+	\includegraphics[width=\smallwidth]{spaghetti/#2_img3_ipol}%
+	\includegraphics[width=\smallwidth]{masses/#1_#2_mstel_vs_mtot}
+}
+
+\newcommand{\inclfign}[2]{
+  \centering
+	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
+	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
+	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
+	\includegraphics[width=\smallwidth]{img/M_encl/#2_M_encl}
+	\includegraphics[width=\smallwidth]{img/nsynth/#2_nsynth}%
+	\includegraphics[width=\smallwidth]{masses/#1_#2_mstel_vs_mtot}
 }
@@
 
-\section{Example systems}
+\section{Example systems}\label{sec:examples}
+
+. topleft: user input; top right: resulting contour map of arrival
+time surface; mid left: synthetic image, renering a conical profile
+source behind the modelled lens; mid right: mass profile\todo{Fix
+  distance factor in $\kappa$.}  ; bottom: lensing mass, obtained from
+the model against estimate of stellar mass, obtained using photometric
+redshift assuming \todo{which population model?}
 
 \begin{figure}
-  \inclfig{SW02}{ASW000619d_011489}
+  \inclfign{SW28}{ASW0007xrs_JHC3J2HYV7}
+  \caption{SW28.  See text in Section~\ref{sec:examples} for details.}
+  \label{fig:SW28}
+\end{figure}
+
+\begin{figure}
+  \inclfign{SW05}{ASW0007k4r_AJIBCHQ6EM}
+  \caption{SW05}
+  \label{fig:SW05}
+\end{figure}
+
+\begin{figure}
+  \inclfign{SW02}{ASW000619d_011489}
   \caption{SW02}
@@
 \begin{figure}
-  \inclfig{SW05}{ASW0007k4r_AJIBCHQ6EM}
-  \caption{SW05}
-  \label{fig:SW05}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW09}{ASW0002asp_5EKMWWVJHL}
+  \inclfign{SW09}{ASW0002asp_5EKMWWVJHL}
   \caption{SW09}
@@
 \begin{figure}
-  \inclfig{SW28}{ASW0007xrs_JHC3J2HYV7}
-  \caption{SW28}
-  \label{fig:SW28}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW29}{ASW0008qsm_TOFS7JNGEK}
+  \inclfign{SW29}{ASW0008qsm_TOFS7JNGEK}
   \caption{SW29}
@@
   \inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
-  \caption{SW58.
-topleft: user input; top right: resulting contour map of arrival time surface; mid left: synthetic image, renering a TODO{profile} source behind the modelled lens; mid right: mass profile; bottom: lensing mass, obtained from the model against estimate of stellar mass, obtained using photometric redshift assuming TODO(which population model?).}
+  \caption{SW58}
   \label{fig:SW58}
@@
   \inclfig{SW36}{ASW000096t_7IPP7LWVOF}
+  \caption{}
+  \label{fig:SW36}
 \end{figure}
@@
   \inclfig{SW19}{ASW0001ld7_OS3CYAKLRT}
+  \caption{}
+  \label{fig:SW19}
 \end{figure}
@@
   \inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
+  \caption{}
+  \label{fig:SW57}
 \end{figure}
@@
   \inclfig{SW42}{ASW00096rm_4Q3YCEWGLN}
-  \caption{outlier because very odd mass ratio}
+  \caption{Models of SW42, a doubtful candidate because of an
+    implausible mass ratio. (See text for details.)}
   \label{fig:SW42}
@@
 
-\todo{REMOVE TODOS at the end}
-
 % Don't change these lines

### 2016-06-24 paper2.tex
editing

@@
 
-. topleft: user input; top right: resulting contour map of arrival
-time surface; mid left: synthetic image, renering a conical profile
-source behind the modelled lens; mid right: mass profile\todo{Fix
-  distance factor in $\kappa$.}  ; bottom: lensing mass, obtained from
-the model against estimate of stellar mass, obtained using photometric
-redshift assuming \todo{which population model?}
+In this section, we discuss ten systems.
 
@@
 
-Plausible
+\begin{figure}
+  \inclfig{SW42}{ASW00096rm_4Q3YCEWGLN}
+  \caption{Models of SW42, a doubtful candidate because of an
+    implausible mass ratio. (See text for details.)}
+  \label{fig:SW42}
+\end{figure}
 
@@
   \label{fig:SW58}
-\end{figure}
-
-Uncertain
-
-\begin{figure}
-  \inclfig{SW36}{ASW000096t_7IPP7LWVOF}
-  \caption{}
-  \label{fig:SW36}
 \end{figure}
@@
 \begin{figure}
+  \inclfig{SW36}{ASW000096t_7IPP7LWVOF}
+  \caption{}
+  \label{fig:SW36}
+\end{figure}
+
+\begin{figure}
   \inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
@@
 \end{figure}
+
+\begin{itemize}
+
+\item Figures~\ref{fig:SW28}--\ref{fig:SW29} show the five most
+  convincing lens candidates.
+
+\item Figure~\ref{fig:SW42} shows a candidate that modelling indicates
+  is doubtful.
+
+\item Figures~\ref{fig:SW58} and \ref{fig:SW19} appear plausible lens
+  candidates.
+
+\item Figures~\ref{fig:SW36} and \ref{fig:SW57} shows {\em unclear\/}
+  cases where modelling failed.
+
+\end{itemize}
+
+Each of Figures~\ref{fig:SW28}--\ref{fig:SW57} show six panels, as
+follows.
+
+\begin{itemize}
+
+\item The upper left panel show a cutout of the Space~Warps image,
+  marked up with a spaghetti diagram.
+
+\item Middle left is a contour map of the arrival-time surface after
+  modelling.
+
+\item Lower left is synthetic image.
+  Figures~\ref{fig:SW28}--\ref{fig:SW29} include source fitting.
+  Figures~\ref{fig:SW42}--\ref{fig:SW57} uses a simple conical
+  profile.
+
+\item Upper right is a mass map.
+
+\item Middle right shows a circularly averaged profile of
+  $\kappa$.\todo{Fix distance factor in $\kappa$.}
+
+\item Lower right shows stellar vs stellar mass.\todo{which population
+  model?}
+
+\end{itemize}
 
@@
 
-\begin{figure}
-  \inclfig{SW42}{ASW00096rm_4Q3YCEWGLN}
-  \caption{Models of SW42, a doubtful candidate because of an
-    implausible mass ratio. (See text for details.)}
-  \label{fig:SW42}
-\end{figure}
+SW42
 

### 2016-06-24 paper2.tex
edits

@@
   \inclfig{SW19}{ASW0001ld7_OS3CYAKLRT}
-  \caption{}
+  \caption{SW19}
   \label{fig:SW19}
@@
   \inclfig{SW36}{ASW000096t_7IPP7LWVOF}
-  \caption{}
+  \caption{SW36}
   \label{fig:SW36}
@@
   \inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
-  \caption{}
+  \caption{SW57}
   \label{fig:SW57}
 \end{figure}
-
-\begin{itemize}
-
-\item Figures~\ref{fig:SW28}--\ref{fig:SW29} show the five most
-  convincing lens candidates.
-
-\item Figure~\ref{fig:SW42} shows a candidate that modelling indicates
-  is doubtful.
-
-\item Figures~\ref{fig:SW58} and \ref{fig:SW19} appear plausible lens
-  candidates.
-
-\item Figures~\ref{fig:SW36} and \ref{fig:SW57} shows {\em unclear\/}
-  cases where modelling failed.
-
-\end{itemize}
 
@@
   model?}
+
+\end{itemize}
+
+\begin{itemize}
+
+\item Figures~\ref{fig:SW28}--\ref{fig:SW29} show the five most
+  convincing lens candidates. SW28 shown in Figure~\ref{fig:SW28} is
+  modelled as an arc with three blended images plus a saddle-point
+  closer to the galaxy.  SW05 shown in Figure~\ref{fig:SW05} has four
+  distinct images (two close to blending).  SW02, SW09 and SW29
+  (Figures~\ref{fig:SW02}--\ref{fig:SW29}) have similar
+  configurations, with a minimum furthest from the galaxy and three
+  images blended into an arc.  All five would be massive ellipticals;
+  SW05 is the most massive of all the candidates, with a galaxy-group
+  scale mass.
+
+\item Figure~\ref{fig:SW42} shows a candidate that modelling indicates
+  is doubtful.  The images appears to have a similar morphology to the
+  last three mentioned.  The implied mass, however, is implausibly
+  high.\todo{Check photometry of this candidate.}
+
+\item Figures~\ref{fig:SW58} and \ref{fig:SW19} appear plausible lens
+  candidates.  Their morphology is similar to SW28, but the
+  saddle-point counterimage is not visible.  We consider these lenses
+  plausible but less convincing.
+
+\item Figures~\ref{fig:SW36} and \ref{fig:SW57} shows {\em unclear\/}
+  cases where modelling failed.
 

### 2016-07-04 paper2.tex
editing text

@@
 \newcommand{\figref}[1]{Figure \ref{fig:#1}}
-\newcommand{\Figref}[1]{Figure \ref{fig:#1}}
 
@@
 \begin{abstract}
-This is a simple template for authors to write new MNRAS papers.
-The abstract should briefly describe the aims, methods, and main results of the paper.
-It should be a single paragraph not more than 250 words (200 words for Letters).
-No references should appear in the abstract.
+We report modelling follow-up of recently-discovered
+gravitational-lens candidates in the CFHT Legacy Survey.  Lens
+modelling was done by a small group of specially-interested volunteers
+from the Space~Warps citizen-science community who originally found
+the candidate lenses.  Models are categorised according to seven
+qualitative and quantitive points.  Also included are some
+improvements to the modelling software used (SpaghettiLens) are
+presented, and discussion of strategies for scaling to future surveys
+with more and frequent discoveries.
+
+The candidates successfully modelled are all galaxies, with inferred
+lensing masses ranging from $\sim10^{11}M_\odot$ to $>10^{13}M_\odot$.
+Stellar masses have also been estimated, using photometry from the
+CFHTLS pipeline and stellar-population models.  The trend well-known
+in nearby galaxies, that star-formation efficiency is maximal for
+total masses of $\approx10^{12}M_\odot$ and reduces for both lower and
+higher masses, is discernable also in these much more distant
+galaxies.
 \end{abstract}
 
-% Select between one and six entries from the list of approved keywords.
-% Don't make up new ones.
 \begin{keywords}
@@
 
-Space Warps \citep{2016MNRAS.455.1171M} found lens candidates
-\citep{2016MNRAS.455.1191M}.
+A passing remark in the {\em Feynman Lectures}\footnote{
+  \cite{1963flp..book.....F}} --- ``if you are looking for a good
+problem, the exact details of how the arms are formed and what
+determine the shapes of these galaxies has not been worked out'' ---
+tells us that circa 1960, galaxy dynamics was expected be an easy
+research puzzle, whose solution was just around the corner.  Yet a
+half-century later, galaxies are not nearly as well-understood as
+stars were then.  Two complications, which are clear now but were not
+so clear then, are: (i)~dynamical chaos, because galaxies are not
+spherical, and (ii)~dark matter.
 
-Modelling method \citep{2015MNRAS.447.2170K}.
+The CFHTLS \citep{2012SPIE.8448E..0MC} has been a rich source of
+lenses by arc-finders, by machine learning \citep{2016arXiv160504309P}
+and by visual inspection \citep{2016MNRAS.455.1171M}.  The latter is
+of particular interest here.
 
-\section{Methods}
-
-\subsection{Stellar mass}
-
-\subsection{Parameterisation of pixel models} \label{sec:parameter}
-In order to fit the set of pixelated models to a single parameterised model, a program was written that took a parameterised function and subtracted from it the mean and the principle components of the data, which were calculated using classical Principle Component Analysis.
-This created the residuals function.
-The number of components defined as principle was varied to test how this affected the output, and it was found that using 5 principle components tended to give a reasonable approximation.
-A masking function was added which selected only the data points that fell inside the image of the lens, and the principal components were clipped in order to keep the values inside the region of the ensemble of models.
-Any value higher than the clip was set to be the clip value.
-This was chosen to be 2.5 as, assuming that the data follows a Gaussian error distribution, almost all the values for the variance should lie between 2 and 3 standard deviations from the mean.
-Minimising the residuals function produces the set of parameters that fit the parameterised function to the original pixelated ensemble most closely.
-A least squares fit was used to perform this minimisation.
-
-The parameterised model function was obtained from the gravitational potential of an isothermal ellipsoid mass distribution \cite{2001astro.ph..2341K}.
-This model is frequently used to describe gravitational lenses as it tends to fit well with observations.
-The isothermal ellipsoid model outputs three useful parameters: the radius of the Einstein ring, the ellipticity of the model and the angle of the ellipticity from the vertical, giving the orientation of the galaxy.
-By applying this model to simulated lenses for which the values of these parameters were already known, it was possible to gain an estimate of the projected accuracy of the results, before applying the model to the candidate lensing galaxies.
+\section{Lens Modelling}
 
@@
 The software allows for subsampling parameters of radius of pixels $r_\text{subs}$ and amount of subpixels per pixel $n_\text{subs}$.
-\Figref{subsampling} shows the results of different settings for $r_\text{subs}$ and $n_\text{subs}$.
+\figref{subsampling} shows the results of different settings for $r_\text{subs}$ and $n_\text{subs}$.
 We can see that even the computationally least expensive settings of $r_\text{subs}=1$ and $n_\text{subs}=3$ leads to drastically improved profiles.
@@
 
+\subsection{Parameterisation of pixel models} \label{sec:parameter}
+In order to fit the set of pixelated models to a single parameterised model, a program was written that took a parameterised function and subtracted from it the mean and the principle components of the data, which were calculated using classical Principle Component Analysis.
+This created the residuals function.
+The number of components defined as principle was varied to test how this affected the output, and it was found that using 5 principle components tended to give a reasonable approximation.
+A masking function was added which selected only the data points that fell inside the image of the lens, and the principal components were clipped in order to keep the values inside the region of the ensemble of models.
+Any value higher than the clip was set to be the clip value.
+This was chosen to be 2.5 as, assuming that the data follows a Gaussian error distribution, almost all the values for the variance should lie between 2 and 3 standard deviations from the mean.
+Minimising the residuals function produces the set of parameters that fit the parameterised function to the original pixelated ensemble most closely.
+A least squares fit was used to perform this minimisation.
+The parameterised model function was obtained from the gravitational potential of an isothermal ellipsoid mass distribution \cite{2001astro.ph..2341K}.
+This model is frequently used to describe gravitational lenses as it tends to fit well with observations.
+The isothermal ellipsoid model outputs three useful parameters: the radius of the Einstein ring, the ellipticity of the model and the angle of the ellipticity from the vertical, giving the orientation of the galaxy.
+By applying this model to simulated lenses for which the values of these parameters were already known, it was possible to gain an estimate of the projected accuracy of the results, before applying the model to the candidate lensing galaxies.
+
+\section{Stellar mass}
+
 \section{Example systems}\label{sec:examples}
@@
 \begin{figure}
-  \inclfign{SW28}{ASW0007xrs_JHC3J2HYV7}
-  \caption{SW28.  See text in Section~\ref{sec:examples} for details.}
-  \label{fig:SW28}
+  \inclfign{SW05}{ASW0007k4r_AJIBCHQ6EM}
+  \caption{SW05.  See text in Section~\ref{sec:examples} for details.}
+  \label{fig:SW05}
 \end{figure}
@@
 \begin{figure}
-  \inclfign{SW05}{ASW0007k4r_AJIBCHQ6EM}
-  \caption{SW05}
-  \label{fig:SW05}
+  \inclfign{SW28}{ASW0007xrs_JHC3J2HYV7}
+  \caption{SW28}
+  \label{fig:SW28}
 \end{figure}
@@
 
-Each of Figures~\ref{fig:SW28}--\ref{fig:SW57} show six panels, as
+Each of Figures~\figref{SW05}--\figref{SW57} show six panels, as
 follows.
@@
 \item Lower left is synthetic image.
-  Figures~\ref{fig:SW28}--\ref{fig:SW29} include source fitting.
-  Figures~\ref{fig:SW42}--\ref{fig:SW57} uses a simple conical
+  Figures~\figref{SW05}--\figref{SW29} include source fitting.
+  Figures~\figref{SW42}--\figref{SW57} uses a simple conical
   profile.
@@
 \item Lower right shows stellar vs stellar mass.\todo{which population
-  model?}
+  model?}  Abundance matching \citep{2010ApJ...710..903M}.
 
@@
 
-\item Figures~\ref{fig:SW28}--\ref{fig:SW29} show the five most
-  convincing lens candidates. SW28 shown in Figure~\ref{fig:SW28} is
+\item Figures~\figref{SW28}--\figref{SW29} show the five most
+  convincing lens candidates. SW28 shown in Figure~\figref{SW28} is
   modelled as an arc with three blended images plus a saddle-point
-  closer to the galaxy.  SW05 shown in Figure~\ref{fig:SW05} has four
+  closer to the galaxy.  SW05 shown in Figure~\figref{SW05} has four
   distinct images (two close to blending).  SW02, SW09 and SW29
-  (Figures~\ref{fig:SW02}--\ref{fig:SW29}) have similar
+  (Figures~\figref{SW02}--\figref{SW29}) have similar
   configurations, with a minimum furthest from the galaxy and three
@@
 
-\item Figure~\ref{fig:SW42} shows a candidate that modelling indicates
+\item Figure~\figref{SW42} shows a candidate that modelling indicates
   is doubtful.  The images appears to have a similar morphology to the
@@
 
-\item Figures~\ref{fig:SW58} and \ref{fig:SW19} appear plausible lens
+\item Figures~\figref{SW58} and \figref{SW19} appear plausible lens
   candidates.  Their morphology is similar to SW28, but the
@@
 
-\item Figures~\ref{fig:SW36} and \ref{fig:SW57} shows {\em unclear\/}
+\item Figures~\figref{SW36} and \figref{SW57} shows {\em unclear\/}
   cases where modelling failed.
@@
 \section{Summary of models}
+
+Table~\ref{tab:models}
+
+\begin{enumerate}
+\item Image morphology.
+\item Whether images unblended.
+\end{enumerate}
 
@@
 
-The canidates that looked the most promising and left little doubt about being lenses were grouped into the category ``convincing''.
-In Figures \ref{fig:SW02} to \ref{fig:SW29} we show all the convincing candidates.
+The candidates that looked the most promising and left little doubt about being lenses were grouped into the category ``convincing''.
+In Figures \figref{SW02} to \figref{SW29} we show all the convincing candidates.
 Following we list the parameters, obtained applying the technique described in section~\ref{sec:parameter}
@@
 
-\section{Discussions}
+\section{Discussion}
 

### 2016-07-05 paper2.tex
editing

@@
 \begin{keywords}
-keyword1 -- keyword2 -- keyword3
+gravitational lensing: strong -- keyword2
 \end{keywords}
@@
 
-A passing remark in the {\em Feynman Lectures}\footnote{
-  \cite{1963flp..book.....F}} --- ``if you are looking for a good
-problem, the exact details of how the arms are formed and what
-determine the shapes of these galaxies has not been worked out'' ---
-tells us that circa 1960, galaxy dynamics was expected be an easy
-research puzzle, whose solution was just around the corner.  Yet a
-half-century later, galaxies are not nearly as well-understood as
-stars were then.  Two complications, which are clear now but were not
-so clear then, are: (i)~dynamical chaos, because galaxies are not
-spherical, and (ii)~dark matter.
+Light deflection at the rim of the Sun is famously $1.75''$.  The
+deflection angle can also be expressed in terms of the escape velocity
+$2v_{\rm esc}^2/c^2$, with $v_{\rm esc}$ at the solar surface being
+$\simeq620\rm\,km/s$.  The Galactic escape velocity at the Sun's
+location is similar: $\approx500\rm\,km/s$, typical of massive
+galaxies.  Thus, the outer regions of massive galaxies have lensing
+deflections comparable to that at the rim of the Sun.  Yet these
+quantitatively similar deflections have qualitatively different
+consequences.  Light deflection by the Sun must be accounted for in
+modern astrometry \citep[see e.g.,][]{2015CQGra..32p5008C} but is not
+itself a physics probe in the way it was a century ago.  With distant
+galaxies, however, light bending by $\sim1''$ introduces two new
+phenomena.  First, for galaxies distant enough that their apparent
+size is comparable to the bending angle, light deflection can cause
+multiple images of background sources, or strong lensing.  Second, the
+gravitational field is dominated by dark matter, hence strong lensing
+becomes a probe of dark matter in galaxies.
 
-The CFHTLS \citep{2012SPIE.8448E..0MC} has been a rich source of
-lenses by arc-finders, by machine learning \citep{2016arXiv160504309P}
-and by visual inspection \citep{2016MNRAS.455.1171M}.  The latter is
-of particular interest here.
+With no unambiguous dark-matter particle detections so far, dark
+matter has studied only through its indirect consequences on galactic
+and larger scales.  In most work, dark matter is taken to be a
+collisionless non-relativistic fluid (cold dark matter or CDM); in
+recent years, the simulation by \cite{2005Natur.435..629S} has been
+particularly influential in studying the formation of CDM structures.
+Other scenarios have also been considered, such as a cold condensing
+boson fluid \citep{2016ApJ...818...89S}.  There is a general
+consensus, however, that the origins of galaxy lie in the
+gravitational collapse, fragmentation, and mergers of dark-matter
+clumps, into which feel gas, cooling through radiative processes to
+form dense clouds and eventually stars.  There is, however, much
+debate about the details, of which \cite{2012RAA....12..917S} provide
+a nice summary.
+
+Strong-lensing galaxies are a useful source of information on the
+mutual dynamics and dark matter and gas in galaxies.  The topic has
+been explored in several studies
+\citep{2009ApJ...703L..51K,2011ApJ...740...97L,2012MNRAS.424..104L,
+  2016MNRAS.459.3677L,2016MNRAS.456..870B} but it is desirable to
+enlarge the samples from tens of lensing galaxies to thousands.  Doing
+so requires finding more lenses, of course, but also modelling their
+masses.
+
+Recent searches through the CFHTLS \citep{2012SPIE.8448E..0MC} using
+arc-finders
+\citep{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G} by
+machine learning \citep{2016arXiv160504309P} and by visual inspection
+\citep{2016MNRAS.455.1191M} have between them discovered an average of
+four lenses per square degree.  So one can be optimistic about finding
+many thousands of lenses in the next generation of wide-field surveys.
+But modelling them all will be very difficult if the process is
+labour-intensive.
+
+One possibility is to enlist the help of citizen-scientists for
+modelling large samples of lenses.  \cite{2015MNRAS.447.2170K}
+developed a system whereby experienced but non-professional lens
+enthusiasts can model newly-discovered lenses collaboratively.
 

### 2016-07-05 paper2.tex
small changes while first read

@@
 qualitative and quantitive points.  Also included are some
-improvements to the modelling software used (SpaghettiLens) are
-presented, and discussion of strategies for scaling to future surveys
+improvements to the modelling software used (SpaghettiLens),
+and discussion of strategies for scaling to future surveys
 with more and frequent discoveries.
@@
 gravitational collapse, fragmentation, and mergers of dark-matter
-clumps, into which feel gas, cooling through radiative processes to
+clumps, into which fell gas, cooling through radiative processes to
 form dense clouds and eventually stars.  There is, however, much

### 2016-07-06 paper2.tex
editing

--- 2016-07-05 paper2.tex
@@
 Stellar masses have also been estimated, using photometry from the
-CFHTLS pipeline and stellar-population models.  The trend well-known
+CFHTLS pipeline and stellar-population models.  A trend well-known
 in nearby galaxies, that star-formation efficiency is maximal for
@@
 machine learning \citep{2016arXiv160504309P} and by visual inspection
-\citep{2016MNRAS.455.1191M} have between them discovered an average of
-four lenses per square degree.  So one can be optimistic about finding
-many thousands of lenses in the next generation of wide-field surveys.
-But modelling them all will be very difficult if the process is
-labour-intensive.
+by a citizen-science volunteers
+\citep[Space~Warps][]{2016MNRAS.455.1171M,2016MNRAS.455.1191M} have
+between them discovered an average of four lenses per square degree.
+So one can be optimistic about finding many thousands of lenses in the
+next generation of wide-field surveys.  But modelling them all will be
+very difficult if the process is labour-intensive.
 
-One possibility is to enlist the help of citizen-scientists for
-modelling large samples of lenses.  \cite{2015MNRAS.447.2170K}
-developed a system whereby experienced but non-professional lens
-enthusiasts can model newly-discovered lenses collaboratively.
+\cite{2015MNRAS.447.2170K} developed a new lens-modelling strategy
+developed, designed to be scaleable to much larger lens samples.  The
+idea was to collaborate with experienced members of the
+citizen-science community, who had already participated in lens
+discovery through Space~Warps, as well as several other projects
+involving astronomical data.  The
+
+One idea for coping with the challenge of modelling many more lenses
+is to enlist the help of citizen scientists, a comm
+
+ have between them discovered an average of
 

### 2016-07-07 paper2.tex
editing

@@
 by a citizen-science volunteers
-\citep[Space~Warps][]{2016MNRAS.455.1171M,2016MNRAS.455.1191M} have
-between them discovered an average of four lenses per square degree.
-So one can be optimistic about finding many thousands of lenses in the
-next generation of wide-field surveys.  But modelling them all will be
-very difficult if the process is labour-intensive.
+\citep[Space~Warps][]{2016MNRAS.455.1191M} have between them
+discovered an average of four lenses per square degree.  So one can be
+optimistic about finding many thousands of lenses in the next
+generation of wide-field surveys.  The expected flood of new lens
+discoveries will need a similarly huge modelling modelling effort to
+reconstruct their mass distributions.
 
-\cite{2015MNRAS.447.2170K} developed a new lens-modelling strategy
-developed, designed to be scaleable to much larger lens samples.  The
-idea was to collaborate with experienced members of the
-citizen-science community, who had already participated in lens
-discovery through Space~Warps, as well as several other projects
-involving astronomical data.  The
+To prepare for the challenge of massive-sample lens modelling,
+\cite{2015MNRAS.447.2170K} developed a new modelling strategy,
+implemented as the SpaghettiLens system.  The idea is to collaborate
+with experienced members of the citizen-science community, who have
+already participated in lens discovery through Space~Warps, as well as
+several other projects involving astronomical data.  The style of
+collaboration differs, however, from Space~Warps itself.  Space~Warps
+works by sourcing a simple task to very large crowd
+
+2016MNRAS.455.1171M,
 

### 2016-07-08 paper2.tex
editing

@@
 \newcommand{\figref}[1]{Figure \ref{fig:#1}}
+
+\newcommand{\Mstel}{M_{\rm stel}}
+\newcommand{\Mhalo}{M_{\rm h}}
 
@@
 \section{Stellar mass}
+
+Based on \cite{2003MNRAS.344.1000B} models.
+
+Following \cite{2010ApJ...710..903M}
+\begin{equation}
+\begin{aligned}
+\frac{\Mstel}{\Mhalo} &= \frac{2C_0}{(\Mhalo/M_1)^{-\beta} +
+                                     (\Mhalo/M_1)^\gamma} \\
+C_0 &= 0.02820, \quad M_1 = 10^{11.884} M_\odot \\
+\beta &= 1.057, \quad \gamma = 0.556.
+\end{aligned}
+\end{equation}
+
+\begin{equation}
+\Theta = \frac{\ln(M/\Mstel)}{\ln(\Mhalo/\Mstel)}
+\end{equation}
+which we may call the halo-matching index.
+\begin{itemize}
+\item $\Theta < 0$ is unphysical because $M<\Mstel$.
+\item $\Theta = 0$ is when the stellar mass exactly accounts for the
+  lensing mass.
+\item $0 < \Theta < 1$ is the typical situation, where the lens
+  includes stars and dark matter, but not the full halo.
+\item $\Theta = 1$ means that the lens consists of the entire halo.
+\item $\Theta > 1$ is in tension with abundance-matching, because the
+  lensing mass exceeds the expected halo mass.
+\end{itemize}
 

### 2016-07-08 paper2.tex
editing

--- 2016-07-07 paper2.tex
@@
 Rafael Kueng,$^{1}$\thanks{E-mail: rafael.kueng@uzh.ch}
-Presenjit Saha,$^{1}$
+Prasenjit Saha,$^{1}$
 Lucy Oswald$^{3}$
@@
 discoveries will need a similarly huge modelling modelling effort to
-reconstruct their mass distributions.
+reconstruct their mass distributions.  To prepare for the challenge of
+massive-sample lens modelling, \cite{2015MNRAS.447.2170K} developed a
+new modelling strategy, implemented as the SpaghettiLens system.  The
+idea is to collaborate with experienced members of the citizen-science
+community, who have already participated in lens discovery through
+Space~Warps, as well as several other projects involving astronomical
+data.  In this paper, we present SpaghettiLens models of
+lens-candidates discovered through Space~Warps.
 
-To prepare for the challenge of massive-sample lens modelling,
-\cite{2015MNRAS.447.2170K} developed a new modelling strategy,
-implemented as the SpaghettiLens system.  The idea is to collaborate
-with experienced members of the citizen-science community, who have
-already participated in lens discovery through Space~Warps, as well as
-several other projects involving astronomical data.  The style of
-collaboration differs, however, from Space~Warps itself.  Space~Warps
-works by sourcing a simple task to very large crowd
+While SpaghettiLens is citizen science and based on Space~Warps, the
+collaboration with volunteers takes a very different form.  In
+Space~Warps, volunteers in a crowd of $\gtrsim10^4$ make independent
+contributions.  Each person is presented with a random selection of
+survey-patches and invited to (in effect) vote on each.  The system
+estimates each volunteer's skill level according to test-patches
+interspersed with the real data, and weights their votes accordingly
+\citep{2016MNRAS.455.1171M}.  There is an active forum for volunteers,
+but since everyone is seeing different data samples with minimal
+overlap, the forum has little if any influence on votes.  With
+SpaghettiLens there is a small group of volunteers and their
+contributions are interdependent.\footnote{For more on how this works,
+  see ``Collaborative gravitational lens modelling\dots'' in {\tt
+    http://letters.zooniverse.org} especially the model tree.}
 
-2016MNRAS.455.1171M,
+Section~\ref{sec:spl}
 
-One idea for coping with the challenge of modelling many more lenses
-is to enlist the help of citizen scientists, a comm
-
- have between them discovered an average of
-
-\section{Lens Modelling}
+\section{Lens Modelling}\label{sec:spl}
 

### 2016-07-08 paper2.tex
editing

--- 2016-07-08 paper2.tex
@@
 \newcommand{\figref}[1]{Figure \ref{fig:#1}}
+
+\newcommand{\Mstel}{M_{\rm stel}}
+\newcommand{\Mhalo}{M_{\rm h}}
+\newcommand{\haloindex}{\mathcal{H}}
 
@@
 
-Section~\ref{sec:spl}
+Section~\ref{sec:spl} explains the SpaghettiLens system.
+
+Section~\ref{sec:stellar-mass} is about stellar mass.
+
+Section~\ref{sec:examples} discusses ten systems in detail.
+
+Section~\ref{sec:summary} has a summary table.
 
@@
 
-\section{Stellar mass}
+\section{Stellar mass}\label{sec:stellar-mass}
+
+Based on \cite{2003MNRAS.344.1000B} models.
+
+Following \cite{2010ApJ...710..903M}
+\begin{equation}
+\begin{aligned}
+\frac{\Mstel}{\Mhalo} &= \frac{2C_0}{(\Mhalo/M_1)^{-\beta} +
+                                     (\Mhalo/M_1)^\gamma} \\
+C_0 &= 0.02820, \quad M_1 = 10^{11.884} M_\odot \\
+\beta &= 1.057, \quad \gamma = 0.556.
+\end{aligned}
+\end{equation}
+
+\begin{equation}
+\haloindex = \frac{\ln(M/\Mstel)}{\ln(\Mhalo/\Mstel)}
+\end{equation}
+which we may call the halo-matching index.
+\begin{itemize}
+\item $\haloindex < 0$ is unphysical because $M<\Mstel$.
+\item $\haloindex = 0$ is when the stellar mass exactly accounts for the
+  lensing mass.
+\item $0 < \haloindex < 1$ is the typical situation, where the lens
+  includes stars and dark matter, but not the full halo.
+\item $\haloindex = 1$ means that the lens consists of the entire halo.
+\item $\haloindex > 1$ is in tension with abundance-matching, because the
+  lensing mass exceeds the expected halo mass.
+\end{itemize}
 
@@
 
-\section{Summary of models}
+\section{Summary of models}\label{sec:summary}
 

### 2016-07-11 paper2.tex
more text

@@
 	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
+	\includegraphics[width=\smallwidth]{spaghetti/#2_img3_ipol}
+	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
 	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
-	\includegraphics[width=\smallwidth]{img/M_encl/#2_M_encl}
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img3_ipol}%
+	\includegraphics[width=\smallwidth]{img/M_encl/#2_M_encl}%
 	\includegraphics[width=\smallwidth]{masses/#1_#2_mstel_vs_mtot}
@@
 	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
+	\includegraphics[width=\smallwidth]{img/nsynth/#2_nsynth}
+	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
 	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
-	\includegraphics[width=\smallwidth]{img/M_encl/#2_M_encl}
-	\includegraphics[width=\smallwidth]{img/nsynth/#2_nsynth}%
+	\includegraphics[width=\smallwidth]{img/M_encl/#2_M_encl}%
 	\includegraphics[width=\smallwidth]{masses/#1_#2_mstel_vs_mtot}
@@
 
-\newcommand{\figref}[1]{Figure \ref{fig:#1}}
+\newcommand{\figref}[1]{\ref{fig:#1}}
 
@@
 
-In this section, we discuss ten systems.
+In this section we show modelling results for ten of the lens
+candidates.  The first five (see Figures~\figref{SW05}--\figref{SW29})
+are the most convincingly modelled systems.  The next three cases
+(Figures~\figref{SW42},\figref{SW58}) are less good but still very
+plausible models, and are representative of the majority of the
+sample.  The last two are examples where the models were unconvincing
+(Figures~\figref{SW36}) or completely failed (\figref{SW57}).
 
@@
   \inclfign{SW05}{ASW0007k4r_AJIBCHQ6EM}
-  \caption{SW05.  See text in Section~\ref{sec:examples} for details.}
+  \caption{Model results for SW05 (J143454.4+522850).  See text in
+    Section~\ref{sec:examples} for details.}
   \label{fig:SW05}
@@
   \inclfign{SW28}{ASW0007xrs_JHC3J2HYV7}
-  \caption{SW28}
+  \caption{Model results for SW28 (J143055.9+572431).}
   \label{fig:SW28}
@@
   \inclfign{SW02}{ASW000619d_011489}
-  \caption{SW02}
+  \caption{Model results for SW02 (J140522.2+574333).}
   \label{fig:SW02}
@@
   \inclfign{SW09}{ASW0002asp_5EKMWWVJHL}
-  \caption{SW09}
+  \caption{Model results for SW09 (J020832.1-043315).}
   \label{fig:SW09}
@@
   \inclfign{SW29}{ASW0008qsm_TOFS7JNGEK}
-  \caption{SW29}
+  \caption{Model results for SW29 (J143838.1+572647).}
   \label{fig:SW29}
@@
   \inclfig{SW42}{ASW00096rm_4Q3YCEWGLN}
-  \caption{Models of SW42, a doubtful candidate because of an
-    implausible mass ratio. (See text for details.)}
+  \caption{Modelling results for SW42 (J221716.5+015826).}
   \label{fig:SW42}
@@
   \inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
-  \caption{SW58}
+  \caption{Model results for SW58 (J143651.6+530705).}
   \label{fig:SW58}
@@
   \inclfig{SW19}{ASW0001ld7_OS3CYAKLRT}
-  \caption{SW19}
+  \caption{Model results for SW19 (J020642.0-095157).}
   \label{fig:SW19}
@@
   \inclfig{SW36}{ASW000096t_7IPP7LWVOF}
-  \caption{SW36}
+  \caption{Model results for SW36 (J090248.4-010232).}
   \label{fig:SW36}
@@
   \inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
-  \caption{SW57}
+  \caption{Model results for SW57 (J143631.5+571131).}
   \label{fig:SW57}
@@
 
-Each of Figures~\figref{SW05}--\figref{SW57} show six panels, as
-follows.
+Let us first consider Figure~\figref{SW05}, which shows model results
+from SW05 (J143454.4+522850).
 
-\begin{itemize}
+\begin{enumerate}
+\item In the upper row we have first a cutout of the Space~Warps
+  image, marked up with a spaghetti diagram.  There are four distinct
+  lensed images, and the spaghetti diagram proposes that they are a
+  minimum nearest to the lensing galaxy, a close minimum-saddle pair,
+  and a minimum further away. In Table~\ref{tab:models} we refer to
+  such configurations as `$1+2+1$'.
+\item Alongside is a synthetic image produced by modelling.  In it,
+  the fitted lensed images are shown in colour, while the lensing
+  galaxy and extraneous objects have been reduced to grayscale.  These
+  two panels are qualitative and display no units, and moreover, the
+  mutual alignment of the two panels is only approximate.
+\item The middle row shows contour maps from the model.  At middle
+  left, we have the arrival-time surface.
+\item At middle right we have the mass distribution in the usual
+  dimensionless form $\kappa$.  Again, these two panels are mainly
+  qualitative: both panels are spatially registered and centred on the
+  density-peak of the lens, but no scales have been included.
+\item The base row supplies spatial and mass scales.  The left panel
+  shows the circularly-averaged $\kappa$ of the model ensemble, with
+  increasing radius (in arcsec).  The four short vertical lines
+  correspond to the minima and saddle points marked in the upper-left
+  panel.  The effective Einstein radius is also shown.  As the radius
+  scale indicates SW05 is comparatively large lens on the
+  sky.\todo{Fix distance factor in $\kappa$.}
+\item Lower right shows the total mass in the model against the
+  estimated stellar mass, alongside the values for the whole sample.
+  The lower-right shaded region is unphysical according to the
+  stellar-population models, because it gives $M<\Mstel$. The
+  upper-left shaded region is unphysical according to abundance
+  matching, because it gives $M>\Mhalo$.  That is to say, the unshaded
+  region is $0<\haloindex<1$.
+\end{enumerate}
 
-\item The upper left panel show a cutout of the Space~Warps image,
-  marked up with a spaghetti diagram.
+Proceeding to Figure~\figref{SW28}, we have one image close to the
+galaxy and an arc further away, which is interpreted as a blend of
+three images (a saddle point with two minima on either side).  We call
+this a '1+3' configuration.  It is an indication of a mass
+distribution elongated along the arc-counterimage direction (along EW
+in this case).
 
-\item Middle left is a contour map of the arrival-time surface after
-  modelling.
+In Figures~\figref{SW02}--\figref{SW29} we see three candidates with
+an arc close the lensing galaxy and one image further away.  The arc
+is interpreted three images (a minimum with two saddle points on
+either side).  We call this a '3+1' configuration.  It is an
+indication of a mass distribution elongated perpendicular to the
+arc-counterimage direction.
 
-\item Lower left is synthetic image.
-  Figures~\figref{SW05}--\figref{SW29} include source fitting.
-  Figures~\figref{SW42}--\figref{SW57} uses a simple conical
-  profile.
+Figures~\figref{SW02}--\figref{SW29} (SW05, SW28, SW02, SW09 and SW29)
+all correspond to the mass range of massive ellipticals.  SW05 is the
+most massive of all the candidates, with a galaxy-group scale mass.
 
-\item Upper right is a mass map.
+Figure~\figref{SW42} shows SW42.  The image morphology is similar to
+SW05 in Figure~\figref{SW05}, but the lens is much smaller on the sky,
+and the inferred mass is at the low end of the sample.  (The synthetic
+image shown is cruder than for the five previous figures, but that
+does not influence the mass models.)  If these preliminary findings
+are confirmed by follow-up observations, this could be the most
+dark-matter dominated lens known.\todo{Check photometry of this
+  candidate.}
 
-\item Middle right shows a circularly averaged profile of
-  $\kappa$.\todo{Fix distance factor in $\kappa$.}
+Figures~\figref{SW58} and \figref{SW19} appear plausible lens
+candidates.  Their morphology is similar to SW28, but the saddle-point
+counterimage is not visible.  We consider these lenses plausible but
+less convincing.
 
-\item Lower right shows stellar vs stellar mass.\todo{which population
-  model?}  Abundance matching \citep{2010ApJ...710..903M}.
-
-\end{itemize}
-
-\begin{itemize}
-
-\item Figures~\figref{SW28}--\figref{SW29} show the five most
-  convincing lens candidates. SW28 shown in Figure~\figref{SW28} is
-  modelled as an arc with three blended images plus a saddle-point
-  closer to the galaxy.  SW05 shown in Figure~\figref{SW05} has four
-  distinct images (two close to blending).  SW02, SW09 and SW29
-  (Figures~\figref{SW02}--\figref{SW29}) have similar
-  configurations, with a minimum furthest from the galaxy and three
-  images blended into an arc.  All five would be massive ellipticals;
-  SW05 is the most massive of all the candidates, with a galaxy-group
-  scale mass.
-
-\item Figure~\figref{SW42} shows a candidate that modelling indicates
-  is doubtful.  The images appears to have a similar morphology to the
-  last three mentioned.  The implied mass, however, is implausibly
-  high.\todo{Check photometry of this candidate.}
-
-\item Figures~\figref{SW58} and \figref{SW19} appear plausible lens
-  candidates.  Their morphology is similar to SW28, but the
-  saddle-point counterimage is not visible.  We consider these lenses
-  plausible but less convincing.
-
-\item Figures~\figref{SW36} and \figref{SW57} shows {\em unclear\/}
-  cases where modelling failed.
-
-\end{itemize}
+Figures~\figref{SW36} and \figref{SW57} are cases where modelling
+failed.
 
@@
 \begin{enumerate}
-\item Image morphology.
-\item Whether images unblended.
+\item The image morphology concisely described: D for double, and
+  quads in sub-categorised in four ways
+  \citep[cf.][]{2003AJ....125.2769S} as LQ for long-axis quads (as in
+  Figure~\figref{SW28}), SQ for short-axis quads (as in
+  Figure~\figref{SW02}, \figref{SW09}, \figref{SW29}, \figref{SW42}),
+  IQ for inclined quads (as in Figure~\figref{SW05}) and CQ for very
+  symmetric core quads.
+\item Whether the images are unblended.  Distinct unblended images (as
+  in Figures~\figref{SW05} and \figref{SW42}) are an advantage in
+  modelling, but not essential.
+\item Whether all images are discernable.  The topography of an
+  arrival-time surface, as encoded by a spaghetti diagram, may require
+  more images than are visible.  For example, in Figure~\figref{SW58},
+  the modeller has put in a conjectural saddle point near the lensing
+  galaxy.
+\item Whether the lens is fairly isolated.
+\item Whether the arrival-time surface and synthetic image are
+  plausible.  In Figure~\figref{SW36} the model implies extra images
+  or a long arc, which are not seen.
+\item Whether the mass map is reasonable.
+\item The halo index $\haloindex$.
 \end{enumerate}
-
-Throu visual inspection of the most popular models generated for each candidate and data generated by those models we classified the candidates in four categories.
-The data available is shown in \figref{SW58}.
-\todo{better explain criterias?}
-The following sections list all the models for all the categories, each with a short explanation of the reasons.
-Additionally, selected models are presented in figures for demonstration.
-
-\subsection{plausible}
-
-The plausible candidates fail in one category, but are quite convincing in all the others.
-One particular reason for a candidate to end up in this category is that is has extended arcs, what is hard to modell with the current version of the program.
-Thats why we recomend them for a following up study, for example for taking spectras or other follow up obersatories and for other modelling programs for a try.
-
-\subsection{unclear}
-
-This categy contains the ones that are hard to say.
-They might look like lenses visually, but the modelling failed or prediced additional images.
-
-\subsection{convincing}
-
-The candidates that looked the most promising and left little doubt about being lenses were grouped into the category ``convincing''.
-In Figures \figref{SW02} to \figref{SW29} we show all the convincing candidates.
-Following we list the parameters, obtained applying the technique described in section~\ref{sec:parameter}
-
-\lenstitle{SW02 (ASW000619d)}
-Nice arc with counter image;
-additional mass at 12 o'clock doesn't seem to influence the image.
-\params{1.04}{0.32}{-5.18}
-
-\lenstitle{SW05 (ASW0007k4r)}
-The model predicts very steep central mass profile, and thus a very high lensing mass;
-looks otherwise very convincing.
-\params{3.80}{0.15}{52.50}
-
-\lenstitle{SW09 (ASW0002asp)}
-\params{1.12}{0.00}{88.39}
-
-\lenstitle{SW28 (ASW0007xrs)}
-Faint, but clearly visible arc and counter image;
-but model sfits nicely
-\params{1.04}{0.33}{66.63}
-
-\lenstitle{SW29 (ASW0008qsm)}
-Faint close arc, but reconstruion works very well;
-parameterisation of ellypticity fails.
-\params{0.73}{0.00}{249.80}
-
-\subsection{doubtful}
-
-SW42
-
-\subsection{missing}
-
-Finally this category lists all the candidates, that miss redshift measurements of the lens and thus further analysis is difficult.
-
-\lenstitle{SW03 (ASW0006mea)}
-\lenstitle{SW14 (ASW0004xjk)}
-\lenstitle{SW25 (ASW00007mq)}
-\lenstitle{SW30 (ASW0002p8y)}
-\lenstitle{SW37 (ASW00086xq)}
-\lenstitle{SW39 (ASW0005qiz)}
-\lenstitle{SW40 (ASW0008wmr)}
-\lenstitle{SW48 (ASW0000g95)}
-\lenstitle{SW49 (ASW00007ls)}
-\lenstitle{SW50 (ASW00008a0)}
-\lenstitle{SW55 (ASW0007t5y)}
-\lenstitle{SW59 (ASW00085cp)}
 
@@
 \end{table*}
-
-\section{Discussion}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \clearpage

### 2016-07-11 paper2.tex
edits

--- 2016-07-08 paper2.tex
@@
 The software allows for subsampling parameters of radius of pixels $r_\text{subs}$ and amount of subpixels per pixel $n_\text{subs}$.
-\figref{subsampling} shows the results of different settings for $r_\text{subs}$ and $n_\text{subs}$.
+Figure~\figref{subsampling} shows the results of different settings for $r_\text{subs}$ and $n_\text{subs}$.
 We can see that even the computationally least expensive settings of $r_\text{subs}=1$ and $n_\text{subs}=3$ leads to drastically improved profiles.
@@
 
-In this section, we discuss ten systems.
+In this section, we discuss ten systems, including the five systems
+most convincingly modelled, but also cases where modelling failed.
 

### 2016-07-11 paper2.tex

--- 2016-07-11 paper2.tex
@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[R. Kueng et al.]{
-Rafael Kueng,$^{1}$\thanks{E-mail: rafael.kueng@uzh.ch}
+\author[R. K\"ung et al.]{
+Rafael K\"ung,$^{1}$\thanks{E-mail: rafael.kueng@uzh.ch}
 Prasenjit Saha,$^{1}$
@@
 SpaghettiLens there is a small group of volunteers and their
-contributions are interdependent.\footnote{For more on how this works,
-  see ``Collaborative gravitational lens modelling\dots'' in {\tt
+contributions are interdependent.\footnote{See ``Collaborative
+  gravitational lens modelling\dots'' in {\tt
     http://letters.zooniverse.org} especially the model tree.}
 
-Section~\ref{sec:spl} explains the SpaghettiLens system.
+Section~\ref{sec:spl} summarises the basics of the SpaghettiLens
+system and discusses its ongoing development.  Basically, the system
+delivers free-form reconstructions (with uncertainties) of the
+sky-projected mass distributions of lens candidates.  These represent
+a consensus among modelling volunteers as to the best that could be
+achieved with the available data and software.  Photometric lens
+redshifts are used; source redshifts are set to $z=2$.  The models
+can, however, be trivially rescaled to use better redshift values, as
+and when they become available.
 
@@
 \section{Lens Modelling}\label{sec:spl}
+
+\cite{2015MNRAS.447.2170K} introduced and implemented two
+main ideas. One is a `spaghetti diagram,' which is a cartoon-like
+markup of a candidate lensing system which encodes a proposal for its
+mass distribution.  It enables volunteers to interact with a
+server-side numerical engine \citep[GLASS, developed
+  by][]{2014MNRAS.445.2181C} in an intuitive way.  The other new idea
+was a `model tree' --- a volunteer can model a lens from scratch, or
+they can modify an existing model and thus try to improve upon it.
+This facility, in conjunction with forum discussion, enables
+development trees of models.  The models reported in this paper are
+the most recent ones for each lens candidate, but typically they are
+descended from previous models through the contributions of more than
+one individual.
 
@@
 \subsection{Parameterisation of pixel models} \label{sec:parameter}
+\todo{}
 In order to fit the set of pixelated models to a single parameterised model, a program was written that took a parameterised function and subtracted from it the mean and the principle components of the data, which were calculated using classical Principle Component Analysis.
@@
 
-Based on \cite{2003MNRAS.344.1000B} models.
+Based on \cite{2003MNRAS.344.1000B} models.\todo{Needs text.}
 

### 2016-07-12 paper2.tex
editing

@@
 
-While SpaghettiLens is citizen science and based on Space~Warps, the
-collaboration with volunteers takes a very different form.  In
-Space~Warps, volunteers in a crowd of $\gtrsim10^4$ make independent
-contributions.  Each person is presented with a random selection of
-survey-patches and invited to (in effect) vote on each.  The system
-estimates each volunteer's skill level according to test-patches
-interspersed with the real data, and weights their votes accordingly
-\citep{2016MNRAS.455.1171M}.  There is an active forum for volunteers,
-but since everyone is seeing different data samples with minimal
-overlap, the forum has little if any influence on votes.  With
-SpaghettiLens there is a small group of volunteers and their
-contributions are interdependent.\footnote{See ``Collaborative
-  gravitational lens modelling\dots'' in {\tt
-    http://letters.zooniverse.org} especially the model tree.}
-
-Section~\ref{sec:spl} summarises the basics of the SpaghettiLens
-system and discusses its ongoing development.  Basically, the system
-delivers free-form reconstructions (with uncertainties) of the
-sky-projected mass distributions of lens candidates.  These represent
-a consensus among modelling volunteers as to the best that could be
-achieved with the available data and software.  Photometric lens
-redshifts are used; source redshifts are set to $z=2$.  The models
-can, however, be trivially rescaled to use better redshift values, as
-and when they become available.
+Section~\ref{sec:spl} summarises the SpaghettiLens system and
+discusses its ongoing development. A SpaghettiLens model consists of a
+statistical ensemble of free-form maps of the sky-projected mass
+distribution responsible for lensing.  Each lens candidates in
+practice gets modelled several times in a collaborative refinement
+process\footnote{See ``Collaborative gravitational lens
+  modelling\dots'' in {\tt http://letters.zooniverse.org} especially
+  the model tree.}  In this paper we report the most recent model for
+each lens, as representing a consensus among modellers, as to the best
+that could be achieved with the available data and software.
+Photometric lens redshifts are used; source redshifts are set to
+$z=2$.  The models can, however, be trivially rescaled to use better
+redshift values, as and when they become available.
+\cite{2015MNRAS.447.2170K} tested the system on simulated lenses and
+identified some areas for improvement.  The first two of those are
+taken up in Section~\ref{sec:spl}, along with a further idea.  In
+\S~\ref{subsec:hires} we show that making mass maps fine-grained in
+the central region relieves a tendency in the earlier work for mass to
+be too shallow. \S~\ref{subsec:sourcefit} we introduce fitting of the
+brightness profiles of the source.  This feature has not yet been
+included in SpaghettiLens, but has been done for in post-processing
+for a few especially interesting candidates. Then in
+\S~\ref{subsec:parameter} we consider the possibility of fitting a
+parametric lens model to the model ensemble; so far we have only been
+successful at extracting an Einstein radius.
 
@@
 \section{Lens Modelling}\label{sec:spl}
+
+SpaghettiLens is an example of a medium-sized collaboration spawned by
+a large citizen-science project (in this case Space~Warps).  While
+collaboration with volunteers is essential to both, the form of
+collaboration is very different.  In Space~Warps, volunteers in a
+crowd of $\gtrsim10^4$ make independent contributions.  Each person is
+presented with a random selection of survey-patches and invited to (in
+effect) vote on each.  The system estimates each volunteer's skill
+level according to test-patches interspersed with the real data, and
+weights their votes accordingly \citep{2016MNRAS.455.1171M}.  There is
+an active forum for volunteers, but since everyone is seeing different
+data samples with minimal overlap, the forum has little if any
+influence on votes.  With SpaghettiLens, on the other hand, there is a
+small group of volunteers and their contributions are interdependent.
 
@@
 
-\subsection{Additional / Improved Synthetic Image}
+\subsection{HiRes / Subsampling of central region}\label{subsec:hires}
+
+In a previous paper \cite{2015MNRAS.447.2170K} we identified the problem of the tendency of the models to be too shallow.
+We pinned down the problem to the central region and are confident to have it fixed with enabling sub pixel sampling in the central area.
+The software allows for subsampling parameters of radius of pixels $r_\text{subs}$ and amount of subpixels per pixel $n_\text{subs}$.
+Figure~\figref{subsampling} shows the results of different settings for $r_\text{subs}$ and $n_\text{subs}$.
+We can see that even the computationally least expensive settings of $r_\text{subs}=1$ and $n_\text{subs}=3$ leads to drastically improved profiles.
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{hires/007022_kappa_encl}
+  \caption{
+    Circularly averaged mass profile for different subsampling of central region.
+    Red line without subsampling, blue lines show subsampling with dash-dot pattern showing the mode.
+    $\cdot / \cdot \cdot \cdot$: $r_\text{subs}=1$ inner pixels, each subdivided into $n_\text{subs}=3$ sub pixels.
+    $\cdot / \cdot \cdot \cdot \cdot \cdot$: $r_\text{subs}=1$, $n_\text{subs}=5$.
+    $\cdot \cdot / \cdot \cdot \cdot $: $r_\text{subs}=2$, $n_\text{subs}=3$.
+    $\cdot \cdot \cdot / \cdot \cdot \cdot $: $r_\text{subs}=3$, $n_\text{subs}=3$.
+    }
+  \label{fig:subsampling}
+\end{figure}
+
+\subsection{Additional / Improved Synthetic Image}\label{subsec:sourcefit}
 
@@
 
-\subsection{HiRes / Subsampling of central region}
-In a previous paper \cite{2015MNRAS.447.2170K} we identified the problem of the tendency of the models to be too shallow.
-We pinned down the problem to the central region and are confident to have it fixed with enabling sub pixel sampling in the central area.
-The software allows for subsampling parameters of radius of pixels $r_\text{subs}$ and amount of subpixels per pixel $n_\text{subs}$.
-Figure~\figref{subsampling} shows the results of different settings for $r_\text{subs}$ and $n_\text{subs}$.
-We can see that even the computationally least expensive settings of $r_\text{subs}=1$ and $n_\text{subs}=3$ leads to drastically improved profiles.
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{hires/007022_kappa_encl}
-  \caption{
-    Circularly averaged mass profile for different subsampling of central region.
-    Red line without subsampling, blue lines show subsampling with dash-dot pattern showing the mode.
-    $\cdot / \cdot \cdot \cdot$: $r_\text{subs}=1$ inner pixels, each subdivided into $n_\text{subs}=3$ sub pixels.
-    $\cdot / \cdot \cdot \cdot \cdot \cdot$: $r_\text{subs}=1$, $n_\text{subs}=5$.
-    $\cdot \cdot / \cdot \cdot \cdot $: $r_\text{subs}=2$, $n_\text{subs}=3$.
-    $\cdot \cdot \cdot / \cdot \cdot \cdot $: $r_\text{subs}=3$, $n_\text{subs}=3$.
-    }
-  \label{fig:subsampling}
-\end{figure}
-
-\subsection{Parameterisation of pixel models} \label{sec:parameter}
+\subsection{Parameterisation of pixel models} \label{subsec:parameter}
 \todo{}

### 2016-07-12 paper2.tex
my hands are typing words

@@
 taken up in Section~\ref{sec:spl}, along with a further idea. In
-\S~\ref{subsec:hires} we show that making mass maps fine-grained in
-the central region relieves a tendency in the earlier work for mass to
-be too shallow. \S~\ref{subsec:sourcefit} we introduce fitting of the
-brightness profiles of the source.  This feature has not yet been
-included in SpaghettiLens, but has been done for in post-processing
-for a few especially interesting candidates. Then in
+\S~\ref{subsec:sourcefit} we introduce fitting of the brightness
+profiles of the source.  This feature has not yet been included in
+SpaghettiLens, but has been carried out in post-processing for a few
+especially interesting candidates.  In \S~\ref{subsec:hires} we show
+that making mass maps fine-grained in the central region relieves a
+tendency in the earlier work for mass to be too shallow. Then in
 \S~\ref{subsec:parameter} we consider the possibility of fitting a
@@
 
-Section~\ref{sec:stellar-mass} is about stellar mass.
+Section~\ref{sec:stellar-mass} explains how we compare the lensing
+mass with the mass in stars in the lensing galaxy.  We estimate the
+stellar mass by comparing galaxy magnitudes from the CFHTLS pipeline
+with the well-known stellar-population models of
+\cite{2003MNRAS.344.1000B}.  We then extrapolate the stellar masses to
+a halo mass using the abundance-matching prescription of
+\cite{2010ApJ...710..903M}.  Naturally, the lensing mass must be more
+than the stellar mass but no more than the total halo mass.  We then
+introduce what we call a halo index $\haloindex$ which gives an idea
+of how the lensing mass compares with these two bounds.
 
-Section~\ref{sec:examples} discusses ten systems in detail.
+Section~\ref{sec:examples} discusses ten of the systems, including six
+systems we found to be particularly interesting.  The online
+supplement gives results for all the modelled systems.
 
-Section~\ref{sec:summary} has a summary table.
+In Section~\ref{sec:summary} and Table~\ref{tab:models} we display a
+concise characterisation of each modelled system, according to the
+image morphology and how clear or indistinct it is, whether the mass
+map and synthetic lensed image appear to be plausible, and how the
+model mass compares with the estimated stellar and full-halo masses.
 
@@
 
-\cite{2015MNRAS.447.2170K} introduced and implemented two
-main ideas. One is a `spaghetti diagram,' which is a cartoon-like
-markup of a candidate lensing system which encodes a proposal for its
-mass distribution.  It enables volunteers to interact with a
-server-side numerical engine \citep[GLASS, developed
-  by][]{2014MNRAS.445.2181C} in an intuitive way.  The other new idea
-was a `model tree' --- a volunteer can model a lens from scratch, or
-they can modify an existing model and thus try to improve upon it.
-This facility, in conjunction with forum discussion, enables
-development trees of models.  The models reported in this paper are
-the most recent ones for each lens candidate, but typically they are
-descended from previous models through the contributions of more than
-one individual.
+A modeller's main input to SpaghettiLens is a sketch of arrival-time
+contours on a lensed system.  It gives the locations (or best-guess
+locations) of images of point-like sources, along with their ordering
+in arrival time, and their parities (minumum, saddle-point or
+maximum).  Such a sketch, which we call a spaghetti diagram, tends to
+resemble the form of lensed arcs, but it also in effect encodes
+encodes a proposal for its mass distribution.  A spaghetti diagram is
+read by a server-side numerical engine \citep[GLASS, developed
+  by][]{2014MNRAS.445.2181C} which then returns a statistical ensemble
+of mass maps.  The mass maps are made up of mass tiles and are
+free-form, except that they are required to be concentrated around the
+identified lens centre.  They are also required to reproduce the given
+image locations, parities and time ordering exactly.  Graphical
+representations of the mass map and arrival-time surface are returned
+to the user for review.  The user can post these results on a forum,
+or discard them and try again.  Volunteers can start the modelling
+process afresh, or they can take an existing model from the forum and
+modify its input spaghetti diagram or its accompanying options, and
+thus obtain a revised model.
 
-\subsection{HiRes / Subsampling of central region}\label{subsec:hires}
+\subsection{Improved synthetic images}\label{subsec:sourcefit}
+
+Volunteers often ask about better indicators to identify wether the
+modelling resulted in a ``good'' or ``bad'' model.  We developed a
+prototype of a better syntetic image than just the rendering of a
+conical profile.  It operates on the composite input image.  The user
+has to mask the supposed lensed images.  The algorithm then
+establishes a grid on the source plane and projects the masked pixels
+of the lense plane back to the source plane.  Multiple lens plane
+pixels fall onto one source plane pixel and get averaged.  The new
+synthetic image then reverses the mapping, coloring each pixel in the
+lens plane with the corresponding values of the source plane pixel.
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{img/new_synth_img_detailed}
+  \caption{
+      Top-left: Orginal image, top-right: improved synthetic image for candidate \sw{5} (\asw{7k4r}) and model \model{12402};
+      bottom from left to right:
+        reconstructed source in color,
+        intensity (grayscale),
+        count of lens plane pixels per source plane pixel,
+        residual of orginal image to improved syntetic image in grayscale
+    }
+  \label{fig:synthimg}
+\end{figure}
+
+\subsection{Sub-sampling of central region}\label{subsec:hires}
 
@@
   \label{fig:subsampling}
-\end{figure}
-
-\subsection{Additional / Improved Synthetic Image}\label{subsec:sourcefit}
-
-Volunteers often ask about better indicators to identify wether the modelling resulted in a ``good'' or ``bad'' model.
-We developped a prototype of a better syntetic image than just the rendering of a \todo{insert currently used source profile} profile.
-It operates on the composite input image.
-The user has to mask the supposed lensed images.
-The algorith then establishes a grid on the source plane and projects the masked pixels of the lense plane back to the source plane.
-Multiple lens plane pixels fall onto one source plane pixel and get averaged.
-The new synthetic image then reverses the mapping, coloring each pixel in the lens plane with the corresponding values of the source plane pixel.
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{img/new_synth_img_detailed}
-  \caption{
-      Top-left: Orginal image, top-right: improved synthetic image for candidate \sw{5} (\asw{7k4r}) and model \model{12402};
-      bottom from left to right:
-        reconstructed source in color,
-        intensity (grayscale),
-        count of lens plane pixels per source plane pixel,
-        residual of orginal image to improved syntetic image in grayscale
-    }
-  \label{fig:synthimg}
 \end{figure}
@@
 are the most convincingly modelled systems.  The next three cases
-(Figures~\figref{SW42},\figref{SW58}) are less good but still very
+(Figures~\figref{SW42}--\figref{SW19}) are less good but still very
 plausible models, and are representative of the majority of the
@@
 
-\subsection{Table}
-
 \begin{table*}
@@
 
-\appendix
-
-\section{Some extra material}
-
-If you want to present additional material which would interrupt the flow of the main paper,
-it can be placed in an Appendix which appears after the list of references.
+% \appendix
 

### 2016-07-13 paper2.tex
edits

@@
 
+The mass maps produced by current implementation of SpaghettiLens are
+based on images of point-like features.  No information about extended
+images is used, except in so far as they help the user identify images
+of point-like features.  The synthetic images offered to users are
+rudimentary, based on sources with conical light profiles.
+
 Volunteers often ask about better indicators to identify wether the
@@
   \includegraphics[width=\linewidth]{img/new_synth_img_detailed}
-  \caption{
-      Top-left: Orginal image, top-right: improved synthetic image for candidate \sw{5} (\asw{7k4r}) and model \model{12402};
-      bottom from left to right:
-        reconstructed source in color,
-        intensity (grayscale),
-        count of lens plane pixels per source plane pixel,
-        residual of orginal image to improved syntetic image in grayscale
-    }
+  \caption{Synthetic image with source-profile fitting in SW05
+    (J143454.4+522850). Top-left: original image; top-right: synthetic
+    image (coloured arcs) with lensing galaxy and unrelated objects in
+    greyscale; bottom from left to right: reconstructed source in
+    colour, intensity (greyscale), count of lens plane pixels per
+    source plane pixel, residual of original image to synthetic
+    image.}
   \label{fig:synthimg}
@@
   the fitted lensed images are shown in colour, while the lensing
-  galaxy and extraneous objects have been reduced to grayscale.  These
-  two panels are qualitative and display no units, and moreover, the
+  galaxy and extraneous objects have been reduced to grayscale.
+  (Figure~\figref{synthmig} in \S~\ref{subsec:sourcefit} shows a
+  synthetic image from another model of the same system.) These two
+  panels are qualitative and display no units, and moreover, the
   mutual alignment of the two panels is only approximate.

### 2016-07-13 paper2.tex
i commit that i thought I already commmited: the authors changes

@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[R. K\"ung et al.]{
-Rafael K\"ung,$^{1}$\thanks{E-mail: rafael.kueng@uzh.ch}
+
+\author[Küng et al]{Rafael Küng,$^{1}$
 Prasenjit Saha,$^{1}$
-Lucy Oswald$^{3}$
-%and Fourth Author$^{4}$
+Ignacio Ferreras,$^{2}$
+Anupreeta More,$^{3}$
+Elisabeth Baeten,$^{4}$
+\newauthor
+Jonathan Coles,$^{5}$
+Claude Cornen,$^{4}$
+Christine Macmillan,$^{4}$
+Phil Marshall,$^{6}$ 
+Lucy Oswald$^{7}$
+\newauthor
+Aprajita Verma$^{8}$
+and Julianne K. Wilcox$^{4}$
+%
 \\
-% List of institutions
-$^{1}$Physik Institut, University of Zurich, Winterthurerstrasse XXX, Zurich 8057, Switzerland\\
-$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
-$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
-%$^{4}$Another Department, Different Institution, Street Address, City Postal Code, Country
+%
+$^{1}$Physik-Institut, University of Zurich, Winterthurerstrasse 190, 8057 Zurich, Switzerland\\
+$^{2}$\\
+$^{3}$Kavli Institute for the Physics and Mathematics of the Universe, University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa-shi 277-8583, Japan\\
+$^{4}$Zooniverse, c/o Astrophysics Department, University of Oxford, Oxford OX1 3RH, UK \\
+$^{5}$Exascale Research Computing Lab, Campus Teratec, 2 Rue de la Piquetterie, 91680 Bruyeres-le-Chatel, France\\
+$^{6}$Kavli Institute for Particle Astrophysics and Cosmology, Stanford University, 452 Lomita Mall, Stanford, CA 94035, USA\\
+$^{7}$\\
+$^{8}$Sub-department of Astrophysics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
 }

### 2016-07-13 paper2.tex
editing

--- 2016-07-13 paper2.tex
@@
 
-Volunteers often ask about better indicators to identify wether the
-modelling resulted in a ``good'' or ``bad'' model.  We developed a
-prototype of a better syntetic image than just the rendering of a
-conical profile.  It operates on the composite input image.  The user
-has to mask the supposed lensed images.  The algorithm then
-establishes a grid on the source plane and projects the masked pixels
-of the lense plane back to the source plane.  Multiple lens plane
-pixels fall onto one source plane pixel and get averaged.  The new
-synthetic image then reverses the mapping, coloring each pixel in the
-lens plane with the corresponding values of the source plane pixel.
+We have now developed a prototype of better way to generate synthetic
+images.  Figure~\figref{synthimg} illustrates.  First, areas
+containing lensed images are selected (green frames in the figure).
+The selected areas must contain no light from the lensing galaxy or
+from extraneous objects.  Pixels within the selected areas are mapped
+to a grid on the source plane, using bending angles given by the mass
+model.  The mapping from lens-plane pixels to source-plane grid cells
+is many-to-one, because of image multiplicity and magnification.  The
+brightness of each source-plane pixel is set to the mean of all the
+lens-plane pixels mapping to it.  Finally, the mapping is run back to
+the lens plane.  The result is a synthetic image.  In effect, one is
+reconstructing a source-plane brightness map by least-squares.
+
+The procedure is not yet implemented in SpaghettiLens but can be
+applied in post-processing.  The new synthetic images could be used to
+improve the mass reconstruction, by weighting the ensemble of maps
+according to how good the synthetic images are, but we have not
+attempted to do so as yet.
 
@@
   \includegraphics[width=\linewidth]{img/new_synth_img_detailed}
-  \caption{Synthetic image with source-profile fitting in SW05
-    (J143454.4+522850). Top-left: original image; top-right: synthetic
-    image (coloured arcs) with lensing galaxy and unrelated objects in
-    greyscale; bottom from left to right: reconstructed source in
-    colour, intensity (greyscale), count of lens plane pixels per
-    source plane pixel, residual of original image to synthetic
-    image.}
+  \caption{Synthetic lensed image with source-profile fitting in SW05
+    (J143454.4+522850). Top-left: original image, with areas
+    containing lensed images enclosed within green frames.  Top-right:
+    synthetic image (coloured arcs) with lensing galaxy and unrelated
+    objects in greyscale.  Bottom from left to right: reconstructed
+    source in colour, intensity (greyscale), count of lens plane
+    pixels per source plane pixel, residual of original image to
+    synthetic image.}
   \label{fig:synthimg}

### 2016-07-13 paper2.tex
more words

--- 2016-07-13 paper2.tex
@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[R. K\"ung et al.]{
-Rafael K\"ung,$^{1}$\thanks{E-mail: rafael.kueng@uzh.ch}
+
+\author[K\"ung et al]{Rafael K\"ung,$^{1}$
 Prasenjit Saha,$^{1}$
-Lucy Oswald$^{3}$
-%and Fourth Author$^{4}$
+Ignacio Ferreras,$^{2}$
+Elisabeth Baeten,$^{3}$
+\newauthor
+Jonathan Coles,$^{4}$
+Claude Cornen,$^{3}$
+Christine Macmillan,$^{3}$
+Phil Marshall,$^{5}$ 
+\newauthor
+Anupreeta More,$^{6}$
+Lucy Oswald$^{7}$
+Aprajita Verma$^{8}$
+and Julianne K. Wilcox$^{4}$
+%
 \\
-% List of institutions
-$^{1}$Physik Institut, University of Zurich, Winterthurerstrasse XXX, Zurich 8057, Switzerland\\
-$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
-$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
-%$^{4}$Another Department, Different Institution, Street Address, City Postal Code, Country
+%
+$^{1}$Physik-Institut, University of Zurich, Winterthurerstrasse 190, 8057 Zurich, Switzerland\\
+$^{2}$Mullard Space Science Laboratory, University College London, Holmbury St Mary, Dorking, Surrey RH5 6NT, UK\\
+$^{3}$Zooniverse, c/o Astrophysics Department, University of Oxford, Oxford OX1 3RH, UK \\
+$^{4}$Exascale Research Computing Lab, Campus Teratec, 2 Rue de la Piquetterie, 91680 Bruyeres-le-Chatel, France\\
+$^{5}$Kavli Institute for Particle Astrophysics and Cosmology, Stanford University, 452 Lomita Mall, Stanford, CA 94035, USA\\
+$^{6}$Kavli Institute for the Physics and Mathematics of the Universe, University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa-shi 277-8583, Japan\\
+$^{7}$Murray Edwards College, University of Cambridge, Cambridge CB3 0DF, UK\\
+$^{8}$Sub-department of Astrophysics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
 }
@@
 \subsection{Parameterisation of pixel models} \label{subsec:parameter}
-\todo{}
 In order to fit the set of pixelated models to a single parameterised model, a program was written that took a parameterised function and subtracted from it the mean and the principle components of the data, which were calculated using classical Principle Component Analysis.
@@
   galaxy and extraneous objects have been reduced to grayscale.
-  (Figure~\figref{synthmig} in \S~\ref{subsec:sourcefit} shows a
+  (Figure~\figref{synthimg} in \S~\ref{subsec:sourcefit} shows a
   synthetic image from another model of the same system.) These two

### 2016-07-14 paper2.tex
removing old imgs

--- 2016-07-13 paper2.tex
@@
 	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
-	\includegraphics[width=\smallwidth]{img/M_encl/#2_M_encl}%
-	\includegraphics[width=\smallwidth]{masses/#1_#2_mstel_vs_mtot}
+	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
+	\includegraphics[width=\smallwidth]{img/mlens_vs_mstel/#1_#2_mstel_vs_mtot}
 }
@@
 
-We have now developed a prototype of better way to generate synthetic
-images.  Figure~\figref{synthimg} illustrates.  First, areas
-containing lensed images are selected (green frames in the figure).
-The selected areas must contain no light from the lensing galaxy or
-from extraneous objects.  Pixels within the selected areas are mapped
-to a grid on the source plane, using bending angles given by the mass
-model.  The mapping from lens-plane pixels to source-plane grid cells
-is many-to-one, because of image multiplicity and magnification.  The
-brightness of each source-plane pixel is set to the mean of all the
-lens-plane pixels mapping to it.  Finally, the mapping is run back to
-the lens plane.  The result is a synthetic image.  In effect, one is
-reconstructing a source-plane brightness map by least-squares.
-
-The procedure is not yet implemented in SpaghettiLens but can be
-applied in post-processing.  The new synthetic images could be used to
-improve the mass reconstruction, by weighting the ensemble of maps
-according to how good the synthetic images are, but we have not
-attempted to do so as yet.
+Volunteers often ask about better indicators to identify wether the
+modelling resulted in a ``good'' or ``bad'' model.  We developed a
+prototype of a better syntetic image than just the rendering of a
+conical profile.  It operates on the composite input image.  The user
+has to mask the supposed lensed images.  The algorithm then
+establishes a grid on the source plane and projects the masked pixels
+of the lense plane back to the source plane.  Multiple lens plane
+pixels fall onto one source plane pixel and get averaged.  The new
+synthetic image then reverses the mapping, coloring each pixel in the
+lens plane with the corresponding values of the source plane pixel.
 
@@
   \includegraphics[width=\linewidth]{img/new_synth_img_detailed}
-  \caption{Synthetic lensed image with source-profile fitting in SW05
-    (J143454.4+522850). Top-left: original image, with areas
-    containing lensed images enclosed within green frames.  Top-right:
-    synthetic image (coloured arcs) with lensing galaxy and unrelated
-    objects in greyscale.  Bottom from left to right: reconstructed
-    source in colour, intensity (greyscale), count of lens plane
-    pixels per source plane pixel, residual of original image to
-    synthetic image.}
+  \caption{Synthetic image with source-profile fitting in SW05
+    (J143454.4+522850). Top-left: original image; top-right: synthetic
+    image (coloured arcs) with lensing galaxy and unrelated objects in
+    greyscale; bottom from left to right: reconstructed source in
+    colour, intensity (greyscale), count of lens plane pixels per
+    source plane pixel, residual of original image to synthetic
+    image.}
   \label{fig:synthimg}
@@
 \begin{figure}
-  \includegraphics[width=\linewidth]{hires/007022_kappa_encl}
+  \includegraphics[width=\linewidth]{img/hires_comparison/ASW0000h2m_7022_11_hires_comparison}
+  \includegraphics[width=\linewidth]{img/hires_comparison/ASW0000h2m_7022_13_hires_comparison}
   \caption{
@@
 \begin{figure}
-  \inclfign{SW05}{ASW0007k4r_AJIBCHQ6EM}
+%  \inclfign{SW05}{ASW0007k4r_AJIBCHQ6EM}
+  \inclfign{SW05}{ASW0007k4r_N7LTELSYTM}
   \caption{Model results for SW05 (J143454.4+522850).  See text in

### 2016-07-19 paper2.tex
temporary

@@
 \begin{figure}
-  \includegraphics[width=\linewidth]{img/hires_comparison/ASW0000h2m_7022_11_hires_comparison}
-  \includegraphics[width=\linewidth]{img/hires_comparison/ASW0000h2m_7022_13_hires_comparison}
-  \caption{
-    Circularly averaged mass profile for different subsampling of central region.
-    Red line without subsampling, blue lines show subsampling with dash-dot pattern showing the mode.
-    $\cdot / \cdot \cdot \cdot$: $r_\text{subs}=1$ inner pixels, each subdivided into $n_\text{subs}=3$ sub pixels.
-    $\cdot / \cdot \cdot \cdot \cdot \cdot$: $r_\text{subs}=1$, $n_\text{subs}=5$.
-    $\cdot \cdot / \cdot \cdot \cdot $: $r_\text{subs}=2$, $n_\text{subs}=3$.
-    $\cdot \cdot \cdot / \cdot \cdot \cdot $: $r_\text{subs}=3$, $n_\text{subs}=3$.
-    }
+  \includegraphics[width=\linewidth]{img/hires_comparison/ASW000102p_6941_11_hires_comparison}
+  \includegraphics[width=\linewidth]{img/hires_comparison/ASW000102p_6941_13_hires_comparison}
+  \includegraphics[width=\linewidth]{img/hires_comparison/ASW000102p_6941_33_hires_comparison}
+  \caption{Same sim as in Figure~3 in the earlier paper.}
   \label{fig:subsampling}
@@
   scale indicates SW05 is comparatively large lens on the
-  sky.\todo{Fix distance factor in $\kappa$.}
+  sky.
 \item Lower right shows the total mass in the model against the

### 2016-07-22 paper2.tex
my hands are typing words
update table with halo index

@@
 	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
+%        \includegraphics[width=\smallwidth]{spaghetti/#2_img2}
+        \includegraphics[width=\smallwidth]{img/kappa_map/#1_#2_kappa_map}
 	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
@@
 	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
+%	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
+        \includegraphics[width=\smallwidth]{img/kappa_map/#1_#2_kappa_map}
 	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
@@
   and a minimum further away. In Table~\ref{tab:models} we refer to
-  such configurations as `$1+2+1$'.
+  such configurations as IQ for inclined quad.
 \item Alongside is a synthetic image produced by modelling.  In it,
@@
 three images (a saddle point with two minima on either side).  We call
-this a '1+3' configuration.  It is an indication of a mass
-distribution elongated along the arc-counterimage direction (along EW
-in this case).
+this a long-axis quad or LQ configuration.  It is an indication of a
+mass distribution elongated along the arc-counterimage direction
+(along EW in this case).
 
@@
 is interpreted three images (a minimum with two saddle points on
-either side).  We call this a '3+1' configuration.  It is an
-indication of a mass distribution elongated perpendicular to the
+either side).  We call this a short-axis quad or SQ configuration.  It
+is an indication of a mass distribution elongated perpendicular to the
 arc-counterimage direction.

### 2016-07-26 paper2.tex
added subsampling text

@@
 
+\begin{figure}
+  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_11_hires_comparison}
+  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_13_hires_comparison}
+  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_33_hires_comparison}
+  \caption{Model improvement resulting from using smaller mass tiles
+    in the inner region of the mass model.  Shown here are the average
+    enclosed $\kappa$ within a given projected radius, for three
+    different reconstructions of a simulated lens (sim) from
+    Space~Warps.  In each panel, the dashed blue curve is the correct
+    answer.  The orange band represents the statistical ensemble from
+    SpaghettiLens, the red line being the ensemble mean.  Locations of
+    images (maximum, saddle point, minimum) are marked with vertical
+    arrows.  Crossing the horizontal $\kappa=1$ line is the effective
+    Einstein radius, and is so labelled. The upper panel is from
+    K\"ung et al., (2015) (see Figure~3 of that paper).  The middle
+    panel is the result when the innermost mass tile is replaced by 9
+    smaller tiles.  The lower panel results from replacing each of the
+    innermost 9 tiles each with 9 smaller tiles.}
+  \label{fig:subsampling}
+\end{figure}
+
 \subsection{Sub-sampling of central region}\label{subsec:hires}
 
-In a previous paper \cite{2015MNRAS.447.2170K} we identified the problem of the tendency of the models to be too shallow.
-We pinned down the problem to the central region and are confident to have it fixed with enabling sub pixel sampling in the central area.
-The software allows for subsampling parameters of radius of pixels $r_\text{subs}$ and amount of subpixels per pixel $n_\text{subs}$.
-Figure~\figref{subsampling} shows the results of different settings for $r_\text{subs}$ and $n_\text{subs}$.
-We can see that even the computationally least expensive settings of $r_\text{subs}=1$ and $n_\text{subs}=3$ leads to drastically improved profiles.
+The models of simulated lenses in \cite{2015MNRAS.447.2170K} showed a
+tendency to be too shallow.  Allowing smaller mass tiles in the
+central region, thus allowing the pass profile to rise more steeply
+near the centre, was suggested as a possible cure.
 
-\begin{figure}
-  \includegraphics[width=\linewidth]{img/hires_comparison/ASW000102p_6941_11_hires_comparison}
-  \includegraphics[width=\linewidth]{img/hires_comparison/ASW000102p_6941_13_hires_comparison}
-  \includegraphics[width=\linewidth]{img/hires_comparison/ASW000102p_6941_33_hires_comparison}
-  \caption{Same sim as in Figure~3 in the earlier paper.}
-  \label{fig:subsampling}
-\end{figure}
+Figure~\figref{subsampling} shows an experiment with smaller mass
+tiles in the inner region.  Replacing the very central mass tile with
+9 smaller tiles allows for steeper central profiles.  Doing the same
+for the 21 innermost mass tiles \todo{Check meaning of hires
+  parameters.} solves the problem completely, but doubles the
+computation time.  The main modelling work in this paper was, however,
+done before the experiments with smaller mass tiles was complete.
+Hence the results in this paper use the intermediate option
+(corresponding to the middle panel in Figure~\figref{subsampling}).
+As the results in this paper mainly concern the enclosed mass in the
+outer regions, the remaining shallowness in the central region should
+be inconsequential.
 

### 2016-07-26 paper2.tex
more detaiols on subsampling

@@
 \newcommand{\haloindex}{\mathcal{H}}
+\newcommand{\ER}{$\Theta_{\text{E}}$} % einstein radius
 
@@
 generation of wide-field surveys.  The expected flood of new lens
-discoveries will need a similarly huge modelling modelling effort to
+discoveries will need a similarly huge modelling effort to
 reconstruct their mass distributions.  To prepare for the challenge of
@@
 maximum).  Such a sketch, which we call a spaghetti diagram, tends to
-resemble the form of lensed arcs, but it also in effect encodes
+resemble the form of lensed arcs, but it also in effect 
 encodes a proposal for its mass distribution.  A spaghetti diagram is
@@
     answer.  The orange band represents the statistical ensemble from
-    SpaghettiLens, the red line being the ensemble mean.  Locations of
+    SpaghettiLens, the orange line being the ensemble mean.  Locations of
     images (maximum, saddle point, minimum) are marked with vertical
     arrows.  Crossing the horizontal $\kappa=1$ line is the effective
-    Einstein radius, and is so labelled. The upper panel is from
+    Einstein radius \ER, and is so labelled. The upper panel is from
     K\"ung et al., (2015) (see Figure~3 of that paper).  The middle
@@
     smaller tiles.  The lower panel results from replacing each of the
-    innermost 9 tiles each with 9 smaller tiles.}
+    innermost 5 by 5 tiles each with 9 smaller tiles.}
   \label{fig:subsampling}
@@
 9 smaller tiles allows for steeper central profiles.  Doing the same
-for the 21 innermost mass tiles \todo{Check meaning of hires
-  parameters.} solves the problem completely, but doubles the
+for the 25 innermost mass tiles solves the problem completely, but increases
+the number of mass tiles by 40% and thus at least triples the
+% in practice, it's more x4 - x5! 87/22, 86/21, 85/16
 computation time.  The main modelling work in this paper was, however,
@@
   correspond to the minima and saddle points marked in the upper-left
-  panel.  The effective Einstein radius is also shown.  As the radius
+  panel.  The effective Einstein radius \ER is also shown.  As the radius
   scale indicates SW05 is comparatively large lens on the

### 2016-07-26 paper2.tex
small extension
notes
edits

@@
 
-\title[Short title, max. 45 characters]{Model of lens candidates from
+\title[Lens models for Space Warps CFHTLS]{Model of lens candidates from
   Space Warps CFHTLS}
-
-% The list of authors, and the short list which is used in the headers.
-% If you need two or more lines of authors, add an extra line using \newauthor
 
@@
 Photometric lens redshifts are used; source redshifts are set to
-$z=2$.  The models can, however, be trivially rescaled to use better
+$z=2$ unless an unambiguous photometric redshift is available.
+The models can, however, be trivially rescaled to use better
 redshift values, as and when they become available.
@@
 9 smaller tiles allows for steeper central profiles.  Doing the same
-for the 25 innermost mass tiles solves the problem completely, but increases
-the number of mass tiles by 40% and thus at least triples the
-% in practice, it's more x4 - x5! 87/22, 86/21, 85/16
-computation time.  The main modelling work in this paper was, however,
-done before the experiments with smaller mass tiles was complete.
-Hence the results in this paper use the intermediate option
-(corresponding to the middle panel in Figure~\figref{subsampling}).
-As the results in this paper mainly concern the enclosed mass in the
-outer regions, the remaining shallowness in the central region should
-be inconsequential.
+for the 25 innermost mass tiles solves the problem completely, but
+increases the number of mass tiles by 40\% and significantly increases
+the computational time.
+% 689 / 489 = 1.40899; in practice, runtime is more like x4 - x5!
+% runtimes from logfiles: 87/22, 86/21, 85/16
+The main modelling work in this paper was, however, done before the
+experiments with smaller mass tiles was complete.  Some of the models
+presented in this paper apply the intermediate option (corresponding
+to the middle panel in Figure~\figref{subsampling}) while others use
+the old system.  The results in this paper, however, mainly concern
+the enclosed mass in the outer regions, so shallowness in the central
+region should be inconsequential.
 
@@
 
+\begin{figure}
+  \caption{}
+  \label{fig:parameter}
+\end{figure}
+
 \section{Stellar mass}\label{sec:stellar-mass}
 
-Based on \cite{2003MNRAS.344.1000B} models.\todo{Needs text.}
+Based on \cite{2003MNRAS.344.1000B} models.\todo{Description of
+  stellar-population models.}
 
@@
 \begin{figure}
-%  \inclfign{SW05}{ASW0007k4r_AJIBCHQ6EM}
   \inclfign{SW05}{ASW0007k4r_N7LTELSYTM}
@@
 
-Table~\ref{tab:models}
+Table~\ref{tab:models} shows a summary of the analysis for many candidates.
+Missing rows are due to photometry data not available.
 

### 2016-07-28 paper2.tex
rE comparison figure
new spaghetti images, updates of all others
minor typos

@@
 	\includegraphics[width=\smallwidth]{spaghetti/#2_img3_ipol}
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
+%	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
+        \includegraphics[width=\smallwidth]{img/arrival_spaghetti/#1_#2_arrival_spaghetti}%
 %        \includegraphics[width=\smallwidth]{spaghetti/#2_img2}
@@
 	\includegraphics[width=\smallwidth]{img/nsynth/#2_nsynth}
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
+%        \includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
+        \includegraphics[width=\smallwidth]{img/arrival_spaghetti/#1_#2_arrival_spaghetti}%
 %	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
@@
 
-\title[Lens models for Space Warps CFHTLS]{Model of lens candidates from
+\title[Lens models for Space Warps CFHTLS]{Models of lens candidates from
   Space Warps CFHTLS}
@@
 tendency to be too shallow.  Allowing smaller mass tiles in the
-central region, thus allowing the pass profile to rise more steeply
+central region, thus allowing the mass profile to rise more steeply
 near the centre, was suggested as a possible cure.
@@
 
+Preliminary results on recovery of Einstein radii are shown in
+Figure~\ref{fig:parameter}. \todo{Einstein radii from parametric
+  model-fitting.}
+
 \begin{figure}
-  \caption{}
+  \includegraphics[width=\linewidth]{img/rE_comp/rE_comp.png}
+  \caption{Comparison of Einstein radii. {\em To be extended.}}
   \label{fig:parameter}

### 2016-09-13 paper2-unstable.tex
rearranging figures

--- 2016-07-28 paper2.tex
@@
 model mass compares with the estimated stellar and full-halo masses.
+
+\def\pwidth{.32\linewidth}
+
+\def\includeten#1#2{
+\includegraphics[width=\pwidth]{#1ASW0007k4r_N7LTELSYTM#2}%
+\includegraphics[width=\pwidth]{#1ASW00096rm_4Q3YCEWGLN#2}%
+\includegraphics[width=\pwidth]{#1ASW0007xrs_JHC3J2HYV7#2}\\
+\includegraphics[width=\pwidth]{#1ASW0007iwp_4XBJWT3COV#2}%
+\includegraphics[width=\pwidth]{#1ASW000619d_011489#2}%
+\includegraphics[width=\pwidth]{#1ASW0001ld7_OS3CYAKLRT#2}\\
+\includegraphics[width=\pwidth]{#1ASW0002asp_5EKMWWVJHL#2}%
+%\includegraphics[width=\pwidth]{#1ASW000096t_7IPP7LWVOF#2}%
+\includegraphics[width=\pwidth]{#1ASW0008qsm_TOFS7JNGEK#2}%
+\includegraphics[width=\pwidth]{#1ASW0008pag_5SXGXQYY6V#2}\\
+}
+
+\def\includezehn#1#2{
+\includegraphics[width=\pwidth]{#1SW05_ASW0007k4r_N7LTELSYTM#2}%
+\includegraphics[width=\pwidth]{#1SW42_ASW00096rm_4Q3YCEWGLN#2}%
+\includegraphics[width=\pwidth]{#1SW28_ASW0007xrs_JHC3J2HYV7#2}\\
+\includegraphics[width=\pwidth]{#1SW58_ASW0007iwp_4XBJWT3COV#2}%
+\includegraphics[width=\pwidth]{#1SW02_ASW000619d_011489#2}%
+\includegraphics[width=\pwidth]{#1SW19_ASW0001ld7_OS3CYAKLRT#2}\\
+\includegraphics[width=\pwidth]{#1SW09_ASW0002asp_5EKMWWVJHL#2}%
+%\includegraphics[width=\pwidth]{#1SW36_ASW000096t_7IPP7LWVOF#2}\\
+\includegraphics[width=\pwidth]{#1SW29_ASW0008qsm_TOFS7JNGEK#2}%
+\includegraphics[width=\pwidth]{#1SW57_ASW0008pag_5SXGXQYY6V#2}\\
+}
+
+\begin{figure*}
+\includeten{spaghetti/}{_input}
+\caption{}
+\end{figure*}
+
+%\begin{figure*}
+%\includeten{spaghetti/}{_nsynth}
+%\caption{}
+%\end{figure*}
+
+\begin{figure*}
+\includezehn{img/arrival_spaghetti/}{_arrival_spaghetti}
+\caption{}
+\end{figure*}
+
+\begin{figure*}
+\includezehn{img/kappa_map/}{_kappa_map}
+\caption{}
+\end{figure*}
+
+\begin{figure*}
+\includezehn{img/kappa_encl/}{_kappa_encl}
+\caption{}
+\end{figure*}
+
+\begin{figure*}
+\includezehn{img/mlens_vs_mstel/}{_mstel_vs_mtot}
+\caption{}
+\end{figure*}
+
+\end{document}
+
+\end{document}
 

### 2016-09-22 paper2.tex
stellar-mass part

@@
 
+\def\pwidth{.32\linewidth}
+
+\def\includeten#1#2{
+\includegraphics[width=\pwidth]{#1ASW0007k4r_N7LTELSYTM#2}%
+\includegraphics[width=\pwidth]{#1ASW00096rm_4Q3YCEWGLN#2}%
+\includegraphics[width=\pwidth]{#1ASW0007xrs_JHC3J2HYV7#2}\\
+\includegraphics[width=\pwidth]{#1ASW0007iwp_4XBJWT3COV#2}%
+\includegraphics[width=\pwidth]{#1ASW000619d_011489#2}%
+\includegraphics[width=\pwidth]{#1ASW0001ld7_OS3CYAKLRT#2}\\
+\includegraphics[width=\pwidth]{#1ASW0002asp_5EKMWWVJHL#2}%
+%\includegraphics[width=\pwidth]{#1ASW000096t_7IPP7LWVOF#2}%
+\includegraphics[width=\pwidth]{#1ASW0008qsm_TOFS7JNGEK#2}%
+\includegraphics[width=\pwidth]{#1ASW0008pag_5SXGXQYY6V#2}\\
+}
+
+\def\includezehn#1#2{
+\includegraphics[width=\pwidth]{#1SW05_ASW0007k4r_N7LTELSYTM#2}%
+\includegraphics[width=\pwidth]{#1SW42_ASW00096rm_4Q3YCEWGLN#2}%
+\includegraphics[width=\pwidth]{#1SW28_ASW0007xrs_JHC3J2HYV7#2}\\
+\includegraphics[width=\pwidth]{#1SW58_ASW0007iwp_4XBJWT3COV#2}%
+\includegraphics[width=\pwidth]{#1SW02_ASW000619d_011489#2}%
+\includegraphics[width=\pwidth]{#1SW19_ASW0001ld7_OS3CYAKLRT#2}\\
+\includegraphics[width=\pwidth]{#1SW09_ASW0002asp_5EKMWWVJHL#2}%
+%\includegraphics[width=\pwidth]{#1SW36_ASW000096t_7IPP7LWVOF#2}\\
+\includegraphics[width=\pwidth]{#1SW29_ASW0008qsm_TOFS7JNGEK#2}%
+\includegraphics[width=\pwidth]{#1SW57_ASW0008pag_5SXGXQYY6V#2}\\
+}
+
+\begin{figure*}
+\includeten{spaghetti/}{_input}
+\caption{}
+\end{figure*}
+
+%\begin{figure*}
+%\includeten{spaghetti/}{_nsynth}
+%\caption{}
+%\end{figure*}
+
+\begin{figure*}
+\includezehn{img/arrival_spaghetti/}{_arrival_spaghetti}
+\caption{}
+\end{figure*}
+
+\begin{figure*}
+\includezehn{img/kappa_map/}{_kappa_map}
+\caption{}
+\end{figure*}
+
+\begin{figure*}
+\includezehn{img/kappa_encl/}{_kappa_encl}
+\caption{}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width=\linewidth]{img/mlens_vs_mstel_one/mstel_vs_mtot_one}
+\caption{}
+\end{figure*}
+
 \section{Lens Modelling}\label{sec:spl}
@@
 
-\section{Stellar mass}\label{sec:stellar-mass}
+\section{Stellar and halo mass estimates}\label{sec:stellar-mass}
 
-Based on \cite{2003MNRAS.344.1000B} models.\todo{Description of
-  stellar-population models.}
+The stellar masses of the lens galaxies are derived by comparison of
+the photometric data with M/L estimates from population synthesis
+models.  In principle, a detailed analysis of the spectral energy
+distribution is needed to derive accurate stellar masses
+\citep[e.g.][]{2009ApJS..185..253G,2011MNRAS.418.1587T}.
+However, estimates to within 0.3\,dex in $\log($M$_s$/M$_\odot)$ can be
+derived with a single colour, preferably tracing a rest-frame colour
+similar to $U-V$ \citep[see fig.~1 of][]{2008MNRAS.383..857F}. This
+paper presents a pilot study of the potential of SpaghettiLens to
+constrain the physical properties of strong lenses. Therefore, we
+further simplify the analysis by assuming a relationship between the
+apparent total magnitude and stellar mass, at the redshift of the
+lens. Note that for typical stellar population parameters, the
+variation of this relation is at most 1\,dex. In this work, we make
+use of the \citet{2003MNRAS.344.1000B} models to derive two functional
+forms of the stellar mass with respect to SDSS-$i$ band
+magnitudes. The models have solar metallicity, with a Chabrier
+IMF, and assume two different age trends: a ``young'' model, with a
+constant 500\,Myr age at all redshifts, and an ``old'' model where the
+age is the oldest one possible at each redshift, adopting a
+standard $\Lambda$CDM model with $H_0=70$\,km\,s$^{-1}$\,Mpc$^{-1}$
+and $\Omega_m=0.3$. We take a geometric mean of the output from these
+two models as the stellar mass of the lens. This rough estimate will
+be improved in future versions by use of the available optical and NIR
+magnitudes to derive more accurate constrains on the stellar
+populations.
 
-Following \cite{2010ApJ...710..903M}
+In addition, we also derive halo masses for the lenses by use of the
+standard abundance matching technique, whereby a comparison of the
+observed stellar mass function of galaxies with the dark matter halo
+mass function from N-body simulations results in a simple relation
+between the two. We emphasize that this derivation of halo mass should
+be considered an ``average'' estimate, and a significant scatter can
+be expected as galaxies with the same stellar mass can be found in
+different environments. We refer the reader to \cite{2012MNRAS.424..104L}
+for an assessment of the effect of abundance matching on the
+derivation of dark matter halo properties in lensing galaxies. We
+follow the prescription of \citet{2010ApJ...710..903M}, namely:
+
 \begin{equation}
@@
 \end{equation}
-
+and define a halo-matching index:
 \begin{equation}
@@
 \end{equation}
-which we may call the halo-matching index.
+that relates the observed lensing to stellar mass, with the
+global ratio expected if the host halo corresponds to the
+average value derived by abundance matching. Several cases
+for $\haloindex$ can be considered:
 \begin{itemize}
@@
 
-\begin{figure}
-  \inclfign{SW05}{ASW0007k4r_N7LTELSYTM}
-  \caption{Model results for SW05 (J143454.4+522850).  See text in
-    Section~\ref{sec:examples} for details.}
-  \label{fig:SW05}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW28}{ASW0007xrs_JHC3J2HYV7}
-  \caption{Model results for SW28 (J143055.9+572431).}
-  \label{fig:SW28}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW02}{ASW000619d_011489}
-  \caption{Model results for SW02 (J140522.2+574333).}
-  \label{fig:SW02}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW09}{ASW0002asp_5EKMWWVJHL}
-  \caption{Model results for SW09 (J020832.1-043315).}
-  \label{fig:SW09}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW29}{ASW0008qsm_TOFS7JNGEK}
-  \caption{Model results for SW29 (J143838.1+572647).}
-  \label{fig:SW29}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW42}{ASW00096rm_4Q3YCEWGLN}
-  \caption{Modelling results for SW42 (J221716.5+015826).}
-  \label{fig:SW42}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
-  \caption{Model results for SW58 (J143651.6+530705).}
-  \label{fig:SW58}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW19}{ASW0001ld7_OS3CYAKLRT}
-  \caption{Model results for SW19 (J020642.0-095157).}
-  \label{fig:SW19}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW36}{ASW000096t_7IPP7LWVOF}
-  \caption{Model results for SW36 (J090248.4-010232).}
-  \label{fig:SW36}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
-  \caption{Model results for SW57 (J143631.5+571131).}
-  \label{fig:SW57}
-\end{figure}
+% \begin{figure}
+%   \inclfign{SW05}{ASW0007k4r_N7LTELSYTM}
+%   \caption{Model results for SW05 (J143454.4+522850).  See text in
+%     Section~\ref{sec:examples} for details.}
+%   \label{fig:SW05}
+% \end{figure}
+% 
+% \begin{figure}
+%   \inclfign{SW28}{ASW0007xrs_JHC3J2HYV7}
+%   \caption{Model results for SW28 (J143055.9+572431).}
+%   \label{fig:SW28}
+% \end{figure}
+% 
+% \begin{figure}
+%   \inclfign{SW02}{ASW000619d_011489}
+%   \caption{Model results for SW02 (J140522.2+574333).}
+%   \label{fig:SW02}
+% \end{figure}
+% 
+% \begin{figure}
+%   \inclfign{SW09}{ASW0002asp_5EKMWWVJHL}
+%   \caption{Model results for SW09 (J020832.1-043315).}
+%   \label{fig:SW09}
+% \end{figure}
+% 
+% \begin{figure}
+%   \inclfign{SW29}{ASW0008qsm_TOFS7JNGEK}
+%   \caption{Model results for SW29 (J143838.1+572647).}
+%   \label{fig:SW29}
+% \end{figure}
+% 
+% \begin{figure}
+%   \inclfig{SW42}{ASW00096rm_4Q3YCEWGLN}
+%   \caption{Modelling results for SW42 (J221716.5+015826).}
+%   \label{fig:SW42}
+% \end{figure}
+% 
+% \begin{figure}
+%   \inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
+%   \caption{Model results for SW58 (J143651.6+530705).}
+%   \label{fig:SW58}
+% \end{figure}
+% 
+% \begin{figure}
+%   \inclfig{SW19}{ASW0001ld7_OS3CYAKLRT}
+%   \caption{Model results for SW19 (J020642.0-095157).}
+%   \label{fig:SW19}
+% \end{figure}
+% 
+% 
+% \begin{figure}
+%   \inclfig{SW36}{ASW000096t_7IPP7LWVOF}
+%   \caption{Model results for SW36 (J090248.4-010232).}
+%   \label{fig:SW36}
+% \end{figure}
+% 
+% \begin{figure}
+%   \inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
+%   \caption{Model results for SW57 (J143631.5+571131).}
+%   \label{fig:SW57}
+% \end{figure}
 

### 2016-10-03 paper2.tex
mixing old and new synthetic images
rearranging text
moving text around

@@
 
+$$
+\begin{matrix}
+\rm SW05 & \rm SW42 & \rm SW28 \\
+\rm SW58 & \rm SW02 & \rm SW19 \\
+\rm SW09 & \rm SW29 & \rm SW57
+\end{matrix}
+$$
+
 \begin{figure*}
 \includeten{spaghetti/}{_input}
+\caption{Marked-up images.}
+\end{figure*}
+
+\begin{figure*}
+\includeten{img/nsynth/}{_nsynth}
 \caption{}
 \end{figure*}
-
-%\begin{figure*}
-%\includeten{spaghetti/}{_nsynth}
-%\caption{}
-%\end{figure*}
 
@@
 thus obtain a revised model.
-
-\subsection{Improved synthetic images}\label{subsec:sourcefit}
-
-The mass maps produced by current implementation of SpaghettiLens are
-based on images of point-like features.  No information about extended
-images is used, except in so far as they help the user identify images
-of point-like features.  The synthetic images offered to users are
-rudimentary, based on sources with conical light profiles.
-
-We have now developed a prototype of better way to generate synthetic
-images.  Figure~\figref{synthimg} illustrates.  First, areas
-containing lensed images are selected (green frames in the figure).
-The selected areas must contain no light from the lensing galaxy or
-from extraneous objects.  Pixels within the selected areas are mapped
-to a grid on the source plane, using bending angles given by the mass
-model.  The mapping from lens-plane pixels to source-plane grid cells
-is many-to-one, because of image multiplicity and magnification.  The
-brightness of each source-plane pixel is set to the mean of all the
-lens-plane pixels mapping to it.  Finally, the mapping is run back to
-the lens plane.  The result is a synthetic image.  In effect, one is
-reconstructing a source-plane brightness map by least-squares.
-
-The procedure is not yet implemented in SpaghettiLens but can be
-applied in post-processing.  The new synthetic images could be used to
-improve the mass reconstruction, by weighting the ensemble of maps
-according to how good the synthetic images are, but we have not
-attempted to do so as yet.
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{img/new_synth_img_detailed}
-  \caption{Synthetic lensed image with source-profile fitting in SW05
-    (J143454.4+522850). Top-left: original image, with areas
-    containing lensed images enclosed within green frames.  Top-right:
-    synthetic image (coloured arcs) with lensing galaxy and unrelated
-    objects in greyscale.  Bottom from left to right: reconstructed
-    source in colour, intensity (greyscale), count of lens plane
-    pixels per source plane pixel, residual of original image to
-    synthetic image.}
-  \label{fig:synthimg}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_11_hires_comparison}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_13_hires_comparison}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_33_hires_comparison}
-  \caption{Model improvement resulting from using smaller mass tiles
-    in the inner region of the mass model.  Shown here are the average
-    enclosed $\kappa$ within a given projected radius, for three
-    different reconstructions of a simulated lens (sim) from
-    Space~Warps.  In each panel, the dashed blue curve is the correct
-    answer.  The orange band represents the statistical ensemble from
-    SpaghettiLens, the orange line being the ensemble mean.  Locations of
-    images (maximum, saddle point, minimum) are marked with vertical
-    arrows.  Crossing the horizontal $\kappa=1$ line is the effective
-    Einstein radius \ER, and is so labelled. The upper panel is from
-    K\"ung et al., (2015) (see Figure~3 of that paper).  The middle
-    panel is the result when the innermost mass tile is replaced by 9
-    smaller tiles.  The lower panel results from replacing each of the
-    innermost 5 by 5 tiles each with 9 smaller tiles.}
-  \label{fig:subsampling}
-\end{figure}
-
-\subsection{Sub-sampling of central region}\label{subsec:hires}
-
-The models of simulated lenses in \cite{2015MNRAS.447.2170K} showed a
-tendency to be too shallow.  Allowing smaller mass tiles in the
-central region, thus allowing the mass profile to rise more steeply
-near the centre, was suggested as a possible cure.
-
-Figure~\figref{subsampling} shows an experiment with smaller mass
-tiles in the inner region.  Replacing the very central mass tile with
-9 smaller tiles allows for steeper central profiles.  Doing the same
-for the 25 innermost mass tiles solves the problem completely, but
-increases the number of mass tiles by 40\% and significantly increases
-the computational time.
-% 689 / 489 = 1.40899; in practice, runtime is more like x4 - x5!
-% runtimes from logfiles: 87/22, 86/21, 85/16
-The main modelling work in this paper was, however, done before the
-experiments with smaller mass tiles was complete.  Some of the models
-presented in this paper apply the intermediate option (corresponding
-to the middle panel in Figure~\figref{subsampling}) while others use
-the old system.  The results in this paper, however, mainly concern
-the enclosed mass in the outer regions, so shallowness in the central
-region should be inconsequential.
-
-\subsection{Parameterisation of pixel models} \label{subsec:parameter}
-In order to fit the set of pixelated models to a single parameterised model, a program was written that took a parameterised function and subtracted from it the mean and the principle components of the data, which were calculated using classical Principle Component Analysis.
-This created the residuals function.
-The number of components defined as principle was varied to test how this affected the output, and it was found that using 5 principle components tended to give a reasonable approximation.
-A masking function was added which selected only the data points that fell inside the image of the lens, and the principal components were clipped in order to keep the values inside the region of the ensemble of models.
-Any value higher than the clip was set to be the clip value.
-This was chosen to be 2.5 as, assuming that the data follows a Gaussian error distribution, almost all the values for the variance should lie between 2 and 3 standard deviations from the mean.
-Minimising the residuals function produces the set of parameters that fit the parameterised function to the original pixelated ensemble most closely.
-A least squares fit was used to perform this minimisation.
-The parameterised model function was obtained from the gravitational potential of an isothermal ellipsoid mass distribution \cite{2001astro.ph..2341K}.
-This model is frequently used to describe gravitational lenses as it tends to fit well with observations.
-The isothermal ellipsoid model outputs three useful parameters: the radius of the Einstein ring, the ellipticity of the model and the angle of the ellipticity from the vertical, giving the orientation of the galaxy.
-By applying this model to simulated lenses for which the values of these parameters were already known, it was possible to gain an estimate of the projected accuracy of the results, before applying the model to the candidate lensing galaxies.
-
-Preliminary results on recovery of Einstein radii are shown in
-Figure~\ref{fig:parameter}. \todo{Einstein radii from parametric
-  model-fitting.}
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{img/rE_comp/rE_comp.png}
-  \caption{Comparison of Einstein radii. {\em To be extended.}}
-  \label{fig:parameter}
-\end{figure}
 
@@
 
-% \begin{figure}
-%   \inclfign{SW05}{ASW0007k4r_N7LTELSYTM}
-%   \caption{Model results for SW05 (J143454.4+522850).  See text in
-%     Section~\ref{sec:examples} for details.}
-%   \label{fig:SW05}
-% \end{figure}
-% 
-% \begin{figure}
-%   \inclfign{SW28}{ASW0007xrs_JHC3J2HYV7}
-%   \caption{Model results for SW28 (J143055.9+572431).}
-%   \label{fig:SW28}
-% \end{figure}
-% 
-% \begin{figure}
-%   \inclfign{SW02}{ASW000619d_011489}
-%   \caption{Model results for SW02 (J140522.2+574333).}
-%   \label{fig:SW02}
-% \end{figure}
-% 
-% \begin{figure}
-%   \inclfign{SW09}{ASW0002asp_5EKMWWVJHL}
-%   \caption{Model results for SW09 (J020832.1-043315).}
-%   \label{fig:SW09}
-% \end{figure}
-% 
-% \begin{figure}
-%   \inclfign{SW29}{ASW0008qsm_TOFS7JNGEK}
-%   \caption{Model results for SW29 (J143838.1+572647).}
-%   \label{fig:SW29}
-% \end{figure}
-% 
-% \begin{figure}
-%   \inclfig{SW42}{ASW00096rm_4Q3YCEWGLN}
-%   \caption{Modelling results for SW42 (J221716.5+015826).}
-%   \label{fig:SW42}
-% \end{figure}
-% 
-% \begin{figure}
-%   \inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
-%   \caption{Model results for SW58 (J143651.6+530705).}
-%   \label{fig:SW58}
-% \end{figure}
-% 
-% \begin{figure}
-%   \inclfig{SW19}{ASW0001ld7_OS3CYAKLRT}
-%   \caption{Model results for SW19 (J020642.0-095157).}
-%   \label{fig:SW19}
-% \end{figure}
-% 
-% 
-% \begin{figure}
-%   \inclfig{SW36}{ASW000096t_7IPP7LWVOF}
-%   \caption{Model results for SW36 (J090248.4-010232).}
-%   \label{fig:SW36}
-% \end{figure}
-% 
-% \begin{figure}
-%   \inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
-%   \caption{Model results for SW57 (J143631.5+571131).}
-%   \label{fig:SW57}
-% \end{figure}
+$$
+\begin{matrix}
+\rm SW05  &\rm SW42  &\rm SW28 \\
+\rm SW58  &\rm SW02  &\rm SW19 \\
+\rm SW09  &\rm SW29  &\rm SW57
+\end{matrix}
+$$
 
@@
 
-% \appendix
+\clearpage
 
-\clearpage
+\appendix
+
+\section{SpaghettiLens developments}
+
+\subsection{Improved synthetic images}\label{subsec:sourcefit}
+
+The mass maps produced by current implementation of SpaghettiLens are
+based on images of point-like features.  No information about extended
+images is used, except in so far as they help the user identify images
+of point-like features.  The synthetic images offered to users are
+rudimentary, corresponding to conical light profiles (that is,
+circular light profiles with brightness decreasing linearly with radius).
+
+We have now developed a prototype of better way to generate synthetic
+images.  Figure~\figref{synthimg} illustrates.  First, areas
+containing lensed images are selected (green frames in the figure).
+The selected areas should be as free as possible from of light from
+the lensing galaxy or from extraneous objects.  Pixels within the
+selected areas are mapped to a grid on the source plane, using bending
+angles given by the mass model.  The mapping from lens-plane pixels to
+source-plane grid cells is many-to-one, because of image multiplicity
+and magnification.  The brightness of each source-plane pixel is set
+to the mean of all the lens-plane pixels mapping to it.  Finally, the
+mapping is run back to the lens plane.  The result is a synthetic
+image.  In effect, one is reconstructing a source-plane brightness map
+by least-squares.
+
+The procedure is not yet implemented in SpaghettiLens but can be
+applied in post-processing.  The new synthetic images could be used to
+improve the mass reconstruction, by weighting the ensemble of maps
+according to how good the synthetic images are, but we have not
+attempted to do so as yet.
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{img/new_synth_img_detailed}
+  \caption{Synthetic lensed image with source-profile fitting in SW05
+    (J143454.4+522850). Top-left: original image, with areas
+    containing lensed images enclosed within green frames.  Top-right:
+    synthetic image (coloured arcs) with lensing galaxy and unrelated
+    objects in greyscale.  Bottom from left to right: reconstructed
+    source in colour, intensity (greyscale), count of lens plane
+    pixels per source plane pixel, residual of original image to
+    synthetic image.}
+  \label{fig:synthimg}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_11_hires_comparison}
+  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_13_hires_comparison}
+  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_33_hires_comparison}
+  \caption{Model improvement resulting from using smaller mass tiles
+    in the inner region of the mass model.  Shown here are the average
+    enclosed $\kappa$ within a given projected radius, for three
+    different reconstructions of a simulated lens (sim) from
+    Space~Warps.  In each panel, the dashed blue curve is the correct
+    answer.  The orange band represents the statistical ensemble from
+    SpaghettiLens, the orange line being the ensemble mean.  Locations of
+    images (maximum, saddle point, minimum) are marked with vertical
+    arrows.  Crossing the horizontal $\kappa=1$ line is the effective
+    Einstein radius \ER, and is so labelled. The upper panel is from
+    K\"ung et al., (2015) (see Figure~3 of that paper).  The middle
+    panel is the result when the innermost mass tile is replaced by 9
+    smaller tiles.  The lower panel results from replacing each of the
+    innermost 5 by 5 tiles each with 9 smaller tiles.}
+  \label{fig:subsampling}
+\end{figure}
+
+\subsection{Sub-sampling of central region}\label{subsec:hires}
+
+The models of simulated lenses in \cite{2015MNRAS.447.2170K} showed a
+tendency to be too shallow.  Allowing smaller mass tiles in the
+central region, thus allowing the mass profile to rise more steeply
+near the centre, was suggested as a possible cure.
+
+Figure~\figref{subsampling} shows an experiment with smaller mass
+tiles in the inner region.  Replacing the very central mass tile with
+9 smaller tiles allows for steeper central profiles.  Doing the same
+for the 25 innermost mass tiles solves the problem completely, but
+increases the number of mass tiles by 40\% and significantly increases
+the computational time.
+% 689 / 489 = 1.40899; in practice, runtime is more like x4 - x5!
+% runtimes from logfiles: 87/22, 86/21, 85/16
+The main modelling work in this paper was, however, done before the
+experiments with smaller mass tiles was complete.  Some of the models
+presented in this paper apply the intermediate option (corresponding
+to the middle panel in Figure~\figref{subsampling}) while others use
+the old system.  The results in this paper, however, mainly concern
+the enclosed mass in the outer regions, so shallowness in the central
+region should be inconsequential.
+
+\subsection{Parameterisation of pixel models} \label{subsec:parameter}
+In order to fit the set of pixelated models to a single parameterised model, a program was written that took a parameterised function and subtracted from it the mean and the principal components of the data, which were calculated using classical Principal Component Analysis.
+This created the residuals function.
+The number of components used in the analysis was varied, to test how this affected the output, and it was found that using 5 principle components tended to give a reasonable approximation.
+A masking function was added which selected only the data points that fell inside the image of the lens, and the principal components were clipped in order to keep the values inside the region of the ensemble of models.
+Any value higher than the clip was set to be the clip value.
+This was chosen to be 2.5 as, assuming that the data follows a Gaussian error distribution, almost all the values for the variance should lie between 2 and 3 standard deviations from the mean.
+Minimising the residuals function produces the set of parameters that fit the parameterised function to the original pixelated ensemble most closely.
+A least squares fit was used to perform this minimisation.
+The parameterised model function was obtained from the gravitational potential of an isothermal ellipsoid mass distribution \citep{2001astro.ph..2341K}.
+This model is frequently used to describe gravitational lenses as it tends to fit well with observations.
+The isothermal ellipsoid model outputs three useful parameters: the radius of the Einstein ring, the ellipticity of the model and the angle of the ellipticity from the vertical, giving the orientation of the galaxy.
+By applying this model to simulated lenses for which the values of these parameters were already known, it was possible to gain an estimate of the projected accuracy of the results, before applying the model to the candidate lensing galaxies.
+
+Preliminary results on recovery of Einstein radii are shown in
+Figure~\ref{fig:parameter}. \todo{Einstein radii from parametric
+  model-fitting.}
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{img/rE_comp/rE_comp.png}
+  \caption{Comparison of Einstein radii. {\em To be extended.}}
+  \label{fig:parameter}
+\end{figure}
 
@@
 \end{document}
+
+% \begin{figure}
+%   \inclfign{SW05}{ASW0007k4r_N7LTELSYTM}
+%   \caption{Model results for SW05 (J143454.4+522850).  See text in
+%     Section~\ref{sec:examples} for details.}
+%   \label{fig:SW05}
+% \end{figure}
+% 
+% \begin{figure}
+%   \inclfign{SW28}{ASW0007xrs_JHC3J2HYV7}
+%   \caption{Model results for SW28 (J143055.9+572431).}
+%   \label{fig:SW28}
+% \end{figure}
+% 
+% \begin{figure}
+%   \inclfign{SW02}{ASW000619d_011489}
+%   \caption{Model results for SW02 (J140522.2+574333).}
+%   \label{fig:SW02}
+% \end{figure}
+% 
+% \begin{figure}
+%   \inclfign{SW09}{ASW0002asp_5EKMWWVJHL}
+%   \caption{Model results for SW09 (J020832.1-043315).}
+%   \label{fig:SW09}
+% \end{figure}
+% 
+% \begin{figure}
+%   \inclfign{SW29}{ASW0008qsm_TOFS7JNGEK}
+%   \caption{Model results for SW29 (J143838.1+572647).}
+%   \label{fig:SW29}
+% \end{figure}
+% 
+% \begin{figure}
+%   \inclfig{SW42}{ASW00096rm_4Q3YCEWGLN}
+%   \caption{Modelling results for SW42 (J221716.5+015826).}
+%   \label{fig:SW42}
+% \end{figure}
+% 
+% \begin{figure}
+%   \inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
+%   \caption{Model results for SW58 (J143651.6+530705).}
+%   \label{fig:SW58}
+% \end{figure}
+% 
+% \begin{figure}
+%   \inclfig{SW19}{ASW0001ld7_OS3CYAKLRT}
+%   \caption{Model results for SW19 (J020642.0-095157).}
+%   \label{fig:SW19}
+% \end{figure}
+% 
+% 
+% \begin{figure}
+%   \inclfig{SW36}{ASW000096t_7IPP7LWVOF}
+%   \caption{Model results for SW36 (J090248.4-010232).}
+%   \label{fig:SW36}
+% \end{figure}
+% 
+% \begin{figure}
+%   \inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
+%   \caption{Model results for SW57 (J143631.5+571131).}
+%   \label{fig:SW57}
+% \end{figure}

### 2016-10-03 paper2.tex
moving text around

@@
 
-\section{Introduction}
-
-Light deflection at the rim of the Sun is famously $1.75''$.  The
-deflection angle can also be expressed in terms of the escape velocity
-$2v_{\rm esc}^2/c^2$, with $v_{\rm esc}$ at the solar surface being
-$\simeq620\rm\,km/s$.  The Galactic escape velocity at the Sun's
-location is similar: $\approx500\rm\,km/s$, typical of massive
-galaxies.  Thus, the outer regions of massive galaxies have lensing
-deflections comparable to that at the rim of the Sun.  Yet these
-quantitatively similar deflections have qualitatively different
-consequences.  Light deflection by the Sun must be accounted for in
-modern astrometry \citep[see e.g.,][]{2015CQGra..32p5008C} but is not
-itself a physics probe in the way it was a century ago.  With distant
-galaxies, however, light bending by $\sim1''$ introduces two new
-phenomena.  First, for galaxies distant enough that their apparent
-size is comparable to the bending angle, light deflection can cause
-multiple images of background sources, or strong lensing.  Second, the
-gravitational field is dominated by dark matter, hence strong lensing
-becomes a probe of dark matter in galaxies.
-
-With no unambiguous dark-matter particle detections so far, dark
-matter has studied only through its indirect consequences on galactic
-and larger scales.  In most work, dark matter is taken to be a
-collisionless non-relativistic fluid (cold dark matter or CDM); in
-recent years, the simulation by \cite{2005Natur.435..629S} has been
-particularly influential in studying the formation of CDM structures.
-Other scenarios have also been considered, such as a cold condensing
-boson fluid \citep{2016ApJ...818...89S}.  There is a general
-consensus, however, that the origins of galaxy lie in the
-gravitational collapse, fragmentation, and mergers of dark-matter
-clumps, into which fell gas, cooling through radiative processes to
-form dense clouds and eventually stars.  There is, however, much
-debate about the details, of which \cite{2012RAA....12..917S} provide
-a nice summary.
-
-Strong-lensing galaxies are a useful source of information on the
-mutual dynamics and dark matter and gas in galaxies.  The topic has
-been explored in several studies
-\citep{2009ApJ...703L..51K,2011ApJ...740...97L,2012MNRAS.424..104L,
-  2016MNRAS.459.3677L,2016MNRAS.456..870B} but it is desirable to
-enlarge the samples from tens of lensing galaxies to thousands.  Doing
-so requires finding more lenses, of course, but also modelling their
-masses.
-
-Recent searches through the CFHTLS \citep{2012SPIE.8448E..0MC} using
-arc-finders
-\citep{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G} by
-machine learning \citep{2016arXiv160504309P} and by visual inspection
-by a citizen-science volunteers
-\citep[Space~Warps][]{2016MNRAS.455.1191M} have between them
-discovered an average of four lenses per square degree.  So one can be
-optimistic about finding many thousands of lenses in the next
-generation of wide-field surveys.  The expected flood of new lens
-discoveries will need a similarly huge modelling effort to
-reconstruct their mass distributions.  To prepare for the challenge of
-massive-sample lens modelling, \cite{2015MNRAS.447.2170K} developed a
-new modelling strategy, implemented as the SpaghettiLens system.  The
-idea is to collaborate with experienced members of the citizen-science
-community, who have already participated in lens discovery through
-Space~Warps, as well as several other projects involving astronomical
-data.  In this paper, we present SpaghettiLens models of
-lens-candidates discovered through Space~Warps.
-
-Section~\ref{sec:spl} summarises the SpaghettiLens system and
-discusses its ongoing development. A SpaghettiLens model consists of a
-statistical ensemble of free-form maps of the sky-projected mass
-distribution responsible for lensing.  Each lens candidates in
-practice gets modelled several times in a collaborative refinement
-process\footnote{See ``Collaborative gravitational lens
-  modelling\dots'' in {\tt http://letters.zooniverse.org} especially
-  the model tree.}  In this paper we report the most recent model for
-each lens, as representing a consensus among modellers, as to the best
-that could be achieved with the available data and software.
-Photometric lens redshifts are used; source redshifts are set to
-$z=2$ unless an unambiguous photometric redshift is available.
-The models can, however, be trivially rescaled to use better
-redshift values, as and when they become available.
-\cite{2015MNRAS.447.2170K} tested the system on simulated lenses and
-identified some areas for improvement.  The first two of those are
-taken up in Section~\ref{sec:spl}, along with a further idea. In
-\S~\ref{subsec:sourcefit} we introduce fitting of the brightness
-profiles of the source.  This feature has not yet been included in
-SpaghettiLens, but has been carried out in post-processing for a few
-especially interesting candidates.  In \S~\ref{subsec:hires} we show
-that making mass maps fine-grained in the central region relieves a
-tendency in the earlier work for mass to be too shallow. Then in
-\S~\ref{subsec:parameter} we consider the possibility of fitting a
-parametric lens model to the model ensemble; so far we have only been
-successful at extracting an Einstein radius.
-
-Section~\ref{sec:stellar-mass} explains how we compare the lensing
-mass with the mass in stars in the lensing galaxy.  We estimate the
-stellar mass by comparing galaxy magnitudes from the CFHTLS pipeline
-with the well-known stellar-population models of
-\cite{2003MNRAS.344.1000B}.  We then extrapolate the stellar masses to
-a halo mass using the abundance-matching prescription of
-\cite{2010ApJ...710..903M}.  Naturally, the lensing mass must be more
-than the stellar mass but no more than the total halo mass.  We then
-introduce what we call a halo index $\haloindex$ which gives an idea
-of how the lensing mass compares with these two bounds.
-
-Section~\ref{sec:examples} discusses ten of the systems, including six
-systems we found to be particularly interesting.  The online
-supplement gives results for all the modelled systems.
-
-In Section~\ref{sec:summary} and Table~\ref{tab:models} we display a
-concise characterisation of each modelled system, according to the
-image morphology and how clear or indistinct it is, whether the mass
-map and synthetic lensed image appear to be plausible, and how the
-model mass compares with the estimated stellar and full-halo masses.
-
 \def\pwidth{.32\linewidth}
@@
 
-$$
-\begin{matrix}
-\rm SW05 & \rm SW42 & \rm SW28 \\
-\rm SW58 & \rm SW02 & \rm SW19 \\
-\rm SW09 & \rm SW29 & \rm SW57
-\end{matrix}
-$$
+\input parts/intro
 
-\begin{figure*}
-\includeten{spaghetti/}{_input}
-\caption{Marked-up images.}
-\end{figure*}
+\input parts/spl
 
-\begin{figure*}
-\includeten{img/nsynth/}{_nsynth}
-\caption{}
-\end{figure*}
+\input parts/massmodel
 
-\begin{figure*}
-\includezehn{img/arrival_spaghetti/}{_arrival_spaghetti}
-\caption{}
-\end{figure*}
+\input parts/synthimage
 
-\begin{figure*}
-\includezehn{img/kappa_map/}{_kappa_map}
-\caption{}
-\end{figure*}
-
-\begin{figure*}
-\includezehn{img/kappa_encl/}{_kappa_encl}
-\caption{}
-\end{figure*}
-
-\begin{figure*}
-\includegraphics[width=\linewidth]{img/mlens_vs_mstel_one/mstel_vs_mtot_one}
-\caption{}
-\end{figure*}
-
-\section{Lens Modelling}\label{sec:spl}
-
-SpaghettiLens is an example of a medium-sized collaboration spawned by
-a large citizen-science project (in this case Space~Warps).  While
-collaboration with volunteers is essential to both, the form of
-collaboration is very different.  In Space~Warps, volunteers in a
-crowd of $\gtrsim10^4$ make independent contributions.  Each person is
-presented with a random selection of survey-patches and invited to (in
-effect) vote on each.  The system estimates each volunteer's skill
-level according to test-patches interspersed with the real data, and
-weights their votes accordingly \citep{2016MNRAS.455.1171M}.  There is
-an active forum for volunteers, but since everyone is seeing different
-data samples with minimal overlap, the forum has little if any
-influence on votes.  With SpaghettiLens, on the other hand, there is a
-small group of volunteers and their contributions are interdependent.
-
-A modeller's main input to SpaghettiLens is a sketch of arrival-time
-contours on a lensed system.  It gives the locations (or best-guess
-locations) of images of point-like sources, along with their ordering
-in arrival time, and their parities (minumum, saddle-point or
-maximum).  Such a sketch, which we call a spaghetti diagram, tends to
-resemble the form of lensed arcs, but it also in effect 
-encodes a proposal for its mass distribution.  A spaghetti diagram is
-read by a server-side numerical engine \citep[GLASS, developed
-  by][]{2014MNRAS.445.2181C} which then returns a statistical ensemble
-of mass maps.  The mass maps are made up of mass tiles and are
-free-form, except that they are required to be concentrated around the
-identified lens centre.  They are also required to reproduce the given
-image locations, parities and time ordering exactly.  Graphical
-representations of the mass map and arrival-time surface are returned
-to the user for review.  The user can post these results on a forum,
-or discard them and try again.  Volunteers can start the modelling
-process afresh, or they can take an existing model from the forum and
-modify its input spaghetti diagram or its accompanying options, and
-thus obtain a revised model.
-
-\section{Stellar and halo mass estimates}\label{sec:stellar-mass}
-
-The stellar masses of the lens galaxies are derived by comparison of
-the photometric data with M/L estimates from population synthesis
-models.  In principle, a detailed analysis of the spectral energy
-distribution is needed to derive accurate stellar masses
-\citep[e.g.][]{2009ApJS..185..253G,2011MNRAS.418.1587T}.
-However, estimates to within 0.3\,dex in $\log($M$_s$/M$_\odot)$ can be
-derived with a single colour, preferably tracing a rest-frame colour
-similar to $U-V$ \citep[see fig.~1 of][]{2008MNRAS.383..857F}. This
-paper presents a pilot study of the potential of SpaghettiLens to
-constrain the physical properties of strong lenses. Therefore, we
-further simplify the analysis by assuming a relationship between the
-apparent total magnitude and stellar mass, at the redshift of the
-lens. Note that for typical stellar population parameters, the
-variation of this relation is at most 1\,dex. In this work, we make
-use of the \citet{2003MNRAS.344.1000B} models to derive two functional
-forms of the stellar mass with respect to SDSS-$i$ band
-magnitudes. The models have solar metallicity, with a Chabrier
-IMF, and assume two different age trends: a ``young'' model, with a
-constant 500\,Myr age at all redshifts, and an ``old'' model where the
-age is the oldest one possible at each redshift, adopting a
-standard $\Lambda$CDM model with $H_0=70$\,km\,s$^{-1}$\,Mpc$^{-1}$
-and $\Omega_m=0.3$. We take a geometric mean of the output from these
-two models as the stellar mass of the lens. This rough estimate will
-be improved in future versions by use of the available optical and NIR
-magnitudes to derive more accurate constrains on the stellar
-populations.
-
-In addition, we also derive halo masses for the lenses by use of the
-standard abundance matching technique, whereby a comparison of the
-observed stellar mass function of galaxies with the dark matter halo
-mass function from N-body simulations results in a simple relation
-between the two. We emphasize that this derivation of halo mass should
-be considered an ``average'' estimate, and a significant scatter can
-be expected as galaxies with the same stellar mass can be found in
-different environments. We refer the reader to \cite{2012MNRAS.424..104L}
-for an assessment of the effect of abundance matching on the
-derivation of dark matter halo properties in lensing galaxies. We
-follow the prescription of \citet{2010ApJ...710..903M}, namely:
-
-\begin{equation}
-\begin{aligned}
-\frac{\Mstel}{\Mhalo} &= \frac{2C_0}{(\Mhalo/M_1)^{-\beta} +
-                                     (\Mhalo/M_1)^\gamma} \\
-C_0 &= 0.02820, \quad M_1 = 10^{11.884} M_\odot \\
-\beta &= 1.057, \quad \gamma = 0.556.
-\end{aligned}
-\end{equation}
-and define a halo-matching index:
-\begin{equation}
-\haloindex = \frac{\ln(M/\Mstel)}{\ln(\Mhalo/\Mstel)}
-\end{equation}
-that relates the observed lensing to stellar mass, with the
-global ratio expected if the host halo corresponds to the
-average value derived by abundance matching. Several cases
-for $\haloindex$ can be considered:
-\begin{itemize}
-\item $\haloindex < 0$ is unphysical because $M<\Mstel$.
-\item $\haloindex = 0$ is when the stellar mass exactly accounts for the
-  lensing mass.
-\item $0 < \haloindex < 1$ is the typical situation, where the lens
-  includes stars and dark matter, but not the full halo.
-\item $\haloindex = 1$ means that the lens consists of the entire halo.
-\item $\haloindex > 1$ is in tension with abundance-matching, because the
-  lensing mass exceeds the expected halo mass.
-\end{itemize}
+\input parts/stelmass
 
@@
 
-$$
-\begin{matrix}
-\rm SW05  &\rm SW42  &\rm SW28 \\
-\rm SW58  &\rm SW02  &\rm SW19 \\
-\rm SW09  &\rm SW29  &\rm SW57
-\end{matrix}
-$$
+\begin{enumerate}
 
-Let us first consider Figure~\figref{SW05}, which shows model results
-from SW05 (J143454.4+522850).
-
-\begin{enumerate}
-\item In the upper row we have first a cutout of the Space~Warps
-  image, marked up with a spaghetti diagram.  There are four distinct
-  lensed images, and the spaghetti diagram proposes that they are a
-  minimum nearest to the lensing galaxy, a close minimum-saddle pair,
-  and a minimum further away. In Table~\ref{tab:models} we refer to
-  such configurations as IQ for inclined quad.
 \item Alongside is a synthetic image produced by modelling.  In it,
@@
 
-Proceeding to Figure~\figref{SW28}, we have one image close to the
-galaxy and an arc further away, which is interpreted as a blend of
-three images (a saddle point with two minima on either side).  We call
-this a long-axis quad or LQ configuration.  It is an indication of a
-mass distribution elongated along the arc-counterimage direction
-(along EW in this case).
-
-In Figures~\figref{SW02}--\figref{SW29} we see three candidates with
-an arc close the lensing galaxy and one image further away.  The arc
-is interpreted three images (a minimum with two saddle points on
-either side).  We call this a short-axis quad or SQ configuration.  It
-is an indication of a mass distribution elongated perpendicular to the
-arc-counterimage direction.
-
 Figures~\figref{SW02}--\figref{SW29} (SW05, SW28, SW02, SW09 and SW29)
@@
 
-Figure~\figref{SW42} shows SW42.  The image morphology is similar to
-SW05 in Figure~\figref{SW05}, but the lens is much smaller on the sky,
-and the inferred mass is at the low end of the sample.  (The synthetic
-image shown is cruder than for the five previous figures, but that
-does not influence the mass models.)  If these preliminary findings
-are confirmed by follow-up observations, this could be the most
-dark-matter dominated lens known.\todo{Check photometry of this
+For SW42 the inferred mass is at the low end of the sample.  (The
+synthetic image shown is cruder than for the five previous figures,
+but that does not influence the mass models.)  If these preliminary
+findings are confirmed by follow-up observations, this could be the
+most dark-matter dominated lens known.\todo{Check photometry of this
   candidate.}
@@
 \section{Summary of models}\label{sec:summary}
-
-Table~\ref{tab:models} shows a summary of the analysis for many candidates.
-Missing rows are due to photometry data not available.
-
-\begin{enumerate}
-\item The image morphology concisely described: D for double, and
-  quads in sub-categorised in four ways
-  \citep[cf.][]{2003AJ....125.2769S} as LQ for long-axis quads (as in
-  Figure~\figref{SW28}), SQ for short-axis quads (as in
-  Figure~\figref{SW02}, \figref{SW09}, \figref{SW29}, \figref{SW42}),
-  IQ for inclined quads (as in Figure~\figref{SW05}) and CQ for very
-  symmetric core quads.
-\item Whether the images are unblended.  Distinct unblended images (as
-  in Figures~\figref{SW05} and \figref{SW42}) are an advantage in
-  modelling, but not essential.
-\item Whether all images are discernable.  The topography of an
-  arrival-time surface, as encoded by a spaghetti diagram, may require
-  more images than are visible.  For example, in Figure~\figref{SW58},
-  the modeller has put in a conjectural saddle point near the lensing
-  galaxy.
-\item Whether the lens is fairly isolated.
-\item Whether the arrival-time surface and synthetic image are
-  plausible.  In Figure~\figref{SW36} the model implies extra images
-  or a long arc, which are not seen.
-\item Whether the mass map is reasonable.
-\item The halo index $\haloindex$.
-\end{enumerate}
 
@@
 \subsection{Improved synthetic images}\label{subsec:sourcefit}
-
-The mass maps produced by current implementation of SpaghettiLens are
-based on images of point-like features.  No information about extended
-images is used, except in so far as they help the user identify images
-of point-like features.  The synthetic images offered to users are
-rudimentary, corresponding to conical light profiles (that is,
-circular light profiles with brightness decreasing linearly with radius).
-
-We have now developed a prototype of better way to generate synthetic
-images.  Figure~\figref{synthimg} illustrates.  First, areas
-containing lensed images are selected (green frames in the figure).
-The selected areas should be as free as possible from of light from
-the lensing galaxy or from extraneous objects.  Pixels within the
-selected areas are mapped to a grid on the source plane, using bending
-angles given by the mass model.  The mapping from lens-plane pixels to
-source-plane grid cells is many-to-one, because of image multiplicity
-and magnification.  The brightness of each source-plane pixel is set
-to the mean of all the lens-plane pixels mapping to it.  Finally, the
-mapping is run back to the lens plane.  The result is a synthetic
-image.  In effect, one is reconstructing a source-plane brightness map
-by least-squares.
-
-The procedure is not yet implemented in SpaghettiLens but can be
-applied in post-processing.  The new synthetic images could be used to
-improve the mass reconstruction, by weighting the ensemble of maps
-according to how good the synthetic images are, but we have not
-attempted to do so as yet.
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{img/new_synth_img_detailed}
-  \caption{Synthetic lensed image with source-profile fitting in SW05
-    (J143454.4+522850). Top-left: original image, with areas
-    containing lensed images enclosed within green frames.  Top-right:
-    synthetic image (coloured arcs) with lensing galaxy and unrelated
-    objects in greyscale.  Bottom from left to right: reconstructed
-    source in colour, intensity (greyscale), count of lens plane
-    pixels per source plane pixel, residual of original image to
-    synthetic image.}
-  \label{fig:synthimg}
-\end{figure}
 

### 2016-10-03 parts/intro.tex
moving text around

--- 2016-07-26 paper2.tex
@@
-\documentclass[fleqn,usenatbib]{mnras}
-
-%%% DEBUG SETTINGS - remove at the end %%%%%%%%%%%%%%%
-\usepackage{silence} % silence error warinings
-\WarningFilter{caption}{Unsupported document class} % caption doesn't know mnras..
-\hbadness = 5000
-\vbadness = 10000
-% \usepackage{}
-
-% MNRAS is set in Times font. If you don't have this installed (most LaTeX
-% installations will be fine) or prefer the old Computer Modern fonts, comment
-% out the following line
-%\usepackage{newtxtext,newtxmath} % not yet supported on arxiv and uni computer
-%\usepackage{txfonts}
-
-% Depending on your LaTeX fonts installation, you might get better results with one of these:
-%\usepackage{mathptmx}
-%\usepackage{txfonts}
-
-% Use vector fonts, so it zooms properly in on-screen viewing software
-% Don't change these lines unless you know what you are doing
-\usepackage[T1]{fontenc} % make sure font is supported
-% \usepackage{ae,aecompl} %obsolete when using modern fonts
-\usepackage[final]{microtype} % make sure font is supported
-% and a suitable font
-\usepackage{lmodern} % use a modern font with T1 support
-%\usepackage{cm-super} % use a modern font with T1 support
-
-%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
-
-% Only include extra packages if you really need them. Common packages are:
-%\usepackage[dvipdfmx]{graphicx}	% Including figure files
-\usepackage{graphicx} % Including figure files
-%\usepackage[skip=0pt]{subcaption}
-\usepackage{amsmath}	% Advanced maths commands
-\usepackage{amssymb}	% Extra maths symbols
-\usepackage{pifont}	% Extra maths symbols
-%\usepackage{bmpsize}  % PS still needs this for correct bounding boxes?
-
-% TODO stuff, comment out for final submit
-\usepackage{todonotes} % as long as we are editing...
-%\usepackage{showframe} % for debug
-%\overfullrule=5pt      % show overfull boxes
-
-% I disabled hyperlink in the cls und included it here because of bugs
-\usepackage{hyperref}   % Hyperlinks
-\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,filecolor=blue,urlcolor=blue}
-
-\edef\smallwidth{0.4\linewidth}
-
-\newcommand{\inclfig}[2]{
-  \centering
-	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img3_ipol}
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
-%        \includegraphics[width=\smallwidth]{spaghetti/#2_img2}
-        \includegraphics[width=\smallwidth]{img/kappa_map/#1_#2_kappa_map}
-	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
-	\includegraphics[width=\smallwidth]{img/mlens_vs_mstel/#1_#2_mstel_vs_mtot}
-}
-
-\newcommand{\inclfign}[2]{
-  \centering
-	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
-	\includegraphics[width=\smallwidth]{img/nsynth/#2_nsynth}
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
-%	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
-        \includegraphics[width=\smallwidth]{img/kappa_map/#1_#2_kappa_map}
-	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
-	\includegraphics[width=\smallwidth]{img/mlens_vs_mstel/#1_#2_mstel_vs_mtot}
-}
-
-\newcommand*{\rot}{\rotatebox{90}}
-\newcommand*{\OK}{\ding{51}}
-\newcommand*{\NO}{\ding{55}}
-
-\newcommand{\lenstitle}[1]{\noindent\textbf{#1} --}
-\newcommand{\params}[3]{(\(\Theta_\text{E}:#1\), $\varepsilon:#2$, $\alpha_\varepsilon:#3$ )}
-
-\newcommand{\asw}[1]{ASW000#1}
-\newcommand{\sw}[1]{SW~#1}
-\newcommand{\model}[1]{SL model~#1}
-
-\newcommand{\figref}[1]{\ref{fig:#1}}
-
-\newcommand{\Mstel}{M_{\rm stel}}
-\newcommand{\Mhalo}{M_{\rm h}}
-\newcommand{\haloindex}{\mathcal{H}}
-\newcommand{\ER}{$\Theta_{\text{E}}$} % einstein radius
-
-\title[Lens models for Space Warps CFHTLS]{Model of lens candidates from
-  Space Warps CFHTLS}
-
-\author[K\"ung et al]{Rafael K\"ung,$^{1}$
-Prasenjit Saha,$^{1}$
-Ignacio Ferreras,$^{2}$
-Elisabeth Baeten,$^{3}$
-\newauthor
-Jonathan Coles,$^{4}$
-Claude Cornen,$^{3}$
-Christine Macmillan,$^{3}$
-Phil Marshall,$^{5}$ 
-\newauthor
-Anupreeta More,$^{6}$
-Lucy Oswald$^{7}$
-Aprajita Verma$^{8}$
-and Julianne K. Wilcox$^{4}$
-%
-\\
-%
-$^{1}$Physik-Institut, University of Zurich, Winterthurerstrasse 190, 8057 Zurich, Switzerland\\
-$^{2}$Mullard Space Science Laboratory, University College London, Holmbury St Mary, Dorking, Surrey RH5 6NT, UK\\
-$^{3}$Zooniverse, c/o Astrophysics Department, University of Oxford, Oxford OX1 3RH, UK \\
-$^{4}$Exascale Research Computing Lab, Campus Teratec, 2 Rue de la Piquetterie, 91680 Bruyeres-le-Chatel, France\\
-$^{5}$Kavli Institute for Particle Astrophysics and Cosmology, Stanford University, 452 Lomita Mall, Stanford, CA 94035, USA\\
-$^{6}$Kavli Institute for the Physics and Mathematics of the Universe, University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa-shi 277-8583, Japan\\
-$^{7}$Murray Edwards College, University of Cambridge, Cambridge CB3 0DF, UK\\
-$^{8}$Sub-department of Astrophysics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
-}
-
-% These dates will be filled out by the publisher
-% \date{Accepted XXX. Received YYY; in original form ZZZ}
-
-% Enter the current year, for the copyright statements etc.
-\pubyear{2016}
-
-% Don't change these lines
-\begin{document}
-\label{firstpage}
-\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\maketitle
-
-\begin{abstract}
-We report modelling follow-up of recently-discovered
-gravitational-lens candidates in the CFHT Legacy Survey.  Lens
-modelling was done by a small group of specially-interested volunteers
-from the Space~Warps citizen-science community who originally found
-the candidate lenses.  Models are categorised according to seven
-qualitative and quantitive points.  Also included are some
-improvements to the modelling software used (SpaghettiLens),
-and discussion of strategies for scaling to future surveys
-with more and frequent discoveries.
-
-The candidates successfully modelled are all galaxies, with inferred
-lensing masses ranging from $\sim10^{11}M_\odot$ to $>10^{13}M_\odot$.
-Stellar masses have also been estimated, using photometry from the
-CFHTLS pipeline and stellar-population models.  A trend well-known
-in nearby galaxies, that star-formation efficiency is maximal for
-total masses of $\approx10^{12}M_\odot$ and reduces for both lower and
-higher masses, is discernable also in these much more distant
-galaxies.
-\end{abstract}
-
-\begin{keywords}
-gravitational lensing: strong -- keyword2
-\end{keywords}
-
 \section{Introduction}
@@
 
-\section{Lens Modelling}\label{sec:spl}
-
-SpaghettiLens is an example of a medium-sized collaboration spawned by
-a large citizen-science project (in this case Space~Warps).  While
-collaboration with volunteers is essential to both, the form of
-collaboration is very different.  In Space~Warps, volunteers in a
-crowd of $\gtrsim10^4$ make independent contributions.  Each person is
-presented with a random selection of survey-patches and invited to (in
-effect) vote on each.  The system estimates each volunteer's skill
-level according to test-patches interspersed with the real data, and
-weights their votes accordingly \citep{2016MNRAS.455.1171M}.  There is
-an active forum for volunteers, but since everyone is seeing different
-data samples with minimal overlap, the forum has little if any
-influence on votes.  With SpaghettiLens, on the other hand, there is a
-small group of volunteers and their contributions are interdependent.
-
-A modeller's main input to SpaghettiLens is a sketch of arrival-time
-contours on a lensed system.  It gives the locations (or best-guess
-locations) of images of point-like sources, along with their ordering
-in arrival time, and their parities (minumum, saddle-point or
-maximum).  Such a sketch, which we call a spaghetti diagram, tends to
-resemble the form of lensed arcs, but it also in effect 
-encodes a proposal for its mass distribution.  A spaghetti diagram is
-read by a server-side numerical engine \citep[GLASS, developed
-  by][]{2014MNRAS.445.2181C} which then returns a statistical ensemble
-of mass maps.  The mass maps are made up of mass tiles and are
-free-form, except that they are required to be concentrated around the
-identified lens centre.  They are also required to reproduce the given
-image locations, parities and time ordering exactly.  Graphical
-representations of the mass map and arrival-time surface are returned
-to the user for review.  The user can post these results on a forum,
-or discard them and try again.  Volunteers can start the modelling
-process afresh, or they can take an existing model from the forum and
-modify its input spaghetti diagram or its accompanying options, and
-thus obtain a revised model.
-
-\subsection{Improved synthetic images}\label{subsec:sourcefit}
-
-The mass maps produced by current implementation of SpaghettiLens are
-based on images of point-like features.  No information about extended
-images is used, except in so far as they help the user identify images
-of point-like features.  The synthetic images offered to users are
-rudimentary, based on sources with conical light profiles.
-
-We have now developed a prototype of better way to generate synthetic
-images.  Figure~\figref{synthimg} illustrates.  First, areas
-containing lensed images are selected (green frames in the figure).
-The selected areas must contain no light from the lensing galaxy or
-from extraneous objects.  Pixels within the selected areas are mapped
-to a grid on the source plane, using bending angles given by the mass
-model.  The mapping from lens-plane pixels to source-plane grid cells
-is many-to-one, because of image multiplicity and magnification.  The
-brightness of each source-plane pixel is set to the mean of all the
-lens-plane pixels mapping to it.  Finally, the mapping is run back to
-the lens plane.  The result is a synthetic image.  In effect, one is
-reconstructing a source-plane brightness map by least-squares.
-
-The procedure is not yet implemented in SpaghettiLens but can be
-applied in post-processing.  The new synthetic images could be used to
-improve the mass reconstruction, by weighting the ensemble of maps
-according to how good the synthetic images are, but we have not
-attempted to do so as yet.
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{img/new_synth_img_detailed}
-  \caption{Synthetic lensed image with source-profile fitting in SW05
-    (J143454.4+522850). Top-left: original image, with areas
-    containing lensed images enclosed within green frames.  Top-right:
-    synthetic image (coloured arcs) with lensing galaxy and unrelated
-    objects in greyscale.  Bottom from left to right: reconstructed
-    source in colour, intensity (greyscale), count of lens plane
-    pixels per source plane pixel, residual of original image to
-    synthetic image.}
-  \label{fig:synthimg}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_11_hires_comparison}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_13_hires_comparison}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_33_hires_comparison}
-  \caption{Model improvement resulting from using smaller mass tiles
-    in the inner region of the mass model.  Shown here are the average
-    enclosed $\kappa$ within a given projected radius, for three
-    different reconstructions of a simulated lens (sim) from
-    Space~Warps.  In each panel, the dashed blue curve is the correct
-    answer.  The orange band represents the statistical ensemble from
-    SpaghettiLens, the orange line being the ensemble mean.  Locations of
-    images (maximum, saddle point, minimum) are marked with vertical
-    arrows.  Crossing the horizontal $\kappa=1$ line is the effective
-    Einstein radius \ER, and is so labelled. The upper panel is from
-    K\"ung et al., (2015) (see Figure~3 of that paper).  The middle
-    panel is the result when the innermost mass tile is replaced by 9
-    smaller tiles.  The lower panel results from replacing each of the
-    innermost 5 by 5 tiles each with 9 smaller tiles.}
-  \label{fig:subsampling}
-\end{figure}
-
-\subsection{Sub-sampling of central region}\label{subsec:hires}
-
-The models of simulated lenses in \cite{2015MNRAS.447.2170K} showed a
-tendency to be too shallow.  Allowing smaller mass tiles in the
-central region, thus allowing the pass profile to rise more steeply
-near the centre, was suggested as a possible cure.
-
-Figure~\figref{subsampling} shows an experiment with smaller mass
-tiles in the inner region.  Replacing the very central mass tile with
-9 smaller tiles allows for steeper central profiles.  Doing the same
-for the 25 innermost mass tiles solves the problem completely, but
-increases the number of mass tiles by 40\% and significantly increases
-the computational time.
-% 689 / 489 = 1.40899; in practice, runtime is more like x4 - x5!
-% runtimes from logfiles: 87/22, 86/21, 85/16
-The main modelling work in this paper was, however, done before the
-experiments with smaller mass tiles was complete.  Some of the models
-presented in this paper apply the intermediate option (corresponding
-to the middle panel in Figure~\figref{subsampling}) while others use
-the old system.  The results in this paper, however, mainly concern
-the enclosed mass in the outer regions, so shallowness in the central
-region should be inconsequential.
-
-\subsection{Parameterisation of pixel models} \label{subsec:parameter}
-In order to fit the set of pixelated models to a single parameterised model, a program was written that took a parameterised function and subtracted from it the mean and the principle components of the data, which were calculated using classical Principle Component Analysis.
-This created the residuals function.
-The number of components defined as principle was varied to test how this affected the output, and it was found that using 5 principle components tended to give a reasonable approximation.
-A masking function was added which selected only the data points that fell inside the image of the lens, and the principal components were clipped in order to keep the values inside the region of the ensemble of models.
-Any value higher than the clip was set to be the clip value.
-This was chosen to be 2.5 as, assuming that the data follows a Gaussian error distribution, almost all the values for the variance should lie between 2 and 3 standard deviations from the mean.
-Minimising the residuals function produces the set of parameters that fit the parameterised function to the original pixelated ensemble most closely.
-A least squares fit was used to perform this minimisation.
-The parameterised model function was obtained from the gravitational potential of an isothermal ellipsoid mass distribution \cite{2001astro.ph..2341K}.
-This model is frequently used to describe gravitational lenses as it tends to fit well with observations.
-The isothermal ellipsoid model outputs three useful parameters: the radius of the Einstein ring, the ellipticity of the model and the angle of the ellipticity from the vertical, giving the orientation of the galaxy.
-By applying this model to simulated lenses for which the values of these parameters were already known, it was possible to gain an estimate of the projected accuracy of the results, before applying the model to the candidate lensing galaxies.
-
-\begin{figure}
-  \caption{}
-  \label{fig:parameter}
-\end{figure}
-
-\section{Stellar mass}\label{sec:stellar-mass}
-
-Based on \cite{2003MNRAS.344.1000B} models.\todo{Description of
-  stellar-population models.}
-
-Following \cite{2010ApJ...710..903M}
-\begin{equation}
-\begin{aligned}
-\frac{\Mstel}{\Mhalo} &= \frac{2C_0}{(\Mhalo/M_1)^{-\beta} +
-                                     (\Mhalo/M_1)^\gamma} \\
-C_0 &= 0.02820, \quad M_1 = 10^{11.884} M_\odot \\
-\beta &= 1.057, \quad \gamma = 0.556.
-\end{aligned}
-\end{equation}
-
-\begin{equation}
-\haloindex = \frac{\ln(M/\Mstel)}{\ln(\Mhalo/\Mstel)}
-\end{equation}
-which we may call the halo-matching index.
-\begin{itemize}
-\item $\haloindex < 0$ is unphysical because $M<\Mstel$.
-\item $\haloindex = 0$ is when the stellar mass exactly accounts for the
-  lensing mass.
-\item $0 < \haloindex < 1$ is the typical situation, where the lens
-  includes stars and dark matter, but not the full halo.
-\item $\haloindex = 1$ means that the lens consists of the entire halo.
-\item $\haloindex > 1$ is in tension with abundance-matching, because the
-  lensing mass exceeds the expected halo mass.
-\end{itemize}
-
-\section{Example systems}\label{sec:examples}
-
-In this section we show modelling results for ten of the lens
-candidates.  The first five (see Figures~\figref{SW05}--\figref{SW29})
-are the most convincingly modelled systems.  The next three cases
-(Figures~\figref{SW42}--\figref{SW19}) are less good but still very
-plausible models, and are representative of the majority of the
-sample.  The last two are examples where the models were unconvincing
-(Figures~\figref{SW36}) or completely failed (\figref{SW57}).
-
-\begin{figure}
-  \inclfign{SW05}{ASW0007k4r_N7LTELSYTM}
-  \caption{Model results for SW05 (J143454.4+522850).  See text in
-    Section~\ref{sec:examples} for details.}
-  \label{fig:SW05}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW28}{ASW0007xrs_JHC3J2HYV7}
-  \caption{Model results for SW28 (J143055.9+572431).}
-  \label{fig:SW28}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW02}{ASW000619d_011489}
-  \caption{Model results for SW02 (J140522.2+574333).}
-  \label{fig:SW02}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW09}{ASW0002asp_5EKMWWVJHL}
-  \caption{Model results for SW09 (J020832.1-043315).}
-  \label{fig:SW09}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW29}{ASW0008qsm_TOFS7JNGEK}
-  \caption{Model results for SW29 (J143838.1+572647).}
-  \label{fig:SW29}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW42}{ASW00096rm_4Q3YCEWGLN}
-  \caption{Modelling results for SW42 (J221716.5+015826).}
-  \label{fig:SW42}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
-  \caption{Model results for SW58 (J143651.6+530705).}
-  \label{fig:SW58}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW19}{ASW0001ld7_OS3CYAKLRT}
-  \caption{Model results for SW19 (J020642.0-095157).}
-  \label{fig:SW19}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW36}{ASW000096t_7IPP7LWVOF}
-  \caption{Model results for SW36 (J090248.4-010232).}
-  \label{fig:SW36}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
-  \caption{Model results for SW57 (J143631.5+571131).}
-  \label{fig:SW57}
-\end{figure}
-
-Let us first consider Figure~\figref{SW05}, which shows model results
-from SW05 (J143454.4+522850).
-
-\begin{enumerate}
-\item In the upper row we have first a cutout of the Space~Warps
-  image, marked up with a spaghetti diagram.  There are four distinct
-  lensed images, and the spaghetti diagram proposes that they are a
-  minimum nearest to the lensing galaxy, a close minimum-saddle pair,
-  and a minimum further away. In Table~\ref{tab:models} we refer to
-  such configurations as IQ for inclined quad.
-\item Alongside is a synthetic image produced by modelling.  In it,
-  the fitted lensed images are shown in colour, while the lensing
-  galaxy and extraneous objects have been reduced to grayscale.
-  (Figure~\figref{synthimg} in \S~\ref{subsec:sourcefit} shows a
-  synthetic image from another model of the same system.) These two
-  panels are qualitative and display no units, and moreover, the
-  mutual alignment of the two panels is only approximate.
-\item The middle row shows contour maps from the model.  At middle
-  left, we have the arrival-time surface.
-\item At middle right we have the mass distribution in the usual
-  dimensionless form $\kappa$.  Again, these two panels are mainly
-  qualitative: both panels are spatially registered and centred on the
-  density-peak of the lens, but no scales have been included.
-\item The base row supplies spatial and mass scales.  The left panel
-  shows the circularly-averaged $\kappa$ of the model ensemble, with
-  increasing radius (in arcsec).  The four short vertical lines
-  correspond to the minima and saddle points marked in the upper-left
-  panel.  The effective Einstein radius \ER is also shown.  As the radius
-  scale indicates SW05 is comparatively large lens on the
-  sky.
-\item Lower right shows the total mass in the model against the
-  estimated stellar mass, alongside the values for the whole sample.
-  The lower-right shaded region is unphysical according to the
-  stellar-population models, because it gives $M<\Mstel$. The
-  upper-left shaded region is unphysical according to abundance
-  matching, because it gives $M>\Mhalo$.  That is to say, the unshaded
-  region is $0<\haloindex<1$.
-\end{enumerate}
-
-Proceeding to Figure~\figref{SW28}, we have one image close to the
-galaxy and an arc further away, which is interpreted as a blend of
-three images (a saddle point with two minima on either side).  We call
-this a long-axis quad or LQ configuration.  It is an indication of a
-mass distribution elongated along the arc-counterimage direction
-(along EW in this case).
-
-In Figures~\figref{SW02}--\figref{SW29} we see three candidates with
-an arc close the lensing galaxy and one image further away.  The arc
-is interpreted three images (a minimum with two saddle points on
-either side).  We call this a short-axis quad or SQ configuration.  It
-is an indication of a mass distribution elongated perpendicular to the
-arc-counterimage direction.
-
-Figures~\figref{SW02}--\figref{SW29} (SW05, SW28, SW02, SW09 and SW29)
-all correspond to the mass range of massive ellipticals.  SW05 is the
-most massive of all the candidates, with a galaxy-group scale mass.
-
-Figure~\figref{SW42} shows SW42.  The image morphology is similar to
-SW05 in Figure~\figref{SW05}, but the lens is much smaller on the sky,
-and the inferred mass is at the low end of the sample.  (The synthetic
-image shown is cruder than for the five previous figures, but that
-does not influence the mass models.)  If these preliminary findings
-are confirmed by follow-up observations, this could be the most
-dark-matter dominated lens known.\todo{Check photometry of this
-  candidate.}
-
-Figures~\figref{SW58} and \figref{SW19} appear plausible lens
-candidates.  Their morphology is similar to SW28, but the saddle-point
-counterimage is not visible.  We consider these lenses plausible but
-less convincing.
-
-Figures~\figref{SW36} and \figref{SW57} are cases where modelling
-failed.
-
-\section{Summary of models}\label{sec:summary}
-
 Table~\ref{tab:models} shows a summary of the analysis for many candidates.
@@
 \end{enumerate}
-
-\begin{table*}
-  \caption{Categorisation of SW models}
-  \label{tab:models}
-  \include{table}
-\end{table*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% The best way to enter references is to use BibTeX:
-\bibliographystyle{mnras}
-\bibliography{bib/bibli} % if your bibtex file is called example.bib
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \appendix
-
-\clearpage
-
-\section{TODO}
-\listoftodos
-
-% Don't change these lines
-\bsp	% typesetting comment
-\label{lastpage}
-\end{document}

### 2016-10-03 parts/massmodel.tex
moving text around

--- 2016-07-26 paper2.tex
@@
-\documentclass[fleqn,usenatbib]{mnras}
+\section{Mass models}
 
-%%% DEBUG SETTINGS - remove at the end %%%%%%%%%%%%%%%
-\usepackage{silence} % silence error warinings
-\WarningFilter{caption}{Unsupported document class} % caption doesn't know mnras..
-\hbadness = 5000
-\vbadness = 10000
-% \usepackage{}
+\begin{figure*}
+\includezehn{img/arrival_spaghetti/}{_arrival_spaghetti}
+\caption{}
+\end{figure*}
 
-% MNRAS is set in Times font. If you don't have this installed (most LaTeX
-% installations will be fine) or prefer the old Computer Modern fonts, comment
-% out the following line
-%\usepackage{newtxtext,newtxmath} % not yet supported on arxiv and uni computer
-%\usepackage{txfonts}
+\begin{figure*}
+\includezehn{img/kappa_map/}{_kappa_map}
+\caption{}
+\end{figure*}
 
-% Depending on your LaTeX fonts installation, you might get better results with one of these:
-%\usepackage{mathptmx}
-%\usepackage{txfonts}
-
-% Use vector fonts, so it zooms properly in on-screen viewing software
-% Don't change these lines unless you know what you are doing
-\usepackage[T1]{fontenc} % make sure font is supported
-% \usepackage{ae,aecompl} %obsolete when using modern fonts
-\usepackage[final]{microtype} % make sure font is supported
-% and a suitable font
-\usepackage{lmodern} % use a modern font with T1 support
-%\usepackage{cm-super} % use a modern font with T1 support
-
-%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
-
-% Only include extra packages if you really need them. Common packages are:
-%\usepackage[dvipdfmx]{graphicx}	% Including figure files
-\usepackage{graphicx} % Including figure files
-%\usepackage[skip=0pt]{subcaption}
-\usepackage{amsmath}	% Advanced maths commands
-\usepackage{amssymb}	% Extra maths symbols
-\usepackage{pifont}	% Extra maths symbols
-%\usepackage{bmpsize}  % PS still needs this for correct bounding boxes?
-
-% TODO stuff, comment out for final submit
-\usepackage{todonotes} % as long as we are editing...
-%\usepackage{showframe} % for debug
-%\overfullrule=5pt      % show overfull boxes
-
-% I disabled hyperlink in the cls und included it here because of bugs
-\usepackage{hyperref}   % Hyperlinks
-\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,filecolor=blue,urlcolor=blue}
-
-\edef\smallwidth{0.4\linewidth}
-
-\newcommand{\inclfig}[2]{
-  \centering
-	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img3_ipol}
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
-%        \includegraphics[width=\smallwidth]{spaghetti/#2_img2}
-        \includegraphics[width=\smallwidth]{img/kappa_map/#1_#2_kappa_map}
-	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
-	\includegraphics[width=\smallwidth]{img/mlens_vs_mstel/#1_#2_mstel_vs_mtot}
-}
-
-\newcommand{\inclfign}[2]{
-  \centering
-	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
-	\includegraphics[width=\smallwidth]{img/nsynth/#2_nsynth}
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
-%	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
-        \includegraphics[width=\smallwidth]{img/kappa_map/#1_#2_kappa_map}
-	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
-	\includegraphics[width=\smallwidth]{img/mlens_vs_mstel/#1_#2_mstel_vs_mtot}
-}
-
-\newcommand*{\rot}{\rotatebox{90}}
-\newcommand*{\OK}{\ding{51}}
-\newcommand*{\NO}{\ding{55}}
-
-\newcommand{\lenstitle}[1]{\noindent\textbf{#1} --}
-\newcommand{\params}[3]{(\(\Theta_\text{E}:#1\), $\varepsilon:#2$, $\alpha_\varepsilon:#3$ )}
-
-\newcommand{\asw}[1]{ASW000#1}
-\newcommand{\sw}[1]{SW~#1}
-\newcommand{\model}[1]{SL model~#1}
-
-\newcommand{\figref}[1]{\ref{fig:#1}}
-
-\newcommand{\Mstel}{M_{\rm stel}}
-\newcommand{\Mhalo}{M_{\rm h}}
-\newcommand{\haloindex}{\mathcal{H}}
-\newcommand{\ER}{$\Theta_{\text{E}}$} % einstein radius
-
-\title[Lens models for Space Warps CFHTLS]{Model of lens candidates from
-  Space Warps CFHTLS}
-
-\author[K\"ung et al]{Rafael K\"ung,$^{1}$
-Prasenjit Saha,$^{1}$
-Ignacio Ferreras,$^{2}$
-Elisabeth Baeten,$^{3}$
-\newauthor
-Jonathan Coles,$^{4}$
-Claude Cornen,$^{3}$
-Christine Macmillan,$^{3}$
-Phil Marshall,$^{5}$ 
-\newauthor
-Anupreeta More,$^{6}$
-Lucy Oswald$^{7}$
-Aprajita Verma$^{8}$
-and Julianne K. Wilcox$^{4}$
-%
-\\
-%
-$^{1}$Physik-Institut, University of Zurich, Winterthurerstrasse 190, 8057 Zurich, Switzerland\\
-$^{2}$Mullard Space Science Laboratory, University College London, Holmbury St Mary, Dorking, Surrey RH5 6NT, UK\\
-$^{3}$Zooniverse, c/o Astrophysics Department, University of Oxford, Oxford OX1 3RH, UK \\
-$^{4}$Exascale Research Computing Lab, Campus Teratec, 2 Rue de la Piquetterie, 91680 Bruyeres-le-Chatel, France\\
-$^{5}$Kavli Institute for Particle Astrophysics and Cosmology, Stanford University, 452 Lomita Mall, Stanford, CA 94035, USA\\
-$^{6}$Kavli Institute for the Physics and Mathematics of the Universe, University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa-shi 277-8583, Japan\\
-$^{7}$Murray Edwards College, University of Cambridge, Cambridge CB3 0DF, UK\\
-$^{8}$Sub-department of Astrophysics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
-}
-
-% These dates will be filled out by the publisher
-% \date{Accepted XXX. Received YYY; in original form ZZZ}
-
-% Enter the current year, for the copyright statements etc.
-\pubyear{2016}
-
-% Don't change these lines
-\begin{document}
-\label{firstpage}
-\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\maketitle
-
-\begin{abstract}
-We report modelling follow-up of recently-discovered
-gravitational-lens candidates in the CFHT Legacy Survey.  Lens
-modelling was done by a small group of specially-interested volunteers
-from the Space~Warps citizen-science community who originally found
-the candidate lenses.  Models are categorised according to seven
-qualitative and quantitive points.  Also included are some
-improvements to the modelling software used (SpaghettiLens),
-and discussion of strategies for scaling to future surveys
-with more and frequent discoveries.
-
-The candidates successfully modelled are all galaxies, with inferred
-lensing masses ranging from $\sim10^{11}M_\odot$ to $>10^{13}M_\odot$.
-Stellar masses have also been estimated, using photometry from the
-CFHTLS pipeline and stellar-population models.  A trend well-known
-in nearby galaxies, that star-formation efficiency is maximal for
-total masses of $\approx10^{12}M_\odot$ and reduces for both lower and
-higher masses, is discernable also in these much more distant
-galaxies.
-\end{abstract}
-
-\begin{keywords}
-gravitational lensing: strong -- keyword2
-\end{keywords}
-
-\section{Introduction}
-
-Light deflection at the rim of the Sun is famously $1.75''$.  The
-deflection angle can also be expressed in terms of the escape velocity
-$2v_{\rm esc}^2/c^2$, with $v_{\rm esc}$ at the solar surface being
-$\simeq620\rm\,km/s$.  The Galactic escape velocity at the Sun's
-location is similar: $\approx500\rm\,km/s$, typical of massive
-galaxies.  Thus, the outer regions of massive galaxies have lensing
-deflections comparable to that at the rim of the Sun.  Yet these
-quantitatively similar deflections have qualitatively different
-consequences.  Light deflection by the Sun must be accounted for in
-modern astrometry \citep[see e.g.,][]{2015CQGra..32p5008C} but is not
-itself a physics probe in the way it was a century ago.  With distant
-galaxies, however, light bending by $\sim1''$ introduces two new
-phenomena.  First, for galaxies distant enough that their apparent
-size is comparable to the bending angle, light deflection can cause
-multiple images of background sources, or strong lensing.  Second, the
-gravitational field is dominated by dark matter, hence strong lensing
-becomes a probe of dark matter in galaxies.
-
-With no unambiguous dark-matter particle detections so far, dark
-matter has studied only through its indirect consequences on galactic
-and larger scales.  In most work, dark matter is taken to be a
-collisionless non-relativistic fluid (cold dark matter or CDM); in
-recent years, the simulation by \cite{2005Natur.435..629S} has been
-particularly influential in studying the formation of CDM structures.
-Other scenarios have also been considered, such as a cold condensing
-boson fluid \citep{2016ApJ...818...89S}.  There is a general
-consensus, however, that the origins of galaxy lie in the
-gravitational collapse, fragmentation, and mergers of dark-matter
-clumps, into which fell gas, cooling through radiative processes to
-form dense clouds and eventually stars.  There is, however, much
-debate about the details, of which \cite{2012RAA....12..917S} provide
-a nice summary.
-
-Strong-lensing galaxies are a useful source of information on the
-mutual dynamics and dark matter and gas in galaxies.  The topic has
-been explored in several studies
-\citep{2009ApJ...703L..51K,2011ApJ...740...97L,2012MNRAS.424..104L,
-  2016MNRAS.459.3677L,2016MNRAS.456..870B} but it is desirable to
-enlarge the samples from tens of lensing galaxies to thousands.  Doing
-so requires finding more lenses, of course, but also modelling their
-masses.
-
-Recent searches through the CFHTLS \citep{2012SPIE.8448E..0MC} using
-arc-finders
-\citep{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G} by
-machine learning \citep{2016arXiv160504309P} and by visual inspection
-by a citizen-science volunteers
-\citep[Space~Warps][]{2016MNRAS.455.1191M} have between them
-discovered an average of four lenses per square degree.  So one can be
-optimistic about finding many thousands of lenses in the next
-generation of wide-field surveys.  The expected flood of new lens
-discoveries will need a similarly huge modelling effort to
-reconstruct their mass distributions.  To prepare for the challenge of
-massive-sample lens modelling, \cite{2015MNRAS.447.2170K} developed a
-new modelling strategy, implemented as the SpaghettiLens system.  The
-idea is to collaborate with experienced members of the citizen-science
-community, who have already participated in lens discovery through
-Space~Warps, as well as several other projects involving astronomical
-data.  In this paper, we present SpaghettiLens models of
-lens-candidates discovered through Space~Warps.
-
-Section~\ref{sec:spl} summarises the SpaghettiLens system and
-discusses its ongoing development. A SpaghettiLens model consists of a
-statistical ensemble of free-form maps of the sky-projected mass
-distribution responsible for lensing.  Each lens candidates in
-practice gets modelled several times in a collaborative refinement
-process\footnote{See ``Collaborative gravitational lens
-  modelling\dots'' in {\tt http://letters.zooniverse.org} especially
-  the model tree.}  In this paper we report the most recent model for
-each lens, as representing a consensus among modellers, as to the best
-that could be achieved with the available data and software.
-Photometric lens redshifts are used; source redshifts are set to
-$z=2$ unless an unambiguous photometric redshift is available.
-The models can, however, be trivially rescaled to use better
-redshift values, as and when they become available.
-\cite{2015MNRAS.447.2170K} tested the system on simulated lenses and
-identified some areas for improvement.  The first two of those are
-taken up in Section~\ref{sec:spl}, along with a further idea. In
-\S~\ref{subsec:sourcefit} we introduce fitting of the brightness
-profiles of the source.  This feature has not yet been included in
-SpaghettiLens, but has been carried out in post-processing for a few
-especially interesting candidates.  In \S~\ref{subsec:hires} we show
-that making mass maps fine-grained in the central region relieves a
-tendency in the earlier work for mass to be too shallow. Then in
-\S~\ref{subsec:parameter} we consider the possibility of fitting a
-parametric lens model to the model ensemble; so far we have only been
-successful at extracting an Einstein radius.
-
-Section~\ref{sec:stellar-mass} explains how we compare the lensing
-mass with the mass in stars in the lensing galaxy.  We estimate the
-stellar mass by comparing galaxy magnitudes from the CFHTLS pipeline
-with the well-known stellar-population models of
-\cite{2003MNRAS.344.1000B}.  We then extrapolate the stellar masses to
-a halo mass using the abundance-matching prescription of
-\cite{2010ApJ...710..903M}.  Naturally, the lensing mass must be more
-than the stellar mass but no more than the total halo mass.  We then
-introduce what we call a halo index $\haloindex$ which gives an idea
-of how the lensing mass compares with these two bounds.
-
-Section~\ref{sec:examples} discusses ten of the systems, including six
-systems we found to be particularly interesting.  The online
-supplement gives results for all the modelled systems.
-
-In Section~\ref{sec:summary} and Table~\ref{tab:models} we display a
-concise characterisation of each modelled system, according to the
-image morphology and how clear or indistinct it is, whether the mass
-map and synthetic lensed image appear to be plausible, and how the
-model mass compares with the estimated stellar and full-halo masses.
-
-\section{Lens Modelling}\label{sec:spl}
-
-SpaghettiLens is an example of a medium-sized collaboration spawned by
-a large citizen-science project (in this case Space~Warps).  While
-collaboration with volunteers is essential to both, the form of
-collaboration is very different.  In Space~Warps, volunteers in a
-crowd of $\gtrsim10^4$ make independent contributions.  Each person is
-presented with a random selection of survey-patches and invited to (in
-effect) vote on each.  The system estimates each volunteer's skill
-level according to test-patches interspersed with the real data, and
-weights their votes accordingly \citep{2016MNRAS.455.1171M}.  There is
-an active forum for volunteers, but since everyone is seeing different
-data samples with minimal overlap, the forum has little if any
-influence on votes.  With SpaghettiLens, on the other hand, there is a
-small group of volunteers and their contributions are interdependent.
-
-A modeller's main input to SpaghettiLens is a sketch of arrival-time
-contours on a lensed system.  It gives the locations (or best-guess
-locations) of images of point-like sources, along with their ordering
-in arrival time, and their parities (minumum, saddle-point or
-maximum).  Such a sketch, which we call a spaghetti diagram, tends to
-resemble the form of lensed arcs, but it also in effect 
-encodes a proposal for its mass distribution.  A spaghetti diagram is
-read by a server-side numerical engine \citep[GLASS, developed
-  by][]{2014MNRAS.445.2181C} which then returns a statistical ensemble
-of mass maps.  The mass maps are made up of mass tiles and are
-free-form, except that they are required to be concentrated around the
-identified lens centre.  They are also required to reproduce the given
-image locations, parities and time ordering exactly.  Graphical
-representations of the mass map and arrival-time surface are returned
-to the user for review.  The user can post these results on a forum,
-or discard them and try again.  Volunteers can start the modelling
-process afresh, or they can take an existing model from the forum and
-modify its input spaghetti diagram or its accompanying options, and
-thus obtain a revised model.
-
-\subsection{Improved synthetic images}\label{subsec:sourcefit}
-
-The mass maps produced by current implementation of SpaghettiLens are
-based on images of point-like features.  No information about extended
-images is used, except in so far as they help the user identify images
-of point-like features.  The synthetic images offered to users are
-rudimentary, based on sources with conical light profiles.
-
-We have now developed a prototype of better way to generate synthetic
-images.  Figure~\figref{synthimg} illustrates.  First, areas
-containing lensed images are selected (green frames in the figure).
-The selected areas must contain no light from the lensing galaxy or
-from extraneous objects.  Pixels within the selected areas are mapped
-to a grid on the source plane, using bending angles given by the mass
-model.  The mapping from lens-plane pixels to source-plane grid cells
-is many-to-one, because of image multiplicity and magnification.  The
-brightness of each source-plane pixel is set to the mean of all the
-lens-plane pixels mapping to it.  Finally, the mapping is run back to
-the lens plane.  The result is a synthetic image.  In effect, one is
-reconstructing a source-plane brightness map by least-squares.
-
-The procedure is not yet implemented in SpaghettiLens but can be
-applied in post-processing.  The new synthetic images could be used to
-improve the mass reconstruction, by weighting the ensemble of maps
-according to how good the synthetic images are, but we have not
-attempted to do so as yet.
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{img/new_synth_img_detailed}
-  \caption{Synthetic lensed image with source-profile fitting in SW05
-    (J143454.4+522850). Top-left: original image, with areas
-    containing lensed images enclosed within green frames.  Top-right:
-    synthetic image (coloured arcs) with lensing galaxy and unrelated
-    objects in greyscale.  Bottom from left to right: reconstructed
-    source in colour, intensity (greyscale), count of lens plane
-    pixels per source plane pixel, residual of original image to
-    synthetic image.}
-  \label{fig:synthimg}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_11_hires_comparison}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_13_hires_comparison}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_33_hires_comparison}
-  \caption{Model improvement resulting from using smaller mass tiles
-    in the inner region of the mass model.  Shown here are the average
-    enclosed $\kappa$ within a given projected radius, for three
-    different reconstructions of a simulated lens (sim) from
-    Space~Warps.  In each panel, the dashed blue curve is the correct
-    answer.  The orange band represents the statistical ensemble from
-    SpaghettiLens, the orange line being the ensemble mean.  Locations of
-    images (maximum, saddle point, minimum) are marked with vertical
-    arrows.  Crossing the horizontal $\kappa=1$ line is the effective
-    Einstein radius \ER, and is so labelled. The upper panel is from
-    K\"ung et al., (2015) (see Figure~3 of that paper).  The middle
-    panel is the result when the innermost mass tile is replaced by 9
-    smaller tiles.  The lower panel results from replacing each of the
-    innermost 5 by 5 tiles each with 9 smaller tiles.}
-  \label{fig:subsampling}
-\end{figure}
-
-\subsection{Sub-sampling of central region}\label{subsec:hires}
-
-The models of simulated lenses in \cite{2015MNRAS.447.2170K} showed a
-tendency to be too shallow.  Allowing smaller mass tiles in the
-central region, thus allowing the pass profile to rise more steeply
-near the centre, was suggested as a possible cure.
-
-Figure~\figref{subsampling} shows an experiment with smaller mass
-tiles in the inner region.  Replacing the very central mass tile with
-9 smaller tiles allows for steeper central profiles.  Doing the same
-for the 25 innermost mass tiles solves the problem completely, but
-increases the number of mass tiles by 40\% and significantly increases
-the computational time.
-% 689 / 489 = 1.40899; in practice, runtime is more like x4 - x5!
-% runtimes from logfiles: 87/22, 86/21, 85/16
-The main modelling work in this paper was, however, done before the
-experiments with smaller mass tiles was complete.  Some of the models
-presented in this paper apply the intermediate option (corresponding
-to the middle panel in Figure~\figref{subsampling}) while others use
-the old system.  The results in this paper, however, mainly concern
-the enclosed mass in the outer regions, so shallowness in the central
-region should be inconsequential.
-
-\subsection{Parameterisation of pixel models} \label{subsec:parameter}
-In order to fit the set of pixelated models to a single parameterised model, a program was written that took a parameterised function and subtracted from it the mean and the principle components of the data, which were calculated using classical Principle Component Analysis.
-This created the residuals function.
-The number of components defined as principle was varied to test how this affected the output, and it was found that using 5 principle components tended to give a reasonable approximation.
-A masking function was added which selected only the data points that fell inside the image of the lens, and the principal components were clipped in order to keep the values inside the region of the ensemble of models.
-Any value higher than the clip was set to be the clip value.
-This was chosen to be 2.5 as, assuming that the data follows a Gaussian error distribution, almost all the values for the variance should lie between 2 and 3 standard deviations from the mean.
-Minimising the residuals function produces the set of parameters that fit the parameterised function to the original pixelated ensemble most closely.
-A least squares fit was used to perform this minimisation.
-The parameterised model function was obtained from the gravitational potential of an isothermal ellipsoid mass distribution \cite{2001astro.ph..2341K}.
-This model is frequently used to describe gravitational lenses as it tends to fit well with observations.
-The isothermal ellipsoid model outputs three useful parameters: the radius of the Einstein ring, the ellipticity of the model and the angle of the ellipticity from the vertical, giving the orientation of the galaxy.
-By applying this model to simulated lenses for which the values of these parameters were already known, it was possible to gain an estimate of the projected accuracy of the results, before applying the model to the candidate lensing galaxies.
-
-\begin{figure}
+\begin{figure*}
+\includezehn{img/kappa_encl/}{_kappa_encl}
 \caption{}
-  \label{fig:parameter}
-\end{figure}
-
-\section{Stellar mass}\label{sec:stellar-mass}
-
-Based on \cite{2003MNRAS.344.1000B} models.\todo{Description of
-  stellar-population models.}
-
-Following \cite{2010ApJ...710..903M}
-\begin{equation}
-\begin{aligned}
-\frac{\Mstel}{\Mhalo} &= \frac{2C_0}{(\Mhalo/M_1)^{-\beta} +
-                                     (\Mhalo/M_1)^\gamma} \\
-C_0 &= 0.02820, \quad M_1 = 10^{11.884} M_\odot \\
-\beta &= 1.057, \quad \gamma = 0.556.
-\end{aligned}
-\end{equation}
-
-\begin{equation}
-\haloindex = \frac{\ln(M/\Mstel)}{\ln(\Mhalo/\Mstel)}
-\end{equation}
-which we may call the halo-matching index.
-\begin{itemize}
-\item $\haloindex < 0$ is unphysical because $M<\Mstel$.
-\item $\haloindex = 0$ is when the stellar mass exactly accounts for the
-  lensing mass.
-\item $0 < \haloindex < 1$ is the typical situation, where the lens
-  includes stars and dark matter, but not the full halo.
-\item $\haloindex = 1$ means that the lens consists of the entire halo.
-\item $\haloindex > 1$ is in tension with abundance-matching, because the
-  lensing mass exceeds the expected halo mass.
-\end{itemize}
-
-\section{Example systems}\label{sec:examples}
-
-In this section we show modelling results for ten of the lens
-candidates.  The first five (see Figures~\figref{SW05}--\figref{SW29})
-are the most convincingly modelled systems.  The next three cases
-(Figures~\figref{SW42}--\figref{SW19}) are less good but still very
-plausible models, and are representative of the majority of the
-sample.  The last two are examples where the models were unconvincing
-(Figures~\figref{SW36}) or completely failed (\figref{SW57}).
-
-\begin{figure}
-  \inclfign{SW05}{ASW0007k4r_N7LTELSYTM}
-  \caption{Model results for SW05 (J143454.4+522850).  See text in
-    Section~\ref{sec:examples} for details.}
-  \label{fig:SW05}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW28}{ASW0007xrs_JHC3J2HYV7}
-  \caption{Model results for SW28 (J143055.9+572431).}
-  \label{fig:SW28}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW02}{ASW000619d_011489}
-  \caption{Model results for SW02 (J140522.2+574333).}
-  \label{fig:SW02}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW09}{ASW0002asp_5EKMWWVJHL}
-  \caption{Model results for SW09 (J020832.1-043315).}
-  \label{fig:SW09}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW29}{ASW0008qsm_TOFS7JNGEK}
-  \caption{Model results for SW29 (J143838.1+572647).}
-  \label{fig:SW29}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW42}{ASW00096rm_4Q3YCEWGLN}
-  \caption{Modelling results for SW42 (J221716.5+015826).}
-  \label{fig:SW42}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
-  \caption{Model results for SW58 (J143651.6+530705).}
-  \label{fig:SW58}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW19}{ASW0001ld7_OS3CYAKLRT}
-  \caption{Model results for SW19 (J020642.0-095157).}
-  \label{fig:SW19}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW36}{ASW000096t_7IPP7LWVOF}
-  \caption{Model results for SW36 (J090248.4-010232).}
-  \label{fig:SW36}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
-  \caption{Model results for SW57 (J143631.5+571131).}
-  \label{fig:SW57}
-\end{figure}
-
-Let us first consider Figure~\figref{SW05}, which shows model results
-from SW05 (J143454.4+522850).
-
-\begin{enumerate}
-\item In the upper row we have first a cutout of the Space~Warps
-  image, marked up with a spaghetti diagram.  There are four distinct
-  lensed images, and the spaghetti diagram proposes that they are a
-  minimum nearest to the lensing galaxy, a close minimum-saddle pair,
-  and a minimum further away. In Table~\ref{tab:models} we refer to
-  such configurations as IQ for inclined quad.
-\item Alongside is a synthetic image produced by modelling.  In it,
-  the fitted lensed images are shown in colour, while the lensing
-  galaxy and extraneous objects have been reduced to grayscale.
-  (Figure~\figref{synthimg} in \S~\ref{subsec:sourcefit} shows a
-  synthetic image from another model of the same system.) These two
-  panels are qualitative and display no units, and moreover, the
-  mutual alignment of the two panels is only approximate.
-\item The middle row shows contour maps from the model.  At middle
-  left, we have the arrival-time surface.
-\item At middle right we have the mass distribution in the usual
-  dimensionless form $\kappa$.  Again, these two panels are mainly
-  qualitative: both panels are spatially registered and centred on the
-  density-peak of the lens, but no scales have been included.
-\item The base row supplies spatial and mass scales.  The left panel
-  shows the circularly-averaged $\kappa$ of the model ensemble, with
-  increasing radius (in arcsec).  The four short vertical lines
-  correspond to the minima and saddle points marked in the upper-left
-  panel.  The effective Einstein radius \ER is also shown.  As the radius
-  scale indicates SW05 is comparatively large lens on the
-  sky.
-\item Lower right shows the total mass in the model against the
-  estimated stellar mass, alongside the values for the whole sample.
-  The lower-right shaded region is unphysical according to the
-  stellar-population models, because it gives $M<\Mstel$. The
-  upper-left shaded region is unphysical according to abundance
-  matching, because it gives $M>\Mhalo$.  That is to say, the unshaded
-  region is $0<\haloindex<1$.
-\end{enumerate}
-
-Proceeding to Figure~\figref{SW28}, we have one image close to the
-galaxy and an arc further away, which is interpreted as a blend of
-three images (a saddle point with two minima on either side).  We call
-this a long-axis quad or LQ configuration.  It is an indication of a
-mass distribution elongated along the arc-counterimage direction
-(along EW in this case).
-
-In Figures~\figref{SW02}--\figref{SW29} we see three candidates with
-an arc close the lensing galaxy and one image further away.  The arc
-is interpreted three images (a minimum with two saddle points on
-either side).  We call this a short-axis quad or SQ configuration.  It
-is an indication of a mass distribution elongated perpendicular to the
-arc-counterimage direction.
-
-Figures~\figref{SW02}--\figref{SW29} (SW05, SW28, SW02, SW09 and SW29)
-all correspond to the mass range of massive ellipticals.  SW05 is the
-most massive of all the candidates, with a galaxy-group scale mass.
-
-Figure~\figref{SW42} shows SW42.  The image morphology is similar to
-SW05 in Figure~\figref{SW05}, but the lens is much smaller on the sky,
-and the inferred mass is at the low end of the sample.  (The synthetic
-image shown is cruder than for the five previous figures, but that
-does not influence the mass models.)  If these preliminary findings
-are confirmed by follow-up observations, this could be the most
-dark-matter dominated lens known.\todo{Check photometry of this
-  candidate.}
-
-Figures~\figref{SW58} and \figref{SW19} appear plausible lens
-candidates.  Their morphology is similar to SW28, but the saddle-point
-counterimage is not visible.  We consider these lenses plausible but
-less convincing.
-
-Figures~\figref{SW36} and \figref{SW57} are cases where modelling
-failed.
-
-\section{Summary of models}\label{sec:summary}
-
-Table~\ref{tab:models} shows a summary of the analysis for many candidates.
-Missing rows are due to photometry data not available.
-
-\begin{enumerate}
-\item The image morphology concisely described: D for double, and
-  quads in sub-categorised in four ways
-  \citep[cf.][]{2003AJ....125.2769S} as LQ for long-axis quads (as in
-  Figure~\figref{SW28}), SQ for short-axis quads (as in
-  Figure~\figref{SW02}, \figref{SW09}, \figref{SW29}, \figref{SW42}),
-  IQ for inclined quads (as in Figure~\figref{SW05}) and CQ for very
-  symmetric core quads.
-\item Whether the images are unblended.  Distinct unblended images (as
-  in Figures~\figref{SW05} and \figref{SW42}) are an advantage in
-  modelling, but not essential.
-\item Whether all images are discernable.  The topography of an
-  arrival-time surface, as encoded by a spaghetti diagram, may require
-  more images than are visible.  For example, in Figure~\figref{SW58},
-  the modeller has put in a conjectural saddle point near the lensing
-  galaxy.
-\item Whether the lens is fairly isolated.
-\item Whether the arrival-time surface and synthetic image are
-  plausible.  In Figure~\figref{SW36} the model implies extra images
-  or a long arc, which are not seen.
-\item Whether the mass map is reasonable.
-\item The halo index $\haloindex$.
-\end{enumerate}
-
-\begin{table*}
-  \caption{Categorisation of SW models}
-  \label{tab:models}
-  \include{table}
-\end{table*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% The best way to enter references is to use BibTeX:
-\bibliographystyle{mnras}
-\bibliography{bib/bibli} % if your bibtex file is called example.bib
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \appendix
-
-\clearpage
-
-\section{TODO}
-\listoftodos
-
-% Don't change these lines
-\bsp	% typesetting comment
-\label{lastpage}
-\end{document}
+\end{figure*}

### 2016-10-03 parts/morph.tex
moving text around

--- 2016-07-26 paper2.tex
@@
-\documentclass[fleqn,usenatbib]{mnras}
+\section{Image morphology}
 
-%%% DEBUG SETTINGS - remove at the end %%%%%%%%%%%%%%%
-\usepackage{silence} % silence error warinings
-\WarningFilter{caption}{Unsupported document class} % caption doesn't know mnras..
-\hbadness = 5000
-\vbadness = 10000
-% \usepackage{}
+Figure~\ref{fig:input} shows cutouts of the Space~Warps image, marked
+up with a spaghetti diagram.
 
-% MNRAS is set in Times font. If you don't have this installed (most LaTeX
-% installations will be fine) or prefer the old Computer Modern fonts, comment
-% out the following line
-%\usepackage{newtxtext,newtxmath} % not yet supported on arxiv and uni computer
-%\usepackage{txfonts}
+The lenses are arranged as follows.
+$$
+\begin{matrix}
+\rm SW05 & \rm SW42 & \rm SW28 \\
+\rm SW58 & \rm SW02 & \rm SW19 \\
+\rm SW09 & \rm SW29 & \rm SW57
+\end{matrix}
+$$ 
+$\{${\em Panels will be labelled, and this little table removed.}$\}$
 
-% Depending on your LaTeX fonts installation, you might get better results with one of these:
-%\usepackage{mathptmx}
-%\usepackage{txfonts}
+Figure~\ref{fig:input}
 
-% Use vector fonts, so it zooms properly in on-screen viewing software
-% Don't change these lines unless you know what you are doing
-\usepackage[T1]{fontenc} % make sure font is supported
-% \usepackage{ae,aecompl} %obsolete when using modern fonts
-\usepackage[final]{microtype} % make sure font is supported
-% and a suitable font
-\usepackage{lmodern} % use a modern font with T1 support
-%\usepackage{cm-super} % use a modern font with T1 support
+Let us first consider from SW05 (J143454.4+522850).
+In SW05 there are four distinct lensed images, and the spaghetti
+diagram proposes that they are a minimum nearest to the lensing
+galaxy, a close minimum-saddle pair, and a minimum further away. In
+Table~\ref{tab:models} we refer to such configurations as IQ for
+inclined quad.
 
-%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
-
-% Only include extra packages if you really need them. Common packages are:
-%\usepackage[dvipdfmx]{graphicx}	% Including figure files
-\usepackage{graphicx} % Including figure files
-%\usepackage[skip=0pt]{subcaption}
-\usepackage{amsmath}	% Advanced maths commands
-\usepackage{amssymb}	% Extra maths symbols
-\usepackage{pifont}	% Extra maths symbols
-%\usepackage{bmpsize}  % PS still needs this for correct bounding boxes?
-
-% TODO stuff, comment out for final submit
-\usepackage{todonotes} % as long as we are editing...
-%\usepackage{showframe} % for debug
-%\overfullrule=5pt      % show overfull boxes
-
-% I disabled hyperlink in the cls und included it here because of bugs
-\usepackage{hyperref}   % Hyperlinks
-\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,filecolor=blue,urlcolor=blue}
-
-\edef\smallwidth{0.4\linewidth}
-
-\newcommand{\inclfig}[2]{
-  \centering
-	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img3_ipol}
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
-%        \includegraphics[width=\smallwidth]{spaghetti/#2_img2}
-        \includegraphics[width=\smallwidth]{img/kappa_map/#1_#2_kappa_map}
-	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
-	\includegraphics[width=\smallwidth]{img/mlens_vs_mstel/#1_#2_mstel_vs_mtot}
-}
-
-\newcommand{\inclfign}[2]{
-  \centering
-	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
-	\includegraphics[width=\smallwidth]{img/nsynth/#2_nsynth}
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
-%	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
-        \includegraphics[width=\smallwidth]{img/kappa_map/#1_#2_kappa_map}
-	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
-	\includegraphics[width=\smallwidth]{img/mlens_vs_mstel/#1_#2_mstel_vs_mtot}
-}
-
-\newcommand*{\rot}{\rotatebox{90}}
-\newcommand*{\OK}{\ding{51}}
-\newcommand*{\NO}{\ding{55}}
-
-\newcommand{\lenstitle}[1]{\noindent\textbf{#1} --}
-\newcommand{\params}[3]{(\(\Theta_\text{E}:#1\), $\varepsilon:#2$, $\alpha_\varepsilon:#3$ )}
-
-\newcommand{\asw}[1]{ASW000#1}
-\newcommand{\sw}[1]{SW~#1}
-\newcommand{\model}[1]{SL model~#1}
-
-\newcommand{\figref}[1]{\ref{fig:#1}}
-
-\newcommand{\Mstel}{M_{\rm stel}}
-\newcommand{\Mhalo}{M_{\rm h}}
-\newcommand{\haloindex}{\mathcal{H}}
-\newcommand{\ER}{$\Theta_{\text{E}}$} % einstein radius
-
-\title[Lens models for Space Warps CFHTLS]{Model of lens candidates from
-  Space Warps CFHTLS}
-
-\author[K\"ung et al]{Rafael K\"ung,$^{1}$
-Prasenjit Saha,$^{1}$
-Ignacio Ferreras,$^{2}$
-Elisabeth Baeten,$^{3}$
-\newauthor
-Jonathan Coles,$^{4}$
-Claude Cornen,$^{3}$
-Christine Macmillan,$^{3}$
-Phil Marshall,$^{5}$ 
-\newauthor
-Anupreeta More,$^{6}$
-Lucy Oswald$^{7}$
-Aprajita Verma$^{8}$
-and Julianne K. Wilcox$^{4}$
-%
-\\
-%
-$^{1}$Physik-Institut, University of Zurich, Winterthurerstrasse 190, 8057 Zurich, Switzerland\\
-$^{2}$Mullard Space Science Laboratory, University College London, Holmbury St Mary, Dorking, Surrey RH5 6NT, UK\\
-$^{3}$Zooniverse, c/o Astrophysics Department, University of Oxford, Oxford OX1 3RH, UK \\
-$^{4}$Exascale Research Computing Lab, Campus Teratec, 2 Rue de la Piquetterie, 91680 Bruyeres-le-Chatel, France\\
-$^{5}$Kavli Institute for Particle Astrophysics and Cosmology, Stanford University, 452 Lomita Mall, Stanford, CA 94035, USA\\
-$^{6}$Kavli Institute for the Physics and Mathematics of the Universe, University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa-shi 277-8583, Japan\\
-$^{7}$Murray Edwards College, University of Cambridge, Cambridge CB3 0DF, UK\\
-$^{8}$Sub-department of Astrophysics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
-}
-
-% These dates will be filled out by the publisher
-% \date{Accepted XXX. Received YYY; in original form ZZZ}
-
-% Enter the current year, for the copyright statements etc.
-\pubyear{2016}
-
-% Don't change these lines
-\begin{document}
-\label{firstpage}
-\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\maketitle
-
-\begin{abstract}
-We report modelling follow-up of recently-discovered
-gravitational-lens candidates in the CFHT Legacy Survey.  Lens
-modelling was done by a small group of specially-interested volunteers
-from the Space~Warps citizen-science community who originally found
-the candidate lenses.  Models are categorised according to seven
-qualitative and quantitive points.  Also included are some
-improvements to the modelling software used (SpaghettiLens),
-and discussion of strategies for scaling to future surveys
-with more and frequent discoveries.
-
-The candidates successfully modelled are all galaxies, with inferred
-lensing masses ranging from $\sim10^{11}M_\odot$ to $>10^{13}M_\odot$.
-Stellar masses have also been estimated, using photometry from the
-CFHTLS pipeline and stellar-population models.  A trend well-known
-in nearby galaxies, that star-formation efficiency is maximal for
-total masses of $\approx10^{12}M_\odot$ and reduces for both lower and
-higher masses, is discernable also in these much more distant
-galaxies.
-\end{abstract}
-
-\begin{keywords}
-gravitational lensing: strong -- keyword2
-\end{keywords}
-
-\section{Introduction}
-
-Light deflection at the rim of the Sun is famously $1.75''$.  The
-deflection angle can also be expressed in terms of the escape velocity
-$2v_{\rm esc}^2/c^2$, with $v_{\rm esc}$ at the solar surface being
-$\simeq620\rm\,km/s$.  The Galactic escape velocity at the Sun's
-location is similar: $\approx500\rm\,km/s$, typical of massive
-galaxies.  Thus, the outer regions of massive galaxies have lensing
-deflections comparable to that at the rim of the Sun.  Yet these
-quantitatively similar deflections have qualitatively different
-consequences.  Light deflection by the Sun must be accounted for in
-modern astrometry \citep[see e.g.,][]{2015CQGra..32p5008C} but is not
-itself a physics probe in the way it was a century ago.  With distant
-galaxies, however, light bending by $\sim1''$ introduces two new
-phenomena.  First, for galaxies distant enough that their apparent
-size is comparable to the bending angle, light deflection can cause
-multiple images of background sources, or strong lensing.  Second, the
-gravitational field is dominated by dark matter, hence strong lensing
-becomes a probe of dark matter in galaxies.
-
-With no unambiguous dark-matter particle detections so far, dark
-matter has studied only through its indirect consequences on galactic
-and larger scales.  In most work, dark matter is taken to be a
-collisionless non-relativistic fluid (cold dark matter or CDM); in
-recent years, the simulation by \cite{2005Natur.435..629S} has been
-particularly influential in studying the formation of CDM structures.
-Other scenarios have also been considered, such as a cold condensing
-boson fluid \citep{2016ApJ...818...89S}.  There is a general
-consensus, however, that the origins of galaxy lie in the
-gravitational collapse, fragmentation, and mergers of dark-matter
-clumps, into which fell gas, cooling through radiative processes to
-form dense clouds and eventually stars.  There is, however, much
-debate about the details, of which \cite{2012RAA....12..917S} provide
-a nice summary.
-
-Strong-lensing galaxies are a useful source of information on the
-mutual dynamics and dark matter and gas in galaxies.  The topic has
-been explored in several studies
-\citep{2009ApJ...703L..51K,2011ApJ...740...97L,2012MNRAS.424..104L,
-  2016MNRAS.459.3677L,2016MNRAS.456..870B} but it is desirable to
-enlarge the samples from tens of lensing galaxies to thousands.  Doing
-so requires finding more lenses, of course, but also modelling their
-masses.
-
-Recent searches through the CFHTLS \citep{2012SPIE.8448E..0MC} using
-arc-finders
-\citep{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G} by
-machine learning \citep{2016arXiv160504309P} and by visual inspection
-by a citizen-science volunteers
-\citep[Space~Warps][]{2016MNRAS.455.1191M} have between them
-discovered an average of four lenses per square degree.  So one can be
-optimistic about finding many thousands of lenses in the next
-generation of wide-field surveys.  The expected flood of new lens
-discoveries will need a similarly huge modelling effort to
-reconstruct their mass distributions.  To prepare for the challenge of
-massive-sample lens modelling, \cite{2015MNRAS.447.2170K} developed a
-new modelling strategy, implemented as the SpaghettiLens system.  The
-idea is to collaborate with experienced members of the citizen-science
-community, who have already participated in lens discovery through
-Space~Warps, as well as several other projects involving astronomical
-data.  In this paper, we present SpaghettiLens models of
-lens-candidates discovered through Space~Warps.
-
-Section~\ref{sec:spl} summarises the SpaghettiLens system and
-discusses its ongoing development. A SpaghettiLens model consists of a
-statistical ensemble of free-form maps of the sky-projected mass
-distribution responsible for lensing.  Each lens candidates in
-practice gets modelled several times in a collaborative refinement
-process\footnote{See ``Collaborative gravitational lens
-  modelling\dots'' in {\tt http://letters.zooniverse.org} especially
-  the model tree.}  In this paper we report the most recent model for
-each lens, as representing a consensus among modellers, as to the best
-that could be achieved with the available data and software.
-Photometric lens redshifts are used; source redshifts are set to
-$z=2$ unless an unambiguous photometric redshift is available.
-The models can, however, be trivially rescaled to use better
-redshift values, as and when they become available.
-\cite{2015MNRAS.447.2170K} tested the system on simulated lenses and
-identified some areas for improvement.  The first two of those are
-taken up in Section~\ref{sec:spl}, along with a further idea. In
-\S~\ref{subsec:sourcefit} we introduce fitting of the brightness
-profiles of the source.  This feature has not yet been included in
-SpaghettiLens, but has been carried out in post-processing for a few
-especially interesting candidates.  In \S~\ref{subsec:hires} we show
-that making mass maps fine-grained in the central region relieves a
-tendency in the earlier work for mass to be too shallow. Then in
-\S~\ref{subsec:parameter} we consider the possibility of fitting a
-parametric lens model to the model ensemble; so far we have only been
-successful at extracting an Einstein radius.
-
-Section~\ref{sec:stellar-mass} explains how we compare the lensing
-mass with the mass in stars in the lensing galaxy.  We estimate the
-stellar mass by comparing galaxy magnitudes from the CFHTLS pipeline
-with the well-known stellar-population models of
-\cite{2003MNRAS.344.1000B}.  We then extrapolate the stellar masses to
-a halo mass using the abundance-matching prescription of
-\cite{2010ApJ...710..903M}.  Naturally, the lensing mass must be more
-than the stellar mass but no more than the total halo mass.  We then
-introduce what we call a halo index $\haloindex$ which gives an idea
-of how the lensing mass compares with these two bounds.
-
-Section~\ref{sec:examples} discusses ten of the systems, including six
-systems we found to be particularly interesting.  The online
-supplement gives results for all the modelled systems.
-
-In Section~\ref{sec:summary} and Table~\ref{tab:models} we display a
-concise characterisation of each modelled system, according to the
-image morphology and how clear or indistinct it is, whether the mass
-map and synthetic lensed image appear to be plausible, and how the
-model mass compares with the estimated stellar and full-halo masses.
-
-\section{Lens Modelling}\label{sec:spl}
-
-SpaghettiLens is an example of a medium-sized collaboration spawned by
-a large citizen-science project (in this case Space~Warps).  While
-collaboration with volunteers is essential to both, the form of
-collaboration is very different.  In Space~Warps, volunteers in a
-crowd of $\gtrsim10^4$ make independent contributions.  Each person is
-presented with a random selection of survey-patches and invited to (in
-effect) vote on each.  The system estimates each volunteer's skill
-level according to test-patches interspersed with the real data, and
-weights their votes accordingly \citep{2016MNRAS.455.1171M}.  There is
-an active forum for volunteers, but since everyone is seeing different
-data samples with minimal overlap, the forum has little if any
-influence on votes.  With SpaghettiLens, on the other hand, there is a
-small group of volunteers and their contributions are interdependent.
-
-A modeller's main input to SpaghettiLens is a sketch of arrival-time
-contours on a lensed system.  It gives the locations (or best-guess
-locations) of images of point-like sources, along with their ordering
-in arrival time, and their parities (minumum, saddle-point or
-maximum).  Such a sketch, which we call a spaghetti diagram, tends to
-resemble the form of lensed arcs, but it also in effect 
-encodes a proposal for its mass distribution.  A spaghetti diagram is
-read by a server-side numerical engine \citep[GLASS, developed
-  by][]{2014MNRAS.445.2181C} which then returns a statistical ensemble
-of mass maps.  The mass maps are made up of mass tiles and are
-free-form, except that they are required to be concentrated around the
-identified lens centre.  They are also required to reproduce the given
-image locations, parities and time ordering exactly.  Graphical
-representations of the mass map and arrival-time surface are returned
-to the user for review.  The user can post these results on a forum,
-or discard them and try again.  Volunteers can start the modelling
-process afresh, or they can take an existing model from the forum and
-modify its input spaghetti diagram or its accompanying options, and
-thus obtain a revised model.
-
-\subsection{Improved synthetic images}\label{subsec:sourcefit}
-
-The mass maps produced by current implementation of SpaghettiLens are
-based on images of point-like features.  No information about extended
-images is used, except in so far as they help the user identify images
-of point-like features.  The synthetic images offered to users are
-rudimentary, based on sources with conical light profiles.
-
-We have now developed a prototype of better way to generate synthetic
-images.  Figure~\figref{synthimg} illustrates.  First, areas
-containing lensed images are selected (green frames in the figure).
-The selected areas must contain no light from the lensing galaxy or
-from extraneous objects.  Pixels within the selected areas are mapped
-to a grid on the source plane, using bending angles given by the mass
-model.  The mapping from lens-plane pixels to source-plane grid cells
-is many-to-one, because of image multiplicity and magnification.  The
-brightness of each source-plane pixel is set to the mean of all the
-lens-plane pixels mapping to it.  Finally, the mapping is run back to
-the lens plane.  The result is a synthetic image.  In effect, one is
-reconstructing a source-plane brightness map by least-squares.
-
-The procedure is not yet implemented in SpaghettiLens but can be
-applied in post-processing.  The new synthetic images could be used to
-improve the mass reconstruction, by weighting the ensemble of maps
-according to how good the synthetic images are, but we have not
-attempted to do so as yet.
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{img/new_synth_img_detailed}
-  \caption{Synthetic lensed image with source-profile fitting in SW05
-    (J143454.4+522850). Top-left: original image, with areas
-    containing lensed images enclosed within green frames.  Top-right:
-    synthetic image (coloured arcs) with lensing galaxy and unrelated
-    objects in greyscale.  Bottom from left to right: reconstructed
-    source in colour, intensity (greyscale), count of lens plane
-    pixels per source plane pixel, residual of original image to
-    synthetic image.}
-  \label{fig:synthimg}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_11_hires_comparison}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_13_hires_comparison}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_33_hires_comparison}
-  \caption{Model improvement resulting from using smaller mass tiles
-    in the inner region of the mass model.  Shown here are the average
-    enclosed $\kappa$ within a given projected radius, for three
-    different reconstructions of a simulated lens (sim) from
-    Space~Warps.  In each panel, the dashed blue curve is the correct
-    answer.  The orange band represents the statistical ensemble from
-    SpaghettiLens, the orange line being the ensemble mean.  Locations of
-    images (maximum, saddle point, minimum) are marked with vertical
-    arrows.  Crossing the horizontal $\kappa=1$ line is the effective
-    Einstein radius \ER, and is so labelled. The upper panel is from
-    K\"ung et al., (2015) (see Figure~3 of that paper).  The middle
-    panel is the result when the innermost mass tile is replaced by 9
-    smaller tiles.  The lower panel results from replacing each of the
-    innermost 5 by 5 tiles each with 9 smaller tiles.}
-  \label{fig:subsampling}
-\end{figure}
-
-\subsection{Sub-sampling of central region}\label{subsec:hires}
-
-The models of simulated lenses in \cite{2015MNRAS.447.2170K} showed a
-tendency to be too shallow.  Allowing smaller mass tiles in the
-central region, thus allowing the pass profile to rise more steeply
-near the centre, was suggested as a possible cure.
-
-Figure~\figref{subsampling} shows an experiment with smaller mass
-tiles in the inner region.  Replacing the very central mass tile with
-9 smaller tiles allows for steeper central profiles.  Doing the same
-for the 25 innermost mass tiles solves the problem completely, but
-increases the number of mass tiles by 40\% and significantly increases
-the computational time.
-% 689 / 489 = 1.40899; in practice, runtime is more like x4 - x5!
-% runtimes from logfiles: 87/22, 86/21, 85/16
-The main modelling work in this paper was, however, done before the
-experiments with smaller mass tiles was complete.  Some of the models
-presented in this paper apply the intermediate option (corresponding
-to the middle panel in Figure~\figref{subsampling}) while others use
-the old system.  The results in this paper, however, mainly concern
-the enclosed mass in the outer regions, so shallowness in the central
-region should be inconsequential.
-
-\subsection{Parameterisation of pixel models} \label{subsec:parameter}
-In order to fit the set of pixelated models to a single parameterised model, a program was written that took a parameterised function and subtracted from it the mean and the principle components of the data, which were calculated using classical Principle Component Analysis.
-This created the residuals function.
-The number of components defined as principle was varied to test how this affected the output, and it was found that using 5 principle components tended to give a reasonable approximation.
-A masking function was added which selected only the data points that fell inside the image of the lens, and the principal components were clipped in order to keep the values inside the region of the ensemble of models.
-Any value higher than the clip was set to be the clip value.
-This was chosen to be 2.5 as, assuming that the data follows a Gaussian error distribution, almost all the values for the variance should lie between 2 and 3 standard deviations from the mean.
-Minimising the residuals function produces the set of parameters that fit the parameterised function to the original pixelated ensemble most closely.
-A least squares fit was used to perform this minimisation.
-The parameterised model function was obtained from the gravitational potential of an isothermal ellipsoid mass distribution \cite{2001astro.ph..2341K}.
-This model is frequently used to describe gravitational lenses as it tends to fit well with observations.
-The isothermal ellipsoid model outputs three useful parameters: the radius of the Einstein ring, the ellipticity of the model and the angle of the ellipticity from the vertical, giving the orientation of the galaxy.
-By applying this model to simulated lenses for which the values of these parameters were already known, it was possible to gain an estimate of the projected accuracy of the results, before applying the model to the candidate lensing galaxies.
-
-\begin{figure}
-  \caption{}
-  \label{fig:parameter}
-\end{figure}
-
-\section{Stellar mass}\label{sec:stellar-mass}
-
-Based on \cite{2003MNRAS.344.1000B} models.\todo{Description of
-  stellar-population models.}
-
-Following \cite{2010ApJ...710..903M}
-\begin{equation}
-\begin{aligned}
-\frac{\Mstel}{\Mhalo} &= \frac{2C_0}{(\Mhalo/M_1)^{-\beta} +
-                                     (\Mhalo/M_1)^\gamma} \\
-C_0 &= 0.02820, \quad M_1 = 10^{11.884} M_\odot \\
-\beta &= 1.057, \quad \gamma = 0.556.
-\end{aligned}
-\end{equation}
-
-\begin{equation}
-\haloindex = \frac{\ln(M/\Mstel)}{\ln(\Mhalo/\Mstel)}
-\end{equation}
-which we may call the halo-matching index.
-\begin{itemize}
-\item $\haloindex < 0$ is unphysical because $M<\Mstel$.
-\item $\haloindex = 0$ is when the stellar mass exactly accounts for the
-  lensing mass.
-\item $0 < \haloindex < 1$ is the typical situation, where the lens
-  includes stars and dark matter, but not the full halo.
-\item $\haloindex = 1$ means that the lens consists of the entire halo.
-\item $\haloindex > 1$ is in tension with abundance-matching, because the
-  lensing mass exceeds the expected halo mass.
-\end{itemize}
-
-\section{Example systems}\label{sec:examples}
-
-In this section we show modelling results for ten of the lens
-candidates.  The first five (see Figures~\figref{SW05}--\figref{SW29})
-are the most convincingly modelled systems.  The next three cases
-(Figures~\figref{SW42}--\figref{SW19}) are less good but still very
-plausible models, and are representative of the majority of the
-sample.  The last two are examples where the models were unconvincing
-(Figures~\figref{SW36}) or completely failed (\figref{SW57}).
-
-\begin{figure}
-  \inclfign{SW05}{ASW0007k4r_N7LTELSYTM}
-  \caption{Model results for SW05 (J143454.4+522850).  See text in
-    Section~\ref{sec:examples} for details.}
-  \label{fig:SW05}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW28}{ASW0007xrs_JHC3J2HYV7}
-  \caption{Model results for SW28 (J143055.9+572431).}
-  \label{fig:SW28}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW02}{ASW000619d_011489}
-  \caption{Model results for SW02 (J140522.2+574333).}
-  \label{fig:SW02}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW09}{ASW0002asp_5EKMWWVJHL}
-  \caption{Model results for SW09 (J020832.1-043315).}
-  \label{fig:SW09}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW29}{ASW0008qsm_TOFS7JNGEK}
-  \caption{Model results for SW29 (J143838.1+572647).}
-  \label{fig:SW29}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW42}{ASW00096rm_4Q3YCEWGLN}
-  \caption{Modelling results for SW42 (J221716.5+015826).}
-  \label{fig:SW42}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
-  \caption{Model results for SW58 (J143651.6+530705).}
-  \label{fig:SW58}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW19}{ASW0001ld7_OS3CYAKLRT}
-  \caption{Model results for SW19 (J020642.0-095157).}
-  \label{fig:SW19}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW36}{ASW000096t_7IPP7LWVOF}
-  \caption{Model results for SW36 (J090248.4-010232).}
-  \label{fig:SW36}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
-  \caption{Model results for SW57 (J143631.5+571131).}
-  \label{fig:SW57}
-\end{figure}
-
-Let us first consider Figure~\figref{SW05}, which shows model results
-from SW05 (J143454.4+522850).
-
-\begin{enumerate}
-\item In the upper row we have first a cutout of the Space~Warps
-  image, marked up with a spaghetti diagram.  There are four distinct
-  lensed images, and the spaghetti diagram proposes that they are a
-  minimum nearest to the lensing galaxy, a close minimum-saddle pair,
-  and a minimum further away. In Table~\ref{tab:models} we refer to
-  such configurations as IQ for inclined quad.
-\item Alongside is a synthetic image produced by modelling.  In it,
-  the fitted lensed images are shown in colour, while the lensing
-  galaxy and extraneous objects have been reduced to grayscale.
-  (Figure~\figref{synthimg} in \S~\ref{subsec:sourcefit} shows a
-  synthetic image from another model of the same system.) These two
-  panels are qualitative and display no units, and moreover, the
-  mutual alignment of the two panels is only approximate.
-\item The middle row shows contour maps from the model.  At middle
-  left, we have the arrival-time surface.
-\item At middle right we have the mass distribution in the usual
-  dimensionless form $\kappa$.  Again, these two panels are mainly
-  qualitative: both panels are spatially registered and centred on the
-  density-peak of the lens, but no scales have been included.
-\item The base row supplies spatial and mass scales.  The left panel
-  shows the circularly-averaged $\kappa$ of the model ensemble, with
-  increasing radius (in arcsec).  The four short vertical lines
-  correspond to the minima and saddle points marked in the upper-left
-  panel.  The effective Einstein radius \ER is also shown.  As the radius
-  scale indicates SW05 is comparatively large lens on the
-  sky.
-\item Lower right shows the total mass in the model against the
-  estimated stellar mass, alongside the values for the whole sample.
-  The lower-right shaded region is unphysical according to the
-  stellar-population models, because it gives $M<\Mstel$. The
-  upper-left shaded region is unphysical according to abundance
-  matching, because it gives $M>\Mhalo$.  That is to say, the unshaded
-  region is $0<\haloindex<1$.
-\end{enumerate}
+Figure~\figref{SW42} shows SW42.  The image morphology is similar to
+SW05 in Figure~\figref{SW05}, but the lens is much smaller on the sky.
 
@@
 
-Figures~\figref{SW02}--\figref{SW29} (SW05, SW28, SW02, SW09 and SW29)
-all correspond to the mass range of massive ellipticals.  SW05 is the
-most massive of all the candidates, with a galaxy-group scale mass.
-
-Figure~\figref{SW42} shows SW42.  The image morphology is similar to
-SW05 in Figure~\figref{SW05}, but the lens is much smaller on the sky,
-and the inferred mass is at the low end of the sample.  (The synthetic
-image shown is cruder than for the five previous figures, but that
-does not influence the mass models.)  If these preliminary findings
-are confirmed by follow-up observations, this could be the most
-dark-matter dominated lens known.\todo{Check photometry of this
-  candidate.}
-
-Figures~\figref{SW58} and \figref{SW19} appear plausible lens
-candidates.  Their morphology is similar to SW28, but the saddle-point
-counterimage is not visible.  We consider these lenses plausible but
-less convincing.
-
-Figures~\figref{SW36} and \figref{SW57} are cases where modelling
-failed.
-
-\section{Summary of models}\label{sec:summary}
-
-Table~\ref{tab:models} shows a summary of the analysis for many candidates.
-Missing rows are due to photometry data not available.
-
-\begin{enumerate}
-\item The image morphology concisely described: D for double, and
-  quads in sub-categorised in four ways
-  \citep[cf.][]{2003AJ....125.2769S} as LQ for long-axis quads (as in
-  Figure~\figref{SW28}), SQ for short-axis quads (as in
-  Figure~\figref{SW02}, \figref{SW09}, \figref{SW29}, \figref{SW42}),
-  IQ for inclined quads (as in Figure~\figref{SW05}) and CQ for very
-  symmetric core quads.
-\item Whether the images are unblended.  Distinct unblended images (as
-  in Figures~\figref{SW05} and \figref{SW42}) are an advantage in
-  modelling, but not essential.
-\item Whether all images are discernable.  The topography of an
-  arrival-time surface, as encoded by a spaghetti diagram, may require
-  more images than are visible.  For example, in Figure~\figref{SW58},
-  the modeller has put in a conjectural saddle point near the lensing
-  galaxy.
-\item Whether the lens is fairly isolated.
-\item Whether the arrival-time surface and synthetic image are
-  plausible.  In Figure~\figref{SW36} the model implies extra images
-  or a long arc, which are not seen.
-\item Whether the mass map is reasonable.
-\item The halo index $\haloindex$.
-\end{enumerate}
-
-\begin{table*}
-  \caption{Categorisation of SW models}
-  \label{tab:models}
-  \include{table}
-\end{table*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% The best way to enter references is to use BibTeX:
-\bibliographystyle{mnras}
-\bibliography{bib/bibli} % if your bibtex file is called example.bib
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \appendix
-
-\clearpage
-
-\section{TODO}
-\listoftodos
-
-% Don't change these lines
-\bsp	% typesetting comment
-\label{lastpage}
-\end{document}
+\begin{figure*}
+\includeten{spaghetti/}{_input}
+\label{fig:input}
+\caption{Marked-up images.}
+\end{figure*}

### 2016-10-03 parts/spl.tex
moving text around

--- 2016-07-26 paper2.tex
@@
-\documentclass[fleqn,usenatbib]{mnras}
-
-%%% DEBUG SETTINGS - remove at the end %%%%%%%%%%%%%%%
-\usepackage{silence} % silence error warinings
-\WarningFilter{caption}{Unsupported document class} % caption doesn't know mnras..
-\hbadness = 5000
-\vbadness = 10000
-% \usepackage{}
-
-% MNRAS is set in Times font. If you don't have this installed (most LaTeX
-% installations will be fine) or prefer the old Computer Modern fonts, comment
-% out the following line
-%\usepackage{newtxtext,newtxmath} % not yet supported on arxiv and uni computer
-%\usepackage{txfonts}
-
-% Depending on your LaTeX fonts installation, you might get better results with one of these:
-%\usepackage{mathptmx}
-%\usepackage{txfonts}
-
-% Use vector fonts, so it zooms properly in on-screen viewing software
-% Don't change these lines unless you know what you are doing
-\usepackage[T1]{fontenc} % make sure font is supported
-% \usepackage{ae,aecompl} %obsolete when using modern fonts
-\usepackage[final]{microtype} % make sure font is supported
-% and a suitable font
-\usepackage{lmodern} % use a modern font with T1 support
-%\usepackage{cm-super} % use a modern font with T1 support
-
-%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
-
-% Only include extra packages if you really need them. Common packages are:
-%\usepackage[dvipdfmx]{graphicx}	% Including figure files
-\usepackage{graphicx} % Including figure files
-%\usepackage[skip=0pt]{subcaption}
-\usepackage{amsmath}	% Advanced maths commands
-\usepackage{amssymb}	% Extra maths symbols
-\usepackage{pifont}	% Extra maths symbols
-%\usepackage{bmpsize}  % PS still needs this for correct bounding boxes?
-
-% TODO stuff, comment out for final submit
-\usepackage{todonotes} % as long as we are editing...
-%\usepackage{showframe} % for debug
-%\overfullrule=5pt      % show overfull boxes
-
-% I disabled hyperlink in the cls und included it here because of bugs
-\usepackage{hyperref}   % Hyperlinks
-\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,filecolor=blue,urlcolor=blue}
-
-\edef\smallwidth{0.4\linewidth}
-
-\newcommand{\inclfig}[2]{
-  \centering
-	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img3_ipol}
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
-%        \includegraphics[width=\smallwidth]{spaghetti/#2_img2}
-        \includegraphics[width=\smallwidth]{img/kappa_map/#1_#2_kappa_map}
-	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
-	\includegraphics[width=\smallwidth]{img/mlens_vs_mstel/#1_#2_mstel_vs_mtot}
-}
-
-\newcommand{\inclfign}[2]{
-  \centering
-	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
-	\includegraphics[width=\smallwidth]{img/nsynth/#2_nsynth}
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
-%	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
-        \includegraphics[width=\smallwidth]{img/kappa_map/#1_#2_kappa_map}
-	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
-	\includegraphics[width=\smallwidth]{img/mlens_vs_mstel/#1_#2_mstel_vs_mtot}
-}
-
-\newcommand*{\rot}{\rotatebox{90}}
-\newcommand*{\OK}{\ding{51}}
-\newcommand*{\NO}{\ding{55}}
-
-\newcommand{\lenstitle}[1]{\noindent\textbf{#1} --}
-\newcommand{\params}[3]{(\(\Theta_\text{E}:#1\), $\varepsilon:#2$, $\alpha_\varepsilon:#3$ )}
-
-\newcommand{\asw}[1]{ASW000#1}
-\newcommand{\sw}[1]{SW~#1}
-\newcommand{\model}[1]{SL model~#1}
-
-\newcommand{\figref}[1]{\ref{fig:#1}}
-
-\newcommand{\Mstel}{M_{\rm stel}}
-\newcommand{\Mhalo}{M_{\rm h}}
-\newcommand{\haloindex}{\mathcal{H}}
-\newcommand{\ER}{$\Theta_{\text{E}}$} % einstein radius
-
-\title[Lens models for Space Warps CFHTLS]{Model of lens candidates from
-  Space Warps CFHTLS}
-
-\author[K\"ung et al]{Rafael K\"ung,$^{1}$
-Prasenjit Saha,$^{1}$
-Ignacio Ferreras,$^{2}$
-Elisabeth Baeten,$^{3}$
-\newauthor
-Jonathan Coles,$^{4}$
-Claude Cornen,$^{3}$
-Christine Macmillan,$^{3}$
-Phil Marshall,$^{5}$ 
-\newauthor
-Anupreeta More,$^{6}$
-Lucy Oswald$^{7}$
-Aprajita Verma$^{8}$
-and Julianne K. Wilcox$^{4}$
-%
-\\
-%
-$^{1}$Physik-Institut, University of Zurich, Winterthurerstrasse 190, 8057 Zurich, Switzerland\\
-$^{2}$Mullard Space Science Laboratory, University College London, Holmbury St Mary, Dorking, Surrey RH5 6NT, UK\\
-$^{3}$Zooniverse, c/o Astrophysics Department, University of Oxford, Oxford OX1 3RH, UK \\
-$^{4}$Exascale Research Computing Lab, Campus Teratec, 2 Rue de la Piquetterie, 91680 Bruyeres-le-Chatel, France\\
-$^{5}$Kavli Institute for Particle Astrophysics and Cosmology, Stanford University, 452 Lomita Mall, Stanford, CA 94035, USA\\
-$^{6}$Kavli Institute for the Physics and Mathematics of the Universe, University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa-shi 277-8583, Japan\\
-$^{7}$Murray Edwards College, University of Cambridge, Cambridge CB3 0DF, UK\\
-$^{8}$Sub-department of Astrophysics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
-}
-
-% These dates will be filled out by the publisher
-% \date{Accepted XXX. Received YYY; in original form ZZZ}
-
-% Enter the current year, for the copyright statements etc.
-\pubyear{2016}
-
-% Don't change these lines
-\begin{document}
-\label{firstpage}
-\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\maketitle
-
-\begin{abstract}
-We report modelling follow-up of recently-discovered
-gravitational-lens candidates in the CFHT Legacy Survey.  Lens
-modelling was done by a small group of specially-interested volunteers
-from the Space~Warps citizen-science community who originally found
-the candidate lenses.  Models are categorised according to seven
-qualitative and quantitive points.  Also included are some
-improvements to the modelling software used (SpaghettiLens),
-and discussion of strategies for scaling to future surveys
-with more and frequent discoveries.
-
-The candidates successfully modelled are all galaxies, with inferred
-lensing masses ranging from $\sim10^{11}M_\odot$ to $>10^{13}M_\odot$.
-Stellar masses have also been estimated, using photometry from the
-CFHTLS pipeline and stellar-population models.  A trend well-known
-in nearby galaxies, that star-formation efficiency is maximal for
-total masses of $\approx10^{12}M_\odot$ and reduces for both lower and
-higher masses, is discernable also in these much more distant
-galaxies.
-\end{abstract}
-
-\begin{keywords}
-gravitational lensing: strong -- keyword2
-\end{keywords}
-
-\section{Introduction}
-
-Light deflection at the rim of the Sun is famously $1.75''$.  The
-deflection angle can also be expressed in terms of the escape velocity
-$2v_{\rm esc}^2/c^2$, with $v_{\rm esc}$ at the solar surface being
-$\simeq620\rm\,km/s$.  The Galactic escape velocity at the Sun's
-location is similar: $\approx500\rm\,km/s$, typical of massive
-galaxies.  Thus, the outer regions of massive galaxies have lensing
-deflections comparable to that at the rim of the Sun.  Yet these
-quantitatively similar deflections have qualitatively different
-consequences.  Light deflection by the Sun must be accounted for in
-modern astrometry \citep[see e.g.,][]{2015CQGra..32p5008C} but is not
-itself a physics probe in the way it was a century ago.  With distant
-galaxies, however, light bending by $\sim1''$ introduces two new
-phenomena.  First, for galaxies distant enough that their apparent
-size is comparable to the bending angle, light deflection can cause
-multiple images of background sources, or strong lensing.  Second, the
-gravitational field is dominated by dark matter, hence strong lensing
-becomes a probe of dark matter in galaxies.
-
-With no unambiguous dark-matter particle detections so far, dark
-matter has studied only through its indirect consequences on galactic
-and larger scales.  In most work, dark matter is taken to be a
-collisionless non-relativistic fluid (cold dark matter or CDM); in
-recent years, the simulation by \cite{2005Natur.435..629S} has been
-particularly influential in studying the formation of CDM structures.
-Other scenarios have also been considered, such as a cold condensing
-boson fluid \citep{2016ApJ...818...89S}.  There is a general
-consensus, however, that the origins of galaxy lie in the
-gravitational collapse, fragmentation, and mergers of dark-matter
-clumps, into which fell gas, cooling through radiative processes to
-form dense clouds and eventually stars.  There is, however, much
-debate about the details, of which \cite{2012RAA....12..917S} provide
-a nice summary.
-
-Strong-lensing galaxies are a useful source of information on the
-mutual dynamics and dark matter and gas in galaxies.  The topic has
-been explored in several studies
-\citep{2009ApJ...703L..51K,2011ApJ...740...97L,2012MNRAS.424..104L,
-  2016MNRAS.459.3677L,2016MNRAS.456..870B} but it is desirable to
-enlarge the samples from tens of lensing galaxies to thousands.  Doing
-so requires finding more lenses, of course, but also modelling their
-masses.
-
-Recent searches through the CFHTLS \citep{2012SPIE.8448E..0MC} using
-arc-finders
-\citep{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G} by
-machine learning \citep{2016arXiv160504309P} and by visual inspection
-by a citizen-science volunteers
-\citep[Space~Warps][]{2016MNRAS.455.1191M} have between them
-discovered an average of four lenses per square degree.  So one can be
-optimistic about finding many thousands of lenses in the next
-generation of wide-field surveys.  The expected flood of new lens
-discoveries will need a similarly huge modelling effort to
-reconstruct their mass distributions.  To prepare for the challenge of
-massive-sample lens modelling, \cite{2015MNRAS.447.2170K} developed a
-new modelling strategy, implemented as the SpaghettiLens system.  The
-idea is to collaborate with experienced members of the citizen-science
-community, who have already participated in lens discovery through
-Space~Warps, as well as several other projects involving astronomical
-data.  In this paper, we present SpaghettiLens models of
-lens-candidates discovered through Space~Warps.
-
-Section~\ref{sec:spl} summarises the SpaghettiLens system and
-discusses its ongoing development. A SpaghettiLens model consists of a
-statistical ensemble of free-form maps of the sky-projected mass
-distribution responsible for lensing.  Each lens candidates in
-practice gets modelled several times in a collaborative refinement
-process\footnote{See ``Collaborative gravitational lens
-  modelling\dots'' in {\tt http://letters.zooniverse.org} especially
-  the model tree.}  In this paper we report the most recent model for
-each lens, as representing a consensus among modellers, as to the best
-that could be achieved with the available data and software.
-Photometric lens redshifts are used; source redshifts are set to
-$z=2$ unless an unambiguous photometric redshift is available.
-The models can, however, be trivially rescaled to use better
-redshift values, as and when they become available.
-\cite{2015MNRAS.447.2170K} tested the system on simulated lenses and
-identified some areas for improvement.  The first two of those are
-taken up in Section~\ref{sec:spl}, along with a further idea. In
-\S~\ref{subsec:sourcefit} we introduce fitting of the brightness
-profiles of the source.  This feature has not yet been included in
-SpaghettiLens, but has been carried out in post-processing for a few
-especially interesting candidates.  In \S~\ref{subsec:hires} we show
-that making mass maps fine-grained in the central region relieves a
-tendency in the earlier work for mass to be too shallow. Then in
-\S~\ref{subsec:parameter} we consider the possibility of fitting a
-parametric lens model to the model ensemble; so far we have only been
-successful at extracting an Einstein radius.
-
-Section~\ref{sec:stellar-mass} explains how we compare the lensing
-mass with the mass in stars in the lensing galaxy.  We estimate the
-stellar mass by comparing galaxy magnitudes from the CFHTLS pipeline
-with the well-known stellar-population models of
-\cite{2003MNRAS.344.1000B}.  We then extrapolate the stellar masses to
-a halo mass using the abundance-matching prescription of
-\cite{2010ApJ...710..903M}.  Naturally, the lensing mass must be more
-than the stellar mass but no more than the total halo mass.  We then
-introduce what we call a halo index $\haloindex$ which gives an idea
-of how the lensing mass compares with these two bounds.
-
-Section~\ref{sec:examples} discusses ten of the systems, including six
-systems we found to be particularly interesting.  The online
-supplement gives results for all the modelled systems.
-
-In Section~\ref{sec:summary} and Table~\ref{tab:models} we display a
-concise characterisation of each modelled system, according to the
-image morphology and how clear or indistinct it is, whether the mass
-map and synthetic lensed image appear to be plausible, and how the
-model mass compares with the estimated stellar and full-halo masses.
-
-\section{Lens Modelling}\label{sec:spl}
+\section{SpaghettiLens}\label{sec:spl}
 
@@
 thus obtain a revised model.
-
-\subsection{Improved synthetic images}\label{subsec:sourcefit}
-
-The mass maps produced by current implementation of SpaghettiLens are
-based on images of point-like features.  No information about extended
-images is used, except in so far as they help the user identify images
-of point-like features.  The synthetic images offered to users are
-rudimentary, based on sources with conical light profiles.
-
-We have now developed a prototype of better way to generate synthetic
-images.  Figure~\figref{synthimg} illustrates.  First, areas
-containing lensed images are selected (green frames in the figure).
-The selected areas must contain no light from the lensing galaxy or
-from extraneous objects.  Pixels within the selected areas are mapped
-to a grid on the source plane, using bending angles given by the mass
-model.  The mapping from lens-plane pixels to source-plane grid cells
-is many-to-one, because of image multiplicity and magnification.  The
-brightness of each source-plane pixel is set to the mean of all the
-lens-plane pixels mapping to it.  Finally, the mapping is run back to
-the lens plane.  The result is a synthetic image.  In effect, one is
-reconstructing a source-plane brightness map by least-squares.
-
-The procedure is not yet implemented in SpaghettiLens but can be
-applied in post-processing.  The new synthetic images could be used to
-improve the mass reconstruction, by weighting the ensemble of maps
-according to how good the synthetic images are, but we have not
-attempted to do so as yet.
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{img/new_synth_img_detailed}
-  \caption{Synthetic lensed image with source-profile fitting in SW05
-    (J143454.4+522850). Top-left: original image, with areas
-    containing lensed images enclosed within green frames.  Top-right:
-    synthetic image (coloured arcs) with lensing galaxy and unrelated
-    objects in greyscale.  Bottom from left to right: reconstructed
-    source in colour, intensity (greyscale), count of lens plane
-    pixels per source plane pixel, residual of original image to
-    synthetic image.}
-  \label{fig:synthimg}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_11_hires_comparison}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_13_hires_comparison}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_33_hires_comparison}
-  \caption{Model improvement resulting from using smaller mass tiles
-    in the inner region of the mass model.  Shown here are the average
-    enclosed $\kappa$ within a given projected radius, for three
-    different reconstructions of a simulated lens (sim) from
-    Space~Warps.  In each panel, the dashed blue curve is the correct
-    answer.  The orange band represents the statistical ensemble from
-    SpaghettiLens, the orange line being the ensemble mean.  Locations of
-    images (maximum, saddle point, minimum) are marked with vertical
-    arrows.  Crossing the horizontal $\kappa=1$ line is the effective
-    Einstein radius \ER, and is so labelled. The upper panel is from
-    K\"ung et al., (2015) (see Figure~3 of that paper).  The middle
-    panel is the result when the innermost mass tile is replaced by 9
-    smaller tiles.  The lower panel results from replacing each of the
-    innermost 5 by 5 tiles each with 9 smaller tiles.}
-  \label{fig:subsampling}
-\end{figure}
-
-\subsection{Sub-sampling of central region}\label{subsec:hires}
-
-The models of simulated lenses in \cite{2015MNRAS.447.2170K} showed a
-tendency to be too shallow.  Allowing smaller mass tiles in the
-central region, thus allowing the pass profile to rise more steeply
-near the centre, was suggested as a possible cure.
-
-Figure~\figref{subsampling} shows an experiment with smaller mass
-tiles in the inner region.  Replacing the very central mass tile with
-9 smaller tiles allows for steeper central profiles.  Doing the same
-for the 25 innermost mass tiles solves the problem completely, but
-increases the number of mass tiles by 40\% and significantly increases
-the computational time.
-% 689 / 489 = 1.40899; in practice, runtime is more like x4 - x5!
-% runtimes from logfiles: 87/22, 86/21, 85/16
-The main modelling work in this paper was, however, done before the
-experiments with smaller mass tiles was complete.  Some of the models
-presented in this paper apply the intermediate option (corresponding
-to the middle panel in Figure~\figref{subsampling}) while others use
-the old system.  The results in this paper, however, mainly concern
-the enclosed mass in the outer regions, so shallowness in the central
-region should be inconsequential.
-
-\subsection{Parameterisation of pixel models} \label{subsec:parameter}
-In order to fit the set of pixelated models to a single parameterised model, a program was written that took a parameterised function and subtracted from it the mean and the principle components of the data, which were calculated using classical Principle Component Analysis.
-This created the residuals function.
-The number of components defined as principle was varied to test how this affected the output, and it was found that using 5 principle components tended to give a reasonable approximation.
-A masking function was added which selected only the data points that fell inside the image of the lens, and the principal components were clipped in order to keep the values inside the region of the ensemble of models.
-Any value higher than the clip was set to be the clip value.
-This was chosen to be 2.5 as, assuming that the data follows a Gaussian error distribution, almost all the values for the variance should lie between 2 and 3 standard deviations from the mean.
-Minimising the residuals function produces the set of parameters that fit the parameterised function to the original pixelated ensemble most closely.
-A least squares fit was used to perform this minimisation.
-The parameterised model function was obtained from the gravitational potential of an isothermal ellipsoid mass distribution \cite{2001astro.ph..2341K}.
-This model is frequently used to describe gravitational lenses as it tends to fit well with observations.
-The isothermal ellipsoid model outputs three useful parameters: the radius of the Einstein ring, the ellipticity of the model and the angle of the ellipticity from the vertical, giving the orientation of the galaxy.
-By applying this model to simulated lenses for which the values of these parameters were already known, it was possible to gain an estimate of the projected accuracy of the results, before applying the model to the candidate lensing galaxies.
-
-\begin{figure}
-  \caption{}
-  \label{fig:parameter}
-\end{figure}
-
-\section{Stellar mass}\label{sec:stellar-mass}
-
-Based on \cite{2003MNRAS.344.1000B} models.\todo{Description of
-  stellar-population models.}
-
-Following \cite{2010ApJ...710..903M}
-\begin{equation}
-\begin{aligned}
-\frac{\Mstel}{\Mhalo} &= \frac{2C_0}{(\Mhalo/M_1)^{-\beta} +
-                                     (\Mhalo/M_1)^\gamma} \\
-C_0 &= 0.02820, \quad M_1 = 10^{11.884} M_\odot \\
-\beta &= 1.057, \quad \gamma = 0.556.
-\end{aligned}
-\end{equation}
-
-\begin{equation}
-\haloindex = \frac{\ln(M/\Mstel)}{\ln(\Mhalo/\Mstel)}
-\end{equation}
-which we may call the halo-matching index.
-\begin{itemize}
-\item $\haloindex < 0$ is unphysical because $M<\Mstel$.
-\item $\haloindex = 0$ is when the stellar mass exactly accounts for the
-  lensing mass.
-\item $0 < \haloindex < 1$ is the typical situation, where the lens
-  includes stars and dark matter, but not the full halo.
-\item $\haloindex = 1$ means that the lens consists of the entire halo.
-\item $\haloindex > 1$ is in tension with abundance-matching, because the
-  lensing mass exceeds the expected halo mass.
-\end{itemize}
-
-\section{Example systems}\label{sec:examples}
-
-In this section we show modelling results for ten of the lens
-candidates.  The first five (see Figures~\figref{SW05}--\figref{SW29})
-are the most convincingly modelled systems.  The next three cases
-(Figures~\figref{SW42}--\figref{SW19}) are less good but still very
-plausible models, and are representative of the majority of the
-sample.  The last two are examples where the models were unconvincing
-(Figures~\figref{SW36}) or completely failed (\figref{SW57}).
-
-\begin{figure}
-  \inclfign{SW05}{ASW0007k4r_N7LTELSYTM}
-  \caption{Model results for SW05 (J143454.4+522850).  See text in
-    Section~\ref{sec:examples} for details.}
-  \label{fig:SW05}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW28}{ASW0007xrs_JHC3J2HYV7}
-  \caption{Model results for SW28 (J143055.9+572431).}
-  \label{fig:SW28}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW02}{ASW000619d_011489}
-  \caption{Model results for SW02 (J140522.2+574333).}
-  \label{fig:SW02}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW09}{ASW0002asp_5EKMWWVJHL}
-  \caption{Model results for SW09 (J020832.1-043315).}
-  \label{fig:SW09}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW29}{ASW0008qsm_TOFS7JNGEK}
-  \caption{Model results for SW29 (J143838.1+572647).}
-  \label{fig:SW29}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW42}{ASW00096rm_4Q3YCEWGLN}
-  \caption{Modelling results for SW42 (J221716.5+015826).}
-  \label{fig:SW42}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
-  \caption{Model results for SW58 (J143651.6+530705).}
-  \label{fig:SW58}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW19}{ASW0001ld7_OS3CYAKLRT}
-  \caption{Model results for SW19 (J020642.0-095157).}
-  \label{fig:SW19}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW36}{ASW000096t_7IPP7LWVOF}
-  \caption{Model results for SW36 (J090248.4-010232).}
-  \label{fig:SW36}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
-  \caption{Model results for SW57 (J143631.5+571131).}
-  \label{fig:SW57}
-\end{figure}
-
-Let us first consider Figure~\figref{SW05}, which shows model results
-from SW05 (J143454.4+522850).
-
-\begin{enumerate}
-\item In the upper row we have first a cutout of the Space~Warps
-  image, marked up with a spaghetti diagram.  There are four distinct
-  lensed images, and the spaghetti diagram proposes that they are a
-  minimum nearest to the lensing galaxy, a close minimum-saddle pair,
-  and a minimum further away. In Table~\ref{tab:models} we refer to
-  such configurations as IQ for inclined quad.
-\item Alongside is a synthetic image produced by modelling.  In it,
-  the fitted lensed images are shown in colour, while the lensing
-  galaxy and extraneous objects have been reduced to grayscale.
-  (Figure~\figref{synthimg} in \S~\ref{subsec:sourcefit} shows a
-  synthetic image from another model of the same system.) These two
-  panels are qualitative and display no units, and moreover, the
-  mutual alignment of the two panels is only approximate.
-\item The middle row shows contour maps from the model.  At middle
-  left, we have the arrival-time surface.
-\item At middle right we have the mass distribution in the usual
-  dimensionless form $\kappa$.  Again, these two panels are mainly
-  qualitative: both panels are spatially registered and centred on the
-  density-peak of the lens, but no scales have been included.
-\item The base row supplies spatial and mass scales.  The left panel
-  shows the circularly-averaged $\kappa$ of the model ensemble, with
-  increasing radius (in arcsec).  The four short vertical lines
-  correspond to the minima and saddle points marked in the upper-left
-  panel.  The effective Einstein radius \ER is also shown.  As the radius
-  scale indicates SW05 is comparatively large lens on the
-  sky.
-\item Lower right shows the total mass in the model against the
-  estimated stellar mass, alongside the values for the whole sample.
-  The lower-right shaded region is unphysical according to the
-  stellar-population models, because it gives $M<\Mstel$. The
-  upper-left shaded region is unphysical according to abundance
-  matching, because it gives $M>\Mhalo$.  That is to say, the unshaded
-  region is $0<\haloindex<1$.
-\end{enumerate}
-
-Proceeding to Figure~\figref{SW28}, we have one image close to the
-galaxy and an arc further away, which is interpreted as a blend of
-three images (a saddle point with two minima on either side).  We call
-this a long-axis quad or LQ configuration.  It is an indication of a
-mass distribution elongated along the arc-counterimage direction
-(along EW in this case).
-
-In Figures~\figref{SW02}--\figref{SW29} we see three candidates with
-an arc close the lensing galaxy and one image further away.  The arc
-is interpreted three images (a minimum with two saddle points on
-either side).  We call this a short-axis quad or SQ configuration.  It
-is an indication of a mass distribution elongated perpendicular to the
-arc-counterimage direction.
-
-Figures~\figref{SW02}--\figref{SW29} (SW05, SW28, SW02, SW09 and SW29)
-all correspond to the mass range of massive ellipticals.  SW05 is the
-most massive of all the candidates, with a galaxy-group scale mass.
-
-Figure~\figref{SW42} shows SW42.  The image morphology is similar to
-SW05 in Figure~\figref{SW05}, but the lens is much smaller on the sky,
-and the inferred mass is at the low end of the sample.  (The synthetic
-image shown is cruder than for the five previous figures, but that
-does not influence the mass models.)  If these preliminary findings
-are confirmed by follow-up observations, this could be the most
-dark-matter dominated lens known.\todo{Check photometry of this
-  candidate.}
-
-Figures~\figref{SW58} and \figref{SW19} appear plausible lens
-candidates.  Their morphology is similar to SW28, but the saddle-point
-counterimage is not visible.  We consider these lenses plausible but
-less convincing.
-
-Figures~\figref{SW36} and \figref{SW57} are cases where modelling
-failed.
-
-\section{Summary of models}\label{sec:summary}
-
-Table~\ref{tab:models} shows a summary of the analysis for many candidates.
-Missing rows are due to photometry data not available.
-
-\begin{enumerate}
-\item The image morphology concisely described: D for double, and
-  quads in sub-categorised in four ways
-  \citep[cf.][]{2003AJ....125.2769S} as LQ for long-axis quads (as in
-  Figure~\figref{SW28}), SQ for short-axis quads (as in
-  Figure~\figref{SW02}, \figref{SW09}, \figref{SW29}, \figref{SW42}),
-  IQ for inclined quads (as in Figure~\figref{SW05}) and CQ for very
-  symmetric core quads.
-\item Whether the images are unblended.  Distinct unblended images (as
-  in Figures~\figref{SW05} and \figref{SW42}) are an advantage in
-  modelling, but not essential.
-\item Whether all images are discernable.  The topography of an
-  arrival-time surface, as encoded by a spaghetti diagram, may require
-  more images than are visible.  For example, in Figure~\figref{SW58},
-  the modeller has put in a conjectural saddle point near the lensing
-  galaxy.
-\item Whether the lens is fairly isolated.
-\item Whether the arrival-time surface and synthetic image are
-  plausible.  In Figure~\figref{SW36} the model implies extra images
-  or a long arc, which are not seen.
-\item Whether the mass map is reasonable.
-\item The halo index $\haloindex$.
-\end{enumerate}
-
-\begin{table*}
-  \caption{Categorisation of SW models}
-  \label{tab:models}
-  \include{table}
-\end{table*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% The best way to enter references is to use BibTeX:
-\bibliographystyle{mnras}
-\bibliography{bib/bibli} % if your bibtex file is called example.bib
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \appendix
-
-\clearpage
-
-\section{TODO}
-\listoftodos
-
-% Don't change these lines
-\bsp	% typesetting comment
-\label{lastpage}
-\end{document}

### 2016-10-03 parts/stelmass.tex
moving text around

\section{Stellar and halo mass estimates}\label{sec:stellar-mass}

The stellar masses of the lens galaxies are derived by comparison of
the photometric data with M/L estimates from population synthesis
models.  In principle, a detailed analysis of the spectral energy
distribution is needed to derive accurate stellar masses
\citep[e.g.][]{2009ApJS..185..253G,2011MNRAS.418.1587T}.
However, estimates to within 0.3\,dex in $\log($M$_s$/M$_\odot)$ can be
derived with a single colour, preferably tracing a rest-frame colour
similar to $U-V$ \citep[see fig.~1 of][]{2008MNRAS.383..857F}. This
paper presents a pilot study of the potential of SpaghettiLens to
constrain the physical properties of strong lenses. Therefore, we
further simplify the analysis by assuming a relationship between the
apparent total magnitude and stellar mass, at the redshift of the
lens. Note that for typical stellar population parameters, the
variation of this relation is at most 1\,dex. In this work, we make
use of the \citet{2003MNRAS.344.1000B} models to derive two functional
forms of the stellar mass with respect to SDSS-$i$ band
magnitudes. The models have solar metallicity, with a Chabrier
IMF, and assume two different age trends: a ``young'' model, with a
constant 500\,Myr age at all redshifts, and an ``old'' model where the
age is the oldest one possible at each redshift, adopting a
standard $\Lambda$CDM model with $H_0=70$\,km\,s$^{-1}$\,Mpc$^{-1}$
and $\Omega_m=0.3$. We take a geometric mean of the output from these
two models as the stellar mass of the lens. This rough estimate will
be improved in future versions by use of the available optical and NIR
magnitudes to derive more accurate constrains on the stellar
populations.

In addition, we also derive halo masses for the lenses by use of the
standard abundance matching technique, whereby a comparison of the
observed stellar mass function of galaxies with the dark matter halo
mass function from N-body simulations results in a simple relation
between the two. We emphasize that this derivation of halo mass should
be considered an ``average'' estimate, and a significant scatter can
be expected as galaxies with the same stellar mass can be found in
different environments. We refer the reader to \cite{2012MNRAS.424..104L}
for an assessment of the effect of abundance matching on the
derivation of dark matter halo properties in lensing galaxies. We
follow the prescription of \citet{2010ApJ...710..903M}, namely:

\begin{equation}
\begin{aligned}
\frac{\Mstel}{\Mhalo} &= \frac{2C_0}{(\Mhalo/M_1)^{-\beta} +
                                     (\Mhalo/M_1)^\gamma} \\
C_0 &= 0.02820, \quad M_1 = 10^{11.884} M_\odot \\
\beta &= 1.057, \quad \gamma = 0.556.
\end{aligned}
\end{equation}
and define a halo-matching index:
\begin{equation}
\haloindex = \frac{\ln(M/\Mstel)}{\ln(\Mhalo/\Mstel)}
\end{equation}
that relates the observed lensing to stellar mass, with the
global ratio expected if the host halo corresponds to the
average value derived by abundance matching. Several cases
for $\haloindex$ can be considered:
\begin{itemize}
\item $\haloindex < 0$ is unphysical because $M<\Mstel$.
\item $\haloindex = 0$ is when the stellar mass exactly accounts for the
  lensing mass.
\item $0 < \haloindex < 1$ is the typical situation, where the lens
  includes stars and dark matter, but not the full halo.
\item $\haloindex = 1$ means that the lens consists of the entire halo.
\item $\haloindex > 1$ is in tension with abundance-matching, because the
  lensing mass exceeds the expected halo mass.
\end{itemize}

\begin{figure*}
\includegraphics[width=\linewidth]{img/mlens_vs_mstel_one/mstel_vs_mtot_one}
\caption{}
\end{figure*}

### 2016-10-03 parts/synthimage.tex
moving text around

--- 2016-07-26 paper2.tex
@@
-\documentclass[fleqn,usenatbib]{mnras}
-
-%%% DEBUG SETTINGS - remove at the end %%%%%%%%%%%%%%%
-\usepackage{silence} % silence error warinings
-\WarningFilter{caption}{Unsupported document class} % caption doesn't know mnras..
-\hbadness = 5000
-\vbadness = 10000
-% \usepackage{}
-
-% MNRAS is set in Times font. If you don't have this installed (most LaTeX
-% installations will be fine) or prefer the old Computer Modern fonts, comment
-% out the following line
-%\usepackage{newtxtext,newtxmath} % not yet supported on arxiv and uni computer
-%\usepackage{txfonts}
-
-% Depending on your LaTeX fonts installation, you might get better results with one of these:
-%\usepackage{mathptmx}
-%\usepackage{txfonts}
-
-% Use vector fonts, so it zooms properly in on-screen viewing software
-% Don't change these lines unless you know what you are doing
-\usepackage[T1]{fontenc} % make sure font is supported
-% \usepackage{ae,aecompl} %obsolete when using modern fonts
-\usepackage[final]{microtype} % make sure font is supported
-% and a suitable font
-\usepackage{lmodern} % use a modern font with T1 support
-%\usepackage{cm-super} % use a modern font with T1 support
-
-%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
-
-% Only include extra packages if you really need them. Common packages are:
-%\usepackage[dvipdfmx]{graphicx}	% Including figure files
-\usepackage{graphicx} % Including figure files
-%\usepackage[skip=0pt]{subcaption}
-\usepackage{amsmath}	% Advanced maths commands
-\usepackage{amssymb}	% Extra maths symbols
-\usepackage{pifont}	% Extra maths symbols
-%\usepackage{bmpsize}  % PS still needs this for correct bounding boxes?
-
-% TODO stuff, comment out for final submit
-\usepackage{todonotes} % as long as we are editing...
-%\usepackage{showframe} % for debug
-%\overfullrule=5pt      % show overfull boxes
-
-% I disabled hyperlink in the cls und included it here because of bugs
-\usepackage{hyperref}   % Hyperlinks
-\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,filecolor=blue,urlcolor=blue}
-
-\edef\smallwidth{0.4\linewidth}
-
-\newcommand{\inclfig}[2]{
-  \centering
-	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img3_ipol}
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
-%        \includegraphics[width=\smallwidth]{spaghetti/#2_img2}
-        \includegraphics[width=\smallwidth]{img/kappa_map/#1_#2_kappa_map}
-	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
-	\includegraphics[width=\smallwidth]{img/mlens_vs_mstel/#1_#2_mstel_vs_mtot}
-}
-
-\newcommand{\inclfign}[2]{
-  \centering
-	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
-	\includegraphics[width=\smallwidth]{img/nsynth/#2_nsynth}
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
-%	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
-        \includegraphics[width=\smallwidth]{img/kappa_map/#1_#2_kappa_map}
-	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
-	\includegraphics[width=\smallwidth]{img/mlens_vs_mstel/#1_#2_mstel_vs_mtot}
-}
-
-\newcommand*{\rot}{\rotatebox{90}}
-\newcommand*{\OK}{\ding{51}}
-\newcommand*{\NO}{\ding{55}}
-
-\newcommand{\lenstitle}[1]{\noindent\textbf{#1} --}
-\newcommand{\params}[3]{(\(\Theta_\text{E}:#1\), $\varepsilon:#2$, $\alpha_\varepsilon:#3$ )}
-
-\newcommand{\asw}[1]{ASW000#1}
-\newcommand{\sw}[1]{SW~#1}
-\newcommand{\model}[1]{SL model~#1}
-
-\newcommand{\figref}[1]{\ref{fig:#1}}
-
-\newcommand{\Mstel}{M_{\rm stel}}
-\newcommand{\Mhalo}{M_{\rm h}}
-\newcommand{\haloindex}{\mathcal{H}}
-\newcommand{\ER}{$\Theta_{\text{E}}$} % einstein radius
-
-\title[Lens models for Space Warps CFHTLS]{Model of lens candidates from
-  Space Warps CFHTLS}
-
-\author[K\"ung et al]{Rafael K\"ung,$^{1}$
-Prasenjit Saha,$^{1}$
-Ignacio Ferreras,$^{2}$
-Elisabeth Baeten,$^{3}$
-\newauthor
-Jonathan Coles,$^{4}$
-Claude Cornen,$^{3}$
-Christine Macmillan,$^{3}$
-Phil Marshall,$^{5}$ 
-\newauthor
-Anupreeta More,$^{6}$
-Lucy Oswald$^{7}$
-Aprajita Verma$^{8}$
-and Julianne K. Wilcox$^{4}$
-%
-\\
-%
-$^{1}$Physik-Institut, University of Zurich, Winterthurerstrasse 190, 8057 Zurich, Switzerland\\
-$^{2}$Mullard Space Science Laboratory, University College London, Holmbury St Mary, Dorking, Surrey RH5 6NT, UK\\
-$^{3}$Zooniverse, c/o Astrophysics Department, University of Oxford, Oxford OX1 3RH, UK \\
-$^{4}$Exascale Research Computing Lab, Campus Teratec, 2 Rue de la Piquetterie, 91680 Bruyeres-le-Chatel, France\\
-$^{5}$Kavli Institute for Particle Astrophysics and Cosmology, Stanford University, 452 Lomita Mall, Stanford, CA 94035, USA\\
-$^{6}$Kavli Institute for the Physics and Mathematics of the Universe, University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa-shi 277-8583, Japan\\
-$^{7}$Murray Edwards College, University of Cambridge, Cambridge CB3 0DF, UK\\
-$^{8}$Sub-department of Astrophysics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
-}
-
-% These dates will be filled out by the publisher
-% \date{Accepted XXX. Received YYY; in original form ZZZ}
-
-% Enter the current year, for the copyright statements etc.
-\pubyear{2016}
-
-% Don't change these lines
-\begin{document}
-\label{firstpage}
-\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\maketitle
-
-\begin{abstract}
-We report modelling follow-up of recently-discovered
-gravitational-lens candidates in the CFHT Legacy Survey.  Lens
-modelling was done by a small group of specially-interested volunteers
-from the Space~Warps citizen-science community who originally found
-the candidate lenses.  Models are categorised according to seven
-qualitative and quantitive points.  Also included are some
-improvements to the modelling software used (SpaghettiLens),
-and discussion of strategies for scaling to future surveys
-with more and frequent discoveries.
-
-The candidates successfully modelled are all galaxies, with inferred
-lensing masses ranging from $\sim10^{11}M_\odot$ to $>10^{13}M_\odot$.
-Stellar masses have also been estimated, using photometry from the
-CFHTLS pipeline and stellar-population models.  A trend well-known
-in nearby galaxies, that star-formation efficiency is maximal for
-total masses of $\approx10^{12}M_\odot$ and reduces for both lower and
-higher masses, is discernable also in these much more distant
-galaxies.
-\end{abstract}
-
-\begin{keywords}
-gravitational lensing: strong -- keyword2
-\end{keywords}
-
-\section{Introduction}
-
-Light deflection at the rim of the Sun is famously $1.75''$.  The
-deflection angle can also be expressed in terms of the escape velocity
-$2v_{\rm esc}^2/c^2$, with $v_{\rm esc}$ at the solar surface being
-$\simeq620\rm\,km/s$.  The Galactic escape velocity at the Sun's
-location is similar: $\approx500\rm\,km/s$, typical of massive
-galaxies.  Thus, the outer regions of massive galaxies have lensing
-deflections comparable to that at the rim of the Sun.  Yet these
-quantitatively similar deflections have qualitatively different
-consequences.  Light deflection by the Sun must be accounted for in
-modern astrometry \citep[see e.g.,][]{2015CQGra..32p5008C} but is not
-itself a physics probe in the way it was a century ago.  With distant
-galaxies, however, light bending by $\sim1''$ introduces two new
-phenomena.  First, for galaxies distant enough that their apparent
-size is comparable to the bending angle, light deflection can cause
-multiple images of background sources, or strong lensing.  Second, the
-gravitational field is dominated by dark matter, hence strong lensing
-becomes a probe of dark matter in galaxies.
-
-With no unambiguous dark-matter particle detections so far, dark
-matter has studied only through its indirect consequences on galactic
-and larger scales.  In most work, dark matter is taken to be a
-collisionless non-relativistic fluid (cold dark matter or CDM); in
-recent years, the simulation by \cite{2005Natur.435..629S} has been
-particularly influential in studying the formation of CDM structures.
-Other scenarios have also been considered, such as a cold condensing
-boson fluid \citep{2016ApJ...818...89S}.  There is a general
-consensus, however, that the origins of galaxy lie in the
-gravitational collapse, fragmentation, and mergers of dark-matter
-clumps, into which fell gas, cooling through radiative processes to
-form dense clouds and eventually stars.  There is, however, much
-debate about the details, of which \cite{2012RAA....12..917S} provide
-a nice summary.
-
-Strong-lensing galaxies are a useful source of information on the
-mutual dynamics and dark matter and gas in galaxies.  The topic has
-been explored in several studies
-\citep{2009ApJ...703L..51K,2011ApJ...740...97L,2012MNRAS.424..104L,
-  2016MNRAS.459.3677L,2016MNRAS.456..870B} but it is desirable to
-enlarge the samples from tens of lensing galaxies to thousands.  Doing
-so requires finding more lenses, of course, but also modelling their
-masses.
-
-Recent searches through the CFHTLS \citep{2012SPIE.8448E..0MC} using
-arc-finders
-\citep{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G} by
-machine learning \citep{2016arXiv160504309P} and by visual inspection
-by a citizen-science volunteers
-\citep[Space~Warps][]{2016MNRAS.455.1191M} have between them
-discovered an average of four lenses per square degree.  So one can be
-optimistic about finding many thousands of lenses in the next
-generation of wide-field surveys.  The expected flood of new lens
-discoveries will need a similarly huge modelling effort to
-reconstruct their mass distributions.  To prepare for the challenge of
-massive-sample lens modelling, \cite{2015MNRAS.447.2170K} developed a
-new modelling strategy, implemented as the SpaghettiLens system.  The
-idea is to collaborate with experienced members of the citizen-science
-community, who have already participated in lens discovery through
-Space~Warps, as well as several other projects involving astronomical
-data.  In this paper, we present SpaghettiLens models of
-lens-candidates discovered through Space~Warps.
-
-Section~\ref{sec:spl} summarises the SpaghettiLens system and
-discusses its ongoing development. A SpaghettiLens model consists of a
-statistical ensemble of free-form maps of the sky-projected mass
-distribution responsible for lensing.  Each lens candidates in
-practice gets modelled several times in a collaborative refinement
-process\footnote{See ``Collaborative gravitational lens
-  modelling\dots'' in {\tt http://letters.zooniverse.org} especially
-  the model tree.}  In this paper we report the most recent model for
-each lens, as representing a consensus among modellers, as to the best
-that could be achieved with the available data and software.
-Photometric lens redshifts are used; source redshifts are set to
-$z=2$ unless an unambiguous photometric redshift is available.
-The models can, however, be trivially rescaled to use better
-redshift values, as and when they become available.
-\cite{2015MNRAS.447.2170K} tested the system on simulated lenses and
-identified some areas for improvement.  The first two of those are
-taken up in Section~\ref{sec:spl}, along with a further idea. In
-\S~\ref{subsec:sourcefit} we introduce fitting of the brightness
-profiles of the source.  This feature has not yet been included in
-SpaghettiLens, but has been carried out in post-processing for a few
-especially interesting candidates.  In \S~\ref{subsec:hires} we show
-that making mass maps fine-grained in the central region relieves a
-tendency in the earlier work for mass to be too shallow. Then in
-\S~\ref{subsec:parameter} we consider the possibility of fitting a
-parametric lens model to the model ensemble; so far we have only been
-successful at extracting an Einstein radius.
-
-Section~\ref{sec:stellar-mass} explains how we compare the lensing
-mass with the mass in stars in the lensing galaxy.  We estimate the
-stellar mass by comparing galaxy magnitudes from the CFHTLS pipeline
-with the well-known stellar-population models of
-\cite{2003MNRAS.344.1000B}.  We then extrapolate the stellar masses to
-a halo mass using the abundance-matching prescription of
-\cite{2010ApJ...710..903M}.  Naturally, the lensing mass must be more
-than the stellar mass but no more than the total halo mass.  We then
-introduce what we call a halo index $\haloindex$ which gives an idea
-of how the lensing mass compares with these two bounds.
-
-Section~\ref{sec:examples} discusses ten of the systems, including six
-systems we found to be particularly interesting.  The online
-supplement gives results for all the modelled systems.
-
-In Section~\ref{sec:summary} and Table~\ref{tab:models} we display a
-concise characterisation of each modelled system, according to the
-image morphology and how clear or indistinct it is, whether the mass
-map and synthetic lensed image appear to be plausible, and how the
-model mass compares with the estimated stellar and full-halo masses.
-
-\section{Lens Modelling}\label{sec:spl}
-
-SpaghettiLens is an example of a medium-sized collaboration spawned by
-a large citizen-science project (in this case Space~Warps).  While
-collaboration with volunteers is essential to both, the form of
-collaboration is very different.  In Space~Warps, volunteers in a
-crowd of $\gtrsim10^4$ make independent contributions.  Each person is
-presented with a random selection of survey-patches and invited to (in
-effect) vote on each.  The system estimates each volunteer's skill
-level according to test-patches interspersed with the real data, and
-weights their votes accordingly \citep{2016MNRAS.455.1171M}.  There is
-an active forum for volunteers, but since everyone is seeing different
-data samples with minimal overlap, the forum has little if any
-influence on votes.  With SpaghettiLens, on the other hand, there is a
-small group of volunteers and their contributions are interdependent.
-
-A modeller's main input to SpaghettiLens is a sketch of arrival-time
-contours on a lensed system.  It gives the locations (or best-guess
-locations) of images of point-like sources, along with their ordering
-in arrival time, and their parities (minumum, saddle-point or
-maximum).  Such a sketch, which we call a spaghetti diagram, tends to
-resemble the form of lensed arcs, but it also in effect 
-encodes a proposal for its mass distribution.  A spaghetti diagram is
-read by a server-side numerical engine \citep[GLASS, developed
-  by][]{2014MNRAS.445.2181C} which then returns a statistical ensemble
-of mass maps.  The mass maps are made up of mass tiles and are
-free-form, except that they are required to be concentrated around the
-identified lens centre.  They are also required to reproduce the given
-image locations, parities and time ordering exactly.  Graphical
-representations of the mass map and arrival-time surface are returned
-to the user for review.  The user can post these results on a forum,
-or discard them and try again.  Volunteers can start the modelling
-process afresh, or they can take an existing model from the forum and
-modify its input spaghetti diagram or its accompanying options, and
-thus obtain a revised model.
-
-\subsection{Improved synthetic images}\label{subsec:sourcefit}
+\section{Synthetic images}
 
@@
 of point-like features.  The synthetic images offered to users are
-rudimentary, based on sources with conical light profiles.
+rudimentary, corresponding to conical light profiles (that is,
+circular light profiles with brightness decreasing linearly with radius).
 
@@
 containing lensed images are selected (green frames in the figure).
-The selected areas must contain no light from the lensing galaxy or
-from extraneous objects.  Pixels within the selected areas are mapped
-to a grid on the source plane, using bending angles given by the mass
-model.  The mapping from lens-plane pixels to source-plane grid cells
-is many-to-one, because of image multiplicity and magnification.  The
-brightness of each source-plane pixel is set to the mean of all the
-lens-plane pixels mapping to it.  Finally, the mapping is run back to
-the lens plane.  The result is a synthetic image.  In effect, one is
-reconstructing a source-plane brightness map by least-squares.
+The selected areas should be as free as possible from of light from
+the lensing galaxy or from extraneous objects.  Pixels within the
+selected areas are mapped to a grid on the source plane, using bending
+angles given by the mass model.  The mapping from lens-plane pixels to
+source-plane grid cells is many-to-one, because of image multiplicity
+and magnification.  The brightness of each source-plane pixel is set
+to the mean of all the lens-plane pixels mapping to it.  Finally, the
+mapping is run back to the lens plane.  The result is a synthetic
+image.  In effect, one is reconstructing a source-plane brightness map
+by least-squares.
 
@@
 
-\begin{figure}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_11_hires_comparison}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_13_hires_comparison}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_33_hires_comparison}
-  \caption{Model improvement resulting from using smaller mass tiles
-    in the inner region of the mass model.  Shown here are the average
-    enclosed $\kappa$ within a given projected radius, for three
-    different reconstructions of a simulated lens (sim) from
-    Space~Warps.  In each panel, the dashed blue curve is the correct
-    answer.  The orange band represents the statistical ensemble from
-    SpaghettiLens, the orange line being the ensemble mean.  Locations of
-    images (maximum, saddle point, minimum) are marked with vertical
-    arrows.  Crossing the horizontal $\kappa=1$ line is the effective
-    Einstein radius \ER, and is so labelled. The upper panel is from
-    K\"ung et al., (2015) (see Figure~3 of that paper).  The middle
-    panel is the result when the innermost mass tile is replaced by 9
-    smaller tiles.  The lower panel results from replacing each of the
-    innermost 5 by 5 tiles each with 9 smaller tiles.}
-  \label{fig:subsampling}
-\end{figure}
-
-\subsection{Sub-sampling of central region}\label{subsec:hires}
-
-The models of simulated lenses in \cite{2015MNRAS.447.2170K} showed a
-tendency to be too shallow.  Allowing smaller mass tiles in the
-central region, thus allowing the pass profile to rise more steeply
-near the centre, was suggested as a possible cure.
-
-Figure~\figref{subsampling} shows an experiment with smaller mass
-tiles in the inner region.  Replacing the very central mass tile with
-9 smaller tiles allows for steeper central profiles.  Doing the same
-for the 25 innermost mass tiles solves the problem completely, but
-increases the number of mass tiles by 40\% and significantly increases
-the computational time.
-% 689 / 489 = 1.40899; in practice, runtime is more like x4 - x5!
-% runtimes from logfiles: 87/22, 86/21, 85/16
-The main modelling work in this paper was, however, done before the
-experiments with smaller mass tiles was complete.  Some of the models
-presented in this paper apply the intermediate option (corresponding
-to the middle panel in Figure~\figref{subsampling}) while others use
-the old system.  The results in this paper, however, mainly concern
-the enclosed mass in the outer regions, so shallowness in the central
-region should be inconsequential.
-
-\subsection{Parameterisation of pixel models} \label{subsec:parameter}
-In order to fit the set of pixelated models to a single parameterised model, a program was written that took a parameterised function and subtracted from it the mean and the principle components of the data, which were calculated using classical Principle Component Analysis.
-This created the residuals function.
-The number of components defined as principle was varied to test how this affected the output, and it was found that using 5 principle components tended to give a reasonable approximation.
-A masking function was added which selected only the data points that fell inside the image of the lens, and the principal components were clipped in order to keep the values inside the region of the ensemble of models.
-Any value higher than the clip was set to be the clip value.
-This was chosen to be 2.5 as, assuming that the data follows a Gaussian error distribution, almost all the values for the variance should lie between 2 and 3 standard deviations from the mean.
-Minimising the residuals function produces the set of parameters that fit the parameterised function to the original pixelated ensemble most closely.
-A least squares fit was used to perform this minimisation.
-The parameterised model function was obtained from the gravitational potential of an isothermal ellipsoid mass distribution \cite{2001astro.ph..2341K}.
-This model is frequently used to describe gravitational lenses as it tends to fit well with observations.
-The isothermal ellipsoid model outputs three useful parameters: the radius of the Einstein ring, the ellipticity of the model and the angle of the ellipticity from the vertical, giving the orientation of the galaxy.
-By applying this model to simulated lenses for which the values of these parameters were already known, it was possible to gain an estimate of the projected accuracy of the results, before applying the model to the candidate lensing galaxies.
-
-\begin{figure}
+\begin{figure*}
+\includeten{img/nsynth/}{_nsynth}
 \caption{}
-  \label{fig:parameter}
-\end{figure}
-
-\section{Stellar mass}\label{sec:stellar-mass}
-
-Based on \cite{2003MNRAS.344.1000B} models.\todo{Description of
-  stellar-population models.}
-
-Following \cite{2010ApJ...710..903M}
-\begin{equation}
-\begin{aligned}
-\frac{\Mstel}{\Mhalo} &= \frac{2C_0}{(\Mhalo/M_1)^{-\beta} +
-                                     (\Mhalo/M_1)^\gamma} \\
-C_0 &= 0.02820, \quad M_1 = 10^{11.884} M_\odot \\
-\beta &= 1.057, \quad \gamma = 0.556.
-\end{aligned}
-\end{equation}
-
-\begin{equation}
-\haloindex = \frac{\ln(M/\Mstel)}{\ln(\Mhalo/\Mstel)}
-\end{equation}
-which we may call the halo-matching index.
-\begin{itemize}
-\item $\haloindex < 0$ is unphysical because $M<\Mstel$.
-\item $\haloindex = 0$ is when the stellar mass exactly accounts for the
-  lensing mass.
-\item $0 < \haloindex < 1$ is the typical situation, where the lens
-  includes stars and dark matter, but not the full halo.
-\item $\haloindex = 1$ means that the lens consists of the entire halo.
-\item $\haloindex > 1$ is in tension with abundance-matching, because the
-  lensing mass exceeds the expected halo mass.
-\end{itemize}
-
-\section{Example systems}\label{sec:examples}
-
-In this section we show modelling results for ten of the lens
-candidates.  The first five (see Figures~\figref{SW05}--\figref{SW29})
-are the most convincingly modelled systems.  The next three cases
-(Figures~\figref{SW42}--\figref{SW19}) are less good but still very
-plausible models, and are representative of the majority of the
-sample.  The last two are examples where the models were unconvincing
-(Figures~\figref{SW36}) or completely failed (\figref{SW57}).
-
-\begin{figure}
-  \inclfign{SW05}{ASW0007k4r_N7LTELSYTM}
-  \caption{Model results for SW05 (J143454.4+522850).  See text in
-    Section~\ref{sec:examples} for details.}
-  \label{fig:SW05}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW28}{ASW0007xrs_JHC3J2HYV7}
-  \caption{Model results for SW28 (J143055.9+572431).}
-  \label{fig:SW28}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW02}{ASW000619d_011489}
-  \caption{Model results for SW02 (J140522.2+574333).}
-  \label{fig:SW02}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW09}{ASW0002asp_5EKMWWVJHL}
-  \caption{Model results for SW09 (J020832.1-043315).}
-  \label{fig:SW09}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW29}{ASW0008qsm_TOFS7JNGEK}
-  \caption{Model results for SW29 (J143838.1+572647).}
-  \label{fig:SW29}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW42}{ASW00096rm_4Q3YCEWGLN}
-  \caption{Modelling results for SW42 (J221716.5+015826).}
-  \label{fig:SW42}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
-  \caption{Model results for SW58 (J143651.6+530705).}
-  \label{fig:SW58}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW19}{ASW0001ld7_OS3CYAKLRT}
-  \caption{Model results for SW19 (J020642.0-095157).}
-  \label{fig:SW19}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW36}{ASW000096t_7IPP7LWVOF}
-  \caption{Model results for SW36 (J090248.4-010232).}
-  \label{fig:SW36}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
-  \caption{Model results for SW57 (J143631.5+571131).}
-  \label{fig:SW57}
-\end{figure}
-
-Let us first consider Figure~\figref{SW05}, which shows model results
-from SW05 (J143454.4+522850).
-
-\begin{enumerate}
-\item In the upper row we have first a cutout of the Space~Warps
-  image, marked up with a spaghetti diagram.  There are four distinct
-  lensed images, and the spaghetti diagram proposes that they are a
-  minimum nearest to the lensing galaxy, a close minimum-saddle pair,
-  and a minimum further away. In Table~\ref{tab:models} we refer to
-  such configurations as IQ for inclined quad.
-\item Alongside is a synthetic image produced by modelling.  In it,
-  the fitted lensed images are shown in colour, while the lensing
-  galaxy and extraneous objects have been reduced to grayscale.
-  (Figure~\figref{synthimg} in \S~\ref{subsec:sourcefit} shows a
-  synthetic image from another model of the same system.) These two
-  panels are qualitative and display no units, and moreover, the
-  mutual alignment of the two panels is only approximate.
-\item The middle row shows contour maps from the model.  At middle
-  left, we have the arrival-time surface.
-\item At middle right we have the mass distribution in the usual
-  dimensionless form $\kappa$.  Again, these two panels are mainly
-  qualitative: both panels are spatially registered and centred on the
-  density-peak of the lens, but no scales have been included.
-\item The base row supplies spatial and mass scales.  The left panel
-  shows the circularly-averaged $\kappa$ of the model ensemble, with
-  increasing radius (in arcsec).  The four short vertical lines
-  correspond to the minima and saddle points marked in the upper-left
-  panel.  The effective Einstein radius \ER is also shown.  As the radius
-  scale indicates SW05 is comparatively large lens on the
-  sky.
-\item Lower right shows the total mass in the model against the
-  estimated stellar mass, alongside the values for the whole sample.
-  The lower-right shaded region is unphysical according to the
-  stellar-population models, because it gives $M<\Mstel$. The
-  upper-left shaded region is unphysical according to abundance
-  matching, because it gives $M>\Mhalo$.  That is to say, the unshaded
-  region is $0<\haloindex<1$.
-\end{enumerate}
-
-Proceeding to Figure~\figref{SW28}, we have one image close to the
-galaxy and an arc further away, which is interpreted as a blend of
-three images (a saddle point with two minima on either side).  We call
-this a long-axis quad or LQ configuration.  It is an indication of a
-mass distribution elongated along the arc-counterimage direction
-(along EW in this case).
-
-In Figures~\figref{SW02}--\figref{SW29} we see three candidates with
-an arc close the lensing galaxy and one image further away.  The arc
-is interpreted three images (a minimum with two saddle points on
-either side).  We call this a short-axis quad or SQ configuration.  It
-is an indication of a mass distribution elongated perpendicular to the
-arc-counterimage direction.
-
-Figures~\figref{SW02}--\figref{SW29} (SW05, SW28, SW02, SW09 and SW29)
-all correspond to the mass range of massive ellipticals.  SW05 is the
-most massive of all the candidates, with a galaxy-group scale mass.
-
-Figure~\figref{SW42} shows SW42.  The image morphology is similar to
-SW05 in Figure~\figref{SW05}, but the lens is much smaller on the sky,
-and the inferred mass is at the low end of the sample.  (The synthetic
-image shown is cruder than for the five previous figures, but that
-does not influence the mass models.)  If these preliminary findings
-are confirmed by follow-up observations, this could be the most
-dark-matter dominated lens known.\todo{Check photometry of this
-  candidate.}
-
-Figures~\figref{SW58} and \figref{SW19} appear plausible lens
-candidates.  Their morphology is similar to SW28, but the saddle-point
-counterimage is not visible.  We consider these lenses plausible but
-less convincing.
-
-Figures~\figref{SW36} and \figref{SW57} are cases where modelling
-failed.
-
-\section{Summary of models}\label{sec:summary}
-
-Table~\ref{tab:models} shows a summary of the analysis for many candidates.
-Missing rows are due to photometry data not available.
-
-\begin{enumerate}
-\item The image morphology concisely described: D for double, and
-  quads in sub-categorised in four ways
-  \citep[cf.][]{2003AJ....125.2769S} as LQ for long-axis quads (as in
-  Figure~\figref{SW28}), SQ for short-axis quads (as in
-  Figure~\figref{SW02}, \figref{SW09}, \figref{SW29}, \figref{SW42}),
-  IQ for inclined quads (as in Figure~\figref{SW05}) and CQ for very
-  symmetric core quads.
-\item Whether the images are unblended.  Distinct unblended images (as
-  in Figures~\figref{SW05} and \figref{SW42}) are an advantage in
-  modelling, but not essential.
-\item Whether all images are discernable.  The topography of an
-  arrival-time surface, as encoded by a spaghetti diagram, may require
-  more images than are visible.  For example, in Figure~\figref{SW58},
-  the modeller has put in a conjectural saddle point near the lensing
-  galaxy.
-\item Whether the lens is fairly isolated.
-\item Whether the arrival-time surface and synthetic image are
-  plausible.  In Figure~\figref{SW36} the model implies extra images
-  or a long arc, which are not seen.
-\item Whether the mass map is reasonable.
-\item The halo index $\haloindex$.
-\end{enumerate}
-
-\begin{table*}
-  \caption{Categorisation of SW models}
-  \label{tab:models}
-  \include{table}
-\end{table*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% The best way to enter references is to use BibTeX:
-\bibliographystyle{mnras}
-\bibliography{bib/bibli} % if your bibtex file is called example.bib
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \appendix
-
-\clearpage
-
-\section{TODO}
-\listoftodos
-
-% Don't change these lines
-\bsp	% typesetting comment
-\label{lastpage}
-\end{document}
+\end{figure*}

### 2016-10-03 paper2.tex
slowly fixing figure refs

@@
 
+\input parts/morph
+
 \input parts/massmodel
 
-\input parts/synthimage
-
 \input parts/stelmass
-
-\section{Example systems}\label{sec:examples}
-
-In this section we show modelling results for ten of the lens
-candidates.  The first five (see Figures~\figref{SW05}--\figref{SW29})
-are the most convincingly modelled systems.  The next three cases
-(Figures~\figref{SW42}--\figref{SW19}) are less good but still very
-plausible models, and are representative of the majority of the
-sample.  The last two are examples where the models were unconvincing
-(Figures~\figref{SW36}) or completely failed (\figref{SW57}).
-
-\begin{enumerate}
-
-\item Alongside is a synthetic image produced by modelling.  In it,
-  the fitted lensed images are shown in colour, while the lensing
-  galaxy and extraneous objects have been reduced to grayscale.
-  (Figure~\figref{synthimg} in \S~\ref{subsec:sourcefit} shows a
-  synthetic image from another model of the same system.) These two
-  panels are qualitative and display no units, and moreover, the
-  mutual alignment of the two panels is only approximate.
-\item The middle row shows contour maps from the model.  At middle
-  left, we have the arrival-time surface.
-\item At middle right we have the mass distribution in the usual
-  dimensionless form $\kappa$.  Again, these two panels are mainly
-  qualitative: both panels are spatially registered and centred on the
-  density-peak of the lens, but no scales have been included.
-\item The base row supplies spatial and mass scales.  The left panel
-  shows the circularly-averaged $\kappa$ of the model ensemble, with
-  increasing radius (in arcsec).  The four short vertical lines
-  correspond to the minima and saddle points marked in the upper-left
-  panel.  The effective Einstein radius \ER is also shown.  As the radius
-  scale indicates SW05 is comparatively large lens on the
-  sky.
-\item Lower right shows the total mass in the model against the
-  estimated stellar mass, alongside the values for the whole sample.
-  The lower-right shaded region is unphysical according to the
-  stellar-population models, because it gives $M<\Mstel$. The
-  upper-left shaded region is unphysical according to abundance
-  matching, because it gives $M>\Mhalo$.  That is to say, the unshaded
-  region is $0<\haloindex<1$.
-\end{enumerate}
-
-Figures~\figref{SW02}--\figref{SW29} (SW05, SW28, SW02, SW09 and SW29)
-all correspond to the mass range of massive ellipticals.  SW05 is the
-most massive of all the candidates, with a galaxy-group scale mass.
-
-For SW42 the inferred mass is at the low end of the sample.  (The
-synthetic image shown is cruder than for the five previous figures,
-but that does not influence the mass models.)  If these preliminary
-findings are confirmed by follow-up observations, this could be the
-most dark-matter dominated lens known.\todo{Check photometry of this
-  candidate.}
-
-Figures~\figref{SW58} and \figref{SW19} appear plausible lens
-candidates.  Their morphology is similar to SW28, but the saddle-point
-counterimage is not visible.  We consider these lenses plausible but
-less convincing.
-
-Figures~\figref{SW36} and \figref{SW57} are cases where modelling
-failed.
-
-\section{Summary of models}\label{sec:summary}
 
@@
 
+\section{TODO}
+\listoftodos
+
 \clearpage
@@
 
-\section{SpaghettiLens developments}
-
-\subsection{Improved synthetic images}\label{subsec:sourcefit}
-
-\begin{figure}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_11_hires_comparison}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_13_hires_comparison}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_33_hires_comparison}
-  \caption{Model improvement resulting from using smaller mass tiles
-    in the inner region of the mass model.  Shown here are the average
-    enclosed $\kappa$ within a given projected radius, for three
-    different reconstructions of a simulated lens (sim) from
-    Space~Warps.  In each panel, the dashed blue curve is the correct
-    answer.  The orange band represents the statistical ensemble from
-    SpaghettiLens, the orange line being the ensemble mean.  Locations of
-    images (maximum, saddle point, minimum) are marked with vertical
-    arrows.  Crossing the horizontal $\kappa=1$ line is the effective
-    Einstein radius \ER, and is so labelled. The upper panel is from
-    K\"ung et al., (2015) (see Figure~3 of that paper).  The middle
-    panel is the result when the innermost mass tile is replaced by 9
-    smaller tiles.  The lower panel results from replacing each of the
-    innermost 5 by 5 tiles each with 9 smaller tiles.}
-  \label{fig:subsampling}
-\end{figure}
-
-\subsection{Sub-sampling of central region}\label{subsec:hires}
-
-The models of simulated lenses in \cite{2015MNRAS.447.2170K} showed a
-tendency to be too shallow.  Allowing smaller mass tiles in the
-central region, thus allowing the mass profile to rise more steeply
-near the centre, was suggested as a possible cure.
-
-Figure~\figref{subsampling} shows an experiment with smaller mass
-tiles in the inner region.  Replacing the very central mass tile with
-9 smaller tiles allows for steeper central profiles.  Doing the same
-for the 25 innermost mass tiles solves the problem completely, but
-increases the number of mass tiles by 40\% and significantly increases
-the computational time.
-% 689 / 489 = 1.40899; in practice, runtime is more like x4 - x5!
-% runtimes from logfiles: 87/22, 86/21, 85/16
-The main modelling work in this paper was, however, done before the
-experiments with smaller mass tiles was complete.  Some of the models
-presented in this paper apply the intermediate option (corresponding
-to the middle panel in Figure~\figref{subsampling}) while others use
-the old system.  The results in this paper, however, mainly concern
-the enclosed mass in the outer regions, so shallowness in the central
-region should be inconsequential.
-
-\subsection{Parameterisation of pixel models} \label{subsec:parameter}
-In order to fit the set of pixelated models to a single parameterised model, a program was written that took a parameterised function and subtracted from it the mean and the principal components of the data, which were calculated using classical Principal Component Analysis.
-This created the residuals function.
-The number of components used in the analysis was varied, to test how this affected the output, and it was found that using 5 principle components tended to give a reasonable approximation.
-A masking function was added which selected only the data points that fell inside the image of the lens, and the principal components were clipped in order to keep the values inside the region of the ensemble of models.
-Any value higher than the clip was set to be the clip value.
-This was chosen to be 2.5 as, assuming that the data follows a Gaussian error distribution, almost all the values for the variance should lie between 2 and 3 standard deviations from the mean.
-Minimising the residuals function produces the set of parameters that fit the parameterised function to the original pixelated ensemble most closely.
-A least squares fit was used to perform this minimisation.
-The parameterised model function was obtained from the gravitational potential of an isothermal ellipsoid mass distribution \citep{2001astro.ph..2341K}.
-This model is frequently used to describe gravitational lenses as it tends to fit well with observations.
-The isothermal ellipsoid model outputs three useful parameters: the radius of the Einstein ring, the ellipticity of the model and the angle of the ellipticity from the vertical, giving the orientation of the galaxy.
-By applying this model to simulated lenses for which the values of these parameters were already known, it was possible to gain an estimate of the projected accuracy of the results, before applying the model to the candidate lensing galaxies.
-
-Preliminary results on recovery of Einstein radii are shown in
-Figure~\ref{fig:parameter}. \todo{Einstein radii from parametric
-  model-fitting.}
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{img/rE_comp/rE_comp.png}
-  \caption{Comparison of Einstein radii. {\em To be extended.}}
-  \label{fig:parameter}
-\end{figure}
-
-\section{TODO}
-\listoftodos
+\input parts/app.tex
 
@@
 \end{document}
-
-% \begin{figure}
-%   \inclfign{SW05}{ASW0007k4r_N7LTELSYTM}
-%   \caption{Model results for SW05 (J143454.4+522850).  See text in
-%     Section~\ref{sec:examples} for details.}
-%   \label{fig:SW05}
-% \end{figure}
-% 
-% \begin{figure}
-%   \inclfign{SW28}{ASW0007xrs_JHC3J2HYV7}
-%   \caption{Model results for SW28 (J143055.9+572431).}
-%   \label{fig:SW28}
-% \end{figure}
-% 
-% \begin{figure}
-%   \inclfign{SW02}{ASW000619d_011489}
-%   \caption{Model results for SW02 (J140522.2+574333).}
-%   \label{fig:SW02}
-% \end{figure}
-% 
-% \begin{figure}
-%   \inclfign{SW09}{ASW0002asp_5EKMWWVJHL}
-%   \caption{Model results for SW09 (J020832.1-043315).}
-%   \label{fig:SW09}
-% \end{figure}
-% 
-% \begin{figure}
-%   \inclfign{SW29}{ASW0008qsm_TOFS7JNGEK}
-%   \caption{Model results for SW29 (J143838.1+572647).}
-%   \label{fig:SW29}
-% \end{figure}
-% 
-% \begin{figure}
-%   \inclfig{SW42}{ASW00096rm_4Q3YCEWGLN}
-%   \caption{Modelling results for SW42 (J221716.5+015826).}
-%   \label{fig:SW42}
-% \end{figure}
-% 
-% \begin{figure}
-%   \inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
-%   \caption{Model results for SW58 (J143651.6+530705).}
-%   \label{fig:SW58}
-% \end{figure}
-% 
-% \begin{figure}
-%   \inclfig{SW19}{ASW0001ld7_OS3CYAKLRT}
-%   \caption{Model results for SW19 (J020642.0-095157).}
-%   \label{fig:SW19}
-% \end{figure}
-% 
-% 
-% \begin{figure}
-%   \inclfig{SW36}{ASW000096t_7IPP7LWVOF}
-%   \caption{Model results for SW36 (J090248.4-010232).}
-%   \label{fig:SW36}
-% \end{figure}
-% 
-% \begin{figure}
-%   \inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
-%   \caption{Model results for SW57 (J143631.5+571131).}
-%   \label{fig:SW57}
-% \end{figure}

### 2016-10-03 parts/app.tex
slowly fixing figure refs

--- 2016-07-28 paper2.tex
@@
-\documentclass[fleqn,usenatbib]{mnras}
+\section{Developments in SpaghettiLens}
 
-%%% DEBUG SETTINGS - remove at the end %%%%%%%%%%%%%%%
-\usepackage{silence} % silence error warinings
-\WarningFilter{caption}{Unsupported document class} % caption doesn't know mnras..
-\hbadness = 5000
-\vbadness = 10000
-% \usepackage{}
-
-% MNRAS is set in Times font. If you don't have this installed (most LaTeX
-% installations will be fine) or prefer the old Computer Modern fonts, comment
-% out the following line
-%\usepackage{newtxtext,newtxmath} % not yet supported on arxiv and uni computer
-%\usepackage{txfonts}
-
-% Depending on your LaTeX fonts installation, you might get better results with one of these:
-%\usepackage{mathptmx}
-%\usepackage{txfonts}
-
-% Use vector fonts, so it zooms properly in on-screen viewing software
-% Don't change these lines unless you know what you are doing
-\usepackage[T1]{fontenc} % make sure font is supported
-% \usepackage{ae,aecompl} %obsolete when using modern fonts
-\usepackage[final]{microtype} % make sure font is supported
-% and a suitable font
-\usepackage{lmodern} % use a modern font with T1 support
-%\usepackage{cm-super} % use a modern font with T1 support
-
-%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
-
-% Only include extra packages if you really need them. Common packages are:
-%\usepackage[dvipdfmx]{graphicx}	% Including figure files
-\usepackage{graphicx} % Including figure files
-%\usepackage[skip=0pt]{subcaption}
-\usepackage{amsmath}	% Advanced maths commands
-\usepackage{amssymb}	% Extra maths symbols
-\usepackage{pifont}	% Extra maths symbols
-%\usepackage{bmpsize}  % PS still needs this for correct bounding boxes?
-
-% TODO stuff, comment out for final submit
-\usepackage{todonotes} % as long as we are editing...
-%\usepackage{showframe} % for debug
-%\overfullrule=5pt      % show overfull boxes
-
-% I disabled hyperlink in the cls und included it here because of bugs
-\usepackage{hyperref}   % Hyperlinks
-\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,filecolor=blue,urlcolor=blue}
-
-\edef\smallwidth{0.4\linewidth}
-
-\newcommand{\inclfig}[2]{
-  \centering
-	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img3_ipol}
-%	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
-        \includegraphics[width=\smallwidth]{img/arrival_spaghetti/#1_#2_arrival_spaghetti}%
-%        \includegraphics[width=\smallwidth]{spaghetti/#2_img2}
-        \includegraphics[width=\smallwidth]{img/kappa_map/#1_#2_kappa_map}
-	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
-	\includegraphics[width=\smallwidth]{img/mlens_vs_mstel/#1_#2_mstel_vs_mtot}
-}
-
-\newcommand{\inclfign}[2]{
-  \centering
-	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
-	\includegraphics[width=\smallwidth]{img/nsynth/#2_nsynth}
-%        \includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
-        \includegraphics[width=\smallwidth]{img/arrival_spaghetti/#1_#2_arrival_spaghetti}%
-%	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
-        \includegraphics[width=\smallwidth]{img/kappa_map/#1_#2_kappa_map}
-	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
-	\includegraphics[width=\smallwidth]{img/mlens_vs_mstel/#1_#2_mstel_vs_mtot}
-}
-
-\newcommand*{\rot}{\rotatebox{90}}
-\newcommand*{\OK}{\ding{51}}
-\newcommand*{\NO}{\ding{55}}
-
-\newcommand{\lenstitle}[1]{\noindent\textbf{#1} --}
-\newcommand{\params}[3]{(\(\Theta_\text{E}:#1\), $\varepsilon:#2$, $\alpha_\varepsilon:#3$ )}
-
-\newcommand{\asw}[1]{ASW000#1}
-\newcommand{\sw}[1]{SW~#1}
-\newcommand{\model}[1]{SL model~#1}
-
-\newcommand{\figref}[1]{\ref{fig:#1}}
-
-\newcommand{\Mstel}{M_{\rm stel}}
-\newcommand{\Mhalo}{M_{\rm h}}
-\newcommand{\haloindex}{\mathcal{H}}
-\newcommand{\ER}{$\Theta_{\text{E}}$} % einstein radius
-
-\title[Lens models for Space Warps CFHTLS]{Models of lens candidates from
-  Space Warps CFHTLS}
-
-\author[K\"ung et al]{Rafael K\"ung,$^{1}$
-Prasenjit Saha,$^{1}$
-Ignacio Ferreras,$^{2}$
-Elisabeth Baeten,$^{3}$
-\newauthor
-Jonathan Coles,$^{4}$
-Claude Cornen,$^{3}$
-Christine Macmillan,$^{3}$
-Phil Marshall,$^{5}$ 
-\newauthor
-Anupreeta More,$^{6}$
-Lucy Oswald$^{7}$
-Aprajita Verma$^{8}$
-and Julianne K. Wilcox$^{4}$
-%
-\\
-%
-$^{1}$Physik-Institut, University of Zurich, Winterthurerstrasse 190, 8057 Zurich, Switzerland\\
-$^{2}$Mullard Space Science Laboratory, University College London, Holmbury St Mary, Dorking, Surrey RH5 6NT, UK\\
-$^{3}$Zooniverse, c/o Astrophysics Department, University of Oxford, Oxford OX1 3RH, UK \\
-$^{4}$Exascale Research Computing Lab, Campus Teratec, 2 Rue de la Piquetterie, 91680 Bruyeres-le-Chatel, France\\
-$^{5}$Kavli Institute for Particle Astrophysics and Cosmology, Stanford University, 452 Lomita Mall, Stanford, CA 94035, USA\\
-$^{6}$Kavli Institute for the Physics and Mathematics of the Universe, University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa-shi 277-8583, Japan\\
-$^{7}$Murray Edwards College, University of Cambridge, Cambridge CB3 0DF, UK\\
-$^{8}$Sub-department of Astrophysics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
-}
-
-% These dates will be filled out by the publisher
-% \date{Accepted XXX. Received YYY; in original form ZZZ}
-
-% Enter the current year, for the copyright statements etc.
-\pubyear{2016}
-
-% Don't change these lines
-\begin{document}
-\label{firstpage}
-\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\maketitle
-
-\begin{abstract}
-We report modelling follow-up of recently-discovered
-gravitational-lens candidates in the CFHT Legacy Survey.  Lens
-modelling was done by a small group of specially-interested volunteers
-from the Space~Warps citizen-science community who originally found
-the candidate lenses.  Models are categorised according to seven
-qualitative and quantitive points.  Also included are some
-improvements to the modelling software used (SpaghettiLens),
-and discussion of strategies for scaling to future surveys
-with more and frequent discoveries.
-
-The candidates successfully modelled are all galaxies, with inferred
-lensing masses ranging from $\sim10^{11}M_\odot$ to $>10^{13}M_\odot$.
-Stellar masses have also been estimated, using photometry from the
-CFHTLS pipeline and stellar-population models.  A trend well-known
-in nearby galaxies, that star-formation efficiency is maximal for
-total masses of $\approx10^{12}M_\odot$ and reduces for both lower and
-higher masses, is discernable also in these much more distant
-galaxies.
-\end{abstract}
-
-\begin{keywords}
-gravitational lensing: strong -- keyword2
-\end{keywords}
-
-\section{Introduction}
-
-Light deflection at the rim of the Sun is famously $1.75''$.  The
-deflection angle can also be expressed in terms of the escape velocity
-$2v_{\rm esc}^2/c^2$, with $v_{\rm esc}$ at the solar surface being
-$\simeq620\rm\,km/s$.  The Galactic escape velocity at the Sun's
-location is similar: $\approx500\rm\,km/s$, typical of massive
-galaxies.  Thus, the outer regions of massive galaxies have lensing
-deflections comparable to that at the rim of the Sun.  Yet these
-quantitatively similar deflections have qualitatively different
-consequences.  Light deflection by the Sun must be accounted for in
-modern astrometry \citep[see e.g.,][]{2015CQGra..32p5008C} but is not
-itself a physics probe in the way it was a century ago.  With distant
-galaxies, however, light bending by $\sim1''$ introduces two new
-phenomena.  First, for galaxies distant enough that their apparent
-size is comparable to the bending angle, light deflection can cause
-multiple images of background sources, or strong lensing.  Second, the
-gravitational field is dominated by dark matter, hence strong lensing
-becomes a probe of dark matter in galaxies.
-
-With no unambiguous dark-matter particle detections so far, dark
-matter has studied only through its indirect consequences on galactic
-and larger scales.  In most work, dark matter is taken to be a
-collisionless non-relativistic fluid (cold dark matter or CDM); in
-recent years, the simulation by \cite{2005Natur.435..629S} has been
-particularly influential in studying the formation of CDM structures.
-Other scenarios have also been considered, such as a cold condensing
-boson fluid \citep{2016ApJ...818...89S}.  There is a general
-consensus, however, that the origins of galaxy lie in the
-gravitational collapse, fragmentation, and mergers of dark-matter
-clumps, into which fell gas, cooling through radiative processes to
-form dense clouds and eventually stars.  There is, however, much
-debate about the details, of which \cite{2012RAA....12..917S} provide
-a nice summary.
-
-Strong-lensing galaxies are a useful source of information on the
-mutual dynamics and dark matter and gas in galaxies.  The topic has
-been explored in several studies
-\citep{2009ApJ...703L..51K,2011ApJ...740...97L,2012MNRAS.424..104L,
-  2016MNRAS.459.3677L,2016MNRAS.456..870B} but it is desirable to
-enlarge the samples from tens of lensing galaxies to thousands.  Doing
-so requires finding more lenses, of course, but also modelling their
-masses.
-
-Recent searches through the CFHTLS \citep{2012SPIE.8448E..0MC} using
-arc-finders
-\citep{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G} by
-machine learning \citep{2016arXiv160504309P} and by visual inspection
-by a citizen-science volunteers
-\citep[Space~Warps][]{2016MNRAS.455.1191M} have between them
-discovered an average of four lenses per square degree.  So one can be
-optimistic about finding many thousands of lenses in the next
-generation of wide-field surveys.  The expected flood of new lens
-discoveries will need a similarly huge modelling effort to
-reconstruct their mass distributions.  To prepare for the challenge of
-massive-sample lens modelling, \cite{2015MNRAS.447.2170K} developed a
-new modelling strategy, implemented as the SpaghettiLens system.  The
-idea is to collaborate with experienced members of the citizen-science
-community, who have already participated in lens discovery through
-Space~Warps, as well as several other projects involving astronomical
-data.  In this paper, we present SpaghettiLens models of
-lens-candidates discovered through Space~Warps.
-
-Section~\ref{sec:spl} summarises the SpaghettiLens system and
-discusses its ongoing development. A SpaghettiLens model consists of a
-statistical ensemble of free-form maps of the sky-projected mass
-distribution responsible for lensing.  Each lens candidates in
-practice gets modelled several times in a collaborative refinement
-process\footnote{See ``Collaborative gravitational lens
-  modelling\dots'' in {\tt http://letters.zooniverse.org} especially
-  the model tree.}  In this paper we report the most recent model for
-each lens, as representing a consensus among modellers, as to the best
-that could be achieved with the available data and software.
-Photometric lens redshifts are used; source redshifts are set to
-$z=2$ unless an unambiguous photometric redshift is available.
-The models can, however, be trivially rescaled to use better
-redshift values, as and when they become available.
-\cite{2015MNRAS.447.2170K} tested the system on simulated lenses and
-identified some areas for improvement.  The first two of those are
-taken up in Section~\ref{sec:spl}, along with a further idea. In
-\S~\ref{subsec:sourcefit} we introduce fitting of the brightness
-profiles of the source.  This feature has not yet been included in
-SpaghettiLens, but has been carried out in post-processing for a few
-especially interesting candidates.  In \S~\ref{subsec:hires} we show
-that making mass maps fine-grained in the central region relieves a
-tendency in the earlier work for mass to be too shallow. Then in
-\S~\ref{subsec:parameter} we consider the possibility of fitting a
-parametric lens model to the model ensemble; so far we have only been
-successful at extracting an Einstein radius.
-
-Section~\ref{sec:stellar-mass} explains how we compare the lensing
-mass with the mass in stars in the lensing galaxy.  We estimate the
-stellar mass by comparing galaxy magnitudes from the CFHTLS pipeline
-with the well-known stellar-population models of
-\cite{2003MNRAS.344.1000B}.  We then extrapolate the stellar masses to
-a halo mass using the abundance-matching prescription of
-\cite{2010ApJ...710..903M}.  Naturally, the lensing mass must be more
-than the stellar mass but no more than the total halo mass.  We then
-introduce what we call a halo index $\haloindex$ which gives an idea
-of how the lensing mass compares with these two bounds.
-
-Section~\ref{sec:examples} discusses ten of the systems, including six
-systems we found to be particularly interesting.  The online
-supplement gives results for all the modelled systems.
-
-In Section~\ref{sec:summary} and Table~\ref{tab:models} we display a
-concise characterisation of each modelled system, according to the
-image morphology and how clear or indistinct it is, whether the mass
-map and synthetic lensed image appear to be plausible, and how the
-model mass compares with the estimated stellar and full-halo masses.
-
-\section{Lens Modelling}\label{sec:spl}
-
-SpaghettiLens is an example of a medium-sized collaboration spawned by
-a large citizen-science project (in this case Space~Warps).  While
-collaboration with volunteers is essential to both, the form of
-collaboration is very different.  In Space~Warps, volunteers in a
-crowd of $\gtrsim10^4$ make independent contributions.  Each person is
-presented with a random selection of survey-patches and invited to (in
-effect) vote on each.  The system estimates each volunteer's skill
-level according to test-patches interspersed with the real data, and
-weights their votes accordingly \citep{2016MNRAS.455.1171M}.  There is
-an active forum for volunteers, but since everyone is seeing different
-data samples with minimal overlap, the forum has little if any
-influence on votes.  With SpaghettiLens, on the other hand, there is a
-small group of volunteers and their contributions are interdependent.
-
-A modeller's main input to SpaghettiLens is a sketch of arrival-time
-contours on a lensed system.  It gives the locations (or best-guess
-locations) of images of point-like sources, along with their ordering
-in arrival time, and their parities (minumum, saddle-point or
-maximum).  Such a sketch, which we call a spaghetti diagram, tends to
-resemble the form of lensed arcs, but it also in effect 
-encodes a proposal for its mass distribution.  A spaghetti diagram is
-read by a server-side numerical engine \citep[GLASS, developed
-  by][]{2014MNRAS.445.2181C} which then returns a statistical ensemble
-of mass maps.  The mass maps are made up of mass tiles and are
-free-form, except that they are required to be concentrated around the
-identified lens centre.  They are also required to reproduce the given
-image locations, parities and time ordering exactly.  Graphical
-representations of the mass map and arrival-time surface are returned
-to the user for review.  The user can post these results on a forum,
-or discard them and try again.  Volunteers can start the modelling
-process afresh, or they can take an existing model from the forum and
-modify its input spaghetti diagram or its accompanying options, and
-thus obtain a revised model.
-
-\subsection{Improved synthetic images}\label{subsec:sourcefit}
+\subsection{Improved synthetic images}
 
@@
   \label{fig:synthimg}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_11_hires_comparison}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_13_hires_comparison}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_33_hires_comparison}
-  \caption{Model improvement resulting from using smaller mass tiles
-    in the inner region of the mass model.  Shown here are the average
-    enclosed $\kappa$ within a given projected radius, for three
-    different reconstructions of a simulated lens (sim) from
-    Space~Warps.  In each panel, the dashed blue curve is the correct
-    answer.  The orange band represents the statistical ensemble from
-    SpaghettiLens, the orange line being the ensemble mean.  Locations of
-    images (maximum, saddle point, minimum) are marked with vertical
-    arrows.  Crossing the horizontal $\kappa=1$ line is the effective
-    Einstein radius \ER, and is so labelled. The upper panel is from
-    K\"ung et al., (2015) (see Figure~3 of that paper).  The middle
-    panel is the result when the innermost mass tile is replaced by 9
-    smaller tiles.  The lower panel results from replacing each of the
-    innermost 5 by 5 tiles each with 9 smaller tiles.}
-  \label{fig:subsampling}
 \end{figure}
@@
 
+\begin{figure}
+  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_11_hires_comparison}
+  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_13_hires_comparison}
+  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_33_hires_comparison}
+  \caption{Model improvement resulting from using smaller mass tiles
+    in the inner region of the mass model.  Shown here are the average
+    enclosed $\kappa$ within a given projected radius, for three
+    different reconstructions of a simulated lens (sim) from
+    Space~Warps.  In each panel, the dashed blue curve is the correct
+    answer.  The orange band represents the statistical ensemble from
+    SpaghettiLens, the orange line being the ensemble mean.  Locations of
+    images (maximum, saddle point, minimum) are marked with vertical
+    arrows.  Crossing the horizontal $\kappa=1$ line is the effective
+    Einstein radius \ER, and is so labelled. The upper panel is from
+    K\"ung et al., (2015) (see Figure~3 of that paper).  The middle
+    panel is the result when the innermost mass tile is replaced by 9
+    smaller tiles.  The lower panel results from replacing each of the
+    innermost 5 by 5 tiles each with 9 smaller tiles.}
+  \label{fig:subsampling}
+\end{figure}
+
 \subsection{Parameterisation of pixel models} \label{subsec:parameter}
-In order to fit the set of pixelated models to a single parameterised model, a program was written that took a parameterised function and subtracted from it the mean and the principle components of the data, which were calculated using classical Principle Component Analysis.
+
+In order to fit the set of pixelated models to a single parameterised model, a program was written that took a parameterised function and subtracted from it the mean and the principal components of the data, which were calculated using classical Principal Component Analysis.
 This created the residuals function.
-The number of components defined as principle was varied to test how this affected the output, and it was found that using 5 principle components tended to give a reasonable approximation.
+The number of components used in the analysis was varied, to test how this affected the output, and it was found that using 5 principle components tended to give a reasonable approximation.
 A masking function was added which selected only the data points that fell inside the image of the lens, and the principal components were clipped in order to keep the values inside the region of the ensemble of models.
@@
 A least squares fit was used to perform this minimisation.
-The parameterised model function was obtained from the gravitational potential of an isothermal ellipsoid mass distribution \cite{2001astro.ph..2341K}.
+The parameterised model function was obtained from the gravitational potential of an isothermal ellipsoid mass distribution \citep{2001astro.ph..2341K}.
 This model is frequently used to describe gravitational lenses as it tends to fit well with observations.
@@
 \end{figure}
-
-\section{Stellar mass}\label{sec:stellar-mass}
-
-Based on \cite{2003MNRAS.344.1000B} models.\todo{Description of
-  stellar-population models.}
-
-Following \cite{2010ApJ...710..903M}
-\begin{equation}
-\begin{aligned}
-\frac{\Mstel}{\Mhalo} &= \frac{2C_0}{(\Mhalo/M_1)^{-\beta} +
-                                     (\Mhalo/M_1)^\gamma} \\
-C_0 &= 0.02820, \quad M_1 = 10^{11.884} M_\odot \\
-\beta &= 1.057, \quad \gamma = 0.556.
-\end{aligned}
-\end{equation}
-
-\begin{equation}
-\haloindex = \frac{\ln(M/\Mstel)}{\ln(\Mhalo/\Mstel)}
-\end{equation}
-which we may call the halo-matching index.
-\begin{itemize}
-\item $\haloindex < 0$ is unphysical because $M<\Mstel$.
-\item $\haloindex = 0$ is when the stellar mass exactly accounts for the
-  lensing mass.
-\item $0 < \haloindex < 1$ is the typical situation, where the lens
-  includes stars and dark matter, but not the full halo.
-\item $\haloindex = 1$ means that the lens consists of the entire halo.
-\item $\haloindex > 1$ is in tension with abundance-matching, because the
-  lensing mass exceeds the expected halo mass.
-\end{itemize}
-
-\section{Example systems}\label{sec:examples}
-
-In this section we show modelling results for ten of the lens
-candidates.  The first five (see Figures~\figref{SW05}--\figref{SW29})
-are the most convincingly modelled systems.  The next three cases
-(Figures~\figref{SW42}--\figref{SW19}) are less good but still very
-plausible models, and are representative of the majority of the
-sample.  The last two are examples where the models were unconvincing
-(Figures~\figref{SW36}) or completely failed (\figref{SW57}).
-
-\begin{figure}
-  \inclfign{SW05}{ASW0007k4r_N7LTELSYTM}
-  \caption{Model results for SW05 (J143454.4+522850).  See text in
-    Section~\ref{sec:examples} for details.}
-  \label{fig:SW05}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW28}{ASW0007xrs_JHC3J2HYV7}
-  \caption{Model results for SW28 (J143055.9+572431).}
-  \label{fig:SW28}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW02}{ASW000619d_011489}
-  \caption{Model results for SW02 (J140522.2+574333).}
-  \label{fig:SW02}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW09}{ASW0002asp_5EKMWWVJHL}
-  \caption{Model results for SW09 (J020832.1-043315).}
-  \label{fig:SW09}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW29}{ASW0008qsm_TOFS7JNGEK}
-  \caption{Model results for SW29 (J143838.1+572647).}
-  \label{fig:SW29}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW42}{ASW00096rm_4Q3YCEWGLN}
-  \caption{Modelling results for SW42 (J221716.5+015826).}
-  \label{fig:SW42}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
-  \caption{Model results for SW58 (J143651.6+530705).}
-  \label{fig:SW58}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW19}{ASW0001ld7_OS3CYAKLRT}
-  \caption{Model results for SW19 (J020642.0-095157).}
-  \label{fig:SW19}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW36}{ASW000096t_7IPP7LWVOF}
-  \caption{Model results for SW36 (J090248.4-010232).}
-  \label{fig:SW36}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
-  \caption{Model results for SW57 (J143631.5+571131).}
-  \label{fig:SW57}
-\end{figure}
-
-Let us first consider Figure~\figref{SW05}, which shows model results
-from SW05 (J143454.4+522850).
-
-\begin{enumerate}
-\item In the upper row we have first a cutout of the Space~Warps
-  image, marked up with a spaghetti diagram.  There are four distinct
-  lensed images, and the spaghetti diagram proposes that they are a
-  minimum nearest to the lensing galaxy, a close minimum-saddle pair,
-  and a minimum further away. In Table~\ref{tab:models} we refer to
-  such configurations as IQ for inclined quad.
-\item Alongside is a synthetic image produced by modelling.  In it,
-  the fitted lensed images are shown in colour, while the lensing
-  galaxy and extraneous objects have been reduced to grayscale.
-  (Figure~\figref{synthimg} in \S~\ref{subsec:sourcefit} shows a
-  synthetic image from another model of the same system.) These two
-  panels are qualitative and display no units, and moreover, the
-  mutual alignment of the two panels is only approximate.
-\item The middle row shows contour maps from the model.  At middle
-  left, we have the arrival-time surface.
-\item At middle right we have the mass distribution in the usual
-  dimensionless form $\kappa$.  Again, these two panels are mainly
-  qualitative: both panels are spatially registered and centred on the
-  density-peak of the lens, but no scales have been included.
-\item The base row supplies spatial and mass scales.  The left panel
-  shows the circularly-averaged $\kappa$ of the model ensemble, with
-  increasing radius (in arcsec).  The four short vertical lines
-  correspond to the minima and saddle points marked in the upper-left
-  panel.  The effective Einstein radius \ER is also shown.  As the radius
-  scale indicates SW05 is comparatively large lens on the
-  sky.
-\item Lower right shows the total mass in the model against the
-  estimated stellar mass, alongside the values for the whole sample.
-  The lower-right shaded region is unphysical according to the
-  stellar-population models, because it gives $M<\Mstel$. The
-  upper-left shaded region is unphysical according to abundance
-  matching, because it gives $M>\Mhalo$.  That is to say, the unshaded
-  region is $0<\haloindex<1$.
-\end{enumerate}
-
-Proceeding to Figure~\figref{SW28}, we have one image close to the
-galaxy and an arc further away, which is interpreted as a blend of
-three images (a saddle point with two minima on either side).  We call
-this a long-axis quad or LQ configuration.  It is an indication of a
-mass distribution elongated along the arc-counterimage direction
-(along EW in this case).
-
-In Figures~\figref{SW02}--\figref{SW29} we see three candidates with
-an arc close the lensing galaxy and one image further away.  The arc
-is interpreted three images (a minimum with two saddle points on
-either side).  We call this a short-axis quad or SQ configuration.  It
-is an indication of a mass distribution elongated perpendicular to the
-arc-counterimage direction.
-
-Figures~\figref{SW02}--\figref{SW29} (SW05, SW28, SW02, SW09 and SW29)
-all correspond to the mass range of massive ellipticals.  SW05 is the
-most massive of all the candidates, with a galaxy-group scale mass.
-
-Figure~\figref{SW42} shows SW42.  The image morphology is similar to
-SW05 in Figure~\figref{SW05}, but the lens is much smaller on the sky,
-and the inferred mass is at the low end of the sample.  (The synthetic
-image shown is cruder than for the five previous figures, but that
-does not influence the mass models.)  If these preliminary findings
-are confirmed by follow-up observations, this could be the most
-dark-matter dominated lens known.\todo{Check photometry of this
-  candidate.}
-
-Figures~\figref{SW58} and \figref{SW19} appear plausible lens
-candidates.  Their morphology is similar to SW28, but the saddle-point
-counterimage is not visible.  We consider these lenses plausible but
-less convincing.
-
-Figures~\figref{SW36} and \figref{SW57} are cases where modelling
-failed.
-
-\section{Summary of models}\label{sec:summary}
-
-Table~\ref{tab:models} shows a summary of the analysis for many candidates.
-Missing rows are due to photometry data not available.
-
-\begin{enumerate}
-\item The image morphology concisely described: D for double, and
-  quads in sub-categorised in four ways
-  \citep[cf.][]{2003AJ....125.2769S} as LQ for long-axis quads (as in
-  Figure~\figref{SW28}), SQ for short-axis quads (as in
-  Figure~\figref{SW02}, \figref{SW09}, \figref{SW29}, \figref{SW42}),
-  IQ for inclined quads (as in Figure~\figref{SW05}) and CQ for very
-  symmetric core quads.
-\item Whether the images are unblended.  Distinct unblended images (as
-  in Figures~\figref{SW05} and \figref{SW42}) are an advantage in
-  modelling, but not essential.
-\item Whether all images are discernable.  The topography of an
-  arrival-time surface, as encoded by a spaghetti diagram, may require
-  more images than are visible.  For example, in Figure~\figref{SW58},
-  the modeller has put in a conjectural saddle point near the lensing
-  galaxy.
-\item Whether the lens is fairly isolated.
-\item Whether the arrival-time surface and synthetic image are
-  plausible.  In Figure~\figref{SW36} the model implies extra images
-  or a long arc, which are not seen.
-\item Whether the mass map is reasonable.
-\item The halo index $\haloindex$.
-\end{enumerate}
-
-\begin{table*}
-  \caption{Categorisation of SW models}
-  \label{tab:models}
-  \include{table}
-\end{table*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% The best way to enter references is to use BibTeX:
-\bibliographystyle{mnras}
-\bibliography{bib/bibli} % if your bibtex file is called example.bib
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \appendix
-
-\clearpage
-
-\section{TODO}
-\listoftodos
-
-% Don't change these lines
-\bsp	% typesetting comment
-\label{lastpage}
-\end{document}

### 2016-10-03 parts/intro.tex
slowly fixing figure refs

@@
 
-\begin{enumerate}
+\begin{itemize}
+\item Morphology from Figure~\ref{fig:markedup}.
+\begin{itemize}
 \item The image morphology concisely described: D for double, and
@@
   \citep[cf.][]{2003AJ....125.2769S} as LQ for long-axis quads (as in
-  Figure~\figref{SW28}), SQ for short-axis quads (as in
-  Figure~\figref{SW02}, \figref{SW09}, \figref{SW29}, \figref{SW42}),
-  IQ for inclined quads (as in Figure~\figref{SW05}) and CQ for very
-  symmetric core quads.
+  SW28), SQ for short-axis quads (as in Figure~SW02,
+  SW09, SW29, SW42), IQ for inclined quads
+  (as in Figure~SW05) and CQ for very symmetric core quads.
 \item Whether the images are unblended.  Distinct unblended images (as
-  in Figures~\figref{SW05} and \figref{SW42}) are an advantage in
+  in Figures~SW05 and SW42) are an advantage in
   modelling, but not essential.
@@
   arrival-time surface, as encoded by a spaghetti diagram, may require
-  more images than are visible.  For example, in Figure~\figref{SW58},
+  more images than are visible.  For example, in Figure~SW58,
   the modeller has put in a conjectural saddle point near the lensing
@@
 \item Whether the lens is fairly isolated.
+\end{itemize}
+\item Mass model
+\begin{itemize}
 \item Whether the arrival-time surface and synthetic image are
-  plausible.  In Figure~\figref{SW36} the model implies extra images
-  or a long arc, which are not seen.
-\item Whether the mass map is reasonable.
-\item The halo index $\haloindex$.
-\end{enumerate}
+  plausible.  For SW36 the model implies extra images or a long arc,
+  which are not seen.  Figures~\ref{fig:arriv} and \ref{fig:synth}.
+\item Whether the mass map is reasonable. Figure~\ref{fig:kappa}.
+\end{itemize}
+\item Stellar mass. Figure~\ref{fig:stelmass}.
+\end{itemize}

### 2016-10-03 parts/massmodel.tex
slowly fixing figure refs

@@
 \begin{figure*}
+\includezehn{img/kappa_map/}{_kappa_map}
+\caption{\label{fig:kappa}}
+\end{figure*}
+
+\begin{figure*}
 \includezehn{img/arrival_spaghetti/}{_arrival_spaghetti}
+\caption{\label{fig:arriv}}
+\end{figure*}
+
+\begin{figure*}
+\includeten{img/nsynth/}{_nsynth}
+\label{fig:synth}
 \caption{}
@@
 
-\begin{figure*}
-\includezehn{img/kappa_map/}{_kappa_map}
-\caption{}
-\end{figure*}
+Alongside is a synthetic image produced by modelling.  In it, the
+fitted lensed images are shown in colour, while the lensing galaxy and
+extraneous objects have been reduced to grayscale.
+(Figure~\figref{synthimg} in \S~\ref{subsec:sourcefit} shows a
+synthetic image from another model of the same system.) These two
+panels are qualitative and display no units, and moreover, the mutual
+alignment of the two panels is only approximate.
 
@@
 \end{figure*}
+
+Figures~\figref{SW58} and \figref{SW19} appear plausible lens
+candidates.  Their morphology is similar to SW28, but the saddle-point
+counterimage is not visible.  We consider these lenses plausible but
+less convincing.
+
+Figures~\figref{SW36} and \figref{SW57} are cases where modelling
+failed.
+
+\begin{enumerate}
+\item The middle row shows contour maps from the model.  At middle
+  left, we have the arrival-time surface.
+\item At middle right we have the mass distribution in the usual
+  dimensionless form $\kappa$.  Again, these two panels are mainly
+  qualitative: both panels are spatially registered and centred on the
+  density-peak of the lens, but no scales have been included.
+\item The base row supplies spatial and mass scales.  The left panel
+  shows the circularly-averaged $\kappa$ of the model ensemble, with
+  increasing radius (in arcsec).  The four short vertical lines
+  correspond to the minima and saddle points marked in the upper-left
+  panel.  The effective Einstein radius \ER is also shown.  As the radius
+  scale indicates SW05 is comparatively large lens on the
+  sky.
+\item 
+\end{enumerate}

### 2016-10-03 parts/morph.tex
slowly fixing figure refs

@@
 
-Figure~\ref{fig:input} shows cutouts of the Space~Warps image, marked
-up with a spaghetti diagram.
+Figure~\ref{fig:markedup} shows cutouts of the Space~Warps image,
+marked up with a spaghetti diagram.
 
@@
 
-Figure~\ref{fig:input}
+We show modelling results for nine of the lens candidates.  The first
+five (see Figures~\figref{SW05}--\figref{SW29}) are the most
+convincingly modelled systems.  The next three cases
+(Figures~\figref{SW42}--\figref{SW19}) are less good but still very
+plausible models, and are representative of the majority of the
+sample.  The last two are examples where the models were unconvincing
+(Figures~\figref{SW36}) or completely failed (\figref{SW57}).
 
@@
 \includeten{spaghetti/}{_input}
-\label{fig:input}
-\caption{Marked-up images.}
+\caption{Marked-up images. \label{fig:markedup}}
 \end{figure*}

### 2016-10-03 parts/stelmass.tex
slowly fixing figure refs

@@
 \includegraphics[width=\linewidth]{img/mlens_vs_mstel_one/mstel_vs_mtot_one}
-\caption{}
+\caption{Total mass in the model against the estimated stellar mass,
+  alongside the values for the whole sample.  The lower-right shaded
+  region is unphysical according to the stellar-population models,
+  because it gives $M<\Mstel$. The upper-left shaded region is
+  unphysical according to abundance matching, because it gives
+  $M>\Mhalo$.  That is to say, the unshaded region is
+  $0<\haloindex<1$. \label{fig:stelmass}}
 \end{figure*}
+
+SW05, SW28, SW02, SW09 and SW29 all correspond to the mass range of
+massive ellipticals.  SW05 is the most massive of all the candidates,
+with a galaxy-group scale mass.
+
+For SW42 the inferred mass is at the low end of the sample.  (The
+synthetic image shown is cruder than for the five previous figures,
+but that does not influence the mass models.)  If these preliminary
+findings are confirmed by follow-up observations, this could be the
+most dark-matter dominated lens known.\todo{Check photometry of this
+  candidate.}

### 2016-11-23 paper2.tex
figure changes

@@
 \def\includeten#1#2{
+\includegraphics[width=\pwidth]{#1ASW0007iwp_4XBJWT3COV#2}%
+\includegraphics[width=\pwidth]{#1ASW0007xrs_JHC3J2HYV7#2}%
+\includegraphics[width=\pwidth]{#1ASW0008pag_5SXGXQYY6V#2}\\
 \includegraphics[width=\pwidth]{#1ASW0007k4r_N7LTELSYTM#2}%
 \includegraphics[width=\pwidth]{#1ASW00096rm_4Q3YCEWGLN#2}%
-\includegraphics[width=\pwidth]{#1ASW0007xrs_JHC3J2HYV7#2}\\
-\includegraphics[width=\pwidth]{#1ASW0007iwp_4XBJWT3COV#2}%
-\includegraphics[width=\pwidth]{#1ASW000619d_011489#2}%
 \includegraphics[width=\pwidth]{#1ASW0001ld7_OS3CYAKLRT#2}\\
 \includegraphics[width=\pwidth]{#1ASW0002asp_5EKMWWVJHL#2}%
+\includegraphics[width=\pwidth]{#1ASW0008qsm_TOFS7JNGEK#2}%
+\includegraphics[width=\pwidth]{#1ASW000619d_011489#2}\\
 %\includegraphics[width=\pwidth]{#1ASW000096t_7IPP7LWVOF#2}%
-\includegraphics[width=\pwidth]{#1ASW0008qsm_TOFS7JNGEK#2}%
-\includegraphics[width=\pwidth]{#1ASW0008pag_5SXGXQYY6V#2}\\
 }
@@
 \def\includezehn#1#2{
-\includegraphics[width=\pwidth]{#1SW05_ASW0007k4r_N7LTELSYTM#2}%
-\includegraphics[width=\pwidth]{#1SW42_ASW00096rm_4Q3YCEWGLN#2}%
-\includegraphics[width=\pwidth]{#1SW28_ASW0007xrs_JHC3J2HYV7#2}\\
-\includegraphics[width=\pwidth]{#1SW58_ASW0007iwp_4XBJWT3COV#2}%
-\includegraphics[width=\pwidth]{#1SW02_ASW000619d_011489#2}%
-\includegraphics[width=\pwidth]{#1SW19_ASW0001ld7_OS3CYAKLRT#2}\\
-\includegraphics[width=\pwidth]{#1SW09_ASW0002asp_5EKMWWVJHL#2}%
-%\includegraphics[width=\pwidth]{#1SW36_ASW000096t_7IPP7LWVOF#2}\\
-\includegraphics[width=\pwidth]{#1SW29_ASW0008qsm_TOFS7JNGEK#2}%
-\includegraphics[width=\pwidth]{#1SW57_ASW0008pag_5SXGXQYY6V#2}\\
+\includegraphics[width=\pwidth]{#1SW58_ASW0007iwp_4XBJWT3COV#2}%   L
+\includegraphics[width=\pwidth]{#1SW28_ASW0007xrs_JHC3J2HYV7#2}%   L
+\includegraphics[width=\pwidth]{#1SW57_ASW0008pag_5SXGXQYY6V#2}\\% X
+\includegraphics[width=\pwidth]{#1SW05_ASW0007k4r_N7LTELSYTM#2}%   I
+\includegraphics[width=\pwidth]{#1SW42_ASW00096rm_4Q3YCEWGLN#2}%   I
+\includegraphics[width=\pwidth]{#1SW19_ASW0001ld7_OS3CYAKLRT#2}\\% I
+\includegraphics[width=\pwidth]{#1SW09_ASW0002asp_5EKMWWVJHL#2}%   S
+\includegraphics[width=\pwidth]{#1SW29_ASW0008qsm_TOFS7JNGEK#2}%   S
+\includegraphics[width=\pwidth]{#1SW02_ASW000619d_011489#2}\\%     S
+%\includegraphics[width=\pwidth]{#1SW36_ASW000096t_7IPP7LWVOF#2}%
 }
@@
 
-\begin{table*}
-  \caption{Categorisation of SW models}
-  \label{tab:models}
-  \include{table}
-\end{table*}
+\clearpage
+
+\input parts/summary
 
@@
 
-% The best way to enter references is to use BibTeX:
 \bibliographystyle{mnras}
-\bibliography{bib/bibli} % if your bibtex file is called example.bib
+\bibliography{bib/bibli}
 
@@
 
-\section{TODO}
-\listoftodos
-
-\clearpage
+% \section{TODO}
+% \listoftodos
 

### 2016-11-23 parts/intro.tex
figure changes

@@
 
+\begin{itemize}
+\item Morphology from Figure~\ref{fig:markedup}.
+\begin{itemize}
+\item The image morphology concisely described: D for double, and
+  quads in sub-categorised in four ways
+  \citep[cf.][]{2003AJ....125.2769S} as LQ for long-axis quads (as in
+  SW28), SQ for short-axis quads (as in Figure~SW02,
+  SW09, SW29, SW42), IQ for inclined quads
+  (as in Figure~SW05) and CQ for very symmetric core quads.
+\item Whether the images are unblended.  Distinct unblended images (as
+  in Figures~SW05 and SW42) are an advantage in
+  modelling, but not essential.
+\item Whether all images are discernable.  The topography of an
+  arrival-time surface, as encoded by a spaghetti diagram, may require
+  more images than are visible.  For example, in Figure~SW58,
+  the modeller has put in a conjectural saddle point near the lensing
+  galaxy.
+\item Whether the lens is fairly isolated.
+\end{itemize}
+\item Mass model
+\begin{itemize}
+\item Whether the mass map is reasonable. Figure~\ref{fig:kappa}.
+\item Whether the arrival-time surface and synthetic image are
+  plausible.  For SW36 the model implies extra images or a long arc,
+  which are not seen.  Figures~\ref{fig:arriv} and \ref{fig:synth}.
+\end{itemize}
+\item Stellar mass. Figure~\ref{fig:stelmass}.
+\end{itemize}
+
 Section~\ref{sec:spl} summarises the SpaghettiLens system and
@@
 supplement gives results for all the modelled systems.
-
-In Section~\ref{sec:summary} and Table~\ref{tab:models} we display a
-concise characterisation of each modelled system, according to the
-image morphology and how clear or indistinct it is, whether the mass
-map and synthetic lensed image appear to be plausible, and how the
-model mass compares with the estimated stellar and full-halo masses.
-
-Table~\ref{tab:models} shows a summary of the analysis for many candidates.
-Missing rows are due to photometry data not available.
-
-\begin{itemize}
-\item Morphology from Figure~\ref{fig:markedup}.
-\begin{itemize}
-\item The image morphology concisely described: D for double, and
-  quads in sub-categorised in four ways
-  \citep[cf.][]{2003AJ....125.2769S} as LQ for long-axis quads (as in
-  SW28), SQ for short-axis quads (as in Figure~SW02,
-  SW09, SW29, SW42), IQ for inclined quads
-  (as in Figure~SW05) and CQ for very symmetric core quads.
-\item Whether the images are unblended.  Distinct unblended images (as
-  in Figures~SW05 and SW42) are an advantage in
-  modelling, but not essential.
-\item Whether all images are discernable.  The topography of an
-  arrival-time surface, as encoded by a spaghetti diagram, may require
-  more images than are visible.  For example, in Figure~SW58,
-  the modeller has put in a conjectural saddle point near the lensing
-  galaxy.
-\item Whether the lens is fairly isolated.
-\end{itemize}
-\item Mass model
-\begin{itemize}
-\item Whether the arrival-time surface and synthetic image are
-  plausible.  For SW36 the model implies extra images or a long arc,
-  which are not seen.  Figures~\ref{fig:arriv} and \ref{fig:synth}.
-\item Whether the mass map is reasonable. Figure~\ref{fig:kappa}.
-\end{itemize}
-\item Stellar mass. Figure~\ref{fig:stelmass}.
-\end{itemize}

### 2016-11-23 parts/summary.tex
figure changes

--- 2016-07-26 paper2.tex
@@
-\documentclass[fleqn,usenatbib]{mnras}
+\section{Summary of models}
 
-%%% DEBUG SETTINGS - remove at the end %%%%%%%%%%%%%%%
-\usepackage{silence} % silence error warinings
-\WarningFilter{caption}{Unsupported document class} % caption doesn't know mnras..
-\hbadness = 5000
-\vbadness = 10000
-% \usepackage{}
-
-% MNRAS is set in Times font. If you don't have this installed (most LaTeX
-% installations will be fine) or prefer the old Computer Modern fonts, comment
-% out the following line
-%\usepackage{newtxtext,newtxmath} % not yet supported on arxiv and uni computer
-%\usepackage{txfonts}
-
-% Depending on your LaTeX fonts installation, you might get better results with one of these:
-%\usepackage{mathptmx}
-%\usepackage{txfonts}
-
-% Use vector fonts, so it zooms properly in on-screen viewing software
-% Don't change these lines unless you know what you are doing
-\usepackage[T1]{fontenc} % make sure font is supported
-% \usepackage{ae,aecompl} %obsolete when using modern fonts
-\usepackage[final]{microtype} % make sure font is supported
-% and a suitable font
-\usepackage{lmodern} % use a modern font with T1 support
-%\usepackage{cm-super} % use a modern font with T1 support
-
-%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
-
-% Only include extra packages if you really need them. Common packages are:
-%\usepackage[dvipdfmx]{graphicx}	% Including figure files
-\usepackage{graphicx} % Including figure files
-%\usepackage[skip=0pt]{subcaption}
-\usepackage{amsmath}	% Advanced maths commands
-\usepackage{amssymb}	% Extra maths symbols
-\usepackage{pifont}	% Extra maths symbols
-%\usepackage{bmpsize}  % PS still needs this for correct bounding boxes?
-
-% TODO stuff, comment out for final submit
-\usepackage{todonotes} % as long as we are editing...
-%\usepackage{showframe} % for debug
-%\overfullrule=5pt      % show overfull boxes
-
-% I disabled hyperlink in the cls und included it here because of bugs
-\usepackage{hyperref}   % Hyperlinks
-\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,filecolor=blue,urlcolor=blue}
-
-\edef\smallwidth{0.4\linewidth}
-
-\newcommand{\inclfig}[2]{
-  \centering
-	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img3_ipol}
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
-%        \includegraphics[width=\smallwidth]{spaghetti/#2_img2}
-        \includegraphics[width=\smallwidth]{img/kappa_map/#1_#2_kappa_map}
-	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
-	\includegraphics[width=\smallwidth]{img/mlens_vs_mstel/#1_#2_mstel_vs_mtot}
-}
-
-\newcommand{\inclfign}[2]{
-  \centering
-	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
-	\includegraphics[width=\smallwidth]{img/nsynth/#2_nsynth}
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
-%	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
-        \includegraphics[width=\smallwidth]{img/kappa_map/#1_#2_kappa_map}
-	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
-	\includegraphics[width=\smallwidth]{img/mlens_vs_mstel/#1_#2_mstel_vs_mtot}
-}
-
-\newcommand*{\rot}{\rotatebox{90}}
-\newcommand*{\OK}{\ding{51}}
-\newcommand*{\NO}{\ding{55}}
-
-\newcommand{\lenstitle}[1]{\noindent\textbf{#1} --}
-\newcommand{\params}[3]{(\(\Theta_\text{E}:#1\), $\varepsilon:#2$, $\alpha_\varepsilon:#3$ )}
-
-\newcommand{\asw}[1]{ASW000#1}
-\newcommand{\sw}[1]{SW~#1}
-\newcommand{\model}[1]{SL model~#1}
-
-\newcommand{\figref}[1]{\ref{fig:#1}}
-
-\newcommand{\Mstel}{M_{\rm stel}}
-\newcommand{\Mhalo}{M_{\rm h}}
-\newcommand{\haloindex}{\mathcal{H}}
-\newcommand{\ER}{$\Theta_{\text{E}}$} % einstein radius
-
-\title[Lens models for Space Warps CFHTLS]{Model of lens candidates from
-  Space Warps CFHTLS}
-
-\author[K\"ung et al]{Rafael K\"ung,$^{1}$
-Prasenjit Saha,$^{1}$
-Ignacio Ferreras,$^{2}$
-Elisabeth Baeten,$^{3}$
-\newauthor
-Jonathan Coles,$^{4}$
-Claude Cornen,$^{3}$
-Christine Macmillan,$^{3}$
-Phil Marshall,$^{5}$ 
-\newauthor
-Anupreeta More,$^{6}$
-Lucy Oswald$^{7}$
-Aprajita Verma$^{8}$
-and Julianne K. Wilcox$^{4}$
-%
-\\
-%
-$^{1}$Physik-Institut, University of Zurich, Winterthurerstrasse 190, 8057 Zurich, Switzerland\\
-$^{2}$Mullard Space Science Laboratory, University College London, Holmbury St Mary, Dorking, Surrey RH5 6NT, UK\\
-$^{3}$Zooniverse, c/o Astrophysics Department, University of Oxford, Oxford OX1 3RH, UK \\
-$^{4}$Exascale Research Computing Lab, Campus Teratec, 2 Rue de la Piquetterie, 91680 Bruyeres-le-Chatel, France\\
-$^{5}$Kavli Institute for Particle Astrophysics and Cosmology, Stanford University, 452 Lomita Mall, Stanford, CA 94035, USA\\
-$^{6}$Kavli Institute for the Physics and Mathematics of the Universe, University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa-shi 277-8583, Japan\\
-$^{7}$Murray Edwards College, University of Cambridge, Cambridge CB3 0DF, UK\\
-$^{8}$Sub-department of Astrophysics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
-}
-
-% These dates will be filled out by the publisher
-% \date{Accepted XXX. Received YYY; in original form ZZZ}
-
-% Enter the current year, for the copyright statements etc.
-\pubyear{2016}
-
-% Don't change these lines
-\begin{document}
-\label{firstpage}
-\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\maketitle
-
-\begin{abstract}
-We report modelling follow-up of recently-discovered
-gravitational-lens candidates in the CFHT Legacy Survey.  Lens
-modelling was done by a small group of specially-interested volunteers
-from the Space~Warps citizen-science community who originally found
-the candidate lenses.  Models are categorised according to seven
-qualitative and quantitive points.  Also included are some
-improvements to the modelling software used (SpaghettiLens),
-and discussion of strategies for scaling to future surveys
-with more and frequent discoveries.
-
-The candidates successfully modelled are all galaxies, with inferred
-lensing masses ranging from $\sim10^{11}M_\odot$ to $>10^{13}M_\odot$.
-Stellar masses have also been estimated, using photometry from the
-CFHTLS pipeline and stellar-population models.  A trend well-known
-in nearby galaxies, that star-formation efficiency is maximal for
-total masses of $\approx10^{12}M_\odot$ and reduces for both lower and
-higher masses, is discernable also in these much more distant
-galaxies.
-\end{abstract}
-
-\begin{keywords}
-gravitational lensing: strong -- keyword2
-\end{keywords}
-
-\section{Introduction}
-
-Light deflection at the rim of the Sun is famously $1.75''$.  The
-deflection angle can also be expressed in terms of the escape velocity
-$2v_{\rm esc}^2/c^2$, with $v_{\rm esc}$ at the solar surface being
-$\simeq620\rm\,km/s$.  The Galactic escape velocity at the Sun's
-location is similar: $\approx500\rm\,km/s$, typical of massive
-galaxies.  Thus, the outer regions of massive galaxies have lensing
-deflections comparable to that at the rim of the Sun.  Yet these
-quantitatively similar deflections have qualitatively different
-consequences.  Light deflection by the Sun must be accounted for in
-modern astrometry \citep[see e.g.,][]{2015CQGra..32p5008C} but is not
-itself a physics probe in the way it was a century ago.  With distant
-galaxies, however, light bending by $\sim1''$ introduces two new
-phenomena.  First, for galaxies distant enough that their apparent
-size is comparable to the bending angle, light deflection can cause
-multiple images of background sources, or strong lensing.  Second, the
-gravitational field is dominated by dark matter, hence strong lensing
-becomes a probe of dark matter in galaxies.
-
-With no unambiguous dark-matter particle detections so far, dark
-matter has studied only through its indirect consequences on galactic
-and larger scales.  In most work, dark matter is taken to be a
-collisionless non-relativistic fluid (cold dark matter or CDM); in
-recent years, the simulation by \cite{2005Natur.435..629S} has been
-particularly influential in studying the formation of CDM structures.
-Other scenarios have also been considered, such as a cold condensing
-boson fluid \citep{2016ApJ...818...89S}.  There is a general
-consensus, however, that the origins of galaxy lie in the
-gravitational collapse, fragmentation, and mergers of dark-matter
-clumps, into which fell gas, cooling through radiative processes to
-form dense clouds and eventually stars.  There is, however, much
-debate about the details, of which \cite{2012RAA....12..917S} provide
-a nice summary.
-
-Strong-lensing galaxies are a useful source of information on the
-mutual dynamics and dark matter and gas in galaxies.  The topic has
-been explored in several studies
-\citep{2009ApJ...703L..51K,2011ApJ...740...97L,2012MNRAS.424..104L,
-  2016MNRAS.459.3677L,2016MNRAS.456..870B} but it is desirable to
-enlarge the samples from tens of lensing galaxies to thousands.  Doing
-so requires finding more lenses, of course, but also modelling their
-masses.
-
-Recent searches through the CFHTLS \citep{2012SPIE.8448E..0MC} using
-arc-finders
-\citep{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G} by
-machine learning \citep{2016arXiv160504309P} and by visual inspection
-by a citizen-science volunteers
-\citep[Space~Warps][]{2016MNRAS.455.1191M} have between them
-discovered an average of four lenses per square degree.  So one can be
-optimistic about finding many thousands of lenses in the next
-generation of wide-field surveys.  The expected flood of new lens
-discoveries will need a similarly huge modelling effort to
-reconstruct their mass distributions.  To prepare for the challenge of
-massive-sample lens modelling, \cite{2015MNRAS.447.2170K} developed a
-new modelling strategy, implemented as the SpaghettiLens system.  The
-idea is to collaborate with experienced members of the citizen-science
-community, who have already participated in lens discovery through
-Space~Warps, as well as several other projects involving astronomical
-data.  In this paper, we present SpaghettiLens models of
-lens-candidates discovered through Space~Warps.
-
-Section~\ref{sec:spl} summarises the SpaghettiLens system and
-discusses its ongoing development. A SpaghettiLens model consists of a
-statistical ensemble of free-form maps of the sky-projected mass
-distribution responsible for lensing.  Each lens candidates in
-practice gets modelled several times in a collaborative refinement
-process\footnote{See ``Collaborative gravitational lens
-  modelling\dots'' in {\tt http://letters.zooniverse.org} especially
-  the model tree.}  In this paper we report the most recent model for
-each lens, as representing a consensus among modellers, as to the best
-that could be achieved with the available data and software.
-Photometric lens redshifts are used; source redshifts are set to
-$z=2$ unless an unambiguous photometric redshift is available.
-The models can, however, be trivially rescaled to use better
-redshift values, as and when they become available.
-\cite{2015MNRAS.447.2170K} tested the system on simulated lenses and
-identified some areas for improvement.  The first two of those are
-taken up in Section~\ref{sec:spl}, along with a further idea. In
-\S~\ref{subsec:sourcefit} we introduce fitting of the brightness
-profiles of the source.  This feature has not yet been included in
-SpaghettiLens, but has been carried out in post-processing for a few
-especially interesting candidates.  In \S~\ref{subsec:hires} we show
-that making mass maps fine-grained in the central region relieves a
-tendency in the earlier work for mass to be too shallow. Then in
-\S~\ref{subsec:parameter} we consider the possibility of fitting a
-parametric lens model to the model ensemble; so far we have only been
-successful at extracting an Einstein radius.
-
-Section~\ref{sec:stellar-mass} explains how we compare the lensing
-mass with the mass in stars in the lensing galaxy.  We estimate the
-stellar mass by comparing galaxy magnitudes from the CFHTLS pipeline
-with the well-known stellar-population models of
-\cite{2003MNRAS.344.1000B}.  We then extrapolate the stellar masses to
-a halo mass using the abundance-matching prescription of
-\cite{2010ApJ...710..903M}.  Naturally, the lensing mass must be more
-than the stellar mass but no more than the total halo mass.  We then
-introduce what we call a halo index $\haloindex$ which gives an idea
-of how the lensing mass compares with these two bounds.
-
-Section~\ref{sec:examples} discusses ten of the systems, including six
-systems we found to be particularly interesting.  The online
-supplement gives results for all the modelled systems.
-
-In Section~\ref{sec:summary} and Table~\ref{tab:models} we display a
-concise characterisation of each modelled system, according to the
-image morphology and how clear or indistinct it is, whether the mass
-map and synthetic lensed image appear to be plausible, and how the
-model mass compares with the estimated stellar and full-halo masses.
-
-\section{Lens Modelling}\label{sec:spl}
-
-SpaghettiLens is an example of a medium-sized collaboration spawned by
-a large citizen-science project (in this case Space~Warps).  While
-collaboration with volunteers is essential to both, the form of
-collaboration is very different.  In Space~Warps, volunteers in a
-crowd of $\gtrsim10^4$ make independent contributions.  Each person is
-presented with a random selection of survey-patches and invited to (in
-effect) vote on each.  The system estimates each volunteer's skill
-level according to test-patches interspersed with the real data, and
-weights their votes accordingly \citep{2016MNRAS.455.1171M}.  There is
-an active forum for volunteers, but since everyone is seeing different
-data samples with minimal overlap, the forum has little if any
-influence on votes.  With SpaghettiLens, on the other hand, there is a
-small group of volunteers and their contributions are interdependent.
-
-A modeller's main input to SpaghettiLens is a sketch of arrival-time
-contours on a lensed system.  It gives the locations (or best-guess
-locations) of images of point-like sources, along with their ordering
-in arrival time, and their parities (minumum, saddle-point or
-maximum).  Such a sketch, which we call a spaghetti diagram, tends to
-resemble the form of lensed arcs, but it also in effect 
-encodes a proposal for its mass distribution.  A spaghetti diagram is
-read by a server-side numerical engine \citep[GLASS, developed
-  by][]{2014MNRAS.445.2181C} which then returns a statistical ensemble
-of mass maps.  The mass maps are made up of mass tiles and are
-free-form, except that they are required to be concentrated around the
-identified lens centre.  They are also required to reproduce the given
-image locations, parities and time ordering exactly.  Graphical
-representations of the mass map and arrival-time surface are returned
-to the user for review.  The user can post these results on a forum,
-or discard them and try again.  Volunteers can start the modelling
-process afresh, or they can take an existing model from the forum and
-modify its input spaghetti diagram or its accompanying options, and
-thus obtain a revised model.
-
-\subsection{Improved synthetic images}\label{subsec:sourcefit}
-
-The mass maps produced by current implementation of SpaghettiLens are
-based on images of point-like features.  No information about extended
-images is used, except in so far as they help the user identify images
-of point-like features.  The synthetic images offered to users are
-rudimentary, based on sources with conical light profiles.
-
-We have now developed a prototype of better way to generate synthetic
-images.  Figure~\figref{synthimg} illustrates.  First, areas
-containing lensed images are selected (green frames in the figure).
-The selected areas must contain no light from the lensing galaxy or
-from extraneous objects.  Pixels within the selected areas are mapped
-to a grid on the source plane, using bending angles given by the mass
-model.  The mapping from lens-plane pixels to source-plane grid cells
-is many-to-one, because of image multiplicity and magnification.  The
-brightness of each source-plane pixel is set to the mean of all the
-lens-plane pixels mapping to it.  Finally, the mapping is run back to
-the lens plane.  The result is a synthetic image.  In effect, one is
-reconstructing a source-plane brightness map by least-squares.
-
-The procedure is not yet implemented in SpaghettiLens but can be
-applied in post-processing.  The new synthetic images could be used to
-improve the mass reconstruction, by weighting the ensemble of maps
-according to how good the synthetic images are, but we have not
-attempted to do so as yet.
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{img/new_synth_img_detailed}
-  \caption{Synthetic lensed image with source-profile fitting in SW05
-    (J143454.4+522850). Top-left: original image, with areas
-    containing lensed images enclosed within green frames.  Top-right:
-    synthetic image (coloured arcs) with lensing galaxy and unrelated
-    objects in greyscale.  Bottom from left to right: reconstructed
-    source in colour, intensity (greyscale), count of lens plane
-    pixels per source plane pixel, residual of original image to
-    synthetic image.}
-  \label{fig:synthimg}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_11_hires_comparison}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_13_hires_comparison}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_33_hires_comparison}
-  \caption{Model improvement resulting from using smaller mass tiles
-    in the inner region of the mass model.  Shown here are the average
-    enclosed $\kappa$ within a given projected radius, for three
-    different reconstructions of a simulated lens (sim) from
-    Space~Warps.  In each panel, the dashed blue curve is the correct
-    answer.  The orange band represents the statistical ensemble from
-    SpaghettiLens, the orange line being the ensemble mean.  Locations of
-    images (maximum, saddle point, minimum) are marked with vertical
-    arrows.  Crossing the horizontal $\kappa=1$ line is the effective
-    Einstein radius \ER, and is so labelled. The upper panel is from
-    K\"ung et al., (2015) (see Figure~3 of that paper).  The middle
-    panel is the result when the innermost mass tile is replaced by 9
-    smaller tiles.  The lower panel results from replacing each of the
-    innermost 5 by 5 tiles each with 9 smaller tiles.}
-  \label{fig:subsampling}
-\end{figure}
-
-\subsection{Sub-sampling of central region}\label{subsec:hires}
-
-The models of simulated lenses in \cite{2015MNRAS.447.2170K} showed a
-tendency to be too shallow.  Allowing smaller mass tiles in the
-central region, thus allowing the pass profile to rise more steeply
-near the centre, was suggested as a possible cure.
-
-Figure~\figref{subsampling} shows an experiment with smaller mass
-tiles in the inner region.  Replacing the very central mass tile with
-9 smaller tiles allows for steeper central profiles.  Doing the same
-for the 25 innermost mass tiles solves the problem completely, but
-increases the number of mass tiles by 40\% and significantly increases
-the computational time.
-% 689 / 489 = 1.40899; in practice, runtime is more like x4 - x5!
-% runtimes from logfiles: 87/22, 86/21, 85/16
-The main modelling work in this paper was, however, done before the
-experiments with smaller mass tiles was complete.  Some of the models
-presented in this paper apply the intermediate option (corresponding
-to the middle panel in Figure~\figref{subsampling}) while others use
-the old system.  The results in this paper, however, mainly concern
-the enclosed mass in the outer regions, so shallowness in the central
-region should be inconsequential.
-
-\subsection{Parameterisation of pixel models} \label{subsec:parameter}
-In order to fit the set of pixelated models to a single parameterised model, a program was written that took a parameterised function and subtracted from it the mean and the principle components of the data, which were calculated using classical Principle Component Analysis.
-This created the residuals function.
-The number of components defined as principle was varied to test how this affected the output, and it was found that using 5 principle components tended to give a reasonable approximation.
-A masking function was added which selected only the data points that fell inside the image of the lens, and the principal components were clipped in order to keep the values inside the region of the ensemble of models.
-Any value higher than the clip was set to be the clip value.
-This was chosen to be 2.5 as, assuming that the data follows a Gaussian error distribution, almost all the values for the variance should lie between 2 and 3 standard deviations from the mean.
-Minimising the residuals function produces the set of parameters that fit the parameterised function to the original pixelated ensemble most closely.
-A least squares fit was used to perform this minimisation.
-The parameterised model function was obtained from the gravitational potential of an isothermal ellipsoid mass distribution \cite{2001astro.ph..2341K}.
-This model is frequently used to describe gravitational lenses as it tends to fit well with observations.
-The isothermal ellipsoid model outputs three useful parameters: the radius of the Einstein ring, the ellipticity of the model and the angle of the ellipticity from the vertical, giving the orientation of the galaxy.
-By applying this model to simulated lenses for which the values of these parameters were already known, it was possible to gain an estimate of the projected accuracy of the results, before applying the model to the candidate lensing galaxies.
-
-\begin{figure}
-  \caption{}
-  \label{fig:parameter}
-\end{figure}
-
-\section{Stellar mass}\label{sec:stellar-mass}
-
-Based on \cite{2003MNRAS.344.1000B} models.\todo{Description of
-  stellar-population models.}
-
-Following \cite{2010ApJ...710..903M}
-\begin{equation}
-\begin{aligned}
-\frac{\Mstel}{\Mhalo} &= \frac{2C_0}{(\Mhalo/M_1)^{-\beta} +
-                                     (\Mhalo/M_1)^\gamma} \\
-C_0 &= 0.02820, \quad M_1 = 10^{11.884} M_\odot \\
-\beta &= 1.057, \quad \gamma = 0.556.
-\end{aligned}
-\end{equation}
-
-\begin{equation}
-\haloindex = \frac{\ln(M/\Mstel)}{\ln(\Mhalo/\Mstel)}
-\end{equation}
-which we may call the halo-matching index.
-\begin{itemize}
-\item $\haloindex < 0$ is unphysical because $M<\Mstel$.
-\item $\haloindex = 0$ is when the stellar mass exactly accounts for the
-  lensing mass.
-\item $0 < \haloindex < 1$ is the typical situation, where the lens
-  includes stars and dark matter, but not the full halo.
-\item $\haloindex = 1$ means that the lens consists of the entire halo.
-\item $\haloindex > 1$ is in tension with abundance-matching, because the
-  lensing mass exceeds the expected halo mass.
-\end{itemize}
-
-\section{Example systems}\label{sec:examples}
-
-In this section we show modelling results for ten of the lens
-candidates.  The first five (see Figures~\figref{SW05}--\figref{SW29})
-are the most convincingly modelled systems.  The next three cases
-(Figures~\figref{SW42}--\figref{SW19}) are less good but still very
-plausible models, and are representative of the majority of the
-sample.  The last two are examples where the models were unconvincing
-(Figures~\figref{SW36}) or completely failed (\figref{SW57}).
-
-\begin{figure}
-  \inclfign{SW05}{ASW0007k4r_N7LTELSYTM}
-  \caption{Model results for SW05 (J143454.4+522850).  See text in
-    Section~\ref{sec:examples} for details.}
-  \label{fig:SW05}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW28}{ASW0007xrs_JHC3J2HYV7}
-  \caption{Model results for SW28 (J143055.9+572431).}
-  \label{fig:SW28}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW02}{ASW000619d_011489}
-  \caption{Model results for SW02 (J140522.2+574333).}
-  \label{fig:SW02}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW09}{ASW0002asp_5EKMWWVJHL}
-  \caption{Model results for SW09 (J020832.1-043315).}
-  \label{fig:SW09}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW29}{ASW0008qsm_TOFS7JNGEK}
-  \caption{Model results for SW29 (J143838.1+572647).}
-  \label{fig:SW29}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW42}{ASW00096rm_4Q3YCEWGLN}
-  \caption{Modelling results for SW42 (J221716.5+015826).}
-  \label{fig:SW42}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
-  \caption{Model results for SW58 (J143651.6+530705).}
-  \label{fig:SW58}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW19}{ASW0001ld7_OS3CYAKLRT}
-  \caption{Model results for SW19 (J020642.0-095157).}
-  \label{fig:SW19}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW36}{ASW000096t_7IPP7LWVOF}
-  \caption{Model results for SW36 (J090248.4-010232).}
-  \label{fig:SW36}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
-  \caption{Model results for SW57 (J143631.5+571131).}
-  \label{fig:SW57}
-\end{figure}
-
-Let us first consider Figure~\figref{SW05}, which shows model results
-from SW05 (J143454.4+522850).
-
-\begin{enumerate}
-\item In the upper row we have first a cutout of the Space~Warps
-  image, marked up with a spaghetti diagram.  There are four distinct
-  lensed images, and the spaghetti diagram proposes that they are a
-  minimum nearest to the lensing galaxy, a close minimum-saddle pair,
-  and a minimum further away. In Table~\ref{tab:models} we refer to
-  such configurations as IQ for inclined quad.
-\item Alongside is a synthetic image produced by modelling.  In it,
-  the fitted lensed images are shown in colour, while the lensing
-  galaxy and extraneous objects have been reduced to grayscale.
-  (Figure~\figref{synthimg} in \S~\ref{subsec:sourcefit} shows a
-  synthetic image from another model of the same system.) These two
-  panels are qualitative and display no units, and moreover, the
-  mutual alignment of the two panels is only approximate.
-\item The middle row shows contour maps from the model.  At middle
-  left, we have the arrival-time surface.
-\item At middle right we have the mass distribution in the usual
-  dimensionless form $\kappa$.  Again, these two panels are mainly
-  qualitative: both panels are spatially registered and centred on the
-  density-peak of the lens, but no scales have been included.
-\item The base row supplies spatial and mass scales.  The left panel
-  shows the circularly-averaged $\kappa$ of the model ensemble, with
-  increasing radius (in arcsec).  The four short vertical lines
-  correspond to the minima and saddle points marked in the upper-left
-  panel.  The effective Einstein radius \ER is also shown.  As the radius
-  scale indicates SW05 is comparatively large lens on the
-  sky.
-\item Lower right shows the total mass in the model against the
-  estimated stellar mass, alongside the values for the whole sample.
-  The lower-right shaded region is unphysical according to the
-  stellar-population models, because it gives $M<\Mstel$. The
-  upper-left shaded region is unphysical according to abundance
-  matching, because it gives $M>\Mhalo$.  That is to say, the unshaded
-  region is $0<\haloindex<1$.
-\end{enumerate}
-
-Proceeding to Figure~\figref{SW28}, we have one image close to the
-galaxy and an arc further away, which is interpreted as a blend of
-three images (a saddle point with two minima on either side).  We call
-this a long-axis quad or LQ configuration.  It is an indication of a
-mass distribution elongated along the arc-counterimage direction
-(along EW in this case).
-
-In Figures~\figref{SW02}--\figref{SW29} we see three candidates with
-an arc close the lensing galaxy and one image further away.  The arc
-is interpreted three images (a minimum with two saddle points on
-either side).  We call this a short-axis quad or SQ configuration.  It
-is an indication of a mass distribution elongated perpendicular to the
-arc-counterimage direction.
-
-Figures~\figref{SW02}--\figref{SW29} (SW05, SW28, SW02, SW09 and SW29)
-all correspond to the mass range of massive ellipticals.  SW05 is the
-most massive of all the candidates, with a galaxy-group scale mass.
-
-Figure~\figref{SW42} shows SW42.  The image morphology is similar to
-SW05 in Figure~\figref{SW05}, but the lens is much smaller on the sky,
-and the inferred mass is at the low end of the sample.  (The synthetic
-image shown is cruder than for the five previous figures, but that
-does not influence the mass models.)  If these preliminary findings
-are confirmed by follow-up observations, this could be the most
-dark-matter dominated lens known.\todo{Check photometry of this
-  candidate.}
-
-Figures~\figref{SW58} and \figref{SW19} appear plausible lens
-candidates.  Their morphology is similar to SW28, but the saddle-point
-counterimage is not visible.  We consider these lenses plausible but
-less convincing.
-
-Figures~\figref{SW36} and \figref{SW57} are cases where modelling
-failed.
-
-\section{Summary of models}\label{sec:summary}
+Now we give a concise characterisation of each modelled system,
+according to the image morphology and how clear or indistinct it is,
+whether the mass map and synthetic lensed image appear to be
+plausible, and how the model mass compares with the estimated stellar
+and full-halo masses.
 
@@
 
-\begin{enumerate}
-\item The image morphology concisely described: D for double, and
-  quads in sub-categorised in four ways
-  \citep[cf.][]{2003AJ....125.2769S} as LQ for long-axis quads (as in
-  Figure~\figref{SW28}), SQ for short-axis quads (as in
-  Figure~\figref{SW02}, \figref{SW09}, \figref{SW29}, \figref{SW42}),
-  IQ for inclined quads (as in Figure~\figref{SW05}) and CQ for very
-  symmetric core quads.
-\item Whether the images are unblended.  Distinct unblended images (as
-  in Figures~\figref{SW05} and \figref{SW42}) are an advantage in
-  modelling, but not essential.
-\item Whether all images are discernable.  The topography of an
-  arrival-time surface, as encoded by a spaghetti diagram, may require
-  more images than are visible.  For example, in Figure~\figref{SW58},
-  the modeller has put in a conjectural saddle point near the lensing
-  galaxy.
-\item Whether the lens is fairly isolated.
-\item Whether the arrival-time surface and synthetic image are
-  plausible.  In Figure~\figref{SW36} the model implies extra images
-  or a long arc, which are not seen.
-\item Whether the mass map is reasonable.
-\item The halo index $\haloindex$.
-\end{enumerate}
+\begin{figure*}
+\includegraphics[width=\linewidth]{img/mlens_vs_mstel_one/mstel_vs_mtot_one}
+\caption{Total mass in the model against the estimated stellar mass,
+  alongside the values for the whole sample.  The lower-right shaded
+  region is unphysical according to the stellar-population models,
+  because it gives $M<\Mstel$. The upper-left shaded region is
+  unphysical according to abundance matching, because it gives
+  $M>\Mhalo$.  That is to say, the unshaded region is
+  $0<\haloindex<1$. \label{fig:stelmass}}
+\end{figure*}
+
+SW05, SW28, SW02, SW09 and SW29 all correspond to the mass range of
+massive ellipticals.  SW05 is the most massive of all the candidates,
+with a galaxy-group scale mass.
+
+For SW42 the inferred mass is at the low end of the sample.  (The
+synthetic image shown is cruder than for the five previous figures,
+but that does not influence the mass models.)  If these preliminary
+findings are confirmed by follow-up observations, this could be the
+most dark-matter dominated lens known.\todo{Check photometry of this
+  candidate.}
 
@@
 \end{table*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% The best way to enter references is to use BibTeX:
-\bibliographystyle{mnras}
-\bibliography{bib/bibli} % if your bibtex file is called example.bib
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \appendix
-
-\clearpage
-
-\section{TODO}
-\listoftodos
-
-% Don't change these lines
-\bsp	% typesetting comment
-\label{lastpage}
-\end{document}

### 2016-12-09 parts/summary.tex
edits

@@
 
-\begin{figure*}
-\includegraphics[width=\linewidth]{img/mlens_vs_mstel_one/mstel_vs_mtot_one}
-\caption{Total mass in the model against the estimated stellar mass,
-  alongside the values for the whole sample.  The lower-right shaded
-  region is unphysical according to the stellar-population models,
-  because it gives $M<\Mstel$. The upper-left shaded region is
-  unphysical according to abundance matching, because it gives
-  $M>\Mhalo$.  That is to say, the unshaded region is
-  $0<\haloindex<1$. \label{fig:stelmass}}
-\end{figure*}
-
 SW05, SW28, SW02, SW09 and SW29 all correspond to the mass range of
@@
   candidate.}
-
-\begin{table*}
-  \caption{Categorisation of SW models}
-  \label{tab:models}
-  \include{table}
-\end{table*}

### 2016-12-12 parts/intro.tex
edits

@@
 generation of wide-field surveys.  The expected flood of new lens
-discoveries will need a similarly huge modelling effort to
-reconstruct their mass distributions.  To prepare for the challenge of
+discoveries will need a similarly huge modelling effort to reconstruct
+their mass distributions.  To prepare for the challenge of
 massive-sample lens modelling, \cite{2015MNRAS.447.2170K} developed a
@@
 Space~Warps, as well as several other projects involving astronomical
-data.  In this paper, we present SpaghettiLens models of
-lens-candidates discovered through Space~Warps.
+data.  In this paper, we present SpaghettiLens models of lens-candidates
+discovered through Space~Warps.
+
+Purpose is twofold.  First, see if plausible mass models can produce
+the overall configuration.  Second, interpretation as lensing
+galaxies.  Introduce some diagnostics.
+
+Each lens candidates in practice gets modelled several times in a
+collaborative refinement process.\footnote{See ``Collaborative
+  gravitational lens modelling\dots'' in {\tt
+    http://letters.zooniverse.org} especially the model tree.}  This
+representing a consensus among modellers, as to the best that could be
+achieved with the available data and software.\footnote{This is in
+  contrast to the main Space~Warps project for discovering lenses, in
+  which volunteers in a crowd of $\gtrsim10^4$ make independent
+  contributions.  Each person is presented with a random selection of
+  survey-patches and invited to (in effect) vote on each.  The system
+  estimates each volunteer's skill level according to test-patches
+  interspersed with the real data, and weights their votes accordingly
+  \citep{2016MNRAS.455.1171M}.  There is an active forum for
+  volunteers, but since everyone is seeing different data samples with
+  minimal overlap, the forum has little if any influence on votes.}
 
 \begin{itemize}
-\item Morphology from Figure~\ref{fig:markedup}.
+\item Section~\ref{sec:morph} discusses nine of the systems, including
+  six systems we found to be particularly interesting.  Morphology
+  from Figure~\ref{fig:markedup}.
 \begin{itemize}
@@
 \end{itemize}
-\item Mass model
+\item Section~\ref{sec:massmodels}
 \begin{itemize}
@@
 \end{itemize}
-\item Stellar mass. Figure~\ref{fig:stelmass}.
-\end{itemize}
-
-Section~\ref{sec:spl} summarises the SpaghettiLens system and
-discusses its ongoing development. A SpaghettiLens model consists of a
-statistical ensemble of free-form maps of the sky-projected mass
-distribution responsible for lensing.  Each lens candidates in
-practice gets modelled several times in a collaborative refinement
-process\footnote{See ``Collaborative gravitational lens
-  modelling\dots'' in {\tt http://letters.zooniverse.org} especially
-  the model tree.}  In this paper we report the most recent model for
-each lens, as representing a consensus among modellers, as to the best
-that could be achieved with the available data and software.
-Photometric lens redshifts are used; source redshifts are set to
-$z=2$ unless an unambiguous photometric redshift is available.
-The models can, however, be trivially rescaled to use better
-redshift values, as and when they become available.
-\cite{2015MNRAS.447.2170K} tested the system on simulated lenses and
-identified some areas for improvement.  The first two of those are
-taken up in Section~\ref{sec:spl}, along with a further idea. In
-\S~\ref{subsec:sourcefit} we introduce fitting of the brightness
-profiles of the source.  This feature has not yet been included in
-SpaghettiLens, but has been carried out in post-processing for a few
-especially interesting candidates.  In \S~\ref{subsec:hires} we show
-that making mass maps fine-grained in the central region relieves a
-tendency in the earlier work for mass to be too shallow. Then in
-\S~\ref{subsec:parameter} we consider the possibility of fitting a
-parametric lens model to the model ensemble; so far we have only been
-successful at extracting an Einstein radius.
-
-Section~\ref{sec:stellar-mass} explains how we compare the lensing
+\item Section~\ref{sec:stellar-mass} explains how we compare the lensing
 mass with the mass in stars in the lensing galaxy.  We estimate the
@@
 of how the lensing mass compares with these two bounds.
+Figure~\ref{fig:stelmass}.
+\end{itemize}
 
-Section~\ref{sec:examples} discusses ten of the systems, including six
-systems we found to be particularly interesting.  The online
-supplement gives results for all the modelled systems.
+In this paper we report the most recent model for each lens, as
+
+Section~\ref{sec:summary} builds Table~\ref{tab:models}.
+The online supplement gives results for all the modelled systems.
+
+Appendices devoted to various technical issues relating to modelling.
+\cite{2015MNRAS.447.2170K} tested the system on simulated lenses and
+identified some areas for improvement.
+In \S~\ref{subsec:sourcefit} we introduce fitting of the brightness
+profiles of the source.  This feature has not yet been included in
+SpaghettiLens, but has been carried out in post-processing for a few
+especially interesting candidates.  In \S~\ref{subsec:hires} we show
+that making mass maps fine-grained in the central region relieves a
+tendency in the earlier work for mass to be too shallow. Then in
+\S~\ref{subsec:parameter} we consider the possibility of fitting a
+parametric lens model to the model ensemble; so far we have only been
+successful at extracting an Einstein radius.

### 2016-12-12 parts/spl.tex
edits

@@
-\section{SpaghettiLens}\label{sec:spl}
-
-SpaghettiLens is an example of a medium-sized collaboration spawned by
-a large citizen-science project (in this case Space~Warps).  While
-collaboration with volunteers is essential to both, the form of
-collaboration is very different.  In Space~Warps, volunteers in a
-crowd of $\gtrsim10^4$ make independent contributions.  Each person is
-presented with a random selection of survey-patches and invited to (in
-effect) vote on each.  The system estimates each volunteer's skill
-level according to test-patches interspersed with the real data, and
-weights their votes accordingly \citep{2016MNRAS.455.1171M}.  There is
-an active forum for volunteers, but since everyone is seeing different
-data samples with minimal overlap, the forum has little if any
-influence on votes.  With SpaghettiLens, on the other hand, there is a
-small group of volunteers and their contributions are interdependent.
-
-A modeller's main input to SpaghettiLens is a sketch of arrival-time
-contours on a lensed system.  It gives the locations (or best-guess
-locations) of images of point-like sources, along with their ordering
-in arrival time, and their parities (minumum, saddle-point or
-maximum).  Such a sketch, which we call a spaghetti diagram, tends to
-resemble the form of lensed arcs, but it also in effect 
-encodes a proposal for its mass distribution.  A spaghetti diagram is
-read by a server-side numerical engine \citep[GLASS, developed
-  by][]{2014MNRAS.445.2181C} which then returns a statistical ensemble
-of mass maps.  The mass maps are made up of mass tiles and are
-free-form, except that they are required to be concentrated around the
-identified lens centre.  They are also required to reproduce the given
-image locations, parities and time ordering exactly.  Graphical
-representations of the mass map and arrival-time surface are returned
-to the user for review.  The user can post these results on a forum,
-or discard them and try again.  Volunteers can start the modelling
-process afresh, or they can take an existing model from the forum and
-modify its input spaghetti diagram or its accompanying options, and
-thus obtain a revised model.
+\section{Characterising the lens models}\label{sec:diag}

### 2016-12-12 parts/figures.tex
this may have forked

--- 2016-07-26 paper2.tex
@@
-\documentclass[fleqn,usenatbib]{mnras}
+\def\pwidth{.32\linewidth}
 
-%%% DEBUG SETTINGS - remove at the end %%%%%%%%%%%%%%%
-\usepackage{silence} % silence error warinings
-\WarningFilter{caption}{Unsupported document class} % caption doesn't know mnras..
-\hbadness = 5000
-\vbadness = 10000
-% \usepackage{}
-
-% MNRAS is set in Times font. If you don't have this installed (most LaTeX
-% installations will be fine) or prefer the old Computer Modern fonts, comment
-% out the following line
-%\usepackage{newtxtext,newtxmath} % not yet supported on arxiv and uni computer
-%\usepackage{txfonts}
-
-% Depending on your LaTeX fonts installation, you might get better results with one of these:
-%\usepackage{mathptmx}
-%\usepackage{txfonts}
-
-% Use vector fonts, so it zooms properly in on-screen viewing software
-% Don't change these lines unless you know what you are doing
-\usepackage[T1]{fontenc} % make sure font is supported
-% \usepackage{ae,aecompl} %obsolete when using modern fonts
-\usepackage[final]{microtype} % make sure font is supported
-% and a suitable font
-\usepackage{lmodern} % use a modern font with T1 support
-%\usepackage{cm-super} % use a modern font with T1 support
-
-%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
-
-% Only include extra packages if you really need them. Common packages are:
-%\usepackage[dvipdfmx]{graphicx}	% Including figure files
-\usepackage{graphicx} % Including figure files
-%\usepackage[skip=0pt]{subcaption}
-\usepackage{amsmath}	% Advanced maths commands
-\usepackage{amssymb}	% Extra maths symbols
-\usepackage{pifont}	% Extra maths symbols
-%\usepackage{bmpsize}  % PS still needs this for correct bounding boxes?
-
-% TODO stuff, comment out for final submit
-\usepackage{todonotes} % as long as we are editing...
-%\usepackage{showframe} % for debug
-%\overfullrule=5pt      % show overfull boxes
-
-% I disabled hyperlink in the cls und included it here because of bugs
-\usepackage{hyperref}   % Hyperlinks
-\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,filecolor=blue,urlcolor=blue}
-
-\edef\smallwidth{0.4\linewidth}
-
-\newcommand{\inclfig}[2]{
-  \centering
-	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img3_ipol}
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
-%        \includegraphics[width=\smallwidth]{spaghetti/#2_img2}
-        \includegraphics[width=\smallwidth]{img/kappa_map/#1_#2_kappa_map}
-	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
-	\includegraphics[width=\smallwidth]{img/mlens_vs_mstel/#1_#2_mstel_vs_mtot}
+\def\includeten#1#2{
+\includegraphics[width=\pwidth]{#1ASW0007iwp_4XBJWT3COV#2}%
+\includegraphics[width=\pwidth]{#1ASW0007xrs_JHC3J2HYV7#2}%
+\includegraphics[width=\pwidth]{#1ASW0008pag_5SXGXQYY6V#2}\\
+\includegraphics[width=\pwidth]{#1ASW0007k4r_N7LTELSYTM#2}%
+\includegraphics[width=\pwidth]{#1ASW00096rm_4Q3YCEWGLN#2}%
+\includegraphics[width=\pwidth]{#1ASW0001ld7_OS3CYAKLRT#2}\\
+\includegraphics[width=\pwidth]{#1ASW0002asp_5EKMWWVJHL#2}%
+\includegraphics[width=\pwidth]{#1ASW0008qsm_TOFS7JNGEK#2}%
+\includegraphics[width=\pwidth]{#1ASW000619d_011489#2}\\
+%\includegraphics[width=\pwidth]{#1ASW000096t_7IPP7LWVOF#2}%
 }
 
-\newcommand{\inclfign}[2]{
-  \centering
-	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
-	\includegraphics[width=\smallwidth]{img/nsynth/#2_nsynth}
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
-%	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
-        \includegraphics[width=\smallwidth]{img/kappa_map/#1_#2_kappa_map}
-	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
-	\includegraphics[width=\smallwidth]{img/mlens_vs_mstel/#1_#2_mstel_vs_mtot}
+\def\includezehn#1#2{
+\includegraphics[width=\pwidth]{#1SW58_ASW0007iwp_4XBJWT3COV#2}%   L
+\includegraphics[width=\pwidth]{#1SW28_ASW0007xrs_JHC3J2HYV7#2}%   L
+\includegraphics[width=\pwidth]{#1SW57_ASW0008pag_5SXGXQYY6V#2}\\% X
+\includegraphics[width=\pwidth]{#1SW05_ASW0007k4r_N7LTELSYTM#2}%   I
+\includegraphics[width=\pwidth]{#1SW42_ASW00096rm_4Q3YCEWGLN#2}%   I
+\includegraphics[width=\pwidth]{#1SW19_ASW0001ld7_OS3CYAKLRT#2}\\% I
+\includegraphics[width=\pwidth]{#1SW09_ASW0002asp_5EKMWWVJHL#2}%   S
+\includegraphics[width=\pwidth]{#1SW29_ASW0008qsm_TOFS7JNGEK#2}%   S
+\includegraphics[width=\pwidth]{#1SW02_ASW000619d_011489#2}\\%     S
+%\includegraphics[width=\pwidth]{#1SW36_ASW000096t_7IPP7LWVOF#2}%
 }
 
-\newcommand*{\rot}{\rotatebox{90}}
-\newcommand*{\OK}{\ding{51}}
-\newcommand*{\NO}{\ding{55}}
+\begin{figure*}
+\includeten{spaghetti/}{_input}
+\caption{Marked-up images. \label{fig:markedup}}
+\end{figure*}
 
-\newcommand{\lenstitle}[1]{\noindent\textbf{#1} --}
-\newcommand{\params}[3]{(\(\Theta_\text{E}:#1\), $\varepsilon:#2$, $\alpha_\varepsilon:#3$ )}
+\begin{figure*}
+\includezehn{img/arrival_spaghetti/}{_arrival_spaghetti}
+\caption{\label{fig:arriv}}
+\end{figure*}
 
-\newcommand{\asw}[1]{ASW000#1}
-\newcommand{\sw}[1]{SW~#1}
-\newcommand{\model}[1]{SL model~#1}
+\begin{figure*}
+\includeten{img/nsynth/}{_nsynth}
+\label{fig:synth}
+\caption{}
+\end{figure*}
 
-\newcommand{\figref}[1]{\ref{fig:#1}}
+\begin{figure*}
+\includezehn{img/kappa_map/}{_kappa_map}
+\caption{\label{fig:kappa}}
+\end{figure*}
 
-\newcommand{\Mstel}{M_{\rm stel}}
-\newcommand{\Mhalo}{M_{\rm h}}
-\newcommand{\haloindex}{\mathcal{H}}
-\newcommand{\ER}{$\Theta_{\text{E}}$} % einstein radius
+\begin{figure*}
+\includezehn{img/kappa_encl/}{_kappa_encl}
+\caption{}
+\end{figure*}
 
-\title[Lens models for Space Warps CFHTLS]{Model of lens candidates from
-  Space Warps CFHTLS}
-
-\author[K\"ung et al]{Rafael K\"ung,$^{1}$
-Prasenjit Saha,$^{1}$
-Ignacio Ferreras,$^{2}$
-Elisabeth Baeten,$^{3}$
-\newauthor
-Jonathan Coles,$^{4}$
-Claude Cornen,$^{3}$
-Christine Macmillan,$^{3}$
-Phil Marshall,$^{5}$ 
-\newauthor
-Anupreeta More,$^{6}$
-Lucy Oswald$^{7}$
-Aprajita Verma$^{8}$
-and Julianne K. Wilcox$^{4}$
-%
-\\
-%
-$^{1}$Physik-Institut, University of Zurich, Winterthurerstrasse 190, 8057 Zurich, Switzerland\\
-$^{2}$Mullard Space Science Laboratory, University College London, Holmbury St Mary, Dorking, Surrey RH5 6NT, UK\\
-$^{3}$Zooniverse, c/o Astrophysics Department, University of Oxford, Oxford OX1 3RH, UK \\
-$^{4}$Exascale Research Computing Lab, Campus Teratec, 2 Rue de la Piquetterie, 91680 Bruyeres-le-Chatel, France\\
-$^{5}$Kavli Institute for Particle Astrophysics and Cosmology, Stanford University, 452 Lomita Mall, Stanford, CA 94035, USA\\
-$^{6}$Kavli Institute for the Physics and Mathematics of the Universe, University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa-shi 277-8583, Japan\\
-$^{7}$Murray Edwards College, University of Cambridge, Cambridge CB3 0DF, UK\\
-$^{8}$Sub-department of Astrophysics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
-}
-
-% These dates will be filled out by the publisher
-% \date{Accepted XXX. Received YYY; in original form ZZZ}
-
-% Enter the current year, for the copyright statements etc.
-\pubyear{2016}
-
-% Don't change these lines
-\begin{document}
-\label{firstpage}
-\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\maketitle
-
-\begin{abstract}
-We report modelling follow-up of recently-discovered
-gravitational-lens candidates in the CFHT Legacy Survey.  Lens
-modelling was done by a small group of specially-interested volunteers
-from the Space~Warps citizen-science community who originally found
-the candidate lenses.  Models are categorised according to seven
-qualitative and quantitive points.  Also included are some
-improvements to the modelling software used (SpaghettiLens),
-and discussion of strategies for scaling to future surveys
-with more and frequent discoveries.
-
-The candidates successfully modelled are all galaxies, with inferred
-lensing masses ranging from $\sim10^{11}M_\odot$ to $>10^{13}M_\odot$.
-Stellar masses have also been estimated, using photometry from the
-CFHTLS pipeline and stellar-population models.  A trend well-known
-in nearby galaxies, that star-formation efficiency is maximal for
-total masses of $\approx10^{12}M_\odot$ and reduces for both lower and
-higher masses, is discernable also in these much more distant
-galaxies.
-\end{abstract}
-
-\begin{keywords}
-gravitational lensing: strong -- keyword2
-\end{keywords}
-
-\section{Introduction}
-
-Light deflection at the rim of the Sun is famously $1.75''$.  The
-deflection angle can also be expressed in terms of the escape velocity
-$2v_{\rm esc}^2/c^2$, with $v_{\rm esc}$ at the solar surface being
-$\simeq620\rm\,km/s$.  The Galactic escape velocity at the Sun's
-location is similar: $\approx500\rm\,km/s$, typical of massive
-galaxies.  Thus, the outer regions of massive galaxies have lensing
-deflections comparable to that at the rim of the Sun.  Yet these
-quantitatively similar deflections have qualitatively different
-consequences.  Light deflection by the Sun must be accounted for in
-modern astrometry \citep[see e.g.,][]{2015CQGra..32p5008C} but is not
-itself a physics probe in the way it was a century ago.  With distant
-galaxies, however, light bending by $\sim1''$ introduces two new
-phenomena.  First, for galaxies distant enough that their apparent
-size is comparable to the bending angle, light deflection can cause
-multiple images of background sources, or strong lensing.  Second, the
-gravitational field is dominated by dark matter, hence strong lensing
-becomes a probe of dark matter in galaxies.
-
-With no unambiguous dark-matter particle detections so far, dark
-matter has studied only through its indirect consequences on galactic
-and larger scales.  In most work, dark matter is taken to be a
-collisionless non-relativistic fluid (cold dark matter or CDM); in
-recent years, the simulation by \cite{2005Natur.435..629S} has been
-particularly influential in studying the formation of CDM structures.
-Other scenarios have also been considered, such as a cold condensing
-boson fluid \citep{2016ApJ...818...89S}.  There is a general
-consensus, however, that the origins of galaxy lie in the
-gravitational collapse, fragmentation, and mergers of dark-matter
-clumps, into which fell gas, cooling through radiative processes to
-form dense clouds and eventually stars.  There is, however, much
-debate about the details, of which \cite{2012RAA....12..917S} provide
-a nice summary.
-
-Strong-lensing galaxies are a useful source of information on the
-mutual dynamics and dark matter and gas in galaxies.  The topic has
-been explored in several studies
-\citep{2009ApJ...703L..51K,2011ApJ...740...97L,2012MNRAS.424..104L,
-  2016MNRAS.459.3677L,2016MNRAS.456..870B} but it is desirable to
-enlarge the samples from tens of lensing galaxies to thousands.  Doing
-so requires finding more lenses, of course, but also modelling their
-masses.
-
-Recent searches through the CFHTLS \citep{2012SPIE.8448E..0MC} using
-arc-finders
-\citep{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G} by
-machine learning \citep{2016arXiv160504309P} and by visual inspection
-by a citizen-science volunteers
-\citep[Space~Warps][]{2016MNRAS.455.1191M} have between them
-discovered an average of four lenses per square degree.  So one can be
-optimistic about finding many thousands of lenses in the next
-generation of wide-field surveys.  The expected flood of new lens
-discoveries will need a similarly huge modelling effort to
-reconstruct their mass distributions.  To prepare for the challenge of
-massive-sample lens modelling, \cite{2015MNRAS.447.2170K} developed a
-new modelling strategy, implemented as the SpaghettiLens system.  The
-idea is to collaborate with experienced members of the citizen-science
-community, who have already participated in lens discovery through
-Space~Warps, as well as several other projects involving astronomical
-data.  In this paper, we present SpaghettiLens models of
-lens-candidates discovered through Space~Warps.
-
-Section~\ref{sec:spl} summarises the SpaghettiLens system and
-discusses its ongoing development. A SpaghettiLens model consists of a
-statistical ensemble of free-form maps of the sky-projected mass
-distribution responsible for lensing.  Each lens candidates in
-practice gets modelled several times in a collaborative refinement
-process\footnote{See ``Collaborative gravitational lens
-  modelling\dots'' in {\tt http://letters.zooniverse.org} especially
-  the model tree.}  In this paper we report the most recent model for
-each lens, as representing a consensus among modellers, as to the best
-that could be achieved with the available data and software.
-Photometric lens redshifts are used; source redshifts are set to
-$z=2$ unless an unambiguous photometric redshift is available.
-The models can, however, be trivially rescaled to use better
-redshift values, as and when they become available.
-\cite{2015MNRAS.447.2170K} tested the system on simulated lenses and
-identified some areas for improvement.  The first two of those are
-taken up in Section~\ref{sec:spl}, along with a further idea. In
-\S~\ref{subsec:sourcefit} we introduce fitting of the brightness
-profiles of the source.  This feature has not yet been included in
-SpaghettiLens, but has been carried out in post-processing for a few
-especially interesting candidates.  In \S~\ref{subsec:hires} we show
-that making mass maps fine-grained in the central region relieves a
-tendency in the earlier work for mass to be too shallow. Then in
-\S~\ref{subsec:parameter} we consider the possibility of fitting a
-parametric lens model to the model ensemble; so far we have only been
-successful at extracting an Einstein radius.
-
-Section~\ref{sec:stellar-mass} explains how we compare the lensing
-mass with the mass in stars in the lensing galaxy.  We estimate the
-stellar mass by comparing galaxy magnitudes from the CFHTLS pipeline
-with the well-known stellar-population models of
-\cite{2003MNRAS.344.1000B}.  We then extrapolate the stellar masses to
-a halo mass using the abundance-matching prescription of
-\cite{2010ApJ...710..903M}.  Naturally, the lensing mass must be more
-than the stellar mass but no more than the total halo mass.  We then
-introduce what we call a halo index $\haloindex$ which gives an idea
-of how the lensing mass compares with these two bounds.
-
-Section~\ref{sec:examples} discusses ten of the systems, including six
-systems we found to be particularly interesting.  The online
-supplement gives results for all the modelled systems.
-
-In Section~\ref{sec:summary} and Table~\ref{tab:models} we display a
-concise characterisation of each modelled system, according to the
-image morphology and how clear or indistinct it is, whether the mass
-map and synthetic lensed image appear to be plausible, and how the
-model mass compares with the estimated stellar and full-halo masses.
-
-\section{Lens Modelling}\label{sec:spl}
-
-SpaghettiLens is an example of a medium-sized collaboration spawned by
-a large citizen-science project (in this case Space~Warps).  While
-collaboration with volunteers is essential to both, the form of
-collaboration is very different.  In Space~Warps, volunteers in a
-crowd of $\gtrsim10^4$ make independent contributions.  Each person is
-presented with a random selection of survey-patches and invited to (in
-effect) vote on each.  The system estimates each volunteer's skill
-level according to test-patches interspersed with the real data, and
-weights their votes accordingly \citep{2016MNRAS.455.1171M}.  There is
-an active forum for volunteers, but since everyone is seeing different
-data samples with minimal overlap, the forum has little if any
-influence on votes.  With SpaghettiLens, on the other hand, there is a
-small group of volunteers and their contributions are interdependent.
-
-A modeller's main input to SpaghettiLens is a sketch of arrival-time
-contours on a lensed system.  It gives the locations (or best-guess
-locations) of images of point-like sources, along with their ordering
-in arrival time, and their parities (minumum, saddle-point or
-maximum).  Such a sketch, which we call a spaghetti diagram, tends to
-resemble the form of lensed arcs, but it also in effect 
-encodes a proposal for its mass distribution.  A spaghetti diagram is
-read by a server-side numerical engine \citep[GLASS, developed
-  by][]{2014MNRAS.445.2181C} which then returns a statistical ensemble
-of mass maps.  The mass maps are made up of mass tiles and are
-free-form, except that they are required to be concentrated around the
-identified lens centre.  They are also required to reproduce the given
-image locations, parities and time ordering exactly.  Graphical
-representations of the mass map and arrival-time surface are returned
-to the user for review.  The user can post these results on a forum,
-or discard them and try again.  Volunteers can start the modelling
-process afresh, or they can take an existing model from the forum and
-modify its input spaghetti diagram or its accompanying options, and
-thus obtain a revised model.
-
-\subsection{Improved synthetic images}\label{subsec:sourcefit}
-
-The mass maps produced by current implementation of SpaghettiLens are
-based on images of point-like features.  No information about extended
-images is used, except in so far as they help the user identify images
-of point-like features.  The synthetic images offered to users are
-rudimentary, based on sources with conical light profiles.
-
-We have now developed a prototype of better way to generate synthetic
-images.  Figure~\figref{synthimg} illustrates.  First, areas
-containing lensed images are selected (green frames in the figure).
-The selected areas must contain no light from the lensing galaxy or
-from extraneous objects.  Pixels within the selected areas are mapped
-to a grid on the source plane, using bending angles given by the mass
-model.  The mapping from lens-plane pixels to source-plane grid cells
-is many-to-one, because of image multiplicity and magnification.  The
-brightness of each source-plane pixel is set to the mean of all the
-lens-plane pixels mapping to it.  Finally, the mapping is run back to
-the lens plane.  The result is a synthetic image.  In effect, one is
-reconstructing a source-plane brightness map by least-squares.
-
-The procedure is not yet implemented in SpaghettiLens but can be
-applied in post-processing.  The new synthetic images could be used to
-improve the mass reconstruction, by weighting the ensemble of maps
-according to how good the synthetic images are, but we have not
-attempted to do so as yet.
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{img/new_synth_img_detailed}
-  \caption{Synthetic lensed image with source-profile fitting in SW05
-    (J143454.4+522850). Top-left: original image, with areas
-    containing lensed images enclosed within green frames.  Top-right:
-    synthetic image (coloured arcs) with lensing galaxy and unrelated
-    objects in greyscale.  Bottom from left to right: reconstructed
-    source in colour, intensity (greyscale), count of lens plane
-    pixels per source plane pixel, residual of original image to
-    synthetic image.}
-  \label{fig:synthimg}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_11_hires_comparison}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_13_hires_comparison}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_33_hires_comparison}
-  \caption{Model improvement resulting from using smaller mass tiles
-    in the inner region of the mass model.  Shown here are the average
-    enclosed $\kappa$ within a given projected radius, for three
-    different reconstructions of a simulated lens (sim) from
-    Space~Warps.  In each panel, the dashed blue curve is the correct
-    answer.  The orange band represents the statistical ensemble from
-    SpaghettiLens, the orange line being the ensemble mean.  Locations of
-    images (maximum, saddle point, minimum) are marked with vertical
-    arrows.  Crossing the horizontal $\kappa=1$ line is the effective
-    Einstein radius \ER, and is so labelled. The upper panel is from
-    K\"ung et al., (2015) (see Figure~3 of that paper).  The middle
-    panel is the result when the innermost mass tile is replaced by 9
-    smaller tiles.  The lower panel results from replacing each of the
-    innermost 5 by 5 tiles each with 9 smaller tiles.}
-  \label{fig:subsampling}
-\end{figure}
-
-\subsection{Sub-sampling of central region}\label{subsec:hires}
-
-The models of simulated lenses in \cite{2015MNRAS.447.2170K} showed a
-tendency to be too shallow.  Allowing smaller mass tiles in the
-central region, thus allowing the pass profile to rise more steeply
-near the centre, was suggested as a possible cure.
-
-Figure~\figref{subsampling} shows an experiment with smaller mass
-tiles in the inner region.  Replacing the very central mass tile with
-9 smaller tiles allows for steeper central profiles.  Doing the same
-for the 25 innermost mass tiles solves the problem completely, but
-increases the number of mass tiles by 40\% and significantly increases
-the computational time.
-% 689 / 489 = 1.40899; in practice, runtime is more like x4 - x5!
-% runtimes from logfiles: 87/22, 86/21, 85/16
-The main modelling work in this paper was, however, done before the
-experiments with smaller mass tiles was complete.  Some of the models
-presented in this paper apply the intermediate option (corresponding
-to the middle panel in Figure~\figref{subsampling}) while others use
-the old system.  The results in this paper, however, mainly concern
-the enclosed mass in the outer regions, so shallowness in the central
-region should be inconsequential.
-
-\subsection{Parameterisation of pixel models} \label{subsec:parameter}
-In order to fit the set of pixelated models to a single parameterised model, a program was written that took a parameterised function and subtracted from it the mean and the principle components of the data, which were calculated using classical Principle Component Analysis.
-This created the residuals function.
-The number of components defined as principle was varied to test how this affected the output, and it was found that using 5 principle components tended to give a reasonable approximation.
-A masking function was added which selected only the data points that fell inside the image of the lens, and the principal components were clipped in order to keep the values inside the region of the ensemble of models.
-Any value higher than the clip was set to be the clip value.
-This was chosen to be 2.5 as, assuming that the data follows a Gaussian error distribution, almost all the values for the variance should lie between 2 and 3 standard deviations from the mean.
-Minimising the residuals function produces the set of parameters that fit the parameterised function to the original pixelated ensemble most closely.
-A least squares fit was used to perform this minimisation.
-The parameterised model function was obtained from the gravitational potential of an isothermal ellipsoid mass distribution \cite{2001astro.ph..2341K}.
-This model is frequently used to describe gravitational lenses as it tends to fit well with observations.
-The isothermal ellipsoid model outputs three useful parameters: the radius of the Einstein ring, the ellipticity of the model and the angle of the ellipticity from the vertical, giving the orientation of the galaxy.
-By applying this model to simulated lenses for which the values of these parameters were already known, it was possible to gain an estimate of the projected accuracy of the results, before applying the model to the candidate lensing galaxies.
-
-\begin{figure}
-  \caption{}
-  \label{fig:parameter}
-\end{figure}
-
-\section{Stellar mass}\label{sec:stellar-mass}
-
-Based on \cite{2003MNRAS.344.1000B} models.\todo{Description of
-  stellar-population models.}
-
-Following \cite{2010ApJ...710..903M}
-\begin{equation}
-\begin{aligned}
-\frac{\Mstel}{\Mhalo} &= \frac{2C_0}{(\Mhalo/M_1)^{-\beta} +
-                                     (\Mhalo/M_1)^\gamma} \\
-C_0 &= 0.02820, \quad M_1 = 10^{11.884} M_\odot \\
-\beta &= 1.057, \quad \gamma = 0.556.
-\end{aligned}
-\end{equation}
-
-\begin{equation}
-\haloindex = \frac{\ln(M/\Mstel)}{\ln(\Mhalo/\Mstel)}
-\end{equation}
-which we may call the halo-matching index.
-\begin{itemize}
-\item $\haloindex < 0$ is unphysical because $M<\Mstel$.
-\item $\haloindex = 0$ is when the stellar mass exactly accounts for the
-  lensing mass.
-\item $0 < \haloindex < 1$ is the typical situation, where the lens
-  includes stars and dark matter, but not the full halo.
-\item $\haloindex = 1$ means that the lens consists of the entire halo.
-\item $\haloindex > 1$ is in tension with abundance-matching, because the
-  lensing mass exceeds the expected halo mass.
-\end{itemize}
-
-\section{Example systems}\label{sec:examples}
-
-In this section we show modelling results for ten of the lens
-candidates.  The first five (see Figures~\figref{SW05}--\figref{SW29})
-are the most convincingly modelled systems.  The next three cases
-(Figures~\figref{SW42}--\figref{SW19}) are less good but still very
-plausible models, and are representative of the majority of the
-sample.  The last two are examples where the models were unconvincing
-(Figures~\figref{SW36}) or completely failed (\figref{SW57}).
-
-\begin{figure}
-  \inclfign{SW05}{ASW0007k4r_N7LTELSYTM}
-  \caption{Model results for SW05 (J143454.4+522850).  See text in
-    Section~\ref{sec:examples} for details.}
-  \label{fig:SW05}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW28}{ASW0007xrs_JHC3J2HYV7}
-  \caption{Model results for SW28 (J143055.9+572431).}
-  \label{fig:SW28}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW02}{ASW000619d_011489}
-  \caption{Model results for SW02 (J140522.2+574333).}
-  \label{fig:SW02}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW09}{ASW0002asp_5EKMWWVJHL}
-  \caption{Model results for SW09 (J020832.1-043315).}
-  \label{fig:SW09}
-\end{figure}
-
-\begin{figure}
-  \inclfign{SW29}{ASW0008qsm_TOFS7JNGEK}
-  \caption{Model results for SW29 (J143838.1+572647).}
-  \label{fig:SW29}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW42}{ASW00096rm_4Q3YCEWGLN}
-  \caption{Modelling results for SW42 (J221716.5+015826).}
-  \label{fig:SW42}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
-  \caption{Model results for SW58 (J143651.6+530705).}
-  \label{fig:SW58}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW19}{ASW0001ld7_OS3CYAKLRT}
-  \caption{Model results for SW19 (J020642.0-095157).}
-  \label{fig:SW19}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW36}{ASW000096t_7IPP7LWVOF}
-  \caption{Model results for SW36 (J090248.4-010232).}
-  \label{fig:SW36}
-\end{figure}
-
-\begin{figure}
-  \inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
-  \caption{Model results for SW57 (J143631.5+571131).}
-  \label{fig:SW57}
-\end{figure}
-
-Let us first consider Figure~\figref{SW05}, which shows model results
-from SW05 (J143454.4+522850).
-
-\begin{enumerate}
-\item In the upper row we have first a cutout of the Space~Warps
-  image, marked up with a spaghetti diagram.  There are four distinct
-  lensed images, and the spaghetti diagram proposes that they are a
-  minimum nearest to the lensing galaxy, a close minimum-saddle pair,
-  and a minimum further away. In Table~\ref{tab:models} we refer to
-  such configurations as IQ for inclined quad.
-\item Alongside is a synthetic image produced by modelling.  In it,
-  the fitted lensed images are shown in colour, while the lensing
-  galaxy and extraneous objects have been reduced to grayscale.
-  (Figure~\figref{synthimg} in \S~\ref{subsec:sourcefit} shows a
-  synthetic image from another model of the same system.) These two
-  panels are qualitative and display no units, and moreover, the
-  mutual alignment of the two panels is only approximate.
-\item The middle row shows contour maps from the model.  At middle
-  left, we have the arrival-time surface.
-\item At middle right we have the mass distribution in the usual
-  dimensionless form $\kappa$.  Again, these two panels are mainly
-  qualitative: both panels are spatially registered and centred on the
-  density-peak of the lens, but no scales have been included.
-\item The base row supplies spatial and mass scales.  The left panel
-  shows the circularly-averaged $\kappa$ of the model ensemble, with
-  increasing radius (in arcsec).  The four short vertical lines
-  correspond to the minima and saddle points marked in the upper-left
-  panel.  The effective Einstein radius \ER is also shown.  As the radius
-  scale indicates SW05 is comparatively large lens on the
-  sky.
-\item Lower right shows the total mass in the model against the
-  estimated stellar mass, alongside the values for the whole sample.
-  The lower-right shaded region is unphysical according to the
-  stellar-population models, because it gives $M<\Mstel$. The
-  upper-left shaded region is unphysical according to abundance
-  matching, because it gives $M>\Mhalo$.  That is to say, the unshaded
-  region is $0<\haloindex<1$.
-\end{enumerate}
-
-Proceeding to Figure~\figref{SW28}, we have one image close to the
-galaxy and an arc further away, which is interpreted as a blend of
-three images (a saddle point with two minima on either side).  We call
-this a long-axis quad or LQ configuration.  It is an indication of a
-mass distribution elongated along the arc-counterimage direction
-(along EW in this case).
-
-In Figures~\figref{SW02}--\figref{SW29} we see three candidates with
-an arc close the lensing galaxy and one image further away.  The arc
-is interpreted three images (a minimum with two saddle points on
-either side).  We call this a short-axis quad or SQ configuration.  It
-is an indication of a mass distribution elongated perpendicular to the
-arc-counterimage direction.
-
-Figures~\figref{SW02}--\figref{SW29} (SW05, SW28, SW02, SW09 and SW29)
-all correspond to the mass range of massive ellipticals.  SW05 is the
-most massive of all the candidates, with a galaxy-group scale mass.
-
-Figure~\figref{SW42} shows SW42.  The image morphology is similar to
-SW05 in Figure~\figref{SW05}, but the lens is much smaller on the sky,
-and the inferred mass is at the low end of the sample.  (The synthetic
-image shown is cruder than for the five previous figures, but that
-does not influence the mass models.)  If these preliminary findings
-are confirmed by follow-up observations, this could be the most
-dark-matter dominated lens known.\todo{Check photometry of this
-  candidate.}
-
-Figures~\figref{SW58} and \figref{SW19} appear plausible lens
-candidates.  Their morphology is similar to SW28, but the saddle-point
-counterimage is not visible.  We consider these lenses plausible but
-less convincing.
-
-Figures~\figref{SW36} and \figref{SW57} are cases where modelling
-failed.
-
-\section{Summary of models}\label{sec:summary}
-
-Table~\ref{tab:models} shows a summary of the analysis for many candidates.
-Missing rows are due to photometry data not available.
-
-\begin{enumerate}
-\item The image morphology concisely described: D for double, and
-  quads in sub-categorised in four ways
-  \citep[cf.][]{2003AJ....125.2769S} as LQ for long-axis quads (as in
-  Figure~\figref{SW28}), SQ for short-axis quads (as in
-  Figure~\figref{SW02}, \figref{SW09}, \figref{SW29}, \figref{SW42}),
-  IQ for inclined quads (as in Figure~\figref{SW05}) and CQ for very
-  symmetric core quads.
-\item Whether the images are unblended.  Distinct unblended images (as
-  in Figures~\figref{SW05} and \figref{SW42}) are an advantage in
-  modelling, but not essential.
-\item Whether all images are discernable.  The topography of an
-  arrival-time surface, as encoded by a spaghetti diagram, may require
-  more images than are visible.  For example, in Figure~\figref{SW58},
-  the modeller has put in a conjectural saddle point near the lensing
-  galaxy.
-\item Whether the lens is fairly isolated.
-\item Whether the arrival-time surface and synthetic image are
-  plausible.  In Figure~\figref{SW36} the model implies extra images
-  or a long arc, which are not seen.
-\item Whether the mass map is reasonable.
-\item The halo index $\haloindex$.
-\end{enumerate}
-
-\begin{table*}
-  \caption{Categorisation of SW models}
-  \label{tab:models}
-  \include{table}
-\end{table*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% The best way to enter references is to use BibTeX:
-\bibliographystyle{mnras}
-\bibliography{bib/bibli} % if your bibtex file is called example.bib
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \appendix
-
-\clearpage
-
-\section{TODO}
-\listoftodos
-
-% Don't change these lines
-\bsp	% typesetting comment
-\label{lastpage}
-\end{document}
+\begin{figure*}
+\includegraphics[width=\linewidth]{img/mlens_vs_mstel_one/mstel_vs_mtot_one}
+\caption{Total mass in the model against the estimated stellar mass,
+  alongside the values for the whole sample.  The lower-right shaded
+  region is unphysical according to the stellar-population models,
+  because it gives $M<\Mstel$. The upper-left shaded region is
+  unphysical according to abundance matching, because it gives
+  $M>\Mhalo$.  That is to say, the unshaded region is
+  $0<\haloindex<1$. \label{fig:stelmass}}
+\end{figure*}

### 2016-12-12 paper2.tex
edits

@@
 \hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,filecolor=blue,urlcolor=blue}
-
-\edef\smallwidth{0.4\linewidth}
-
-\newcommand{\inclfig}[2]{
-  \centering
-	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
-	\includegraphics[width=\smallwidth]{spaghetti/#2_img3_ipol}
-%	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
-        \includegraphics[width=\smallwidth]{img/arrival_spaghetti/#1_#2_arrival_spaghetti}%
-%        \includegraphics[width=\smallwidth]{spaghetti/#2_img2}
-        \includegraphics[width=\smallwidth]{img/kappa_map/#1_#2_kappa_map}
-	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
-	\includegraphics[width=\smallwidth]{img/mlens_vs_mstel/#1_#2_mstel_vs_mtot}
-}
-
-\newcommand{\inclfign}[2]{
-  \centering
-	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
-	\includegraphics[width=\smallwidth]{img/nsynth/#2_nsynth}
-%        \includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
-        \includegraphics[width=\smallwidth]{img/arrival_spaghetti/#1_#2_arrival_spaghetti}%
-%	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
-        \includegraphics[width=\smallwidth]{img/kappa_map/#1_#2_kappa_map}
-	\includegraphics[width=\smallwidth]{img/kappa_encl/#1_#2_kappa_encl}%
-	\includegraphics[width=\smallwidth]{img/mlens_vs_mstel/#1_#2_mstel_vs_mtot}
-}
 
@@
 
-\def\pwidth{.32\linewidth}
-
-\def\includeten#1#2{
-\includegraphics[width=\pwidth]{#1ASW0007iwp_4XBJWT3COV#2}%
-\includegraphics[width=\pwidth]{#1ASW0007xrs_JHC3J2HYV7#2}%
-\includegraphics[width=\pwidth]{#1ASW0008pag_5SXGXQYY6V#2}\\
-\includegraphics[width=\pwidth]{#1ASW0007k4r_N7LTELSYTM#2}%
-\includegraphics[width=\pwidth]{#1ASW00096rm_4Q3YCEWGLN#2}%
-\includegraphics[width=\pwidth]{#1ASW0001ld7_OS3CYAKLRT#2}\\
-\includegraphics[width=\pwidth]{#1ASW0002asp_5EKMWWVJHL#2}%
-\includegraphics[width=\pwidth]{#1ASW0008qsm_TOFS7JNGEK#2}%
-\includegraphics[width=\pwidth]{#1ASW000619d_011489#2}\\
-%\includegraphics[width=\pwidth]{#1ASW000096t_7IPP7LWVOF#2}%
-}
-
-\def\includezehn#1#2{
-\includegraphics[width=\pwidth]{#1SW58_ASW0007iwp_4XBJWT3COV#2}%   L
-\includegraphics[width=\pwidth]{#1SW28_ASW0007xrs_JHC3J2HYV7#2}%   L
-\includegraphics[width=\pwidth]{#1SW57_ASW0008pag_5SXGXQYY6V#2}\\% X
-\includegraphics[width=\pwidth]{#1SW05_ASW0007k4r_N7LTELSYTM#2}%   I
-\includegraphics[width=\pwidth]{#1SW42_ASW00096rm_4Q3YCEWGLN#2}%   I
-\includegraphics[width=\pwidth]{#1SW19_ASW0001ld7_OS3CYAKLRT#2}\\% I
-\includegraphics[width=\pwidth]{#1SW09_ASW0002asp_5EKMWWVJHL#2}%   S
-\includegraphics[width=\pwidth]{#1SW29_ASW0008qsm_TOFS7JNGEK#2}%   S
-\includegraphics[width=\pwidth]{#1SW02_ASW000619d_011489#2}\\%     S
-%\includegraphics[width=\pwidth]{#1SW36_ASW000096t_7IPP7LWVOF#2}%
-}
-
 \input parts/intro
 
-\input parts/spl
+% \input parts/spl
 
@@
 \input parts/stelmass
-
-\clearpage
 
@@
 
+\clearpage
+
+\input parts/figures
+
+\clearpage
+
 % \section{TODO}

### 2016-12-12 parts/massmodel.tex
figure changes
edits

@@
-\section{Mass models}
+\section{Mass models}\label{sec:massmodels}
 
-\begin{figure*}
-\includezehn{img/kappa_map/}{_kappa_map}
-\caption{\label{fig:kappa}}
-\end{figure*}
+A SpaghettiLens model consists of a statistical ensemble of free-form
+maps of the sky-projected mass distribution responsible for lensing.
+  Photometric lens
+redshifts are used; source redshifts are set to $z=2$ unless an
+unambiguous photometric redshift is available.  The models can,
+however, be trivially rescaled to use better redshift values, as and
+when they become available.
 
-\begin{figure*}
-\includezehn{img/arrival_spaghetti/}{_arrival_spaghetti}
-\caption{\label{fig:arriv}}
-\end{figure*}
-
-\begin{figure*}
-\includeten{img/nsynth/}{_nsynth}
-\label{fig:synth}
-\caption{}
-\end{figure*}
+A spaghetti diagram is read by a server-side numerical engine
+\citep[GLASS, developed by][]{2014MNRAS.445.2181C} which then returns
+a statistical ensemble of mass maps.  The mass maps are made up of
+mass tiles and are free-form, except that they are required to be
+concentrated around the identified lens centre.  They are also
+required to reproduce the given image locations, parities and time
+ordering exactly.  Graphical representations of the mass map and
+arrival-time surface are returned to the user for review.  The user
+can post these results on a forum, or discard them and try again.
+Volunteers can start the modelling process afresh, or they can take an
+existing model from the forum and modify its input spaghetti diagram
+or its accompanying options, and thus obtain a revised model.
 
@@
 alignment of the two panels is only approximate.
-
-\begin{figure*}
-\includezehn{img/kappa_encl/}{_kappa_encl}
-\caption{}
-\end{figure*}
 

### 2016-12-12 parts/morph.tex
figure changes
edits

@@
-\section{Image morphology}
+\section{Image morphology}\label{sec:morph}
+
+A modeller's main input to SpaghettiLens is a sketch of arrival-time
+contours on a lensed system.  It gives the locations (or best-guess
+locations) of images of point-like sources, along with their ordering
+in arrival time, and their parities (minumum, saddle-point or
+maximum).  Such a sketch, which we call a spaghetti diagram, tends to
+resemble the form of lensed arcs, but it also in effect 
+encodes a proposal for its mass distribution.
 
@@
 \begin{matrix}
-\rm SW05 & \rm SW42 & \rm SW28 \\
-\rm SW58 & \rm SW02 & \rm SW19 \\
-\rm SW09 & \rm SW29 & \rm SW57
+\rm SW58 & \rm SW28 & \rm SW57 \\
+\rm SW05 & \rm SW42 & \rm SW19 \\
+\rm SW09 & \rm SW29 & \rm SW02
 \end{matrix}
@@
 arc-counterimage direction.
-
-\begin{figure*}
-\includeten{spaghetti/}{_input}
-\caption{Marked-up images. \label{fig:markedup}}
-\end{figure*}

### 2016-12-12 parts/summary.tex

@@
-\section{Summary of models}
-
-Now we give a concise characterisation of each modelled system,
-according to the image morphology and how clear or indistinct it is,
-whether the mass map and synthetic lensed image appear to be
-plausible, and how the model mass compares with the estimated stellar
-and full-halo masses.
+\section{Summary of models}\label{sec:summary}
 
@@
 Missing rows are due to photometry data not available.
+
+Accordingly the the characterisation of each modelled system is
+(i)~according to the image morphology and how clear or indistinct it
+is, (ii)~whether the mass map and synthetic lensed image appear to be
+plausible, and (iii)~how the model mass compares with the estimated
+stellar and full-halo masses.
 
@@
 findings are confirmed by follow-up observations, this could be the
-most dark-matter dominated lens known.\todo{Check photometry of this
-  candidate.}
+most dark-matter dominated lens known.

### 2016-12-16 parts/stelmass.tex
figure changes
edits

--- 2016-10-03 parts/stelmass.tex
@@
 distribution is needed to derive accurate stellar masses
-\citep[e.g.][]{2009ApJS..185..253G,2011MNRAS.418.1587T}.
-However, estimates to within 0.3\,dex in $\log($M$_s$/M$_\odot)$ can be
-derived with a single colour, preferably tracing a rest-frame colour
-similar to $U-V$ \citep[see fig.~1 of][]{2008MNRAS.383..857F}. This
-paper presents a pilot study of the potential of SpaghettiLens to
-constrain the physical properties of strong lenses. Therefore, we
-further simplify the analysis by assuming a relationship between the
-apparent total magnitude and stellar mass, at the redshift of the
-lens. Note that for typical stellar population parameters, the
-variation of this relation is at most 1\,dex. In this work, we make
-use of the \citet{2003MNRAS.344.1000B} models to derive two functional
-forms of the stellar mass with respect to SDSS-$i$ band
-magnitudes. The models have solar metallicity, with a Chabrier
-IMF, and assume two different age trends: a ``young'' model, with a
+\citep[e.g.][]{2009ApJS..185..253G,2011MNRAS.418.1587T}.  However,
+estimates to within 0.3\,dex in $\log($M$_s$/M$_\odot)$ can be derived
+with a single colour, preferably tracing a rest-frame colour similar
+to $U-V$ \citep[see fig.~1 of][]{2008MNRAS.383..857F}.
+
+In this paper we further simplify the analysis by assuming a
+relationship between the apparent total magnitude and stellar mass, at
+the redshift of the lens.  For typical stellar population parameters,
+the variation of this relation is at most 1\,dex.  A further possible
+systematic error is contamination of the light of the lensing galaxy
+by the lensed galaxy.  Reducing or eliminating the latter would
+require detailed fitting of light distributions for each candidate,
+which we have not yet attempted.  These caveats notwithstanding, it is
+still interesting to compare the derived stellar mass with the lensing
+mass.
+
+We make use of the \citet{2003MNRAS.344.1000B} models to derive two
+functional forms of the stellar mass with respect to SDSS-$i$ band
+magnitudes. The models have solar metallicity, with a Chabrier IMF,
+and assume two different age trends: a ``young'' model, with a
 constant 500\,Myr age at all redshifts, and an ``old'' model where the
-age is the oldest one possible at each redshift, adopting a
-standard $\Lambda$CDM model with $H_0=70$\,km\,s$^{-1}$\,Mpc$^{-1}$
-and $\Omega_m=0.3$. We take a geometric mean of the output from these
-two models as the stellar mass of the lens. This rough estimate will
-be improved in future versions by use of the available optical and NIR
+age is the oldest one possible at each redshift, adopting a standard
+$\Lambda$CDM model with $H_0=70$\,km\,s$^{-1}$\,Mpc$^{-1}$ and
+$\Omega_m=0.3$. We take a geometric mean of the output from these two
+models as the stellar mass of the lens. This rough estimate will be
+improved in future versions by use of the available optical and NIR
 magnitudes to derive more accurate constrains on the stellar
@@
 \end{itemize}
-
-\begin{figure*}
-\includegraphics[width=\linewidth]{img/mlens_vs_mstel_one/mstel_vs_mtot_one}
-\caption{}
-\end{figure*}

### 2016-12-20 paper2.tex
bash magic rename
edits

@@
 $^{3}$Zooniverse, c/o Astrophysics Department, University of Oxford, Oxford OX1 3RH, UK \\
-$^{4}$Exascale Research Computing Lab, Campus Teratec, 2 Rue de la Piquetterie, 91680 Bruyeres-le-Chatel, France\\
+%$^{4}$Exascale Research Computing Lab, Campus Teratec, 2 Rue de la Piquetterie, 91680 Bruyeres-le-Chatel, France\\
+$^{4}$Physik-Department, Technische Universit\"at M\"unchen
+James-Franck-Str.~1, 85748 Garching, Germany\\
 $^{5}$Kavli Institute for Particle Astrophysics and Cosmology, Stanford University, 452 Lomita Mall, Stanford, CA 94035, USA\\

### 2016-12-20 parts/intro.tex
edits

@@
 Each lens candidates in practice gets modelled several times in a
-collaborative refinement process.\footnote{See ``Collaborative
+collaborative refinement process.\footnote{ See ``Collaborative
   gravitational lens modelling\dots'' in {\tt
-    http://letters.zooniverse.org} especially the model tree.}  This
-representing a consensus among modellers, as to the best that could be
-achieved with the available data and software.\footnote{This is in
-  contrast to the main Space~Warps project for discovering lenses, in
-  which volunteers in a crowd of $\gtrsim10^4$ make independent
-  contributions.  Each person is presented with a random selection of
-  survey-patches and invited to (in effect) vote on each.  The system
-  estimates each volunteer's skill level according to test-patches
-  interspersed with the real data, and weights their votes accordingly
+    http://letters.zooniverse.org} $\{${\em Appears no longer
+    available.}$\}$} This represents a consensus among modellers, as
+to the best that could be achieved with the available data and
+software.\footnote{This is in contrast to the main Space~Warps project
+  for discovering lenses, in which volunteers in a crowd of
+  $\gtrsim10^4$ make independent contributions.  Each person is
+  presented with a random selection of survey-patches and invited to
+  (in effect) vote on each.  The system estimates each volunteer's
+  skill level according to test-patches interspersed with the real
+  data, and weights their votes accordingly
   \citep{2016MNRAS.455.1171M}.  There is an active forum for

### 2016-12-20 img/model_assignment.tex

% Look up table, SWID -> Index:
% 02 AC
% 04 AE
% 05 AF
% 06 AG
% 08 AI
% 09 AJ
% 10 BA
% 11 BB
% 12 BC
% 13 BD
% 15 BF
% 16 BG
% 17 BH
% 18 BI
% 19 BJ
% 20 CA
% 21 CB
% 22 CC
% 23 CD
% 24 CE
% 26 CG
% 27 CH
% 28 CI
% 29 CJ
% 31 DB
% 33 DD
% 34 DE
% 35 DF
% 36 DG
% 38 DI
% 41 EB
% 42 EC
% 43 ED
% 44 EE
% 45 EF
% 46 EG
% 47 EH
% 53 FD
% 54 FE
% 56 FG
% 57 FH
% 58 FI

\newcommand{\inclAC}[1]{\includegraphics[width=\pwidth]{img/#1/SW02_ASW000619d_011489_#1}}
\newcommand{\inclAE}[1]{\includegraphics[width=\pwidth]{img/#1/SW04_ASW0009cjs_NJ5CC5YJAQ_#1}}
\newcommand{\inclAF}[1]{\includegraphics[width=\pwidth]{img/#1/SW05_ASW0007k4r_012771_#1}}
\newcommand{\inclAG}[1]{\includegraphics[width=\pwidth]{img/#1/SW06_ASW0008swn_BCY2NOUSLK_#1}}
\newcommand{\inclAI}[1]{\includegraphics[width=\pwidth]{img/#1/SW08_ASW00099ed_HISGRAIZL2_#1}}
\newcommand{\inclAJ}[1]{\includegraphics[width=\pwidth]{img/#1/SW09_ASW0002asp_5EKMWWVJHL_#1}}
\newcommand{\inclBA}[1]{\includegraphics[width=\pwidth]{img/#1/SW10_ASW0002bmc_VQYCYNONVW_#1}}
\newcommand{\inclBB}[1]{\includegraphics[width=\pwidth]{img/#1/SW11_ASW0002qtn_3TUJKHGED4_#1}}
\newcommand{\inclBC}[1]{\includegraphics[width=\pwidth]{img/#1/SW12_ASW0003wsu_012712_#1}}
\newcommand{\inclBD}[1]{\includegraphics[width=\pwidth]{img/#1/SW13_ASW00047ae_TGTIIF7HCV_#1}}
\newcommand{\inclBF}[1]{\includegraphics[width=\pwidth]{img/#1/SW15_ASW0004nan_QUOGDU2NN6_#1}}
\newcommand{\inclBG}[1]{\includegraphics[width=\pwidth]{img/#1/SW16_ASW0009bp2_013421_#1}}
\newcommand{\inclBH}[1]{\includegraphics[width=\pwidth]{img/#1/SW17_ASW0005rnb_AAKHMTYTMS_#1}}
\newcommand{\inclBI}[1]{\includegraphics[width=\pwidth]{img/#1/SW18_ASW0007hu2_D4UQI6M3ZU_#1}}
\newcommand{\inclBJ}[1]{\includegraphics[width=\pwidth]{img/#1/SW19_ASW0001ld7_OS3CYAKLRT_#1}}
\newcommand{\inclCA}[1]{\includegraphics[width=\pwidth]{img/#1/SW20_ASW0002dx7_3NYJG67KRT_#1}}
\newcommand{\inclCB}[1]{\includegraphics[width=\pwidth]{img/#1/SW21_ASW0004m3x_QZROE23AUH_#1}}
\newcommand{\inclCC}[1]{\includegraphics[width=\pwidth]{img/#1/SW22_ASW0009ab8_TGM4U2TZBS_#1}}
\newcommand{\inclCD}[1]{\includegraphics[width=\pwidth]{img/#1/SW23_ASW0003r61_002481_#1}}
\newcommand{\inclCE}[1]{\includegraphics[width=\pwidth]{img/#1/SW24_ASW00050sk_013406_#1}}
\newcommand{\inclCG}[1]{\includegraphics[width=\pwidth]{img/#1/SW26_ASW0005ma2_5ZZKUM3SWL_#1}}
\newcommand{\inclCH}[1]{\includegraphics[width=\pwidth]{img/#1/SW27_ASW0006jh5_5URN3BQFSV_#1}}
\newcommand{\inclCI}[1]{\includegraphics[width=\pwidth]{img/#1/SW28_ASW0007xrs_JHC3J2HYV7_#1}}
\newcommand{\inclCJ}[1]{\includegraphics[width=\pwidth]{img/#1/SW29_ASW0008qsm_TOFS7JNGEK_#1}}
\newcommand{\inclDB}[1]{\includegraphics[width=\pwidth]{img/#1/SW31_ASW00021r0_CIFSR5JFFU_#1}}
\newcommand{\inclDD}[1]{\includegraphics[width=\pwidth]{img/#1/SW33_ASW0003s0m_ECXCIRBDUJ_#1}}
\newcommand{\inclDE}[1]{\includegraphics[width=\pwidth]{img/#1/SW34_ASW00051ld_000291_#1}}
\newcommand{\inclDF}[1]{\includegraphics[width=\pwidth]{img/#1/SW35_ASW0004wgd_VWJ2LNN3VZ_#1}}
\newcommand{\inclDG}[1]{\includegraphics[width=\pwidth]{img/#1/SW36_ASW000096t_7IPP7LWVOF_#1}}
\newcommand{\inclDI}[1]{\includegraphics[width=\pwidth]{img/#1/SW38_ASW0009cp0_Z6IFI4SLLM_#1}}
\newcommand{\inclEB}[1]{\includegraphics[width=\pwidth]{img/#1/SW41_ASW0008xbu_BFXRMIQEAT_#1}}
\newcommand{\inclEC}[1]{\includegraphics[width=\pwidth]{img/#1/SW42_ASW00096rm_4Q3YCEWGLN_#1}}
\newcommand{\inclED}[1]{\includegraphics[width=\pwidth]{img/#1/SW43_ASW0001c3j_5R6UYQZUTI_#1}}
\newcommand{\inclEE}[1]{\includegraphics[width=\pwidth]{img/#1/SW44_ASW0002k40_000899_#1}}
\newcommand{\inclEF}[1]{\includegraphics[width=\pwidth]{img/#1/SW45_ASW00024id_013557_#1}}
\newcommand{\inclEG}[1]{\includegraphics[width=\pwidth]{img/#1/SW46_ASW00024q6_012523_#1}}
\newcommand{\inclEH}[1]{\includegraphics[width=\pwidth]{img/#1/SW47_ASW0003r6c_4HC3CREEAD_#1}}
\newcommand{\inclFD}[1]{\includegraphics[width=\pwidth]{img/#1/SW53_ASW00070vl_BPAV4GVOPP_#1}}
\newcommand{\inclFE}[1]{\includegraphics[width=\pwidth]{img/#1/SW54_ASW0007sez_SI4ELBAKL2_#1}}
\newcommand{\inclFG}[1]{\includegraphics[width=\pwidth]{img/#1/SW56_ASW0007pga_VHV6RQYYKZ_#1}}
\newcommand{\inclFH}[1]{\includegraphics[width=\pwidth]{img/#1/SW57_ASW0008pag_5SXGXQYY6V_#1}}
\newcommand{\inclFI}[1]{\includegraphics[width=\pwidth]{img/#1/SW58_ASW0007iwp_4XBJWT3COV_#1}}

\newcommand{\inclGrid}[1]{ %
\inclFI{#1} \inclCI{#1} \inclFH{#1}
\inclAF{#1} \inclEC{#1} \inclBJ{#1}
\inclAJ{#1} \inclCJ{#1} \inclAC{#1}
}

### 2016-12-27 parts/massmodel.tex
editing

@@
 extraneous objects have been reduced to grayscale.
-(Figure~\figref{synthimg} in \S~\ref{subsec:sourcefit} shows a
+(Figure~\figref{synthimg} in Appendix~\ref{subsec:sourcefit} shows a
 synthetic image from another model of the same system.) These two

### 2016-12-27 parts/morph.tex
editing

@@
 
-Figure~\ref{fig:markedup} shows cutouts of the Space~Warps image,
+Figure~\ref{fig:splinput} shows cutouts of the Space~Warps image,
 marked up with a spaghetti diagram.
-
-The lenses are arranged as follows.
-$$
-\begin{matrix}
-\rm SW58 & \rm SW28 & \rm SW57 \\
-\rm SW05 & \rm SW42 & \rm SW19 \\
-\rm SW09 & \rm SW29 & \rm SW02
-\end{matrix}
-$$ 
-$\{${\em Panels will be labelled, and this little table removed.}$\}$
 

### 2016-12-27 parts/summary.tex
editing

@@
 
-Table~\ref{tab:models} shows a summary of the analysis for many candidates.
-Missing rows are due to photometry data not available.
+This work follows up on lens candidates reported in
+\cite{2016MNRAS.455.1191M} from citizen-science volunteers, with
+modelling.  Volunteers role is collaborative.  No robotic competitors.
 
-Accordingly the the characterisation of each modelled system is
+Table~\ref{tab:models} characterises each modelled system is
 (i)~according to the image morphology and how clear or indistinct it
@@
 plausible, and (iii)~how the model mass compares with the estimated
-stellar and full-halo masses.
+stellar and full-halo masses.  Missing rows are due to photometry data
+not available.
+
+Figure~\ref{fig:stelmass} summarises the properties of the lens
+candidates
 

### 2017-01-20 parts/summary.tex
edits

@@
-\section{Summary of models}\label{sec:summary}
+\section{Discussion}\label{sec:summary}
 
@@
 Figure~\ref{fig:stelmass} summarises the properties of the lens
-candidates
-
-SW05, SW28, SW02, SW09 and SW29 all correspond to the mass range of
+candidates.  Most appear to have stellar and total mass typical of
 massive ellipticals.  SW05 is the most massive of all the candidates,
-with a galaxy-group scale mass.
-
-For SW42 the inferred mass is at the low end of the sample.  (The
-synthetic image shown is cruder than for the five previous figures,
-but that does not influence the mass models.)  If these preliminary
-findings are confirmed by follow-up observations, this could be the
-most dark-matter dominated lens known.
+with a galaxy-group scale mass.  Two systems, SW19 and SW42 have low
+mass; the lens models are not entirely satisfactory, but seems
+plausible.  If these are lenses, they are very interesting.  In
+particular SW42 could be the most dark-matter dominated lens known.

### 2017-02-10 parts/figures.tex
clean up all images
bash magic rename
fix figures
add input images with scalebar, fixes#4
editing
editing text

@@
-\def\pwidth{.32\linewidth}
-
-\def\includeten#1#2{
-\includegraphics[width=\pwidth]{#1ASW0007iwp_4XBJWT3COV#2}%
-\includegraphics[width=\pwidth]{#1ASW0007xrs_JHC3J2HYV7#2}%
-\includegraphics[width=\pwidth]{#1ASW0008pag_5SXGXQYY6V#2}\\
-\includegraphics[width=\pwidth]{#1ASW0007k4r_N7LTELSYTM#2}%
-\includegraphics[width=\pwidth]{#1ASW00096rm_4Q3YCEWGLN#2}%
-\includegraphics[width=\pwidth]{#1ASW0001ld7_OS3CYAKLRT#2}\\
-\includegraphics[width=\pwidth]{#1ASW0002asp_5EKMWWVJHL#2}%
-\includegraphics[width=\pwidth]{#1ASW0008qsm_TOFS7JNGEK#2}%
-\includegraphics[width=\pwidth]{#1ASW000619d_011489#2}\\
-%\includegraphics[width=\pwidth]{#1ASW000096t_7IPP7LWVOF#2}%
-}
-
-\def\includezehn#1#2{
-\includegraphics[width=\pwidth]{#1SW58_ASW0007iwp_4XBJWT3COV#2}%   L
-\includegraphics[width=\pwidth]{#1SW28_ASW0007xrs_JHC3J2HYV7#2}%   L
-\includegraphics[width=\pwidth]{#1SW57_ASW0008pag_5SXGXQYY6V#2}\\% X
-\includegraphics[width=\pwidth]{#1SW05_ASW0007k4r_N7LTELSYTM#2}%   I
-\includegraphics[width=\pwidth]{#1SW42_ASW00096rm_4Q3YCEWGLN#2}%   I
-\includegraphics[width=\pwidth]{#1SW19_ASW0001ld7_OS3CYAKLRT#2}\\% I
-\includegraphics[width=\pwidth]{#1SW09_ASW0002asp_5EKMWWVJHL#2}%   S
-\includegraphics[width=\pwidth]{#1SW29_ASW0008qsm_TOFS7JNGEK#2}%   S
-\includegraphics[width=\pwidth]{#1SW02_ASW000619d_011489#2}\\%     S
-%\includegraphics[width=\pwidth]{#1SW36_ASW000096t_7IPP7LWVOF#2}%
-}
-
 \begin{figure*}
-\includeten{spaghetti/}{_input}
-\caption{Marked-up images. \label{fig:markedup}}
+\inclGrid{spl-input}
+\caption{Nine of the lens candidates marked up with spaghetti
+  diagrams.  Red, blue and green dots are proposed locations for
+  maxima, minima and saddle points of the arrival time.  The curves
+  help guide the placement of the dots, but their precise appearance
+  has no significance.  This selection includes the best-modelled
+  systems, but also one case (SW57 at upper right) of unsuccessful
+  modelling. \label{fig:splinput}}
 \end{figure*}
@@
 \begin{figure*}
-\includezehn{img/arrival_spaghetti/}{_arrival_spaghetti}
-\caption{\label{fig:arriv}}
+\inclGrid{arrival_spaghetti}
+\caption{Arrival-time surfaces of the candidates from
+  Figure~\ref{fig:splinput}.
+  \label{fig:arriv}}
 \end{figure*}
@@
 \begin{figure*}
-\includeten{img/nsynth/}{_nsynth}
-\label{fig:synth}
-\caption{}
+\inclGrid{nsynth}
+\caption{Synthetic images of the systems from
+  Figures~\ref{fig:splinput}--\ref{fig:arriv}.
+  \label{fig:synth}}
 \end{figure*}
@@
 \begin{figure*}
-\includezehn{img/kappa_map/}{_kappa_map}
-\caption{\label{fig:kappa}}
+\inclGrid{kappa_map_interpol}
+\caption{Mass distribution $\kappa$ in the systems from
+  Figures~\ref{fig:splinput}--\ref{fig:synth}.
+  \label{fig:kappa}}
 \end{figure*}
@@
 \begin{figure*}
-\includezehn{img/kappa_encl/}{_kappa_encl}
-\caption{}
+\inclGrid{kappa_encl}
+\caption{Enclosed mass $\kappa$ in the systems from
+  Figures~\ref{fig:splinput}--\ref{fig:kappa}.
+  \label{fig:encl}}
 \end{figure*}
@@
 \end{figure*}
+
+\begin{table*}
+  \caption{Categorisation of SW models}
+  \label{tab:models}
+  \include{table}
+\end{table*}

### 2017-02-10 parts/intro.tex
editing text

--- 2016-12-12 parts/intro.tex
@@
 the overall configuration.  Second, interpretation as lensing
-galaxies.  Introduce some diagnostics.
+galaxies.
 
 Each lens candidates in practice gets modelled several times in a
-collaborative refinement process.\footnote{See ``Collaborative
-  gravitational lens modelling\dots'' in {\tt
-    http://letters.zooniverse.org} especially the model tree.}  This
-representing a consensus among modellers, as to the best that could be
-achieved with the available data and software.\footnote{This is in
-  contrast to the main Space~Warps project for discovering lenses, in
-  which volunteers in a crowd of $\gtrsim10^4$ make independent
-  contributions.  Each person is presented with a random selection of
-  survey-patches and invited to (in effect) vote on each.  The system
-  estimates each volunteer's skill level according to test-patches
-  interspersed with the real data, and weights their votes accordingly
-  \citep{2016MNRAS.455.1171M}.  There is an active forum for
-  volunteers, but since everyone is seeing different data samples with
-  minimal overlap, the forum has little if any influence on votes.}
+collaborative refinement process.  This represents a consensus among
+modellers, as to the best that could be achieved with the available
+data and software.
+
+We introduce some diagnostics.  There are three kinds of diagnostics.
 
 \begin{itemize}
-\item Section~\ref{sec:morph} discusses nine of the systems, including
-  six systems we found to be particularly interesting.  Morphology
-  from Figure~\ref{fig:markedup}.
+\item First we have diagnostics based on morphology of the system.
+  Section~\ref{sec:morph} and Figure~\ref{fig:splinput} explain.
 \begin{itemize}
@@
   SW28), SQ for short-axis quads (as in Figure~SW02,
-  SW09, SW29, SW42), IQ for inclined quads
-  (as in Figure~SW05) and CQ for very symmetric core quads.
+  SW09, SW29, SW42), IQ for inclined quads and CQ for very symmetric core quads.
 \item Whether the images are unblended.  Distinct unblended images (as
@@
 \end{itemize}
-\item Section~\ref{sec:massmodels}
+\item Second we have mass models, covered in Section~\ref{sec:massmodels}.
 \begin{itemize}
@@
   plausible.  For SW36 the model implies extra images or a long arc,
-  which are not seen.  Figures~\ref{fig:arriv} and \ref{fig:synth}.
+  which are not seen.  Figures~\ref{fig:arriv} and \ref{fig:synth} and
+  \ref{fig:encl}.
 \end{itemize}
-\item Section~\ref{sec:stellar-mass} explains how we compare the lensing
-mass with the mass in stars in the lensing galaxy.  We estimate the
-stellar mass by comparing galaxy magnitudes from the CFHTLS pipeline
-with the well-known stellar-population models of
-\cite{2003MNRAS.344.1000B}.  We then extrapolate the stellar masses to
-a halo mass using the abundance-matching prescription of
-\cite{2010ApJ...710..903M}.  Naturally, the lensing mass must be more
-than the stellar mass but no more than the total halo mass.  We then
-introduce what we call a halo index $\haloindex$ which gives an idea
-of how the lensing mass compares with these two bounds.
-Figure~\ref{fig:stelmass}.
+\item Third, whether the implied lensing mass is plausible, given the
+  star-light in the lensing galaxy.  Section~\ref{sec:stellar-mass}
+  explains how we compare the lensing mass with the mass in stars in
+  the lensing galaxy.  We estimate the stellar mass by comparing
+  galaxy magnitudes from the CFHTLS pipeline with the well-known
+  stellar-population models of \cite{2003MNRAS.344.1000B}.  We then
+  extrapolate the stellar masses to a halo mass using the
+  abundance-matching prescription of \cite{2010ApJ...710..903M}.
+  Naturally, the lensing mass must be more than the stellar mass but
+  no more than the total halo mass.  We then introduce what we call a
+  halo index $\haloindex$ which gives an idea of how the lensing mass
+  compares with these two bounds.  Figure~\ref{fig:stelmass}.
 \end{itemize}
 
-In this paper we report the most recent model for each lens, as
+Section~\ref{sec:summary} summarises and tabulates the diagnostics in
+Table~\ref{tab:models}.
 
-Section~\ref{sec:summary} builds Table~\ref{tab:models}.
 The online supplement gives results for all the modelled systems.

### 2017-02-10 parts/summary.tex
editing text

@@
 particular SW42 could be the most dark-matter dominated lens known.
+
+Collorative modelling\footnote{ See ``Collaborative gravitational lens
+  modelling\dots'' in {\tt http://letters.zooniverse.org} $\{${\em
+    Appears no longer available.}$\}$}
+by volunteers.\footnote{In the
+  main Space~Warps project for discovering lenses, volunteers in a
+  crowd of $\gtrsim10^4$ make independent contributions.  Each person
+  is presented with a random selection of survey-patches and invited
+  to (in effect) vote on each.  The system estimates each volunteer's
+  skill level according to test-patches interspersed with the real
+  data, and weights their votes accordingly
+  \citep{2016MNRAS.455.1171M}.  There is an active forum for
+  volunteers, but since everyone is seeing different data samples with
+  minimal overlap, the forum has little if any influence on votes.}

### 2017-02-13 parts/morph.tex
morphological diagnostics described

--- 2016-10-03 parts/morph.tex
@@
-\section{Image morphology}
+\section{Image morphology}\label{sec:morph}
 
-Figure~\ref{fig:markedup} shows cutouts of the Space~Warps image,
-marked up with a spaghetti diagram.
+A modeller's main input to the lens-modelling process is a markup of
+the candidate lens system, with what we call a spaghetti diagram.
+This is a sketch of the arrival-time surface from a point-like source,
+with proposed locations of maxima, minima and saddle points, and an
+implied time-ordering of the images.  Such information encodes a
+starting proposal for the mass distribution.  A spaghetti diagram is
+thus a completely abstract construction, and moreover it refers to a
+simplified system with a point source.  However, spaghetti diagrams
+are intuitive because they tend to resemble the form of lensed arcs,
+and of course they are simple to draw, and easy to vary and refine in
+an open collaborative environment.  This makes them very practical for
+non-professional lens enthusiasts in the citizen-science community.
+Details and tests are given in \cite{2015MNRAS.447.2170K}.
 
-The lenses are arranged as follows.
-$$
-\begin{matrix}
-\rm SW05 & \rm SW42 & \rm SW28 \\
-\rm SW58 & \rm SW02 & \rm SW19 \\
-\rm SW09 & \rm SW29 & \rm SW57
-\end{matrix}
-$$ 
-$\{${\em Panels will be labelled, and this little table removed.}$\}$
+We now discuss the diagnostics that can be given from the process of
+drawing the spaghetti diagram, even before detailed mass-modelling
+takes place.  Figure~\ref{fig:splinput} shows nine examples, each
+consisting of a cutout of the Space~Warps image of a lens candidate,
+marked up with a spaghetti diagrams.  The online supplement includes
+variant spaghetti diagrams for each of these systems, and similarly
+for all the modelled candidates.
 
-We show modelling results for nine of the lens candidates.  The first
-five (see Figures~\figref{SW05}--\figref{SW29}) are the most
-convincingly modelled systems.  The next three cases
-(Figures~\figref{SW42}--\figref{SW19}) are less good but still very
-plausible models, and are representative of the majority of the
-sample.  The last two are examples where the models were unconvincing
-(Figures~\figref{SW36}) or completely failed (\figref{SW57}).
+All the examples in Figure~\ref{fig:splinput} identify five locations:
+the centre of the main lensing galaxy, which is also a maximum of the
+arrival time surface (red dots); two minima (blue dots); and two
+saddle points (green dots and also self-intersections of the curves).
+Only two (SW05 and SW42) of the nine systems, however, have five
+distinct features in plausible locations.  In the other seven
+examples, an arc is interpreted as a blend of three or four images.
+This gives the `unblended images' diagnostic.  Note that this
+characterisation could be different if the spaghetti diagram is
+different.  For example, SW28 has also been modelled with the arc on
+the right interpreted as a single image, rather than as three images
+as shown in the figure; for such a model, `unblended images' would be
+true.
+
+The second diagnostic is whether all images are visible.  For example,
+we see in SW58 at the top left of Figure~\ref{fig:splinput} that an
+image at the second minimum is conjectural and does not correspond to
+any visible feature.
+
+The third diagnostic is whether the lens is fairly isolated, or
+whether there are other galaxies in the field that probably contribute
+significantly to the lensing.  For this, we do not consider stars or
+other clearly foregound objects.  Secondary lensing galaxies can be
+marked by the volunteer alongside the spaghetti diagrams.  An example
+can be seen as the grey dot and circle in the cutout with SW57 at the
+top right of Figure~\ref{fig:splinput}.  Objects marked in this way
+are modelled as point masses.  Other possible contributors to lensing
+are galaxies or groups or that are not in the immediately vicinity of
+the lensed images, yet massive enough to have an effect.  These are
+allowed for by allowing a constant but adjustable external shear.
+
+We remark that blended images or missing images or perturbing galaxies
+do not imply that a given candidate is unlikely to be a lens.  They
+mean, rather, that the models are more uncertain and perhaps could be
+more easily improved by trying further variations in the markup.
+
+The fourth diagnostic is based on the fact that the arrangement of
+lensed images of a pointlike source through a non-circular
+gravitational lens depends on the location of the source relative to
+the long and short axes of the lens.  This dependence is quite robust
+and independent of many other details of the lensing mass
+distribution.  Sources close to being dead-centre behind a lens tend
+to produce quads, sources at larger transverse distance tend to
+produce doubles.  We denote these as Q and D respectively, and add a
+prefix to the Q systems, as follows: we write LQ if the source is
+inferred as displaced along the long axis of the lens, SQ if displaced
+along the short axis, IQ if inclined to both axes.  Although the
+unlensed source and its location are obviously not seen, the LQ, SQ
+and IQ cases correspond to easily-seen image morphologies \citep[see,
+  e.g.,][]{2003AJ....125.2769S}.
+\begin{itemize}
+\item The simplest is the SQ case: this creates a saddle point and two
+  minima in an arc, with the second saddle point on the other side of
+  the lensing galaxy, and closer to the galaxy than the arc is.  SW58
+  and SW28 in the upper row of Figure~\ref{fig:splinput} are typical
+  examples of SQ.
+\item The middle row of Figure~\ref{fig:splinput} shows three IQ
+  systems, SW05, SW42 and SW19.  This type has a characteristic
+  asymmetry, often with two images close together.
+\item The lower row of Figure~\ref{fig:splinput} shows three LQ
+  systems, SW09, SW29 and SW02, and the failed model SW57 at top right
+  also possibly belonging to this category.  Here the images have a
+  fairly symmetric arrangement with an arc and a counter-image on the
+  other side, but the spaghetti diagram is completely asymmetric.  LQ
+  can be visually distinguished from SQ from the relative distances of
+  the arc and the counter-image.  For LQ the arc is closer, for SQ the
+  counter-image is closer.
+\end{itemize}
+
+\endinput
 

### 2017-02-15 parts/figures.tex
morphological diagnostics described
editing

@@
   systems, but also one case (SW57 at upper right) of unsuccessful
-  modelling. \label{fig:splinput}}
+  modelling.  Since the modelling process is collaborative among the
+  volunteers, with anyone welcome to contribute new models or modify
+  existing ones, there are variant spaghetti diagrams for all the
+  modelled systems.  The online supplement displays all the models
+  presented for discussion during this work.
+\label{fig:splinput}}
+\end{figure*}
+
+\begin{figure*}
+\inclGrid{kappa_map_interpol}
+\caption{Mass distribution $\kappa$ in the systems from
+  Figures~\ref{fig:splinput}.
+\label{fig:kappa}}
+\end{figure*}
+
+\begin{figure*}
+\inclGrid{kappa_encl}
+\caption{Enclosed mass within a given projected radius, expressed as
+  the mean $\kappa$ with a given number of arcsec from the centre of
+  the lensing galaxy.  The systems are the same as in
+  Figures~\ref{fig:splinput}--\ref{fig:kappa}.  The orange band in
+  each panel refers to the full ensemble of mass maps in the model,
+  while the red curve is the ensemble average.  The dashed vertical
+  line indicates the notional Einstein radius, or where the mean
+  enclosed $\kappa$ is unity.  The short vertical arrows indicate the
+  positions of the images (maxima, saddle points and minima).
+  \label{fig:encl}}
 \end{figure*}
@@
 \inclGrid{arrival_spaghetti}
-\caption{Arrival-time surfaces of the candidates from
-  Figure~\ref{fig:splinput}.
+\caption{Arrival-time surfaces of the systems from
+  Figure~\ref{fig:splinput}--\ref{fig:encl}.
   \label{fig:arriv}}
@@
   \label{fig:synth}}
-\end{figure*}
-
-\begin{figure*}
-\inclGrid{kappa_map_interpol}
-\caption{Mass distribution $\kappa$ in the systems from
-  Figures~\ref{fig:splinput}--\ref{fig:synth}.
-  \label{fig:kappa}}
-\end{figure*}
-
-\begin{figure*}
-\inclGrid{kappa_encl}
-\caption{Enclosed mass $\kappa$ in the systems from
-  Figures~\ref{fig:splinput}--\ref{fig:kappa}.
-  \label{fig:encl}}
 \end{figure*}

### 2017-02-15 parts/massmodel.tex
editing

--- 2016-10-03 parts/massmodel.tex
@@
-\section{Mass models}
+\section{Mass models}\label{sec:massmodels}
 
-\begin{figure*}
-\includezehn{img/kappa_map/}{_kappa_map}
-\caption{\label{fig:kappa}}
-\end{figure*}
+Once a spaghetti diagram has been drawn on a web browser, it is
+forwarded to a server-side numerical framework, which searches for
+mass maps consistent with the given image locations, parities and time
+ordering.  The mass maps are made up of mass tiles and are free-form,
+but are required to be concentrated around the identified lens centre
+\citep[see][for the precise formulation of the search
+  problem.]{2014MNRAS.445.2181C} Assuming such mass distributions can
+be found (in practise, usually the case) a statistical ensemble of
+two-dimensional mass maps is returned.  This ensemble, along with
+derived quantities and uncertainties, makes up one SpaghettiLens
+model.
 
-\begin{figure*}
-\includezehn{img/arrival_spaghetti/}{_arrival_spaghetti}
-\caption{\label{fig:arriv}}
-\end{figure*}
+The mass distribution will naturally depend on the lens and source
+redshifts, which are unknown when a lens candidate is first
+identified.  But this is not a problem, because a model can be
+trivially rescaled to use better redshift values, as and when they
+become available.  This paper uses pipeline photometric redshifts for
+the candidate lensing galaxies.  Source redshifts are set to $z=2$
+unless an unambiguous photometric redshift is available.
 
-\begin{figure*}
-\includeten{img/nsynth/}{_nsynth}
-\label{fig:synth}
-\caption{}
-\end{figure*}
+Figure~\ref{fig:kappa}
+
+Figure~\ref{fig:encl} shows the circularly-averaged $\kappa$ of the
+model ensemble, with increasing radius (in arcsec).  The effective
+Einstein radius \ER is also shown.
+
+Figure~\ref{fig:arriv}
+
+Figure~\ref{fig:synth}
+New method, see also Figure~\figref{synthimg} in
+Appendix~\ref{subsec:sourcefit}.
+
+\endinput
+
+  The ensemble average
+can, however, be a useful representative of the whole ensemble.  The
+user interface of SpaghettiLens returns graphical representations of
+the ensemble-average mass map and some derived quantities to the
+modeller for review.  The modeller can post these results on a forum,
+or discard them and try again.  Other volunteers can start the
+modelling process afresh, or they can take an existing model from the
+forum and modify its input spaghetti diagram or its accompanying
+options, and thus obtain a revised model.
 
@@
 extraneous objects have been reduced to grayscale.
-(Figure~\figref{synthimg} in \S~\ref{subsec:sourcefit} shows a
-synthetic image from another model of the same system.) These two
+) These two
 panels are qualitative and display no units, and moreover, the mutual
 alignment of the two panels is only approximate.
-
-\begin{figure*}
-\includezehn{img/kappa_encl/}{_kappa_encl}
-\caption{}
-\end{figure*}
 
@@
 \item The base row supplies spatial and mass scales.  The left panel
-  shows the circularly-averaged $\kappa$ of the model ensemble, with
-  increasing radius (in arcsec).  The four short vertical lines
-  correspond to the minima and saddle points marked in the upper-left
-  panel.  The effective Einstein radius \ER is also shown.  As the radius
-  scale indicates SW05 is comparatively large lens on the
-  sky.
+
 \item 

### 2017-02-15 parts/figures.tex
edits

@@
 \begin{figure*}
-\inclGrid{kappa_map_interpol}
-\caption{Mass distribution $\kappa$ in the systems from
-  Figures~\ref{fig:splinput}.
-\label{fig:kappa}}
-\end{figure*}
-
-\begin{figure*}
-\inclGrid{kappa_encl}
-\caption{Enclosed mass within a given projected radius, expressed as
-  the mean $\kappa$ with a given number of arcsec from the centre of
-  the lensing galaxy.  The systems are the same as in
-  Figures~\ref{fig:splinput}--\ref{fig:kappa}.  The orange band in
-  each panel refers to the full ensemble of mass maps in the model,
-  while the red curve is the ensemble average.  The dashed vertical
-  line indicates the notional Einstein radius, or where the mean
-  enclosed $\kappa$ is unity.  The short vertical arrows indicate the
-  positions of the images (maxima, saddle points and minima).
-  \label{fig:encl}}
-\end{figure*}
-
-\begin{figure*}
 \inclGrid{arrival_spaghetti}
-\caption{Arrival-time surfaces of the systems from
-  Figure~\ref{fig:splinput}--\ref{fig:encl}.
+\caption{Arrival-time surfaces for models of the systems from
+  Figure~\ref{fig:splinput}.  These are cleaned-up versions of the
+  original spaghetti diagrams.  The registration differs slightly from
+  Figure~\ref{fig:splinput}, but the coloured dots represent exactly
+  the sky positions specified in the earlier figure.  The orange
+  contours only qualitatively resemble the earlier pink curves, as
+  they are now precise saddle-point contours from lens models.
   \label{fig:arriv}}
@@
 \caption{Synthetic images of the systems from
-  Figures~\ref{fig:splinput}--\ref{fig:arriv}.
+  Figures~\ref{fig:splinput}, derived from the lens models.  The
+  reconstructed lensed features are keep the Space~Warps false-colour
+  scheme from Figures~\ref{fig:splinput}.  The rest has been changed
+  to black-and-white.
   \label{fig:synth}}
+\end{figure*}
+
+\begin{figure*}
+\inclGrid{kappa_map_interpol}
+\caption{Mass distribution $\kappa$ for which the results
+  Figures~\ref{fig:arriv}--\ref{fig:synth} were derived.
+\label{fig:kappa}}
+\end{figure*}
+
+\begin{figure*}
+\inclGrid{kappa_encl}
+\caption{Cumulative circular-averages of the mass maps from
+  \ref{fig:kappa}, with uncertainties.  More precisely, we show the
+  enclosed mass within a given projected radius, expressed as the mean
+  $\kappa$ with a given number of arcsec from the centre of the
+  lensing galaxy.  The orange bands refer to the full ensemble of mass
+  maps for the models, while the red curves show the ensemble
+  averages.  The dashed vertical line indicates the notional Einstein
+  radius, or where the mean enclosed $\kappa$ is unity.  The short
+  vertical arrows marks the positions of the images (maxima, saddle
+  points and minima).
+  \label{fig:encl}}
 \end{figure*}
@@
 \caption{Total mass in the model against the estimated stellar mass,
-  alongside the values for the whole sample.  The lower-right shaded
-  region is unphysical according to the stellar-population models,
-  because it gives $M<\Mstel$. The upper-left shaded region is
+  alongside the values for the whole sample.  (The labelled orange
+  bars are the systems shown in detail in
+  Figures~\ref{fig:splinput}--\ref{fig:encl}.)  The lower-right
+  shaded region is unphysical according to the stellar-population
+  models, because it gives $M<\Mstel$. The upper-left shaded region is
   unphysical according to abundance matching, because it gives

### 2017-02-16 parts/intro.tex

@@
 Space~Warps, as well as several other projects involving astronomical
-data.  In this paper, we present SpaghettiLens models of lens-candidates
-discovered through Space~Warps.
+data.
 
-Purpose is twofold.  First, see if plausible mass models can produce
-the overall configuration.  Second, interpretation as lensing
-galaxies.
+In this paper, we present SpaghettiLens models of lens-candidates
+discovered through Space~Warps.  Purpose is twofold.  First, see if
+plausible mass models can produce the overall configuration.  Second,
+interpretation as lensing galaxies.
 
-Each lens candidates in practice gets modelled several times in a
-collaborative refinement process.  This represents a consensus among
-modellers, as to the best that could be achieved with the available
-data and software.
+Each lens candidates is modelled in a collaborative refinement
+process, where anyone interested can creata a new model or modify an
+existing model to try and make it better.\footnote{This is in contrast
+  to the main Space~Warps project for discovering lenses, where
+  volunteers in a crowd of $\gtrsim10^4$ make independent
+  contributions.  Each person is presented with a random selection of
+  survey-patches and invited to (in effect) vote on each.  The system
+  estimates each volunteer's skill level according to test-patches
+  interspersed with the real data, and weights their votes accordingly
+  \citep{2016MNRAS.455.1171M}.  There is an active forum for
+  volunteers, but since everyone is seeing different data samples with
+  minimal overlap, the forum has little if any influence on votes.}
+The result represents a consensus among contributors, as to the best
+that could be achieved with the available data and software.
 
-We introduce some diagnostics.  There are three kinds of diagnostics.
+The modelling process assigns seven diagnostics to each lens
+candidate, as follows.
 
 \begin{itemize}
-\item First we have diagnostics based on morphology of the system.
-  Section~\ref{sec:morph} and Figure~\ref{fig:splinput} explain.
+\item First we have diagnostics based on morphology of the
+  system.\todo{Make ordering consistent in text and
+    Table~\ref{tab:models}.}  Section~\ref{sec:morph} and
+  Figure~\ref{fig:splinput} explain.
 \begin{itemize}
-\item The image morphology concisely described: D for double, and
-  quads in sub-categorised in four ways
-  \citep[cf.][]{2003AJ....125.2769S} as LQ for long-axis quads (as in
-  SW28), SQ for short-axis quads (as in Figure~SW02,
-  SW09, SW29, SW42), IQ for inclined quads and CQ for very symmetric core quads.
-\item Whether the images are unblended.  Distinct unblended images (as
-  in Figures~SW05 and SW42) are an advantage in
-  modelling, but not essential.
+\item Whether the images are unblended.  Distinct unblended images are
+  an advantage in modelling, but not essential.
 \item Whether all images are discernable.  The topography of an
   arrival-time surface, as encoded by a spaghetti diagram, may require
-  more images than are visible.  For example, in Figure~SW58,
-  the modeller has put in a conjectural saddle point near the lensing
-  galaxy.
+  more images than are visible, in which case the modeller has to
+  insert conjectural image positions.
 \item Whether the lens is fairly isolated.
+\item The image morphology concisely described: double or quads,
+  further sub-categorised to indicate the elongation direction of the
+  lensing mass.
 \end{itemize}

### 2017-02-16 parts/morph.tex

@@
 consisting of a cutout of the Space~Warps image of a lens candidate,
-marked up with a spaghetti diagrams.  The online supplement includes
-variant spaghetti diagrams for each of these systems, and similarly
-for all the modelled candidates.
+marked up with a spaghetti diagrams.
 
@@
 \end{itemize}
+Although the labels `short-axis quad' and so on are not standard in
+the literature, the morphological classification they express is
+familiar to experienced modellers.  Hence they can be useful to
+researchers wishing to apply other modelling methods to the same
+systems.
 

### 2017-02-17 parts/massmodel.tex
editing

@@
 
-The mass distribution will naturally depend on the lens and source
-redshifts, which are unknown when a lens candidate is first
-identified.  But this is not a problem, because a model can be
-trivially rescaled to use better redshift values, as and when they
-become available.  This paper uses pipeline photometric redshifts for
-the candidate lensing galaxies.  Source redshifts are set to $z=2$
-unless an unambiguous photometric redshift is available.
+The mass will naturally depend on the lens and source redshifts, which
+are unknown when a lens candidate is first identified.  But this is
+not a problem, because a model can be trivially rescaled to use better
+redshift values, as and when they become available.  This work applies
+photometric redshifts from the CFHTLS pipeline to the candidate
+lensing galaxies.  Source redshifts are set to $z=2$ unless an
+unambiguous photometric redshift is available.
+
+The ensemble of mass maps can be post-processed in many different
+ways.  Four different graphical quantities are particularly useful.
+
+Figure~\ref{fig:arriv} shows arrival-time surfaces corresponding to
+the spaghetti diagrams in Figure~\ref{fig:splinput}.  The arrival-time
+contours look like a machine-made elaborations of the input spaghetti
+diagrams.  If the saddle-point contours in the arrival time are
+qualitatively the same as the curves in the spaghetti diagram (the
+detailed shape of the spaghetti curves is unimportant), it immediately
+suggests a successful model.  On the other hand, if the arrival-time
+surface has unexpected minima or saddle points, and especially if the
+unexpected features are far from identified lens images, that signals
+a doubtful model.  Figure~\ref{fig:synth} shows what we call synthetic
+images, meaning reconstructions of the extended lensed features by
+fitting for a source.  These were generated by new method, explained
+in Appendix~\ref{subsec:sourcefit}, implemented in offline
+post-processing after the modelling process was complete.  The
+synthetic images provided by SpaghettiLens during the collaborative
+modelling and discussion were more crude.
+
+The arrival-time surface and synthetic image are summarised by one
+diagnostic, the most important of all: are the lensed features
+satisfactorily repoduced?  This diagnostic remains a judgement call by
+modellers.  A useful quantitative criterion for whether the synthetic
+image is consistent with the data would need to allow for PSF
+dependence and unmodelled substructure ---otherwise all models would
+be summarily rejected--- and it is not clear how to do this.
 
@@
 
-Figure~\ref{fig:encl} shows the circularly-averaged $\kappa$ of the
-model ensemble, with increasing radius (in arcsec).  The effective
-Einstein radius \ER is also shown.
-
-Figure~\ref{fig:arriv}
-
-Figure~\ref{fig:synth}
-New method, see also Figure~\figref{synthimg} in
-Appendix~\ref{subsec:sourcefit}.
+Figure~\ref{fig:encl}. Appendix~\ref{subsec:hires} describes
+improvements made since our earlier work \citep{2015MNRAS.447.2170K}
 

### 2017-02-17 parts/figures.tex
editing
more text

@@
 \caption{Arrival-time surfaces for models of the systems from
-  Figure~\ref{fig:splinput}.  These are cleaned-up versions of the
-  original spaghetti diagrams.  The registration differs slightly from
+  Figure~\ref{fig:splinput}.  The registration differs slightly from
   Figure~\ref{fig:splinput}, but the coloured dots represent exactly
@@
 \caption{Cumulative circular-averages of the mass maps from
-  \ref{fig:kappa}, with uncertainties.  More precisely, we show the
-  enclosed mass within a given projected radius, expressed as the mean
-  $\kappa$ with a given number of arcsec from the centre of the
+  Figure~\ref{fig:kappa}, with uncertainties.  More precisely, we show
+  the enclosed mass within a given projected radius, expressed as the
+  mean $\kappa$ with a given number of arcsec from the centre of the
   lensing galaxy.  The orange bands refer to the full ensemble of mass
@@
   bars are the systems shown in detail in
-  Figures~\ref{fig:splinput}--\ref{fig:encl}.)  The lower-right
-  shaded region is unphysical according to the stellar-population
-  models, because it gives $M<\Mstel$. The upper-left shaded region is
-  unphysical according to abundance matching, because it gives
-  $M>\Mhalo$.  That is to say, the unshaded region is
+  Figures~\ref{fig:splinput}--\ref{fig:encl}.)  The lower-right shaded
+  region is unphysical according to the stellar-population models,
+  because it gives $M<\Mstel$. The upper-left shaded region is
+  unphysical according to abundance matching (see
+  Section~\ref{sec:stellar-mass}) because it gives $M>\Mhalo$.  That
+  is to say, the unshaded region is
   $0<\haloindex<1$. \label{fig:stelmass}}

### 2017-02-17 parts/intro.tex
more text

@@
 \citep{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G} by
-machine learning \citep{2016arXiv160504309P} and by visual inspection
+machine learning \citep{2016A&A...592A..75P} and by visual inspection
 by a citizen-science volunteers

### 2017-02-17 parts/massmodel.tex
more text

@@
 
-Figure~\ref{fig:kappa}
+Figure~\ref{fig:kappa} shows projected mass maps of the example
+systems.  This figure shows the tiled character of the mass map.  (The
+mass maps displayed during modelling interpolated over the tiles.)
+The modelling numerics uses an analytical integral over square tiles,
+so the lens equation is always continuous and the arrival time is
+smooth.  We also remark that this figure refers to the ensemble
+average of each model, and the spread in the ensemble is not shown
+here; the arrival-time surfaces and synthetic images in the two
+previous figures also derive from the ensemble-average mass
+distribution.  Figure~\ref{fig:encl} shows the enclosed-mass profiles,
+expressed as the average convergence $\kappa$ within circles of given
+projected radius.  This time, uncertainties are included.
+Appendix~\ref{subsec:hires} describes improvements made since our
+earlier work \citep{2015MNRAS.447.2170K}, to allow for steeper
+profiles in the inner regions.  The enclosed mass is typically best
+constrained at the notional Einstein radius, becoming more uncertain
+at larger and smaller radii.
 
-Figure~\ref{fig:encl}. Appendix~\ref{subsec:hires} describes
-improvements made since our earlier work \citep{2015MNRAS.447.2170K}
+The mass maps and mass profiles are the basis of a further diagnostic:
+are the mass distributions plausible?
 

### 2017-02-19 parts/massmodel.tex
edits

@@
   problem.]{2014MNRAS.445.2181C} Assuming such mass distributions can
-be found (in practise, usually the case) a statistical ensemble of
-two-dimensional mass maps is returned.  This ensemble, along with
-derived quantities and uncertainties, makes up one SpaghettiLens
-model.
+be found (which in practise is usually the case) a statistical
+ensemble of two-dimensional mass maps is returned.  This ensemble,
+along with derived quantities and uncertainties, makes up one
+SpaghettiLens model.
 
@@
 Figure~\ref{fig:kappa} shows projected mass maps of the example
-systems.  This figure shows the tiled character of the mass map.  (The
-mass maps displayed during modelling interpolated over the tiles.)
-The modelling numerics uses an analytical integral over square tiles,
-so the lens equation is always continuous and the arrival time is
-smooth.  We also remark that this figure refers to the ensemble
-average of each model, and the spread in the ensemble is not shown
-here; the arrival-time surfaces and synthetic images in the two
-previous figures also derive from the ensemble-average mass
-distribution.  Figure~\ref{fig:encl} shows the enclosed-mass profiles,
+systems.  Actually, this figure only shows the ensemble-average mass
+maps, and not the variation within the ensemble, from which
+uncertainties can be inferred.  (The same applies to the arrival-time
+surfaces and synthetic images in the two previous figures.
+Uncertainties will be shown in a concise form later, with
+Figure~\ref{fig:encl}.)  Figure~\ref{fig:kappa} makes evident the
+tiled nature of the mass model.  The tiles can be smoothed over by
+interpolating, and this was actually done in the mass maps shown
+online during the modelling process.  It is interesting, however, to
+see the tiling artifacts, if only as a reminder that the substructure
+in the mass distribution are very uncertain, even if some integrated
+quantities are very well constrained.  How the free-form mass maps
+relate to parameterised lens models is discussed in
+Appendix~\ref{subsec:parameter}.  Note that the arrival-time surface
+does not have discontinuous jumps, because the modelling numerics uses
+an analytical integral over square tiles; likewise the lens equation.
+
+Figure~\ref{fig:encl} shows the enclosed-mass profiles,
 expressed as the average convergence $\kappa$ within circles of given

### 2017-02-20 parts/figures.tex

@@
 \inclGrid{kappa_map_interpol}
-\caption{Mass distribution $\kappa$ for which the results
-  Figures~\ref{fig:arriv}--\ref{fig:synth} were derived.
+\caption{Ensemble-average mass distribution $\kappa$ for which the
+  results Figures~\ref{fig:arriv}--\ref{fig:synth} were derived.  Most
+  of the mass maps have a $180^\circ$-rotation symmetry, which is
+  imposed by default.  For SW02 and SW57, where the lensing mass is
+  clearly asymmetric, the modeller chose to turn
+  off the symmetry.
 \label{fig:kappa}}

### 2017-02-20 parts/stelmass.tex
editing

@@
 $\Lambda$CDM model with $H_0=70$\,km\,s$^{-1}$\,Mpc$^{-1}$ and
-$\Omega_m=0.3$. We take a geometric mean of the output from these two
-models as the stellar mass of the lens. This rough estimate will be
-improved in future versions by use of the available optical and NIR
-magnitudes to derive more accurate constrains on the stellar
-populations.
+$\Omega_m=0.3$.
+
+Figure~\ref{fig:stelmass} \todo{Fix overlapping labels SW28/SW29.}
+shows a comparison of stellar and total masses.  The comparatitvely
+large uncertainty in the stellar mass will be improved in future work
+by using available optical and NIR magnitudes to derive more accurate
+constrains on the stellar populations.
 
@@
 follow the prescription of \citet{2010ApJ...710..903M}, namely:
-
 \begin{equation}
@@
 \end{itemize}
+This is the last of our model diagnostics, expressing whether the
+lensing mass is plausible given the light from the candidate lensing
+galaxy.

### 2017-02-20 parts/summary.tex
morphological diagnostics described
missded those images???

--- 2017-01-20 parts/summary.tex
@@
 
-This work follows up on lens candidates reported in
-\cite{2016MNRAS.455.1191M} from citizen-science volunteers, with
-modelling.  Volunteers role is collaborative.  No robotic competitors.
+Table~\ref{tab:models} is a summary of our results.  It characterises
+each modelled system with seven diagnostics, indicating (a)~the image
+morphology and how clear or indistinct it is, (b)~whether the mass map
+and synthetic lensed image appear to be plausible, and (c)~how the
+model mass compares with the estimated stellar and full-halo masses.
+Missing rows are due to photometry data not available.
 
-Table~\ref{tab:models} characterises each modelled system is
-(i)~according to the image morphology and how clear or indistinct it
-is, (ii)~whether the mass map and synthetic lensed image appear to be
-plausible, and (iii)~how the model mass compares with the estimated
-stellar and full-halo masses.  Missing rows are due to photometry data
-not available.
+Figure~\ref{fig:stelmass} is another summary.  It shows most of the
+candidates having stellar and total mass typical of massive
+ellipticals.  SW05 is the most massive of all the candidates, with a
+mass of galaxy-group scale.  It is a particularly attractive system
+for follow-up observations at higher resolution, as it large system
+with clear multiple-image features, and modelling leaves little doubt
+that it is a lens.  The two lowest-mass systems, SW19 and SW42, are
+important if they are indeed lenses, because of their low mass.  The
+models in both cases are plausible but not entirely satisfactory.
 
-Figure~\ref{fig:stelmass} summarises the properties of the lens
-candidates.  Most appear to have stellar and total mass typical of
-massive ellipticals.  SW05 is the most massive of all the candidates,
-with a galaxy-group scale mass.  Two systems, SW19 and SW42 have low
-mass; the lens models are not entirely satisfactory, but seems
-plausible.  If these are lenses, they are very interesting.  In
-particular SW42 could be the most dark-matter dominated lens known.
+The trend in Figure~\ref{fig:stelmass}, that higher-mass galaxies get
+progressively more dark-matter dominated, is expected and gratifying
+to see.  With future data, it would be interesting to compare enclosed
+stellar and total mass as a function of radius, going from
+star-dominated inner regions to dark halos.
+\cite{2011ApJ...740...97L} illustrate this behaviour in their
+Figure~5, but the present sample could go an order of magnitude higher
+in mass.

### 2017-02-27 parts/app.tex
edits
editing

@@
 
-\subsection{Improved synthetic images}
+\subsection{Improved synthetic images}\label{subsec:sourcefit}
 
@@
 9 smaller tiles allows for steeper central profiles.  Doing the same
-for the 25 innermost mass tiles solves the problem completely, but
-increases the number of mass tiles by 40\% and significantly increases
-the computational time.
+for the 25 innermost mass tiles allows for still steeper central
+profiles, eliminating the systematic shallowness.  This is, however,
+still not a completely satisfactory solution, because (a)~it increases
+the number of mass tiles by 40\% and significantly increases the
+computational time, and (b)~the square boundary between area with
+different tile sizes is rather undesirable.
 % 689 / 489 = 1.40899; in practice, runtime is more like x4 - x5!
@@
 Figure~\ref{fig:parameter}. \todo{Einstein radii from parametric
-  model-fitting.}
+  model-fitting for more candidates}
 
@@
   \includegraphics[width=\linewidth]{img/rE_comp/rE_comp.png}
-  \caption{Comparison of Einstein radii. {\em To be extended.}}
+  \caption{Comparison of Einstein radii.}
   \label{fig:parameter}

### 2017-02-28 parts/intro.tex
edits
update intro, morph and table

@@
 collisionless non-relativistic fluid (cold dark matter or CDM); in
-recent years, the simulation by \cite{2005Natur.435..629S} has been
+recent years, the ``millenium'' simulation by \cite{2005Natur.435..629S} has been
 particularly influential in studying the formation of CDM structures.
@@
 In this paper, we present SpaghettiLens models of lens-candidates
-discovered through Space~Warps.  Purpose is twofold.  First, see if
+discovered through Space~Warps.  It's purpose is twofold: First, see if
 plausible mass models can produce the overall configuration.  Second,
@@
 
-Each lens candidates is modelled in a collaborative refinement
-process, where anyone interested can creata a new model or modify an
+Each lens candidate is modelled in a collaborative refinement
+process, where anyone interested can create a new model or modify an
 existing model to try and make it better.\footnote{This is in contrast
@@
 \item First we have diagnostics based on morphology of the
-  system.\todo{Make ordering consistent in text and
-    Table~\ref{tab:models}.}  Section~\ref{sec:morph} and
-  Figure~\ref{fig:splinput} explain.
+  system.
+  Section~\ref{sec:morph} and Figure~\ref{fig:splinput} explain.
 \begin{itemize}
+\item The image morphology concisely described: double or quads,
+  further sub-categorised to indicate the elongation direction of the
+  lensing mass.
 \item Whether the images are unblended.  Distinct unblended images are
@@
 \item Whether the lens is fairly isolated.
-\item The image morphology concisely described: double or quads,
-  further sub-categorised to indicate the elongation direction of the
-  lensing mass.
 \end{itemize}
@@
 \item Whether the arrival-time surface and synthetic image are
-  plausible.  For SW36 the model implies extra images or a long arc,
-  which are not seen.  Figures~\ref{fig:arriv} and \ref{fig:synth} and
-  \ref{fig:encl}.
+  plausible.  In particular, additional images are implied in regions
+  where they are not observed signal an unsatisfactory model.
+  Figures~\ref{fig:arriv} and \ref{fig:synth} and \ref{fig:encl}.
 \end{itemize}
@@
   stellar-population models of \cite{2003MNRAS.344.1000B}.  We then
-  extrapolate the stellar masses to a halo mass using the
+  extrapolate the stellar mass to a halo mass using the
   abundance-matching prescription of \cite{2010ApJ...710..903M}.
@@
 
-The online supplement gives results for all the modelled systems.
+The online supplement gives results for all the modelled systems generated
+for all the lensing candidates.
 

### 2017-02-28 parts/morph.tex
update intro, morph and table

@@
 consisting of a cutout of the Space~Warps image of a lens candidate,
-marked up with a spaghetti diagrams.
+marked up with a spaghetti diagram.
 
@@
 inferred as displaced along the long axis of the lens, SQ if displaced
-along the short axis, IQ if inclined to both axes.  Although the
-unlensed source and its location are obviously not seen, the LQ, SQ
-and IQ cases correspond to easily-seen image morphologies \citep[see,
+along the short axis, IQ if inclined to both axes, CQ if only very little to
+no inclination.  Although the
+unlensed source and its location are obviously not seen, the LQ, SQ, IQ and CQ
+cases correspond to easily-seen image morphologies \citep[see,
   e.g.,][]{2003AJ....125.2769S}.

### 2017-02-28 parts/stelmass.tex
last typo

@@
 with a single colour, preferably tracing a rest-frame colour similar
-to $U-V$ \citep[see fig.~1 of][]{2008MNRAS.383..857F}.
+to $U-V$ \citep[see Fig.~1 of][]{2008MNRAS.383..857F}.
 

### 2017-03-01 parts/app.tex
clean up
last bugfixes, rearrange table and intro

@@
     arrows.  Crossing the horizontal $\kappa=1$ line is the effective
-    Einstein radius \ER, and is so labelled. The upper panel is from
+    Einstein radius \ER. The upper panel is from
     K\"ung et al., (2015) (see Figure~3 of that paper).  The middle
@@
 Preliminary results on recovery of Einstein radii are shown in
-Figure~\ref{fig:parameter}. \todo{Einstein radii from parametric
-  model-fitting for more candidates}
+Figure~\ref{fig:parameter}.
 
@@
   \includegraphics[width=\linewidth]{img/rE_comp/rE_comp.png}
-  \caption{Comparison of Einstein radii.}
+  \caption{
+    Comparison of Einstein radii \ER obtained from mass tiles directly to those obtained from a parameterized model to test the performance of the conversion algorythm.
+    The parameterized model was generated using princible componant analysis on the ensemble of models.
+    The blue dashed line represents a perfect recovery of \ER.
+    }
   \label{fig:parameter}

### 2017-03-01 parts/app.tex
very last bugfixes

@@
   \caption{
-    Comparison of Einstein radii \ER obtained from mass tiles directly to those obtained from a parameterized model to test the performance of the conversion algorythm.
+    Comparison of Einstein radii \ER obtained from mass tiles directly to those obtained from a parameterized model to test the performance of the parametrisation algorythm.
     The parameterized model was generated using princible componant analysis on the ensemble of models.

### 2017-03-03 parts/intro.tex
fix intro
last bugfixes, rearrange table and intro
work on intro

@@
 collisionless non-relativistic fluid (cold dark matter or CDM); in
-recent years, the ``millenium'' simulation by \cite{2005Natur.435..629S} has been
+recent years, the millenium simulation by \cite{2005Natur.435..629S} has been
 particularly influential in studying the formation of CDM structures.
@@
 Strong-lensing galaxies are a useful source of information on the
-mutual dynamics and dark matter and gas in galaxies.  The topic has
+mutual dynamics of dark matter and gas in galaxies.  The topic has
 been explored in several studies
@@
 machine learning \citep{2016A&A...592A..75P} and by visual inspection
-by a citizen-science volunteers
+by citizen-science volunteers
 \citep[Space~Warps][]{2016MNRAS.455.1191M} have between them
@@
 
-In this paper, we present SpaghettiLens models of lens-candidates
-discovered through Space~Warps.  It's purpose is twofold: First, see if
-plausible mass models can produce the overall configuration.  Second,
-interpretation as lensing galaxies.
+In this paper, we present SpaghettiLens models of lens-candidates discovered through Space~Warps.
+It's purpose is twofold.
+First to check if the created models look like plausible lenses and whether the shortcomings diagnosed in \cite{2015MNRAS.447.2170K} were fixed.
+Second to introduce diagnostic criteria that help filter out the most probable lens candidates and the possibly most rewarding for future follow up observations.
+While introducing these diagnostic criteria, we also gain some preliminary estimations of some properties of the lens-candidates as galaxies.
+
+The analysis presented in this paper is somewhat limited by the fact that no source redshifts are available\footnote{Source redshifts were set to z=2 for all systems.} yet and that the redshifts of the lenses have large error bars.
+Nevertheless it is interesting to see what trends we can observe with the already available data.
+One should also keep in mind that the existing pipeline allows to replace those values with more precise ones as soon as they are available and rerun this analysis without any further work involved.
+
+% It's purpose is twofold: First, to see if
+% plausible mass models can produce the overall configuration.  Second, to
+% check their interpretation as lensing galaxies.
 
@@
 \begin{itemize}
-\item The image morphology concisely described: double or quads,
-  further sub-categorised to indicate the elongation direction of the
-  lensing mass.
 \item Whether the images are unblended.  Distinct unblended images are
@@
 \item Whether the lens is fairly isolated.
+\item The image morphology concisely described: double or quads,
+  further sub-categorised to indicate the elongation direction of the
+  lensing mass.
 \end{itemize}

### 2017-03-16 paper2.tex
add input images with scalebar, fixes#4
editing
update intro, morph and table
clean up
rm todolist
ignacio changes

@@
-\documentclass[fleqn,usenatbib]{mnras}
+\documentclass[fleqn,usenatbib]{template/mnras}
 
@@
 
+\def\pwidth{.32\linewidth}
+
+\input{img/model_assignment}
+
 \title[Lens models for Space Warps CFHTLS]{Models of lens candidates from
@@
 % These dates will be filled out by the publisher
-% \date{Accepted XXX. Received YYY; in original form ZZZ}
+\date{Accepted XXX. Received YYY; in original form ZZZ}
 
 % Enter the current year, for the copyright statements etc.
-\pubyear{2016}
+\pubyear{2017}
 
@@
 from the Space~Warps citizen-science community who originally found
-the candidate lenses.  Models are categorised according to seven
-qualitative and quantitive points.  Also included are some
+the candidate lenses.  Models are categorized according to seven
+qualitative and quantitative points.  Also included are some
 improvements to the modelling software used (SpaghettiLens),
@@
 total masses of $\approx10^{12}M_\odot$ and reduces for both lower and
-higher masses, is discernable also in these much more distant
+higher masses, is discernible also in these much more distant
 galaxies.
@@
 \begin{keywords}
-gravitational lensing: strong -- keyword2
+gravitational lensing: strong -- citizen science
 \end{keywords}
 
-\input parts/intro
+\input{parts/intro}
 
@@
 
-\input parts/morph
+\input{parts/morph}
 
-\input parts/massmodel
+\input{parts/massmodel}
 
-\input parts/stelmass
+\input{parts/stelmass}
 
-\input parts/summary
+\input{parts/summary}
 
@@
 
-\bibliographystyle{mnras}
+\bibliographystyle{template/mnras}
 \bibliography{bib/bibli}
@@
 
-\input parts/figures
+\input{parts/figures}
 
@@
 
-% \section{TODO}
-% \listoftodos
-
 \appendix
 
-\input parts/app.tex
+\input{parts/app.tex}
+
+%\section{TODO}
+%\listoftodos
 

### 2017-03-16 parts/app.tex
ignacio changes

@@
 
-The mass maps produced by current implementation of SpaghettiLens are
+The mass maps produced by the current implementation of SpaghettiLens are
 based on images of point-like features.  No information about extended
@@
 
-We have now developed a prototype of better way to generate synthetic
+We have now developed a prototype to improve the generation of synthetic
 images.  Figure~\figref{synthimg} illustrates.  First, areas
@@
 The models of simulated lenses in \cite{2015MNRAS.447.2170K} showed a
-tendency to be too shallow.  Allowing smaller mass tiles in the
+tendency to produce too shallow density profiles.
+Allowing smaller mass tiles in the
 central region, thus allowing the mass profile to rise more steeply
@@
 This created the residuals function.
-The number of components used in the analysis was varied, to test how this affected the output, and it was found that using 5 principle components tended to give a reasonable approximation.
+The number of components used in the analysis was varied, to test how this affected the output, and it was found that using 5 principal components tended to give a reasonable approximation.
 A masking function was added which selected only the data points that fell inside the image of the lens, and the principal components were clipped in order to keep the values inside the region of the ensemble of models.

### 2017-03-16 parts/figures.tex
edits
last bugfixes, rearrange table and intro
ignacio changes

@@
   diagrams.  Red, blue and green dots are proposed locations for
-  maxima, minima and saddle points of the arrival time.  The curves
+  maxima, minima and saddle points of the arrival time respectively.
+
+	The curves
   help guide the placement of the dots, but their precise appearance
@@
 \caption{Synthetic images of the systems from
-  Figures~\ref{fig:splinput}, derived from the lens models.  The
+  Figure~\ref{fig:splinput}, derived from the lens models.  The
   reconstructed lensed features are keep the Space~Warps false-colour
@@
 \caption{Ensemble-average mass distribution $\kappa$ for which the
-  results Figures~\ref{fig:arriv}--\ref{fig:synth} were derived.  Most
-  of the mass maps have a $180^\circ$-rotation symmetry, which is
-  imposed by default.  For SW02 and SW57, where the lensing mass is
-  clearly asymmetric, the modeller chose to turn
-  off the symmetry.
+  results Figures~\ref{fig:arriv}--\ref{fig:synth} were derived.  The
+  dashed curves denote $\kappa=1$.  Most of the mass maps have a
+  $180^\circ$-rotation symmetry, which is imposed by default.  For
+  SW02 and SW57, where the lensing mass is clearly asymmetric, the
+  modeller chose to turn off the symmetry.
 \label{fig:kappa}}
@@
   \label{tab:models}
-  \include{table}
+  \include{parts/table}
 \end{table*}

### 2017-03-16 parts/intro.tex
ignacio changes

@@
 
-Light deflection at the rim of the Sun is famously $1.75''$.  The
+Light deflection at the rim of the Sun due to its gravitational field is famously $1.75''$.  The
 deflection angle can also be expressed in terms of the escape velocity
@@
 With no unambiguous dark-matter particle detections so far, dark
-matter has studied only through its indirect consequences on galactic
+matter has been studied only through its indirect consequences on galactic
 and larger scales.  In most work, dark matter is taken to be a
 collisionless non-relativistic fluid (cold dark matter or CDM); in
-recent years, the millenium simulation by \cite{2005Natur.435..629S} has been
+recent years, the millennium simulation by \cite{2005Natur.435..629S} has been
 particularly influential in studying the formation of CDM structures.
 Other scenarios have also been considered, such as a cold condensing
-boson fluid \citep{2016ApJ...818...89S}.  There is a general
-consensus, however, that the origins of galaxy lie in the
+boson fluid \citep{2016ApJ...818...89S} 
+or even dark matter particles with internal degrees of freedom 
+\citep{2011MNRAS..405...77}. %(Saxton & Ferreras 2010 MNRAS 405, 77)
+There is a general
+consensus, however, that 
+basic mechanism of galaxy formation involve
 gravitational collapse, fragmentation, and mergers of dark-matter
-clumps, into which fell gas, cooling through radiative processes to
+clumps, into which gas fell, cooling through radiative processes to
 form dense clouds and eventually stars.  There is, however, much
 debate about the details, of which \cite{2012RAA....12..917S} provide
-a nice summary.
+a summary.
 
-Strong-lensing galaxies are a useful source of information on the
+Strong gravitational lensing over galaxy scales provides
+a useful source of information on the
 mutual dynamics of dark matter and gas in galaxies.  The topic has
-been explored in several studies
+been explored in numerous studies
 \citep{2009ApJ...703L..51K,2011ApJ...740...97L,2012MNRAS.424..104L,
@@
 enlarge the samples from tens of lensing galaxies to thousands.  Doing
-so requires finding more lenses, of course, but also modelling their
+so requires both finding more lenses and also modelling their
 masses.
@@
 by citizen-science volunteers
-\citep[Space~Warps][]{2016MNRAS.455.1191M} have between them
+\citep[Space~Warps][]{2016MNRAS.455.1191M} have, between them,
 discovered an average of four lenses per square degree.  So one can be
@@
 generation of wide-field surveys.  The expected flood of new lens
-discoveries will need a similarly huge modelling effort to reconstruct
+discoveries
+with surveys such as Euclid or WFIRST,
+will need a similarly huge modelling effort to reconstruct
 their mass distributions.  To prepare for the challenge of
@@
 In this paper, we present SpaghettiLens models of lens-candidates discovered through Space~Warps.
-It's purpose is twofold.
+Its purpose is twofold.
 First to check if the created models look like plausible lenses and whether the shortcomings diagnosed in \cite{2015MNRAS.447.2170K} were fixed.
@@
 
-The analysis presented in this paper is somewhat limited by the fact that no source redshifts are available\footnote{Source redshifts were set to z=2 for all systems.} yet and that the redshifts of the lenses have large error bars.
+The analysis presented in this paper is somewhat limited by the fact that no source redshifts are available yet and that the redshifts of the lenses have large error bars.
+Source redshifts were set to z=2 for all systems. %TODO justify z=2.
+
 Nevertheless it is interesting to see what trends we can observe with the already available data.
@@
   an advantage in modelling, but not essential.
-\item Whether all images are discernable.  The topography of an
+\item Whether all images are discernible.  The topography of an
   arrival-time surface, as encoded by a spaghetti diagram, may require
@@
 \item Third, whether the implied lensing mass is plausible, given the
-  star-light in the lensing galaxy.  Section~\ref{sec:stellar-mass}
+  photometric data of the lensing galaxy.  Section~\ref{sec:stellar-mass}
   explains how we compare the lensing mass with the mass in stars in
@@
   no more than the total halo mass.  We then introduce what we call a
-  halo index $\haloindex$ which gives an idea of how the lensing mass
-  compares with these two bounds.  Figure~\ref{fig:stelmass}.
+  halo index ($\haloindex$) which gives an idea of how the lensing mass
+  compares with these two contraints.  Figure~\ref{fig:stelmass}.
 \end{itemize}
@@
 
-Appendices devoted to various technical issues relating to modelling.
+There is an appendix section
+devoted to various technical issues relating to modelling.
 \cite{2015MNRAS.447.2170K} tested the system on simulated lenses and

### 2017-03-16 parts/massmodel.tex
edits
ignacio changes

@@
 images, meaning reconstructions of the extended lensed features by
-fitting for a source.  These were generated by new method, explained
+fitting for a source.  These were generated by a new method, explained
 in Appendix~\ref{subsec:sourcefit}, implemented in offline
@@
 synthetic images provided by SpaghettiLens during the collaborative
-modelling and discussion were more crude.
+modelling and discussion were more crude; these are included in the
+online supplement.
 
@@
 diagnostic, the most important of all: are the lensed features
-satisfactorily repoduced?  This diagnostic remains a judgement call by
+satisfactorily reproduced?  This diagnostic remains a judgment call by
 modellers.  A useful quantitative criterion for whether the synthetic

### 2017-03-16 parts/stelmass.tex
clean up
ignacio changes

@@
 by the lensed galaxy.  Reducing or eliminating the latter would
-require detailed fitting of light distributions for each candidate,
+require detailed fitting of light distributions for each candidate
+%TODO cite Leier et al 2011 \citep{}
+,
 which we have not yet attempted.  These caveats notwithstanding, it is
@@
 
-Figure~\ref{fig:stelmass} \todo{Fix overlapping labels SW28/SW29.}
-shows a comparison of stellar and total masses.  The comparatitvely
+Figure~\ref{fig:stelmass}
+shows a comparison of stellar and total masses.  The comparatively
 large uncertainty in the stellar mass will be improved in future work

### 2017-03-16 parts/massmodel.tex
removed dreaded endinputs

@@
 are the mass distributions plausible?
-
-\endinput
-
-  The ensemble average
-can, however, be a useful representative of the whole ensemble.  The
-user interface of SpaghettiLens returns graphical representations of
-the ensemble-average mass map and some derived quantities to the
-modeller for review.  The modeller can post these results on a forum,
-or discard them and try again.  Other volunteers can start the
-modelling process afresh, or they can take an existing model from the
-forum and modify its input spaghetti diagram or its accompanying
-options, and thus obtain a revised model.
-
-Alongside is a synthetic image produced by modelling.  In it, the
-fitted lensed images are shown in colour, while the lensing galaxy and
-extraneous objects have been reduced to grayscale.
-) These two
-panels are qualitative and display no units, and moreover, the mutual
-alignment of the two panels is only approximate.
-
-Figures~\figref{SW58} and \figref{SW19} appear plausible lens
-candidates.  Their morphology is similar to SW28, but the saddle-point
-counterimage is not visible.  We consider these lenses plausible but
-less convincing.
-
-Figures~\figref{SW36} and \figref{SW57} are cases where modelling
-failed.
-
-\begin{enumerate}
-\item The middle row shows contour maps from the model.  At middle
-  left, we have the arrival-time surface.
-\item At middle right we have the mass distribution in the usual
-  dimensionless form $\kappa$.  Again, these two panels are mainly
-  qualitative: both panels are spatially registered and centred on the
-  density-peak of the lens, but no scales have been included.
-\item The base row supplies spatial and mass scales.  The left panel
-
-\item 
-\end{enumerate}

### 2017-03-16 parts/intro.tex
editing intro

@@
 
-Light deflection at the rim of the Sun due to its gravitational field is famously $1.75''$.  The
-deflection angle can also be expressed in terms of the escape velocity
-$2v_{\rm esc}^2/c^2$, with $v_{\rm esc}$ at the solar surface being
-$\simeq620\rm\,km/s$.  The Galactic escape velocity at the Sun's
-location is similar: $\approx500\rm\,km/s$, typical of massive
-galaxies.  Thus, the outer regions of massive galaxies have lensing
-deflections comparable to that at the rim of the Sun.  Yet these
-quantitatively similar deflections have qualitatively different
-consequences.  Light deflection by the Sun must be accounted for in
-modern astrometry \citep[see e.g.,][]{2015CQGra..32p5008C} but is not
-itself a physics probe in the way it was a century ago.  With distant
-galaxies, however, light bending by $\sim1''$ introduces two new
-phenomena.  First, for galaxies distant enough that their apparent
-size is comparable to the bending angle, light deflection can cause
-multiple images of background sources, or strong lensing.  Second, the
-gravitational field is dominated by dark matter, hence strong lensing
-becomes a probe of dark matter in galaxies.
+By coincidence, the typical escape velocity of massive galaxies is
+such that $v_{\rm esc}^2/c^2$ is comparable to the apparent sizes of a
+galaxies at cosmological distances.  This coincidence is fortunate,
+because it makes the lensing deflection angle (which is $2v_{\rm
+  esc}^2/c^2$) of distant galaxies comparable to their size on the
+sky, and as a result, strong lensing by galaxies tends to produce
+images that probe the dark halos of those galaxies.  This is
+important, because while there is a general consensus that basic
+mechanism of galaxy formation involve gravitational collapse,
+fragmentation, and mergers of dark-matter clumps, into which gas fell,
+cooling through radiative processes to form dense clouds and
+eventually stars, there is much debate about the details \citep[for a
+  summary, see][]{2012RAA....12..917S}.  In particular, the nature of
+dark matter remains mysterious: most researchers take it to be a
+collisionless non-relativistic fluid (cold dark matter or CDM) readily
+studied by simulations \citep[for example, the millenium simulation
+  by][which has been particularly influential]{2005Natur.435..629S}.
+But other scenarios have also been considered, such as a cold
+condensing boson fluid \citep{2016ApJ...818...89S}, or dark matter
+particles with internal degrees of freedom
+\citep{2010MNRAS.405...77S}, or not matter at all but a modification
+of gravity \citep{2016PhRvL.117t1101M}.
 
-With no unambiguous dark-matter particle detections so far, dark
-matter has been studied only through its indirect consequences on galactic
-and larger scales.  In most work, dark matter is taken to be a
-collisionless non-relativistic fluid (cold dark matter or CDM); in
-recent years, the millennium simulation by \cite{2005Natur.435..629S} has been
-particularly influential in studying the formation of CDM structures.
-Other scenarios have also been considered, such as a cold condensing
-boson fluid \citep{2016ApJ...818...89S} 
-or even dark matter particles with internal degrees of freedom 
-\citep{2011MNRAS..405...77}. %(Saxton & Ferreras 2010 MNRAS 405, 77)
-There is a general
-consensus, however, that 
-basic mechanism of galaxy formation involve
-gravitational collapse, fragmentation, and mergers of dark-matter
-clumps, into which gas fell, cooling through radiative processes to
-form dense clouds and eventually stars.  There is, however, much
-debate about the details, of which \cite{2012RAA....12..917S} provide
-a summary.
-
-Strong gravitational lensing over galaxy scales provides
-a useful source of information on the
-mutual dynamics of dark matter and gas in galaxies.  The topic has
-been explored in numerous studies
+All this motivates using galaxy lenses to study the mutual dynamics of
+dark matter and gas in galaxies.  Several studies in recent years have
+done so
 \citep{2009ApJ...703L..51K,2011ApJ...740...97L,2012MNRAS.424..104L,
@@
 enlarge the samples from tens of lensing galaxies to thousands.  Doing
-so requires both finding more lenses and also modelling their
-masses.
-
+so requires both finding more lenses and also modelling their masses.
 Recent searches through the CFHTLS \citep{2012SPIE.8448E..0MC} using
@@
 machine learning \citep{2016A&A...592A..75P} and by visual inspection
-by citizen-science volunteers
-\citep[Space~Warps][]{2016MNRAS.455.1191M} have, between them,
-discovered an average of four lenses per square degree.  So one can be
-optimistic about finding many thousands of lenses in the next
-generation of wide-field surveys.  The expected flood of new lens
-discoveries
-with surveys such as Euclid or WFIRST,
-will need a similarly huge modelling effort to reconstruct
-their mass distributions.  To prepare for the challenge of
-massive-sample lens modelling, \cite{2015MNRAS.447.2170K} developed a
-new modelling strategy, implemented as the SpaghettiLens system.  The
-idea is to collaborate with experienced members of the citizen-science
-community, who have already participated in lens discovery through
-Space~Warps, as well as several other projects involving astronomical
-data.
+by citizen-science volunteers in Space~Warps
+\citep{2016MNRAS.455.1191M} have, between them, discovered an average
+of four lenses per square degree.  So one can be optimistic about
+finding many thousands of lenses in the next generation of wide-field
+surveys, from the LSST in optical and the SKA in radio on the ground,
+and Euclid and WFIRST in orbit.  The expected flood of new lens
+discoveries will need a similarly huge modelling effort to reconstruct
+their mass distributions.
+
+To prepare for the challenge of massive-sample lens modelling,
+\cite{2015MNRAS.447.2170K} developed a new modelling strategy,
+implemented as the SpaghettiLens system.  The idea is to collaborate
+with experienced members of the citizen-science community, who have
+already participated in lens discovery through Space~Warps, as well as
+several other projects involving astronomical data.
 

### 2017-03-17 parts/morph.tex
ignacio changes

@@
 the lensed images, yet massive enough to have an effect.  These are
-allowed for by allowing a constant but adjustable external shear.
+contributed for by allowing a constant but adjustable external shear.
 
@@
 systems.
-
-\endinput
-
-Let us first consider from SW05 (J143454.4+522850).
-In SW05 there are four distinct lensed images, and the spaghetti
-diagram proposes that they are a minimum nearest to the lensing
-galaxy, a close minimum-saddle pair, and a minimum further away. In
-Table~\ref{tab:models} we refer to such configurations as IQ for
-inclined quad.
-
-Figure~\figref{SW42} shows SW42.  The image morphology is similar to
-SW05 in Figure~\figref{SW05}, but the lens is much smaller on the sky.
-
-Proceeding to Figure~\figref{SW28}, we have one image close to the
-galaxy and an arc further away, which is interpreted as a blend of
-three images (a saddle point with two minima on either side).  We call
-this a long-axis quad or LQ configuration.  It is an indication of a
-mass distribution elongated along the arc-counterimage direction
-(along EW in this case).
-
-In Figures~\figref{SW02}--\figref{SW29} we see three candidates with
-an arc close the lensing galaxy and one image further away.  The arc
-is interpreted three images (a minimum with two saddle points on
-either side).  We call this a short-axis quad or SQ configuration.  It
-is an indication of a mass distribution elongated perpendicular to the
-arc-counterimage direction.

### 2017-03-20 parts/intro.tex
editing introduction

@@
 surveys, from the LSST in optical and the SKA in radio on the ground,
-and Euclid and WFIRST in orbit.  The expected flood of new lens
-discoveries will need a similarly huge modelling effort to reconstruct
-their mass distributions.
+and Euclid and WFIRST in orbit.
 
-To prepare for the challenge of massive-sample lens modelling,
+The expected flood of new lens discoveries will need a similarly huge
+modelling effort to reconstruct their mass distributions.  To prepare
+for the challenge of massive-sample lens modelling,
 \cite{2015MNRAS.447.2170K} developed a new modelling strategy,
@@
 already participated in lens discovery through Space~Warps, as well as
-several other projects involving astronomical data.
+several other projects involving astronomical data.  This paper
+continues by applying SpaghettiLens to lens-candidates discovered
+through Space~Warps.  We present results from modelling of 42 of the
+59 lens candidates reported by \cite{2016MNRAS.455.1191M}.
 
-In this paper, we present SpaghettiLens models of lens-candidates discovered through Space~Warps.
-Its purpose is twofold.
-First to check if the created models look like plausible lenses and whether the shortcomings diagnosed in \cite{2015MNRAS.447.2170K} were fixed.
-Second to introduce diagnostic criteria that help filter out the most probable lens candidates and the possibly most rewarding for future follow up observations.
-While introducing these diagnostic criteria, we also gain some preliminary estimations of some properties of the lens-candidates as galaxies.
+The aim of this work is twofold.  First, one would like to identify
+the most probable lens and the systems likely to be most rewarding for
+future follow-up observations.  For this we introduce some
+diagnostics; these
+
+  Its purpose is twofold.  First to check if the
+created models look like plausible lenses and whether the shortcomings
+diagnosed in \cite{2015MNRAS.447.2170K} were fixed.  Second to
+introduce diagnostic criteria that help filter out   While introducing these diagnostic criteria, we also
+gain some preliminary estimations of some properties of the
+lens-candidates as galaxies.
 

### 2017-03-20 parts/massmodel.tex
edits to intro

@@
 photometric redshifts from the CFHTLS pipeline to the candidate
-lensing galaxies.  Source redshifts are set to $z=2$ unless an
-unambiguous photometric redshift is available.
+lensing galaxies; the values range from $z=0.2$ to $z=1$ (see
+Table~\ref{tab:models}).  Source redshifts are set to $z=2$ unless an
+unambiguous photometric redshift is available.  The mass normalisation
+depends only weakly on the source redshift, provided it is not close
+to the lens redshift.
 

### 2017-03-20 parts/intro.tex

@@
 already participated in lens discovery through Space~Warps, as well as
-several other projects involving astronomical data.  This paper
-continues by applying SpaghettiLens to lens-candidates discovered
-through Space~Warps.  We present results from modelling of 42 of the
-59 lens candidates reported by \cite{2016MNRAS.455.1191M}.
+several other projects involving astronomical data.  The system was
+tested on a sample of simulated lenses from Space~Warps.
 
-The aim of this work is twofold.  First, one would like to identify
-the most probable lens and the systems likely to be most rewarding for
-future follow-up observations.  For this we introduce some
-diagnostics; these
-
-  Its purpose is twofold.  First to check if the
-created models look like plausible lenses and whether the shortcomings
-diagnosed in \cite{2015MNRAS.447.2170K} were fixed.  Second to
-introduce diagnostic criteria that help filter out   While introducing these diagnostic criteria, we also
-gain some preliminary estimations of some properties of the
-lens-candidates as galaxies.
-
-The analysis presented in this paper is somewhat limited by the fact that no source redshifts are available yet and that the redshifts of the lenses have large error bars.
-Source redshifts were set to z=2 for all systems. %TODO justify z=2.
-
-Nevertheless it is interesting to see what trends we can observe with the already available data.
-One should also keep in mind that the existing pipeline allows to replace those values with more precise ones as soon as they are available and rerun this analysis without any further work involved.
-
-% It's purpose is twofold: First, to see if
-% plausible mass models can produce the overall configuration.  Second, to
-% check their interpretation as lensing galaxies.
-
-Each lens candidate is modelled in a collaborative refinement
+This paper continues by applying SpaghettiLens to lens-candidates
+discovered through Space~Warps.  We present results from modelling of
+42 of the 59 lens candidates reported by \cite{2016MNRAS.455.1191M}.
+Each lens candidate was modelled in a collaborative refinement
 process, where anyone interested can create a new model or modify an
@@
   minimal overlap, the forum has little if any influence on votes.}
-The result represents a consensus among contributors, as to the best
-that could be achieved with the available data and software.
+The result model represents a consensus among contributors, as to the
+best that could be achieved with the available data and software.
 
-The modelling process assigns seven diagnostics to each lens
-candidate, as follows.
+We characterise each model with seven diagnostics, whose purpose is to
+help identify which systems are most probably lenses, and which ones
+are likely to be most rewarding for future follow-up observations.
+The diagnostics are as follows.
 
@@
 Section~\ref{sec:summary} summarises and tabulates the diagnostics in
-Table~\ref{tab:models}.
+Table~\ref{tab:models}.  Interpretation of the results is preliminary,
+because the systems are candidates at this stage, not secure lenses.
+Moreover the candidate-lens redshifts have large uncertainties, while
+the candidate-source redshifts can only be guessed at present.
+Nevertheless it is interesting to see what trends we can observe with
+the already-available data.
 
-The online supplement gives results for all the modelled systems generated
-for all the lensing candidates.
-
-There is an appendix section
-devoted to various technical issues relating to modelling.
-\cite{2015MNRAS.447.2170K} tested the system on simulated lenses and
-identified some areas for improvement.
-In \S~\ref{subsec:sourcefit} we introduce fitting of the brightness
+There are three appendices devoted to various technical issues
+relating to modelling.  \cite{2015MNRAS.447.2170K} tested the system
+on simulated lenses and identified some areas for improvement.  In
+\S~\ref{subsec:sourcefit} we introduce fitting of the brightness
 profiles of the source.  This feature has not yet been included in
@@
 successful at extracting an Einstein radius.
+
+The online supplement gives results for all the modelled systems generated
+for all the lensing candidates.

### 2017-03-20 parts/massmodel.tex
remove endinput

--- 2017-03-16 parts/massmodel.tex
@@
 images, meaning reconstructions of the extended lensed features by
-fitting for a source.  These were generated by a new method, explained
+fitting for a source.  These were generated by new method, explained
 in Appendix~\ref{subsec:sourcefit}, implemented in offline
@@
 diagnostic, the most important of all: are the lensed features
-satisfactorily reproduced?  This diagnostic remains a judgment call by
+satisfactorily repoduced?  This diagnostic remains a judgement call by
 modellers.  A useful quantitative criterion for whether the synthetic

### 2017-03-20 paper2.tex
many minor update, incl TABLEgit status

@@
 \WarningFilter{caption}{Unsupported document class} % caption doesn't know mnras..
-\hbadness = 5000
+\hbadness = 10000
 \vbadness = 10000
@@
 %\usepackage{showframe} % for debug
-%\overfullrule=5pt      % show overfull boxes
+\overfullrule=5pt      % show overfull boxes
 
@@
 $^{5}$Kavli Institute for Particle Astrophysics and Cosmology, Stanford University, 452 Lomita Mall, Stanford, CA 94035, USA\\
-$^{6}$Kavli Institute for the Physics and Mathematics of the Universe, University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa-shi 277-8583, Japan\\
+%$^{6}$Kavli Institute for the Physics and Mathematics of the Universe, University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa-shi 277-8583, Japan\\
+$^{6}$Kavli IPMU (WPI), UTIAS, University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
 $^{7}$Murray Edwards College, University of Cambridge, Cambridge CB3 0DF, UK\\

### 2017-03-21 img/model_assignment.tex
updated table and desc

@@
 % Look up table, SWID -> Index:
+% 01 AB
 % 02 AC
+% 03 AD
 % 04 AE
@@
 % 06 AG
+% 07 AH
 % 08 AI
@@
 % 13 BD
+% 14 BE
 % 15 BF
@@
 % 29 CJ
+% 30 DA
 % 31 DB
+% 32 DC
 % 33 DD
@@
 % 36 DG
+% 37 DH
 % 38 DI
+% 40 EA
 % 41 EB
@@
 % 47 EH
+% 48 EI
+% 50 FA
+% 51 FB
+% 52 FC
 % 53 FD
 % 54 FE
+% 55 FF
 % 56 FG
@@
 % 58 FI
+% 59 FJ
 
+\newcommand{\inclAB}[1]{\includegraphics[width=\pwidth]{img/#1/SW01_ASW0004dv8_EUTVAVV6XJ_#1}}
 \newcommand{\inclAC}[1]{\includegraphics[width=\pwidth]{img/#1/SW02_ASW000619d_011489_#1}}
+\newcommand{\inclAD}[1]{\includegraphics[width=\pwidth]{img/#1/SW03_ASW0006mea_XZDGINWFYY_#1}}
 \newcommand{\inclAE}[1]{\includegraphics[width=\pwidth]{img/#1/SW04_ASW0009cjs_NJ5CC5YJAQ_#1}}
@@
 \newcommand{\inclAG}[1]{\includegraphics[width=\pwidth]{img/#1/SW06_ASW0008swn_BCY2NOUSLK_#1}}
+\newcommand{\inclAH}[1]{\includegraphics[width=\pwidth]{img/#1/SW07_ASW0007e08_008009_#1}}
 \newcommand{\inclAI}[1]{\includegraphics[width=\pwidth]{img/#1/SW08_ASW00099ed_HISGRAIZL2_#1}}
@@
 \newcommand{\inclBD}[1]{\includegraphics[width=\pwidth]{img/#1/SW13_ASW00047ae_TGTIIF7HCV_#1}}
+\newcommand{\inclBE}[1]{\includegraphics[width=\pwidth]{img/#1/SW14_ASW0004xjk_P5W2HUVWX3_#1}}
 \newcommand{\inclBF}[1]{\includegraphics[width=\pwidth]{img/#1/SW15_ASW0004nan_QUOGDU2NN6_#1}}
@@
 \newcommand{\inclCJ}[1]{\includegraphics[width=\pwidth]{img/#1/SW29_ASW0008qsm_TOFS7JNGEK_#1}}
+\newcommand{\inclDA}[1]{\includegraphics[width=\pwidth]{img/#1/SW30_ASW0002p8y_3BJQ2QZN65_#1}}
 \newcommand{\inclDB}[1]{\includegraphics[width=\pwidth]{img/#1/SW31_ASW00021r0_CIFSR5JFFU_#1}}
+\newcommand{\inclDC}[1]{\includegraphics[width=\pwidth]{img/#1/SW32_ASW0004iye_002360_#1}}
 \newcommand{\inclDD}[1]{\includegraphics[width=\pwidth]{img/#1/SW33_ASW0003s0m_ECXCIRBDUJ_#1}}
@@
 \newcommand{\inclDG}[1]{\includegraphics[width=\pwidth]{img/#1/SW36_ASW000096t_7IPP7LWVOF_#1}}
+\newcommand{\inclDH}[1]{\includegraphics[width=\pwidth]{img/#1/SW37_ASW00086xq_BYQATMOXCM_#1}}
 \newcommand{\inclDI}[1]{\includegraphics[width=\pwidth]{img/#1/SW38_ASW0009cp0_Z6IFI4SLLM_#1}}
+\newcommand{\inclEA}[1]{\includegraphics[width=\pwidth]{img/#1/SW40_ASW0008wmr_HJ2STCIBPO_#1}}
 \newcommand{\inclEB}[1]{\includegraphics[width=\pwidth]{img/#1/SW41_ASW0008xbu_BFXRMIQEAT_#1}}
@@
 \newcommand{\inclEH}[1]{\includegraphics[width=\pwidth]{img/#1/SW47_ASW0003r6c_4HC3CREEAD_#1}}
+\newcommand{\inclEI}[1]{\includegraphics[width=\pwidth]{img/#1/SW48_ASW0000g95_A6UPEGOHT5_#1}}
+\newcommand{\inclFA}[1]{\includegraphics[width=\pwidth]{img/#1/SW50_ASW00008a0_XPHGTJUNLN_#1}}
+\newcommand{\inclFB}[1]{\includegraphics[width=\pwidth]{img/#1/SW51_ASW0006e0o_S2LA5MRACS_#1}}
+\newcommand{\inclFC}[1]{\includegraphics[width=\pwidth]{img/#1/SW52_ASW0006a07_Y7SAF7WWVG_#1}}
 \newcommand{\inclFD}[1]{\includegraphics[width=\pwidth]{img/#1/SW53_ASW00070vl_BPAV4GVOPP_#1}}
 \newcommand{\inclFE}[1]{\includegraphics[width=\pwidth]{img/#1/SW54_ASW0007sez_SI4ELBAKL2_#1}}
+\newcommand{\inclFF}[1]{\includegraphics[width=\pwidth]{img/#1/SW55_ASW0007t5y_VDDLM6H2JN_#1}}
 \newcommand{\inclFG}[1]{\includegraphics[width=\pwidth]{img/#1/SW56_ASW0007pga_VHV6RQYYKZ_#1}}
@@
 \newcommand{\inclFI}[1]{\includegraphics[width=\pwidth]{img/#1/SW58_ASW0007iwp_4XBJWT3COV_#1}}
+\newcommand{\inclFJ}[1]{\includegraphics[width=\pwidth]{img/#1/SW59_ASW00085cp_6IU7DLN5GK_#1}}
 

### 2017-03-21 parts/summary.tex
ignacio changes
many minor update, incl TABLEgit status
updated table and desc

@@
 model mass compares with the estimated stellar and full-halo masses.
-Missing rows are due to photometry data not available.
+Missing entires are due to photometry data not being available, whereas
+missing rows are due to models not having been created.
 
@@
 The trend in Figure~\ref{fig:stelmass}, that higher-mass galaxies get
-progressively more dark-matter dominated, is expected and gratifying
-to see.  With future data, it would be interesting to compare enclosed
+progressively more dark-matter dominated, is expected
+, e.g. see \cite{2005ApJ...623L...5F}.
+With future data, it would be interesting to compare enclosed
 stellar and total mass as a function of radius, going from

### 2017-03-21 parts/morph.tex
remove endinput
checking claudes issues

@@
 are modelled as point masses.  Other possible contributors to lensing
-are galaxies or groups or that are not in the immediately vicinity of
+are galaxies or groups that are not in the immediately vicinity of
 the lensed images, yet massive enough to have an effect.  These are

### 2017-03-21 parts/app.tex
feedback JC, fix trivial ones

@@
   \caption{
-    Comparison of Einstein radii \ER obtained from mass tiles directly to those obtained from a parameterized model to test the performance of the parametrisation algorythm.
+    Comparison of Einstein radii \ER\ obtained from mass tiles directly to those obtained from a parameterized model to test the performance of the parametrisation algorythm.
     The parameterized model was generated using princible componant analysis on the ensemble of models.

### 2017-03-21 parts/intro.tex
nothing
feedback JC, fix trivial ones

@@
 \citep{2016MNRAS.455.1191M} have, between them, discovered an average
-of four lenses per square degree.  So one can be optimistic about
+of four lenses per square degree, so one can be optimistic about
 finding many thousands of lenses in the next generation of wide-field
@@
 
-We characterise each model with seven diagnostics, whose purpose is to
-help identify which systems are most probably lenses, and which ones
-are likely to be most rewarding for future follow-up observations.
-The diagnostics are as follows.
+We characterise each model with seven diagnostics, grouped into three 
+categories, whose purpose is to help identify which systems are most probably 
+lenses, and which ones are likely to be most rewarding for future follow-up 
+observations. The diagnostics are as follows.
 

### 2017-03-21 parts/stelmass.tex
feedback JC, fix trivial ones

@@
 \citep[e.g.][]{2009ApJS..185..253G,2011MNRAS.418.1587T}.  However,
-estimates to within 0.3\,dex in $\log($M$_s$/M$_\odot)$ can be derived
+estimates to within 0.3\,dex in $\log(\Mstel/\Msun)$ can be derived
 with a single colour, preferably tracing a rest-frame colour similar
@@
 require detailed fitting of light distributions for each candidate
-%TODO cite Leier et al 2011 \citep{}
-,
-which we have not yet attempted.  These caveats notwithstanding, it is
-still interesting to compare the derived stellar mass with the lensing
-mass.
+\citep[see][]{2011ApJ...740...97L}, which we have not yet attempted.  These 
+caveats notwithstanding, it is still interesting to compare the derived
+stellar mass with the lensing mass.
 
@@
 by using available optical and NIR magnitudes to derive more accurate
-constrains on the stellar populations.
+constraints on the stellar populations.
 
@@
 \begin{aligned}
-\frac{\Mstel}{\Mhalo} &= \frac{2C_0}{(\Mhalo/M_1)^{-\beta} +
-                                     (\Mhalo/M_1)^\gamma} \\
-C_0 &= 0.02820, \quad M_1 = 10^{11.884} M_\odot \\
+\frac{\Mstel}{\Mhalo} &= \frac{2C_0}{(\Mhalo/\Mone)^{-\beta} +
+                                     (\Mhalo/\Mone)^\gamma} \\
+C_0 &= 0.02820, \quad \Mone = 10^{11.884} \Msun \\
 \beta &= 1.057, \quad \gamma = 0.556.

### 2017-03-21 parts/summary.tex
feedback JC, fix trivial ones

@@
 mass of galaxy-group scale.  It is a particularly attractive system
-for follow-up observations at higher resolution, as it large system
+for follow-up observations at higher resolution, as it is a large system
 with clear multiple-image features, and modelling leaves little doubt

### 2017-03-22 parts/intro.tex
small edits

@@
 collisionless non-relativistic fluid (cold dark matter or CDM) readily
-studied by simulations \citep[for example, the millenium simulation
-  by][which has been particularly influential]{2005Natur.435..629S}.
-But other scenarios have also been considered, such as a cold
-condensing boson fluid \citep{2016ApJ...818...89S}, or dark matter
-particles with internal degrees of freedom
-\citep{2010MNRAS.405...77S}, or not matter at all but a modification
-of gravity \citep{2016PhRvL.117t1101M}.
+studied by simulations \citep[for example, the influential millenium
+  simulation by][]{2005Natur.435..629S}.  But other scenarios have
+also been considered, such as a cold condensing boson fluid
+\citep{2016ApJ...818...89S}, or dark matter particles with internal
+degrees of freedom \citep{2010MNRAS.405...77S}, or not matter at all
+but a modification of gravity \citep{2016PhRvL.117t1101M}.
 
@@
 discovered through Space~Warps.  We present results from modelling of
-42 of the 59 lens candidates reported by \cite{2016MNRAS.455.1191M}.
+56 of the 59 lens candidates reported by \cite{2016MNRAS.455.1191M}.
 Each lens candidate was modelled in a collaborative refinement

### 2017-03-22 parts/intro.tex

@@
 arc-finders
-\citep{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G} by
-machine learning \citep{2016A&A...592A..75P} and by visual inspection
-by citizen-science volunteers in Space~Warps
+\citep[e.g.,][]{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G}
+by machine learning
+\citep[e.g.,][]{2016A&A...592A..75P,2017arXiv170302642L} and by visual
+inspection by citizen-science volunteers in Space~Warps
 \citep{2016MNRAS.455.1191M} have, between them, discovered an average

### 2017-03-22 parts/stelmass.tex
dbg

@@
 
-Figure~\ref{fig:stelmass}
-shows a comparison of stellar and total masses.  The comparatively
-large uncertainty in the stellar mass will be improved in future work
-by using available optical and NIR magnitudes to derive more accurate
-constraints on the stellar populations.
+Figure~\ref{fig:stelmass} shows a comparison of stellar and total
+masses.  The comparatively large uncertainty in the stellar mass will
+be improved in future work by using available optical and NIR
+magnitudes to derive more accurate constraints on the stellar
+populations.
 
@@
 observed stellar mass function of galaxies with the dark matter halo
-mass function from N-body simulations results in a simple relation
+mass function from $N$-body simulations results in a simple relation
 between the two. We emphasize that this derivation of halo mass should
@@
 \end{equation}
-and define a halo-matching index:
+%Figure~\ref{fig:stelmass} may be compared with Figure~4 in
+%\cite{2011ApJ...734...69M}.
+
+The comparison of lensing and stellar masses provides us with the last
+of our model diagnostics.  This is a halo-matching index:
 \begin{equation}
@@
 \end{itemize}
-This is the last of our model diagnostics, expressing whether the
-lensing mass is plausible given the light from the candidate lensing
-galaxy.
+The halo-matching index expresses whether the lensing mass is
+plausible given the light from the candidate lensing galaxy.

### 2017-03-29 paper2.tex
add unkown entry for table
feedback JC, fix trivial ones
BritEng
fix affiliation, fixes #33
something
feedback AV, simple things

@@
 \newcommand*{\NO}{\ding{55}}
+\newcommand*{\UK}{--}
 
@@
 
+\newcommand{\SW}{Space~Warps}
+\newcommand{\SpL}{SpaghettiLens}
 \newcommand{\asw}[1]{ASW000#1}
@@
 
-\newcommand{\Mstel}{M_{\rm stel}}
-\newcommand{\Mhalo}{M_{\rm h}}
+%\newcommand{\Mstel}{\ensuremath{M_{\rm stel}}}
+%\newcommand{\Mhalo}{\ensuremath{M_{\rm h}}}
+\newcommand{\Mstel}{\ensuremath{M_\text{stel}}}
+\newcommand{\Mhalo}{\ensuremath{M_\text{halo}}}
+\newcommand{\Msun}{\ensuremath{M_\odot}}
+\newcommand{\Mone}{\ensuremath{M_1}}
 \newcommand{\haloindex}{\mathcal{H}}
-\newcommand{\ER}{$\Theta_{\text{E}}$} % einstein radius
+%\newcommand{\ER}{$\Theta_{\text{E}}$} % einstein radius
+\newcommand{\ER}{\ensuremath{r_\text{E}}} % einstein radius
 
@@
 
-\title[Lens models for Space Warps CFHTLS]{Models of lens candidates from
+\title[Lens models for Space Warps CFHTLS]{Models of gravitational lens candidates from
   Space Warps CFHTLS}
@@
 Aprajita Verma$^{8}$
-and Julianne K. Wilcox$^{4}$
+and Julianne K. Wilcox$^{3}$
 %
@@
 \begin{abstract}
-We report modelling follow-up of recently-discovered
-gravitational-lens candidates in the CFHT Legacy Survey.  Lens
+This paper reports on modelling of recently discovered gravitational lens candidates discovered in the wide Canada France Hawaii Telescope Legacy Survey.
+The candidate lens modelling was carried out by a small group of interested citizen scientists who participated in the \SW project in which the new candidate lenses were discovered.
+Lens
 modelling was done by a small group of specially-interested volunteers
 from the Space~Warps citizen-science community who originally found
-the candidate lenses.  Models are categorized according to seven
+the candidate lenses.  Models are categorised according to seven
 qualitative and quantitative points.  Also included are some
@@
 \input{parts/intro}
-
-% \input parts/spl
 

### 2017-03-29 parts/app.tex
feedback AV, simple things

--- 2017-03-16 parts/app.tex
@@
   \caption{
-    Comparison of Einstein radii \ER obtained from mass tiles directly to those obtained from a parameterized model to test the performance of the parametrisation algorythm.
-    The parameterized model was generated using princible componant analysis on the ensemble of models.
+    Comparison of Einstein radii \ER\ obtained from mass tiles directly to those obtained from a parameterized model to test the performance of the parametrisation algorithm.
+    The parameterized model was generated using princible component analysis on the ensemble of models.
     The blue dashed line represents a perfect recovery of \ER.

### 2017-03-29 parts/intro.tex
fix affiliation, fixes #33
feedback AV, simple things

@@
 important, because while there is a general consensus that basic
-mechanism of galaxy formation involve gravitational collapse,
+mechanism of galaxy formation involves gravitational collapse,
 fragmentation, and mergers of dark-matter clumps, into which gas fell,
@@
 All this motivates using galaxy lenses to study the mutual dynamics of
-dark matter and gas in galaxies.  Several studies in recent years have
-done so
+dark matter, gas and stars in galaxies.  Several studies in recent
+years have done so
 \citep{2009ApJ...703L..51K,2011ApJ...740...97L,2012MNRAS.424..104L,
@@
 inspection by citizen-science volunteers in Space~Warps
-\citep{2016MNRAS.455.1191M} have, between them, discovered an average
+\citep{2016MNRAS.455.1191M,2016MNRAS.455.1171M} have, between them,
+discovered an average
 of four lenses per square degree, so one can be optimistic about
@@
 modelling effort to reconstruct their mass distributions.  To prepare
-for the challenge of massive-sample lens modelling,
+for the challenge of large-sample lens modelling,
 \cite{2015MNRAS.447.2170K} developed a new modelling strategy,
@@
 with experienced members of the citizen-science community, who have
-already participated in lens discovery through Space~Warps, as well as
+already participated in lens discovery through {\SW}, as well as
 several other projects involving astronomical data.  The system was
-tested on a sample of simulated lenses from Space~Warps.
+tested on a sample of simulated lenses generated as part of the
+training set used in {\SW} (see
+\cite{2016MNRAS.455.1191M,2016MNRAS.455.1171M} for further information).
 
-This paper continues by applying SpaghettiLens to lens-candidates
+This paper continues that study by applying SpaghettiLens to
+lens-candidates
 discovered through Space~Warps.  We present results from modelling of
@@
 \item Third, whether the implied lensing mass is plausible, given the
-  photometric data of the lensing galaxy.  Section~\ref{sec:stellar-mass}
+  photometry data of the lensing galaxy.  Section~\ref{sec:stellar-mass}
   explains how we compare the lensing mass with the mass in stars in
@@
   halo index ($\haloindex$) which gives an idea of how the lensing mass
-  compares with these two contraints.  Figure~\ref{fig:stelmass}.
+  compares with these two constraints.  Figure~\ref{fig:stelmass}.
 \end{itemize}
@@
 Section~\ref{sec:summary} summarises and tabulates the diagnostics in
-Table~\ref{tab:models}.  Interpretation of the results is preliminary,
-because the systems are candidates at this stage, not secure lenses.
+Table~\ref{tab:models}.  Interpretation of the results is tentative,
+because the systems are lens candidates at this stage, not secure lenses.
 Moreover the candidate-lens redshifts have large uncertainties, while
@@
 especially interesting candidates.  In \S~\ref{subsec:hires} we show
-that making mass maps fine-grained in the central region relieves a
+that making high resolution mass maps in the central region relieves a
 tendency in the earlier work for mass to be too shallow. Then in

### 2017-03-29 parts/massmodel.tex
feedback JC, fix trivial ones
feedback AV, simple things

--- 2017-03-20 parts/massmodel.tex
@@
   problem.]{2014MNRAS.445.2181C} Assuming such mass distributions can
-be found (which in practise is usually the case) a statistical
+be found (which in practice is usually the case) a statistical
 ensemble of two-dimensional mass maps is returned.  This ensemble,
@@
 the spaghetti diagrams in Figure~\ref{fig:splinput}.  The arrival-time
-contours look like a machine-made elaborations of the input spaghetti
+contours look like machine-made elaborations of the input spaghetti
 diagrams.  If the saddle-point contours in the arrival time are

### 2017-03-29 parts/morph.tex
feedback JC, fix trivial ones
feedback AV, simple things

@@
 
-A modeller's main input to the lens-modelling process is a markup of
-the candidate lens system, with what we call a spaghetti diagram.
+A citizen modeller's main input to the lens-modelling process is a markup of
+the candidate lens system, which we call a spaghetti diagram.
 This is a sketch of the arrival-time surface from a point-like source,
-with proposed locations of maxima, minima and saddle points, and an
+with user-proposed locations of maxima, minima and saddle points, and an
 implied time-ordering of the images.  Such information encodes a
@@
 
-We now discuss the diagnostics that can be given from the process of
+We now discuss the diagnostics that can be taken from the process of
 drawing the spaghetti diagram, even before detailed mass-modelling
@@
 the right interpreted as a single image, rather than as three images
-as shown in the figure; for such a model, `unblended images' would be
-true.
+as shown in the figure; for such a model, `unblended images'
+diagnostic would be true.
 
@@
 significantly to the lensing.  For this, we do not consider stars or
-other clearly foregound objects.  Secondary lensing galaxies can be
+other clearly foregound objects.  Additional galaxies contributing to
+the lensing mass can be
 marked by the volunteer alongside the spaghetti diagrams.  An example
@@
 are modelled as point masses.  Other possible contributors to lensing
-are galaxies or groups that are not in the immediately vicinity of
+are galaxies or groups that are not in the immediate vicinity of
 the lensed images, yet massive enough to have an effect.  These are
-contributed for by allowing a constant but adjustable external shear.
+accounted for by allowing a constant but adjustable external shear.
 

### 2017-03-29 parts/stelmass.tex
dbg
revert
feedback AV, simple things

@@
 systematic error is contamination of the light of the lensing galaxy
-by the lensed galaxy.  Reducing or eliminating the latter would
+by the lensed background galaxy.  Reducing or eliminating the latter would
 require detailed fitting of light distributions for each candidate
@@
 \begin{aligned}
-\frac{\Mstel}{\Mhalo} &= \frac{2C_0}{(\Mhalo/\Mone)^{-\beta} +
-                                     (\Mhalo/\Mone)^\gamma} \\
-C_0 &= 0.02820, \quad \Mone = 10^{11.884} \Msun \\
+\frac{\Mstel}{\Mhalo} &= \frac{2C_0}{(\Mhalo/M_1)^{-\beta} +
+                                     (\Mhalo/M_1)^\gamma} \\
+C_0 &= 0.02820, \quad M_1 = 10^{11.884} M_\odot \\
 \beta &= 1.057, \quad \gamma = 0.556.
@@
 \end{equation}
-%Figure~\ref{fig:stelmass} may be compared with Figure~4 in
-%\cite{2011ApJ...734...69M}.
+Figure~\ref{fig:stelmass} may be compared with Figure~4 in
+\cite{2011ApJ...734...69M}.
 

### 2017-03-29 parts/summary.tex
something
nconc step1

@@
-\section{Discussion}\label{sec:summary}
+\section{Summary and conclusions}\label{sec:summary}
+
+We report on a first set of mass distributions and follow up diagnostics for the \SW lens candidates created with a novel approach that aims to be scalable by orders of magnitudes to prepare for the many thousands of lenses the next generation of wide field surveys will yield.
+
+The way of discovering lenses is changing with the introduction of machine learning and citizen science, combined with the coverage of huge areas by modern surveys.
+The way mass models are generated however remains the same and isn't prepared for the increasing influx of lenses to be modelled.
+We combine the classical approach, where a small team of experts invest many hours into creation of a single model with the approach of citizen science, where a crowd of non trained volunteers make independent contributions.
+We recruit motivated citizen scientists and train them to be expert modelers and ask them to create early stage models as soon as a lens candidate is announced.
+
+To assists the expert modelers assessing their models, we introduce a set of diagnostics allowing the categorisation of the lenses, and the
+
+% way of discovering lenses changed, way of creating models didn't
+% factors for c-scientists
+
+Our conclusions are as follows.
 
@@
 model mass compares with the estimated stellar and full-halo masses.
-Missing entires are due to photometry data not being available, whereas
-missing rows are due to models not having been created.
+Missing entries are due to photometry data not being available, whereas
+missing rows are due to models not having been created for this particular
+candidate.
 
@@
 in mass.
+
+% outlook
+pop synth not yet automated

### 2017-03-30 parts/figures.tex
updated table and desc
edited stelmass

@@
   maxima, minima and saddle points of the arrival time respectively.
-
-	The curves
-  help guide the placement of the dots, but their precise appearance
-  has no significance.  This selection includes the best-modelled
-  systems, but also one case (SW57 at upper right) of unsuccessful
-  modelling.  Since the modelling process is collaborative among the
-  volunteers, with anyone welcome to contribute new models or modify
-  existing ones, there are variant spaghetti diagrams for all the
-  modelled systems.  The online supplement displays all the models
-  presented for discussion during this work.
+  The curves help guide the placement of the dots, but their precise
+  appearance has no significance.  This selection includes the
+  best-modelled systems, but also one case (SW57 at upper right) of
+  unsuccessful modelling.  Since the modelling process is
+  collaborative among the volunteers, with anyone welcome to
+  contribute new models or modify existing ones, there are variant
+  spaghetti diagrams for all the modelled systems.  The online
+  supplement displays all the models presented for discussion during
+  this work.
 \label{fig:splinput}}
@@
   bars are the systems shown in detail in
-  Figures~\ref{fig:splinput}--\ref{fig:encl}.)  The lower-right shaded
-  region is unphysical according to the stellar-population models,
-  because it gives $M<\Mstel$. The upper-left shaded region is
-  unphysical according to abundance matching (see
-  Section~\ref{sec:stellar-mass}) because it gives $M>\Mhalo$.  That
-  is to say, the unshaded region is
+  Figures~\ref{fig:splinput}--\ref{fig:encl}.)  The horizontal and
+  vertical extents of each bar indicate the uncertainties in the
+  stellar and total masses.  The lower-right shaded region is
+  unphysical according to the stellar-population models, because it
+  gives $M<\Mstel$. The upper-left shaded region is unphysical
+  according to abundance matching (see Section~\ref{sec:stellar-mass})
+  because it gives $M>\Mhalo$.  That is to say, the unshaded region is
   $0<\haloindex<1$. \label{fig:stelmass}}
@@
 \begin{table*}
-  \caption{Categorisation of SW models}
+  \caption{Diagnostics of a selected model for each Space Warps candidate
+    (see Section~\ref{sec:summary}).}
   \label{tab:models}

### 2017-03-30 parts/stelmass.tex
todo for PS
edited stelmass

@@
 relationship between the apparent total magnitude and stellar mass, at
-the redshift of the lens.  For typical stellar population parameters,
+the redshift of the lens.  For typical stellar-population parameters,
 the variation of this relation is at most 1\,dex.  A further possible
 systematic error is contamination of the light of the lensing galaxy
-by the lensed background galaxy.  Reducing or eliminating the latter would
-require detailed fitting of light distributions for each candidate
-\citep[see][]{2011ApJ...740...97L}, which we have not yet attempted.  These 
-caveats notwithstanding, it is still interesting to compare the derived
-stellar mass with the lensing mass.
+by the lensed background galaxy.  Reducing or eliminating the latter
+would require detailed fitting of light distributions for each
+candidate \citep[see][]{2011ApJ...740...97L}, which we have not yet
+attempted.  Nonetheless, because the lensing masses range over two
+order of magnitude, it is still interesting to compare with very rough
+stellar masses.
 
@@
 
-In addition, we also derive halo masses for the lenses by use of the
-standard abundance matching technique, whereby a comparison of the
-observed stellar mass function of galaxies with the dark matter halo
-mass function from $N$-body simulations results in a simple relation
-between the two. We emphasize that this derivation of halo mass should
-be considered an ``average'' estimate, and a significant scatter can
-be expected as galaxies with the same stellar mass can be found in
-different environments. We refer the reader to \cite{2012MNRAS.424..104L}
-for an assessment of the effect of abundance matching on the
-derivation of dark matter halo properties in lensing galaxies. We
-follow the prescription of \citet{2010ApJ...710..903M}, namely:
+In addition, we also derive halo masses for the lenses using an
+abundance-matching formula.  This technique matches the distribution
+function of observed stellar mass in galaxies with that of dark-halo
+masses in $N$-body simulations to derive simple relation between
+stellar mass and halo mass.  We emphasize that a halo mass from
+abundance matching should be considered an ``average'' estimate, and a
+significant scatter can be expected as galaxies with the same stellar
+mass can be found in different environments. We refer the reader to
+\cite{2012MNRAS.424..104L} for an assessment of the effect of
+abundance matching on the derivation of dark matter halo properties in
+lensing galaxies. We follow the prescription of
+\citet{2010ApJ...710..903M}, namely:
 \begin{equation}

### 2017-03-30 parts/stelmass.tex
edited stelmass

@@
 function of observed stellar mass in galaxies with that of dark-halo
-masses in $N$-body simulations to derive simple relation between
+masses in $N$-body simulations to derive a simple relation between
 stellar mass and halo mass.  We emphasize that a halo mass from

### 2017-03-30 parts/figures.tex
AV: 2nd round of changes, updated table

--- 2017-03-16 parts/figures.tex
@@
   is to say, the unshaded region is
-  $0<\haloindex<1$. \label{fig:stelmass}}
+  $0<\haloindex<1$.
+  The width of the bars represent the error in $\Mstel$, where the
+  lower and upper bounds are given assuming a ``young'' / ``old'' age trend
+  for the population synthesis models (see Section~\ref{sec:stellar-mass}).
+  The height of the bar is given by the minima and maxima values in $\Mhalo$
+  obtained from the statistical ensemble of mass maps that make up
+  one {\SpL} model (see Section~\ref{sec:massmodels}).
+  \label{fig:stelmass}}
 \end{figure*}

### 2017-03-30 parts/intro.tex
AV: 2nd round of changes, updated table

@@
 modelling effort to reconstruct their mass distributions.  To prepare
-for the challenge of large-sample lens modelling,
+for the challenge of massive-sample lens modelling,
 \cite{2015MNRAS.447.2170K} developed a new modelling strategy,
@@
 several other projects involving astronomical data.  The system was
-tested on a sample of simulated lenses generated as part of the
-training set used in {\SW} (see
-\cite{2016MNRAS.455.1191M,2016MNRAS.455.1171M} for further information).
+tested on a sample of simulated lenses\footnote{
+  Those simulated lenses were generated as part of the training set used
+  in {\SW} (see \cite{2016MNRAS.455.1191M,2016MNRAS.455.1171M} for further
+  information)}
+from \SW.
 
@@
 \item Third, whether the implied lensing mass is plausible, given the
-  photometry data of the lensing galaxy.  Section~\ref{sec:stellar-mass}
+  photometry of the lensing galaxy.  Section~\ref{sec:stellar-mass}
   explains how we compare the lensing mass with the mass in stars in
@@
 the already-available data.
+%TODO there is more info about uncertainies here:
+% https://arxiv.org/pdf/0811.3326.pdf
 
@@
 especially interesting candidates.  In \S~\ref{subsec:hires} we show
-that making high resolution mass maps in the central region relieves a
-tendency in the earlier work for mass to be too shallow. Then in
+that making mass maps fine-grained in the central region relieves a
+tendency in the earlier work for mass profile to be too shallow. Then in
 \S~\ref{subsec:parameter} we consider the possibility of fitting a

### 2017-03-30 parts/massmodel.tex
AV: 2nd round of changes, updated table

@@
 lensing galaxies; the values range from $z=0.2$ to $z=1$ (see
-Table~\ref{tab:models}).  Source redshifts are set to $z=2$ unless an
-unambiguous photometric redshift is available.  The mass normalisation
-depends only weakly on the source redshift, provided it is not close
-to the lens redshift.
+Table~\ref{tab:models}).  As the mass normalisation depends only weakly
+on source redshift, provided it is larger than to the lens redshift,
+we assumed all sources to lie at $z=2$ unless an unambiguous photometric
+redshift is available.
 

### 2017-03-30 parts/morph.tex
AV: 2nd round of changes, updated table

@@
 
-A citizen modeller's main input to the lens-modelling process is a markup of
+A modeller's main input to the lens-modelling process is a markup of
 the candidate lens system, which we call a spaghetti diagram.
 This is a sketch of the arrival-time surface from a point-like source,
-with user-proposed locations of maxima, minima and saddle points, and an
+with proposed locations of maxima, minima and saddle points, and an
 implied time-ordering of the images.  Such information encodes a

### 2017-03-30 parts/figures.tex

--- 2017-03-30 parts/figures.tex
@@
   bars are the systems shown in detail in
-  Figures~\ref{fig:splinput}--\ref{fig:encl}.)  The horizontal and
-  vertical extents of each bar indicate the uncertainties in the
-  stellar and total masses.  The lower-right shaded region is
+  Figures~\ref{fig:splinput}--\ref{fig:encl}.)
+  The horizontal extend of each bar indicates the uncertainties in the stellar
+  mass, esitmated assuming a ``young'' and ``old'' age trend
+  for the population synthesis models; whereas the vertical extents indicade
+  the spread of total halo mass in one ensemble of models.
+  The lower-right shaded region is
   unphysical according to the stellar-population models, because it

### 2017-03-30 parts/figures.tex
typo

--- 2017-03-30 parts/figures.tex
@@
   bars are the systems shown in detail in
-  Figures~\ref{fig:splinput}--\ref{fig:encl}.)  The horizontal and
-  vertical extents of each bar indicate the uncertainties in the
-  stellar and total masses.  The lower-right shaded region is
+  Figures~\ref{fig:splinput}--\ref{fig:encl}.)
+  The horizontal extend of each bar indicates the uncertainties in the stellar
+  mass, esitmated assuming a ``young'' and ``old'' age trend
+  for the population synthesis models; whereas the vertical extent indicades
+  the spread of total halo mass in one model ensemble.
+  The lower-right shaded region is
   unphysical according to the stellar-population models, because it

### 2017-03-31 parts/summary.tex
new summary, first draft

--- 2017-03-21 parts/summary.tex
@@
-\section{Discussion}\label{sec:summary}
+\section{Summary and conclusions}\label{sec:summary}
+
+We report on a first set of mass distributions and follow up diagnostics for 
+the {\SW} lens candidates created with a novel approach that aims to be scalable 
+by orders of magnitudes to prepare for the many thousands of lenses the next 
+generation of wide field surveys will yield.
+
+The way of discovering lenses is changing with the introduction of machine 
+learning and citizen science, combined with the coverage of huge areas by 
+modern surveys.
+The way mass models are generated however remains the same and isn't prepared 
+for the increasing influx of lenses to be modelled.
+We combine the classical approach, where a small team of experts invest many 
+hours into the creation of a single model with the approach of citizen science, 
+where a crowd of amateur volunteers make independent contributions.
+We recruit motivated citizen scientists, train them to be enthusiast modellers 
+and ask them to create early stage models as soon as a lens candidate is 
+announced.
+
+To assists the enthusiast modellers assessing their models, we introduce a set 
+of diagnostics allowing the qualification of the lenses and the generated 
+models and present them alongside the generated models. At a later stage, we 
+encourage enthusiast modellers to apply those diagnostics themselves to get a 
+preliminary feedback on the plausibility of their models.
 
@@
 candidates having stellar and total mass typical of massive
-ellipticals.  SW05 is the most massive of all the candidates, with a
+ellipticals.  SW05 is one of the most massive of all the candidates, with a
 mass of galaxy-group scale.  It is a particularly attractive system
@@
 with clear multiple-image features, and modelling leaves little doubt
-that it is a lens.  The two lowest-mass systems, SW19 and SW42, are
-important if they are indeed lenses, because of their low mass.  The
-models in both cases are plausible but not entirely satisfactory.
+that it is a lens.
+SW04 seems to be even more massive, but the diagnostics leave some doubts
+about this model.
+The two lowest-mass systems, SW19 and SW42, are
+important if they are indeed lenses, because of their low mass.
+The models in both cases are plausible but not entirely satisfactory.
+Their follow up, especially the one on SW42, would either confirm that
+abundance matching and the halo-matching index $\haloindex$ are good
+criteria for filtering possible candidates or it would lead to a really
+interesting new, very low mass galaxy that is highly dominated by dark matter.
 
 The trend in Figure~\ref{fig:stelmass}, that higher-mass galaxies get
-progressively more dark-matter dominated, is expected
-, e.g. see \cite{2005ApJ...623L...5F}.
+progressively more dark-matter dominated, is expected,
+e.g. see \cite{2005ApJ...623L...5F}, as is the span of about one order
+of magnitude for the stellar mass and the two order of magnitudes for the total
+mass.
 With future data, it would be interesting to compare enclosed
@@
 in mass.
+
+The quick creation of many models for the {\SW} candidates successfully showed
+that a subset of citizen scientists are interested in being involved in more
+challenging tasks that take some time to learn. A next steps involves
+recruiting more lensing enthusiasts, as soon as the next round of {\SW} is
+started.
+In the meantime, the improvements shown in the appendix have to been integrated
+into regular {\SpL} usage.
+Additionally, photometric fitting could be integrated into {\SpL}.
+This would allow the lensing enthusiasts to generate precise photometric
+redshifts and thus better stellar masses for all models, without requiring
+data from external pipelines.

### 2017-04-02 paper2.tex
edits

@@
 \begin{abstract}
-This paper reports on modelling of recently discovered gravitational lens candidates discovered in the wide Canada France Hawaii Telescope Legacy Survey.
-The candidate lens modelling was carried out by a small group of interested citizen scientists who participated in the \SW project in which the new candidate lenses were discovered.
-Lens
-modelling was done by a small group of specially-interested volunteers
-from the Space~Warps citizen-science community who originally found
-the candidate lenses.  Models are categorised according to seven
-qualitative and quantitative points.  Also included are some
-improvements to the modelling software used (SpaghettiLens),
-and discussion of strategies for scaling to future surveys
-with more and frequent discoveries.
+We report modelling follow-up of recently-discovered
+gravitational-lens candidates in the Canada France Hawaii Telescope
+Legacy Survey. Lens modelling was done by a small group of
+specially-interested volunteers from the \SW citizen-science community
+who originally found the candidate lenses.  Models are categorised
+according to seven diagnostics indicating (a)~the image morphology and
+how clear or indistinct it is, (b)~whether the mass map and synthetic
+lensed image appear to be plausible, and (c)~how the lens-model mass
+compares with compares with the abundance-matched halo mass derived
+from photometry of the lensing galaxy.
 
-The candidates successfully modelled are all galaxies, with inferred
-lensing masses ranging from $\sim10^{11}M_\odot$ to $>10^{13}M_\odot$.
-Stellar masses have also been estimated, using photometry from the
-CFHTLS pipeline and stellar-population models.  A trend well-known
-in nearby galaxies, that star-formation efficiency is maximal for
-total masses of $\approx10^{12}M_\odot$ and reduces for both lower and
-higher masses, is discernible also in these much more distant
-galaxies.
+The lens-model masses range from $\sim10^{11}M_\odot$ to
+$>10^{13}M_\odot$.  Preliminary estimates of the stellar masses show
+(with two outliers) a smaller spread in stellar mass: a factor of a
+few below or above $\sim10^{11}M_\odot$.  That is, the stellar-mass
+fraction declines sharply as total mass increases.  The most massive
+system is J1434+522 (SW05).  The two low-mass outliers are J0206-095
+(SW19) and J2217+015 (SW42).  If they are indeed lenses, they are
+probing an interesting regime of very low star-formation efficiency.
+
+Some improvements to the modelling software used (SpaghettiLens), and
+discussion of strategies for scaling to future surveys with more and
+frequent discoveries, are also included.
 \end{abstract}

### 2017-04-02 parts/figures.tex
edits

@@
   bars are the systems shown in detail in
-  Figures~\ref{fig:splinput}--\ref{fig:encl}.)
-  The horizontal extend of each bar indicates the uncertainties in the stellar
-  mass, esitmated assuming a ``young'' and ``old'' age trend
-  for the population synthesis models; whereas the vertical extent indicades
-  the spread of total halo mass in one model ensemble.
-  The lower-right shaded region is
-  unphysical according to the stellar-population models, because it
-  gives $M<\Mstel$. The upper-left shaded region is unphysical
-  according to abundance matching (see Section~\ref{sec:stellar-mass})
-  because it gives $M>\Mhalo$.  That is to say, the unshaded region is
+  Figures~\ref{fig:splinput}--\ref{fig:encl}.)  The horizontal extent
+  of each bar indicates the extreme cases of a young (0.5~Gyr-old)
+  stellar population and the oldest possible population at the given
+  redshift.  The vertical extent indicates the spread of masses in
+  lens-model ensemble.  The lower-right shaded region is unphysical
+  according to the stellar-population models, because it gives
+  $M<\Mstel$. The upper-left shaded region is unphysical according to
+  abundance matching (see Section~\ref{sec:stellar-mass}) because it
+  gives $M>\Mhalo$.  That is to say, the unshaded region is
   $0<\haloindex<1$. \label{fig:stelmass}}

### 2017-04-02 parts/intro.tex
edits

@@
 studied by simulations \citep[for example, the influential millenium
-  simulation by][]{2005Natur.435..629S}.  But other scenarios have
-also been considered, such as a cold condensing boson fluid
-\citep{2016ApJ...818...89S}, or dark matter particles with internal
-degrees of freedom \citep{2010MNRAS.405...77S}, or not matter at all
-but a modification of gravity \citep{2016PhRvL.117t1101M}.
+  simulation by][]{2005Natur.435..629S}.  But other scenarios, where
+dark matter has exotic dynamical properties
+\citep{2010MNRAS.405...77S,2016ApJ...818...89S}, or is not really
+matter at all but a modification of gravity
+\citep{2016PhRvL.117t1101M}, have also been considered.
 
@@
 inspection by citizen-science volunteers in Space~Warps
-\citep{2016MNRAS.455.1191M,2016MNRAS.455.1171M} have, between them,
-discovered an average
+\citep{2016MNRAS.455.1191M} have, between them, discovered an average
 of four lenses per square degree, so one can be optimistic about
@@
 with experienced members of the citizen-science community, who have
-already participated in lens discovery through {\SW}, as well as
-several other projects involving astronomical data.  The system was
-tested on a sample of simulated lenses\footnote{
-  Those simulated lenses were generated as part of the training set used
-  in {\SW} (see \cite{2016MNRAS.455.1191M,2016MNRAS.455.1171M} for further
-  information)}
-from \SW.
+already participated in lens discovery through \SW, as well as several
+other projects involving astronomical data.  The system was tested on
+a sample of simulated lenses, which were part of the training and
+testing set in \SW.
 
 This paper continues that study by applying SpaghettiLens to
-lens-candidates
-discovered through Space~Warps.  We present results from modelling of
-56 of the 59 lens candidates reported by \cite{2016MNRAS.455.1191M}.
-Each lens candidate was modelled in a collaborative refinement
-process, where anyone interested can create a new model or modify an
-existing model to try and make it better.\footnote{This is in contrast
-  to the main Space~Warps project for discovering lenses, where
-  volunteers in a crowd of $\gtrsim10^4$ make independent
-  contributions.  Each person is presented with a random selection of
-  survey-patches and invited to (in effect) vote on each.  The system
-  estimates each volunteer's skill level according to test-patches
-  interspersed with the real data, and weights their votes accordingly
-  \citep{2016MNRAS.455.1171M}.  There is an active forum for
-  volunteers, but since everyone is seeing different data samples with
-  minimal overlap, the forum has little if any influence on votes.}
-The result model represents a consensus among contributors, as to the
-best that could be achieved with the available data and software.
+lens-candidates discovered through Space~Warps.  We present results
+from modelling of 56 of the 59 lens candidates reported by
+\cite{2016MNRAS.455.1191M}.  Each lens candidate was modelled in a
+collaborative refinement process, where anyone interested can create a
+new model or modify an existing model to try and make it
+better.\footnote{This is in contrast to the main Space~Warps project
+  for discovering lenses, where volunteers in a crowd of $\gtrsim10^4$
+  make independent contributions.  Each person is presented with a
+  random selection of survey-patches and invited to (in effect) vote
+  on each.  The system estimates each volunteer's skill level
+  according to test-patches interspersed with the real data, and
+  weights their votes accordingly \citep{2016MNRAS.455.1171M}.  There
+  is an active forum for volunteers, but since everyone is seeing
+  different data samples with minimal overlap, the forum has little if
+  any influence on votes.}  The result model represents a consensus
+among contributors, as to the best that could be achieved with the
+available data and software.
 

### 2017-04-03 parts/summary.tex
edits

@@
 
-The way of discovering lenses is changing with the introduction of machine 
-learning and citizen science, combined with the coverage of huge areas by 
-modern surveys.
-The way mass models are generated however remains the same and isn't prepared 
-for the increasing influx of lenses to be modelled.
-We combine the classical approach, where a small team of experts invest many 
-hours into the creation of a single model with the approach of citizen science, 
-where a crowd of amateur volunteers make independent contributions.
-We recruit motivated citizen scientists, train them to be enthusiast modellers 
-and ask them to create early stage models as soon as a lens candidate is 
-announced.
+The way of discovering lenses is changing with the introduction of
+machine learning and citizen science, combined with the coverage of
+huge areas by modern surveys.  The way mass models also needs to
+change, in order to be prepared for the increasing influx of lenses to
+be modelled.  This work is a hybrid of the classical style, where a
+small team of experts invest many hours into the creation of a single
+model, with the approach of citizen science, where a crowd of amateur
+volunteers make independent contributions.  We are a collaboration of
+professionals and experienced citizen-science volunteers, aiming to
+create early-stage lens models as soon as a lens candidate is found.
 
-To assists the enthusiast modellers assessing their models, we introduce a set 
-of diagnostics allowing the qualification of the lenses and the generated 
-models and present them alongside the generated models. At a later stage, we 
-encourage enthusiast modellers to apply those diagnostics themselves to get a 
-preliminary feedback on the plausibility of their models.
+To assists volunteer modellers assessing their models, we introduce a
+set of diagnostics allowing the qualification of the lenses and the
+generated models and present them alongside the generated models. At a
+later stage, we encourage modellers to apply those diagnostics
+themselves to get a preliminary feedback on the plausibility of their
+models.
 
@@
 started.
-In the meantime, the improvements shown in the appendix have to been integrated
+In the meantime, the improvements shown in the Appendix have to been integrated
 into regular {\SpL} usage.
 Additionally, photometric fitting could be integrated into {\SpL}.
-This would allow the lensing enthusiasts to generate precise photometric
-redshifts and thus better stellar masses for all models, without requiring
-data from external pipelines.
+This would allow experienced citizen scientists to generate photometric
+redshifts and stellar masses, and thus generate preliminary dark-matter maps
+as soon as a lens-candidate is identified.

### 2017-04-03 paper2.tex
edits

@@
 few below or above $\sim10^{11}M_\odot$.  That is, the stellar-mass
-fraction declines sharply as total mass increases.  The most massive
-system is J1434+522 (SW05).  The two low-mass outliers are J0206-095
-(SW19) and J2217+015 (SW42).  If they are indeed lenses, they are
-probing an interesting regime of very low star-formation efficiency.
+fraction declines sharply as total mass increases.  The highest-mass
+system with a convincing model is J1434+522 (SW05).  The two low-mass
+outliers are J0206-095 (SW19) and J2217+015 (SW42); if these two are
+indeed lenses, they are probing an interesting regime of very low
+star-formation efficiency.
 

### 2017-04-03 parts/summary.tex
edits

@@
 The models in both cases are plausible but not entirely satisfactory.
-Their follow up, especially the one on SW42, would either confirm that
-abundance matching and the halo-matching index $\haloindex$ are good
-criteria for filtering possible candidates or it would lead to a really
-interesting new, very low mass galaxy that is highly dominated by dark matter.
+In particular, for SW42 the halo-matching index is unphysically high.
+If this candidate turns out not to be a lens, that would support
+the halo-matching index $\haloindex$ as a good
+criterion for filtering possible candidates; if SW42 is a lens,
+it would be an interesting new, very low mass galaxy that is highly
+dominated by dark matter.
 

### 2017-04-03 parts/summary.tex
adding comments about SW57, fixes #25

--- 2017-04-03 parts/summary.tex
@@
 The two lowest-mass systems, SW19 and SW42, are
-important if they are indeed lenses, because of their low mass.
-The models in both cases are plausible but not entirely satisfactory.
-Their follow up, especially the one on SW42, would either confirm that
-abundance matching and the halo-matching index $\haloindex$ are good
-criteria for filtering possible candidates or it would lead to a really
-interesting new, very low mass galaxy that is highly dominated by dark matter.
+important if they are indeed lenses, as they would be low-mass lenses dominated 
+by dark matter.  All the modelled systems have reasonable stellar-mass 
+fractions, except for two cases where the stellar-mass fraction is too low 
+(halo-matching index $>1$): these are SW42 and SW57.  In the case of SW57, the 
+model has poor diagnostics and should be discounted.  The model for SW42, on the 
+other hand, is quite convincing --- except for the high halo-matching index.  
+If SW42 turns out not to be a lens, that would support the halo-matching index 
+as an effective criterion for filtering models.
 

### 2017-04-03 parts/figures.tex
added remark for bluring, fixes #31

@@
   The curves help guide the placement of the dots, but their precise
-  appearance has no significance.  This selection includes the
+  appearance has no significance.  This images are screenshots from the 
+  SpaghettiLens user interface, which applies interpolation to background
+  images. The scaling is adjusted to fit the other images.
+  This selection includes the
   best-modelled systems, but also one case (SW57 at upper right) of
@@
   Figure~\ref{fig:splinput}, derived from the lens models.  The
-  reconstructed lensed features are keep the Space~Warps false-colour
+  reconstructed lensed features keep the Space~Warps false-colour
   scheme from Figures~\ref{fig:splinput}.  The rest has been changed

### 2017-06-15 parts/morph.tex
editing

@@
 along the short axis, IQ if inclined to both axes, CQ if only very little to
-no inclination.  Although the
+no displacement.  Although the
 unlensed source and its location are obviously not seen, the LQ, SQ, IQ and CQ
@@
   and SW28 in the upper row of Figure~\ref{fig:splinput} are typical
-  examples of SQ.
+  examples of SQ.  If the source would move outwards along the short
+  axis, the minimum-saddle-minimum would merge into a single minimum,
+  leaving a D system; the transition is known as cusp catastrophe.
 \item The middle row of Figure~\ref{fig:splinput} shows three IQ
   systems, SW05, SW42 and SW19.  This type has a characteristic
-  asymmetry, often with two images close together.
+  asymmetry, often with two images close together.  If the source
+  would move outwards, the minimum-saddle pair would merge and
+  mutually cancel, again leaving a D system; the transition is known
+  as a fold catastrophe.
 \item The lower row of Figure~\ref{fig:splinput} shows three LQ
@@
   fairly symmetric arrangement with an arc and a counter-image on the
-  other side, but the spaghetti diagram is completely asymmetric.  LQ
-  can be visually distinguished from SQ from the relative distances of
-  the arc and the counter-image.  For LQ the arc is closer, for SQ the
-  counter-image is closer.
+  other side, but the spaghetti diagram is completely asymmetric.  If
+  the source would move outwards along the long axis, the
+  saddle-minimum-saddle would merge into a single saddle --- another
+  form of cusp catastrophe.  LQ can be visually distinguished from SQ
+  from the relative distances of the arc and the counter-image.  For
+  LQ the arc is closer, for SQ the counter-image is closer.
 \end{itemize}
-Although the labels `short-axis quad' and so on are not standard in
-the literature, the morphological classification they express is
-familiar to experienced modellers.  Hence they can be useful to
-researchers wishing to apply other modelling methods to the same
-systems.
+CQ systems are often called `cross' or `Einstein-cross' systems; IQ
+systems are sometimes called `folds', with `cusp' commonly used for
+both SQ and LQ.  The labels `short-axis quad' and so on are not
+standard in the literature, but the morphological classification they
+express is familiar to experienced modellers.  Hence they can be
+useful to researchers wishing to apply other modelling methods to the
+same systems.

### 2017-06-29 paper2.tex
adding comments about SW57, fixes #25
forgotten last minute changes on main.tex
continuing response

@@
 %%% DEBUG SETTINGS - remove at the end %%%%%%%%%%%%%%%
-\usepackage{silence} % silence error warinings
-\WarningFilter{caption}{Unsupported document class} % caption doesn't know mnras..
-\hbadness = 10000
-\vbadness = 10000
+
+%\usepackage{silence} % silence error warinings
+%\WarningFilter{caption}{Unsupported document class} % caption doesn't know mnras..
+%\hbadness = 10000
+%\vbadness = 10000
+
 % \usepackage{}
@@
 Legacy Survey. Lens modelling was done by a small group of
-specially-interested volunteers from the \SW citizen-science community
+specially-interested volunteers from the \SW\ citizen-science community
 who originally found the candidate lenses.  Models are categorised
@@
 \begin{keywords}
-gravitational lensing: strong -- citizen science
+gravitational lensing: strong -- galaxies: general
 \end{keywords}

### 2017-06-29 parts/app.tex
adding comments about SW57, fixes #25
liewrap
continuing response

--- 2017-03-16 parts/app.tex
@@
 
-The models of simulated lenses in \cite{2015MNRAS.447.2170K} showed a
-tendency to produce too shallow density profiles.
+The models of simulated lenses in \cite{2015MNRAS.447.2170K} showed a tendency 
+to produce density profiles which were too shallow, resulting typically
+in overestimates of the Einstein radius.
 Allowing smaller mass tiles in the
@@
 
-\subsection{Parameterisation of pixel models} \label{subsec:parameter}
+\subsection{Parametrization of pixel models} \label{subsec:parameter}
 
-In order to fit the set of pixelated models to a single parameterised model, a program was written that took a parameterised function and subtracted from it the mean and the principal components of the data, which were calculated using classical Principal Component Analysis.
+In order to fit the set of pixelated models to a single parametrized model, a 
+program was written that took a parametrized function and subtracted from it 
+the mean and the principal components of the data, which were calculated using 
+classical Principal Component Analysis.
 This created the residuals function.
-The number of components used in the analysis was varied, to test how this affected the output, and it was found that using 5 principal components tended to give a reasonable approximation.
-A masking function was added which selected only the data points that fell inside the image of the lens, and the principal components were clipped in order to keep the values inside the region of the ensemble of models.
+The number of components used in the analysis was varied, to test how this 
+affected the output, and it was found that using 5 principal components tended 
+to give a reasonable approximation.
+A masking function was added which selected only the data points that fell 
+inside the image of the lens, and the principal components were clipped in 
+order to keep the values inside the region of the ensemble of models.
 Any value higher than the clip was set to be the clip value.
-This was chosen to be 2.5 as, assuming that the data follows a Gaussian error distribution, almost all the values for the variance should lie between 2 and 3 standard deviations from the mean.
-Minimising the residuals function produces the set of parameters that fit the parameterised function to the original pixelated ensemble most closely.
+This was chosen to be 2.5 because, assuming that the data follows a Gaussian error 
+distribution, almost all the values for the variance should lie between 2 and 3 
+standard deviations from the mean.
+Minimising the residuals function produces the set of parameters that fit the 
+parametrized function to the original pixelated ensemble most closely.
 A least squares fit was used to perform this minimisation.
-The parameterised model function was obtained from the gravitational potential of an isothermal ellipsoid mass distribution \citep{2001astro.ph..2341K}.
-This model is frequently used to describe gravitational lenses as it tends to fit well with observations.
-The isothermal ellipsoid model outputs three useful parameters: the radius of the Einstein ring, the ellipticity of the model and the angle of the ellipticity from the vertical, giving the orientation of the galaxy.
-By applying this model to simulated lenses for which the values of these parameters were already known, it was possible to gain an estimate of the projected accuracy of the results, before applying the model to the candidate lensing galaxies.
+The parametrized model function was obtained from the gravitational potential 
+of an isothermal ellipsoid mass distribution \citep{2001astro.ph..2341K}.
+This model is frequently used to describe gravitational lenses as it tends to 
+fit well with observations.
+The isothermal ellipsoid model outputs three useful parameters: the radius of 
+the Einstein ring, the ellipticity of the model and the angle of the 
+ellipticity from the vertical, giving the orientation of the galaxy.
+By applying this model to simulated lenses for which the values of these 
+parameters were already known, it was possible to gain an estimate of the 
+projected accuracy of the results, before applying the model to the candidate 
+lensing galaxies.
 
@@
   \caption{
-    Comparison of Einstein radii \ER obtained from mass tiles directly to those obtained from a parameterized model to test the performance of the parametrisation algorythm.
-    The parameterized model was generated using princible componant analysis on the ensemble of models.
-    The blue dashed line represents a perfect recovery of \ER.
+    Comparison of Einstein radii \ER\ obtained from mass tiles directly to 
+    those obtained from a parameterized model to test the performance of the 
+    parametrization algorithm.  The parameterized model was generated using 
+    principal component analysis on the ensemble of models.  The blue dashed
+    line represents a perfect recovery of \ER.
     }

### 2017-07-18 parts/intro.tex

@@
 
-By coincidence, the typical escape velocity of massive galaxies is
+By a curious coincidence, the typical escape velocity of massive galaxies is
 such that $v_{\rm esc}^2/c^2$ is comparable to the apparent sizes of a
@@
 arc-finders
-\citep[e.g.,][]{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G}
+\citep[e.g.,][]{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G,2017arXiv170401585S}
 by machine learning
@@
   different data samples with minimal overlap, the forum has little if
-  any influence on votes.}  The result model represents a consensus
+  any influence on votes.}  The resulting model represents a consensus
 among contributors, as to the best that could be achieved with the

### 2017-07-18 parts/massmodel.tex

--- 2017-03-29 parts/massmodel.tex
@@
 lensing galaxies; the values range from $z=0.2$ to $z=1$ (see
-Table~\ref{tab:models}).  Source redshifts are set to $z=2$ unless an
-unambiguous photometric redshift is available.  The mass normalisation
-depends only weakly on the source redshift, provided it is not close
-to the lens redshift.
+Table~\ref{tab:models}).  As the mass normalisation depends only weakly
+on source redshift, provided it is larger than the lens redshift,
+we assumed all sources to lie at $z=2$ unless an unambiguous photometric
+redshift is available.
 

### 2017-08-21 parts/summary.tex
continuing response
editing

--- 2017-04-03 parts/summary.tex
@@
 machine learning and citizen science, combined with the coverage of
-huge areas by modern surveys.  The way mass models also needs to
+huge areas by modern surveys.  The way mass models are constructed also needs to
 change, in order to be prepared for the increasing influx of lenses to
@@
 
-Figure~\ref{fig:stelmass} is another summary.  It shows most of the
-candidates having stellar and total mass typical of massive
-ellipticals.  SW05 is one of the most massive of all the candidates, with a
-mass of galaxy-group scale.  It is a particularly attractive system
-for follow-up observations at higher resolution, as it is a large system
-with clear multiple-image features, and modelling leaves little doubt
-that it is a lens.
-SW04 seems to be even more massive, but the diagnostics leave some doubts
-about this model.
-The two lowest-mass systems, SW19 and SW42, are
-important if they are indeed lenses, because of their low mass.
-The models in both cases are plausible but not entirely satisfactory.
-Their follow up, especially the one on SW42, would either confirm that
-abundance matching and the halo-matching index $\haloindex$ are good
-criteria for filtering possible candidates or it would lead to a really
-interesting new, very low mass galaxy that is highly dominated by dark matter.
-
 The trend in Figure~\ref{fig:stelmass}, that higher-mass galaxies get

### 2017-08-23 parts/stelmass.tex

@@
 with a single colour, preferably tracing a rest-frame colour similar
-to $U-V$ \citep[see Fig.~1 of][]{2008MNRAS.383..857F}.
+to $U-V$ \citep[see Fig.~1 of][]{2008MNRAS.383..857F}.  There is some
+evidence from spectral lines that massive galaxies tend to have a more
+bottom-heavy IMF than the Milky Way, but a much higher stellar
+mass-to-light would over-predict the mass in some lensing systems
+\citep{2015MNRAS.454L..71S}.
 
@@
 plausible given the light from the candidate lensing galaxy.
+
+Figure~\ref{fig:stelmass} shows most of the candidates having stellar
+and total mass typical of massive ellipticals.  SW05 is one of the
+most massive of all the candidates, with a mass of galaxy-group scale.
+It is a particularly attractive system for follow-up observations at
+higher resolution, as it is a large system with clear multiple-image
+features, and modelling leaves little doubt that it is a lens.  SW04
+seems to be even more massive, but the diagnostics leave some doubts
+about this model.  The two lowest-mass systems, SW19 and SW42, are
+important if they are indeed lenses, as they would be low-mass lenses
+dominated by dark matter.  All the modelled systems have reasonable
+stellar-mass fractions, except for two cases where the stellar-mass
+fraction is too low (halo-matching index $>1$): these are SW42 and
+SW57.  In the case of SW57, the model has poor diagnostics and should
+be discounted.  The model for SW42, on the other hand, is quite
+convincing --- except for the high halo-matching index.  If SW42 turns
+out not to be a lens, that would support the halo-matching index as an
+effective criterion for filtering models.

### 2017-08-23 parts/app.tex
some changes

@@
 \begin{figure}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_11_hires_comparison}
-  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_13_hires_comparison}
+  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_11_hires_comparison}\\
+  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_13_hires_comparison}\\
   \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_33_hires_comparison}

### 2017-08-23 parts/intro.tex
edits
some changes

@@
 
+Interpretation of the results is tentative,
+because the systems are lens candidates at this stage, not secure lenses.
+Moreover the candidate-lens redshifts have large uncertainties, while
+the candidate-source redshifts can only be guessed at present.
+Nevertheless it is interesting to see what trends we can observe with
+the already-available data.
+%TODO there is more info about uncertainies here:
+% https://arxiv.org/pdf/0811.3326.pdf
+
+The online supplement gives results for all the modelled systems generated
+for all the lensing candidates.
+
+\section{The candidates and models}
+
 We characterise each model with seven diagnostics, grouped into three 
@@
   Section~\ref{sec:morph} and Figure~\ref{fig:splinput} explain.
-\begin{itemize}
+\begin{enumerate}
 \item Whether the images are unblended.  Distinct unblended images are
@@
   lensing mass.
-\end{itemize}
+\end{enumerate}
 \item Second we have mass models, covered in Section~\ref{sec:massmodels}.
-\begin{itemize}
+\begin{enumerate}
+\setcounter{enumi}{4}
 \item Whether the mass map is reasonable. Figure~\ref{fig:kappa}.
@@
   Figures~\ref{fig:arriv} and \ref{fig:synth} and \ref{fig:encl}.
-\end{itemize}
-\item Third, whether the implied lensing mass is plausible, given the
+\end{enumerate}
+\item Third, whether the total implied lensing mass\footnote{
+    In this work we define lensing mass as the sum of all mass tiles
+    needed to model a lens. Those tiles reach out to typically twice
+    the radius of the the outermost image. }
+  determined from the lens model is plausible, given the
   photometry of the lensing galaxy.  Section~\ref{sec:stellar-mass}
@@
   Naturally, the lensing mass must be more than the stellar mass but
-  no more than the total halo mass.  We then introduce what we call a
-  halo index ($\haloindex$) which gives an idea of how the lensing mass
-  compares with these two constraints.  Figure~\ref{fig:stelmass}.
+  no more than the total halo mass.
+\begin{enumerate}
+\setcounter{enumi}{6}
+\item We then introduce what we call a halo index ($\haloindex$) which
+  gives an idea of how the lensing mass compares with these two
+  constraints.  Figure~\ref{fig:stelmass}.
+\end{enumerate}
 \end{itemize}
@@
 Section~\ref{sec:summary} summarises and tabulates the diagnostics in
-Table~\ref{tab:models}.  Interpretation of the results is tentative,
-because the systems are lens candidates at this stage, not secure lenses.
-Moreover the candidate-lens redshifts have large uncertainties, while
-the candidate-source redshifts can only be guessed at present.
-Nevertheless it is interesting to see what trends we can observe with
-the already-available data.
-%TODO there is more info about uncertainies here:
-% https://arxiv.org/pdf/0811.3326.pdf
+Table~\ref{tab:models}.
 
@@
 successful at extracting an Einstein radius.
-
-The online supplement gives results for all the modelled systems generated
-for all the lensing candidates.

### 2017-08-23 parts/morph.tex
some changes
fix image cutout zoom

@@
-\section{Image morphology}\label{sec:morph}
+\section{Image morphology}
+\label{sec:morph}
 
@@
 marked up with a spaghetti diagram.
+The volunteers are initially presented the original Space~Warps image of
+length and height 82\arcsec (440~pixels) in full size, but they have the
+ability to zoom in individually.
+The cutouts presented in Figures~\ref{fig:splinput} to \ref{fig:encl}
+are rescaled in post processing relative to the outermost image identified.
+% it's a factor L/(L-4) with L=pixradius, for L=12 -> 1.5
+% maprad = rmax * L / (L-4)
 

### 2017-08-24 parts/massmodel.tex
about mass map diagnostic

@@
 
-The mass maps and mass profiles are the basis of a further diagnostic:
-are the mass distributions plausible?
+The mass maps and mass profiles are the basis of a further diagnostic: are 
+the mass distributions plausible? This again is a judgment call by 
+modellers, but it showed to be a powerful diagnostic, summarizing three 
+aspects. Usually the overall shape is forced to be $180^\circ$-rotation 
+symmetric and turns out plausible, but volunteers can deactivate this 
+constraint. The profile slope turned out to be a good indicator for 
+plausible models, as can seen by comparing the model \sw{57} to others: 
+The missing core in Figure~\ref{fig:kappa} and the flat profile in 
+Figure~\ref{fig:encl} disqualify this model. The clumpiness of the mass 
+map is another one. Flat profile slopes can often be identified directly 
+in the mass map, where the mass tiles form a checkerboard pattern.

### 2017-08-24 parts/stelmass.tex
some changes
elaborate M_stell error range in fig6

@@
-\section{Stellar and halo mass estimates}\label{sec:stellar-mass}
+\section{Stellar and halo mass estimates}
+\label{sec:stellar-mass}
 
@@
 Figure~\ref{fig:stelmass} shows a comparison of stellar and total
-masses.  The comparatively large uncertainty in the stellar mass will
+masses.  The comparatively large span in the stellar mass shows the range 
+between the masses derived using the two age trends respectively.
+It will 
 be improved in future work by using available optical and NIR

### 2017-08-24 parts/stelmass.tex
replace total mass with lensing mass
replace total mass with lensing mass 2

@@
 
-Figure~\ref{fig:stelmass} shows a comparison of stellar and total
+Figure~\ref{fig:stelmass} shows a comparison of stellar and lensing
 masses.  The comparatively large span in the stellar mass shows the range 
@@
 Figure~\ref{fig:stelmass} shows most of the candidates having stellar
-and total mass typical of massive ellipticals.  SW05 is one of the
+and lensing mass typical of massive ellipticals.  SW05 is one of the
 most massive of all the candidates, with a mass of galaxy-group scale.

### 2017-08-24 parts/summary.tex
replace total mass with lensing mass 2

@@
 The trend in Figure~\ref{fig:stelmass}, that higher-mass galaxies get 
-progressively more dark-matter dominated, is expected,
-e.g. see \cite{2005ApJ...623L...5F}, as is the span of about one order
-of magnitude for the stellar mass and the two order of magnitudes for the total
-mass.
-With future data, it would be interesting to compare enclosed
-stellar and total mass as a function of radius, going from
-star-dominated inner regions to dark halos.
-\cite{2011ApJ...740...97L} illustrate this behaviour in their
-Figure~5, but the present sample could go an order of magnitude higher
-in mass.
+progressively more dark-matter dominated, is expected, e.g. see 
+\cite{2005ApJ...623L...5F}, as is the span of about one order of magnitude for 
+the stellar mass and the two order of magnitudes for the lensing mass. With 
+future data, it would be interesting to compare enclosed stellar and lensing 
+mass as a function of radius, going from star-dominated inner regions to dark 
+halos. \cite{2011ApJ...740...97L} illustrate this behaviour in their Figure~5, 
+but the present sample could go an order of magnitude higher in mass.
 
@@
 recruiting more lensing enthusiasts, as soon as the next round of {\SW} is 
-started.
-In the meantime, the improvements shown in the Appendix have to been integrated
-into regular {\SpL} usage.
-Additionally, photometric fitting could be integrated into {\SpL}.
-This would allow experienced citizen scientists to generate photometric
-redshifts and stellar masses, and thus generate preliminary dark-matter maps
-as soon as a lens-candidate is identified.
+started. In the meantime, the improvements shown in the Appendix have to been 
+integrated into regular {\SpL} usage. Additionally, photometric fitting could 
+be integrated into {\SpL}. This would allow experienced citizen scientists to 
+generate photometric redshifts and stellar masses, and thus generate 
+preliminary dark-matter maps as soon as a lens-candidate is identified.

### 2017-08-25 parts/app.tex
smaller fixes, revert of tablesgit status! (dont use uncorrected massesgit status)

@@
 
-The models of simulated lenses in \cite{2015MNRAS.447.2170K} showed a tendency 
+The models of simulated lenses in \cite{2015MNRAS.447.2170K} showed a 
+tendency 
 to produce density profiles which were too shallow, resulting typically
 in overestimates of the Einstein radius.
-Allowing smaller mass tiles in the
+Volunteers could already set the size of the pixels by defining the radius of 
+the lens in pixels, typical values range between 8 and 12.
+Additionally allowing smaller mass tiles in the
 central region, thus allowing the mass profile to rise more steeply
@@
     Einstein radius \ER. The upper panel is from
-    K\"ung et al., (2015) (see Figure~3 of that paper).  The middle
+    \citet{2015MNRAS.447.2170K}, see Figure~3 of that paper.  The middle
     panel is the result when the innermost mass tile is replaced by 9
@@
 program was written that took a parametrized function and subtracted from it 
-the mean and the principal components of the data, which were calculated using 
+the mean and the principal components of the data, which were calculated 
+using 
 classical Principal Component Analysis.
@@
 The number of components used in the analysis was varied, to test how this 
-affected the output, and it was found that using 5 principal components tended 
+affected the output, and it was found that using 5 principal components 
+tended 
 to give a reasonable approximation.
@@
 Any value higher than the clip was set to be the clip value.
-This was chosen to be 2.5 because, assuming that the data follows a Gaussian error 
-distribution, almost all the values for the variance should lie between 2 and 3 
+This was chosen to be 2.5 because, assuming that the data follows a Gaussian 
+error 
+distribution, almost all the values for the variance should lie between 2 and 
+3 
 standard deviations from the mean.

### 2017-08-25 parts/old_classification.tex
clean up
smaller fixes, revert of tablesgit status! (dont use uncorrected massesgit status)

--- 2016-05-20 old_classification.tex
@@
 The data available is shown in \figref{SW58}.
-\todo{better explain criterias?}
+
 The following sections list all the models for all the categories, each with a short explanation of the reasons.
@@
 Faint close arc, but reconstruion works very well;
-parameterisation of ellypticity fails.
+parameterization of ellypticity fails.
 \params{0.73}{0.00}{249.80}

### 2017-08-27 parts/massmodel.tex
several edits

@@
 redshift values, as and when they become available.  This work applies
-photometric redshifts from the CFHTLS pipeline to the candidate
+photometric redshifts from the CFHTLS pipeline
+\citep{2009A&A...500..981C}
+to the candidate
 lensing galaxies; the values range from $z=0.2$ to $z=1$ (see

### 2017-08-27 parts/stelmass.tex
several edits

@@
 masses.  The comparatively large span in the stellar mass shows the range 
-between the masses derived using the two age trends respectively.
-It will 
-be improved in future work by using available optical and NIR
-magnitudes to derive more accurate constraints on the stellar
-populations.
-
+between the masses derived using the two age trends respectively
+and lies between 0.4 and 0.8~dex.
+It will be improved in future work by using available optical and NIR 
+magnitudes to derive more accurate constraints on the stellar populations.
 In addition, we also derive halo masses for the lenses using an
@@
 
-Figure~\ref{fig:stelmass} shows most of the candidates having stellar
-and lensing mass typical of massive ellipticals.  SW05 is one of the
+Figure~\ref{fig:stelmass} and Table~\ref{tab:models} show most of the
+candidates having stellar
+and lensing mass typical of massive ellipticals\footnote{
+  Exact values can be found in the online version of Table~\ref{tab:models}}.
+SW05 is one of the
 most massive of all the candidates, with a mass of galaxy-group scale.
@@
 stellar-mass fractions, except for two cases where the stellar-mass
-fraction is too low (halo-matching index $>1$): these are SW42 and
+fraction is too low ($\haloindex > 1$): these are SW42 and
 SW57.  In the case of SW57, the model has poor diagnostics and should

### 2017-08-27 parts/summary.tex
discussion about criteria

@@
 themselves to get a preliminary feedback on the plausibility of their
-models.
+models and possibly suggest additional diagnostics.
+
+The diagnostics (i) -- (iv) turned out to be useful for evaluating how difficult a system is to model, but they weren't necessary conditions for a promising model.
+They can help select systems to present to novice volunteers to introduce them to the modelling process.
+Diagnostics (v) and (vi) on the other hand can be considered as necessary criteria for a good model.
+Volunteers employed those to evaluate their models and they turned out to be easy enough to grasp for new volunteers.
+The halo-matching index $\haloindex$, diagnostic (vii), is an interesting criterion that might be useful for volunteers, but needs further investigation to be established.
 

### 2017-08-27 parts/summary.tex
time thing

@@
 create early-stage lens models as soon as a lens candidate is found.
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{img/timelapse}
+  \caption{Activity of volunteers; amount of models, summed over all candidates, after the first model was generated.
+8 users contributed more than five models.
+vertical lines show 1 minute, one hour, one day, one week, one month, one year, two years.
+Dashed vertical line shows the start of the SW01 modelling challenge.}
+  \label{fig:time}
+\end{figure}
 

### 2017-08-30 parts/intro.tex
move appendix eplanation back to chapt1
z errors

@@
 
+There are three appendices devoted to various technical issues
+relating to modelling.  \cite{2015MNRAS.447.2170K} tested the system
+on simulated lenses and identified some areas for improvement.  In
+\S~\ref{subsec:sourcefit} we introduce fitting of the brightness
+profiles of the source.  This feature has not yet been included in
+SpaghettiLens, but has been carried out in post-processing for a few
+especially interesting candidates.  In \S~\ref{subsec:hires} we show
+that making mass maps fine-grained in the central region relieves a
+tendency in the earlier work for mass profile to be too shallow. Then in
+\S~\ref{subsec:parameter} we consider the possibility of fitting a
+parametric lens model to the model ensemble; so far we have only been
+successful at extracting an Einstein radius.
+
 \section{The candidates and models}
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{img/timelapse3}
+  \caption{Amount of generated models over time, since an arb.
+starting point; top Figure shows all models, bottom Figure shows 5 selected candidates with most activity.
+8 users contributed more than five models.
+}
+  \label{fig:time}
+\end{figure}
+
+The volunteers were encouraged to create models of objects found in Space~Warps before they were classified as plausible candidates.
+Figure~\ref{fig:time} shows the evolution of the total number of models the users generated, but only for the candidates, models created for system that turned out to be non candidates were not counted.
+The first beta version of SpaghettiLens was launched around day 140 and was tested and improved on the fly.
+It saw 8 volunteers with major contributions.
+At day 820 the first full version of SpaghettiLens was presented online, around the same time the list of identified candidates was available.
+Around day 200 the volunteers started a modelling challenge for the candidate later to be identified as SW01.
+65 days later 30 models have been created for this particular and this group converged to a set of favorite models that they presented in an online letter.
 
@@
 Table~\ref{tab:models}.
-
-There are three appendices devoted to various technical issues
-relating to modelling.  \cite{2015MNRAS.447.2170K} tested the system
-on simulated lenses and identified some areas for improvement.  In
-\S~\ref{subsec:sourcefit} we introduce fitting of the brightness
-profiles of the source.  This feature has not yet been included in
-SpaghettiLens, but has been carried out in post-processing for a few
-especially interesting candidates.  In \S~\ref{subsec:hires} we show
-that making mass maps fine-grained in the central region relieves a
-tendency in the earlier work for mass profile to be too shallow. Then in
-\S~\ref{subsec:parameter} we consider the possibility of fitting a
-parametric lens model to the model ensemble; so far we have only been
-successful at extracting an Einstein radius.

### 2017-08-30 parts/intro.tex
adding time image

@@
   \includegraphics[width=\linewidth]{img/timelapse3}
-  \caption{Amount of generated models over time, since an arb.
-starting point; top Figure shows all models, bottom Figure shows 5 selected candidates with most activity.
-8 users contributed more than five models.
+  \caption{ Amount of generated models over time, since an arb.
+starting point; top figure shows all models, bottom figure shows five selected candidates with the most activity in logarithmic scaling.
+Eight users contributed more than five models per person for 56 lens candidates.
 }
@@
 Around day 200 the volunteers started a modelling challenge for the candidate later to be identified as SW01.
-65 days later 30 models have been created for this particular and this group converged to a set of favorite models that they presented in an online letter.
+This group of volunteers converged to a set of favorite models that they presented in an online letter after about 65 days and 30 models have been created for this particular system.
 

### 2017-08-30 parts/intro.tex
improving text

@@
 The volunteers were encouraged to create models of objects found in Space~Warps before they were classified as plausible candidates.
-Figure~\ref{fig:time} shows the evolution of the total number of models the users generated, but only for the candidates, models created for system that turned out to be non candidates were not counted.
-The first beta version of SpaghettiLens was launched around day 140 and was tested and improved on the fly.
+Figure~\ref{fig:time} shows the evolution of the total number of models the users generated, models created for systems that turned out to be non candidates were not included.
+The first beta version of SpaghettiLens was launched around day 140 and additional features were implemented on the fly.
 It saw 8 volunteers with major contributions.
-At day 820 the first full version of SpaghettiLens was presented online, around the same time the list of identified candidates was available.
-Around day 200 the volunteers started a modelling challenge for the candidate later to be identified as SW01.
+Around day 200 some volunteers started a modelling challenge for the candidate later to be identified as SW~01.
 This group of volunteers converged to a set of favorite models that they presented in an online letter after about 65 days and 30 models have been created for this particular system.
+At day 820 the first full version of SpaghettiLens was presented online for testing, around the same time the list of identified candidates was available.
+At this stage, we can see for example with candidate SW~29, the volunteers converged to a favorable model after 15 models generated in 30 days.
 

### 2017-08-30 parts/intro.tex
more better words

@@
 The first beta version of SpaghettiLens was launched around day 140 and additional features were implemented on the fly.
-It saw 8 volunteers with major contributions.
-Around day 200 some volunteers started a modelling challenge for the candidate later to be identified as SW~01.
-This group of volunteers converged to a set of favorite models that they presented in an online letter after about 65 days and 30 models have been created for this particular system.
+The system was tested by eight major contributors, volunteers that at least generated five models.
+Around day 200 a modelling challenge for the candidate later to be identified as SW~01 was proposed.
+A group of five volunteers converged to a set of favorite models that they presented in an online letter after about 65 days and 30 models have been created for this particular system.
 At day 820 the first full version of SpaghettiLens was presented online for testing, around the same time the list of identified candidates was available.

### 2017-08-30 parts/intro.tex
changes
working on time

@@
 
+TODO: very short summary of the following sections
+
 The online supplement gives results for all the modelled systems generated
 for all the lensing candidates.
+
+\section{The candidates and models}
+
+TODO: About SW sample
+
+TODO: about SpL
 
@@
 
-\section{The candidates and models}
-
 \begin{figure}
   \includegraphics[width=\linewidth]{img/timelapse3}
-  \caption{ Amount of generated models over time, since an arb.
-starting point; top figure shows all models, bottom figure shows five selected candidates with the most activity in logarithmic scaling.
-Eight users contributed more than five models per person for 56 lens candidates.
+  \caption{ Number of models generated over time in days since an arbitrary starting point; black line shows all models, colored lines show five most active candidates.
+Total of 365 models were generated for 56 lens candidates, eight users contributed more than five models per person.
 }
@@
 
-The volunteers were encouraged to create models of objects found in Space~Warps before they were classified as plausible candidates.
-Figure~\ref{fig:time} shows the evolution of the total number of models the users generated, models created for systems that turned out to be non candidates were not included.
-The first beta version of SpaghettiLens was launched around day 140 and additional features were implemented on the fly.
+The volunteers were encouraged to create models of objects found in \SW before they were classified as plausible candidates.
+Figure~\ref{fig:time} shows the total number of models generated over time, models created for systems that turned out to be non candidates were not included.
+The first beta version of \SpL was launched around day 140 and additional features were implemented on the fly.
 The system was tested by eight major contributors, volunteers that at least generated five models.
-Around day 200 a modelling challenge for the candidate later to be identified as SW~01 was proposed.
+Around day 200 (Aug. 2013) a modelling challenge for the candidate later to be identified as \sw{01} was launched.
 A group of five volunteers converged to a set of favorite models that they presented in an online letter after about 65 days and 30 models have been created for this particular system.
-At day 820 the first full version of SpaghettiLens was presented online for testing, around the same time the list of identified candidates was available.
-At this stage, we can see for example with candidate SW~29, the volunteers converged to a favorable model after 15 models generated in 30 days.
+Around day 820 (Apr.
+2015) the first full version of \SpL was presented for testing, around the same time the list of identified candidates was available \citep[as a preprint of the later work][]{2016MNRAS.455.1191M}.
+At this stage, after a call to model candidates that have been neglected up to that date, candidate \sw{29} shows that the volunteers converged to a favorable model after 15 models generated in 30 days.
 
@@
 \end{enumerate}
-\item Third, whether the total implied lensing mass\footnote{
+\item Third, whether the total implied lensing mass
+  determined from the lens model is plausible, given the
+  photometry of the lensing galaxy.
   In this work we define lensing mass as the sum of all mass tiles
-    needed to model a lens. Those tiles reach out to typically twice
-    the radius of the the outermost image. }
-  determined from the lens model is plausible, given the
-  photometry of the lensing galaxy.  Section~\ref{sec:stellar-mass}
+  needed to model a lens. These mass tiles reach out to typically twice
+  the radius of the the outermost image.
+  Section~\ref{sec:stellar-mass}
   explains how we compare the lensing mass with the mass in stars in

### 2017-08-30 paper2.tex
about mass map diagnostic
replace total mass with lensing mass 2
bigger labels for all plots
several edits
working on time
overhaul

@@
 %\usepackage{bmpsize}  % PS still needs this for correct bounding boxes?
+\usepackage{xspace} % handling of spaces after shortcuts
 
@@
 \newcommand*{\NO}{\ding{55}}
-\newcommand*{\UK}{--}
+\newcommand*{\UK}{\ensuremath{\text{--}}}
 
-\newcommand{\lenstitle}[1]{\noindent\textbf{#1} --}
-\newcommand{\params}[3]{(\(\Theta_\text{E}:#1\), $\varepsilon:#2$, $\alpha_\varepsilon:#3$ )}
+%\newcommand{\lenstitle}[1]{\noindent\textbf{#1} --}
+%\newcommand{\params}[3]{(\(\Theta_\text{E}:#1\), $\varepsilon:#2$, $\alpha_\varepsilon:#3$ )}
 
-\newcommand{\SW}{Space~Warps}
-\newcommand{\SpL}{SpaghettiLens}
-\newcommand{\asw}[1]{ASW000#1}
-\newcommand{\sw}[1]{SW~#1}
-\newcommand{\model}[1]{SL model~#1}
+\newcommand{\SW}{Space\,Warps\xspace}
+\newcommand{\SpL}{SpaghettiLens\xspace}
+\newcommand{\asw}[1]{ASW000#1\xspace}
+\newcommand{\sw}[1]{SW\,#1\xspace}
+%\newcommand{\model}[1]{SL model~#1}
 
@@
 \newcommand{\ER}{\ensuremath{r_\text{E}}} % einstein radius
+
+\newcommand{\sqdeg}{\ensuremath{\text{deg}^2}}
 
@@
 from photometry of the lensing galaxy.
-
 The lens-model masses range from $\sim10^{11}M_\odot$ to
@@
 few below or above $\sim10^{11}M_\odot$.  That is, the stellar-mass
-fraction declines sharply as total mass increases.  The highest-mass
-system with a convincing model is J1434+522 (SW05).  The two low-mass
-outliers are J0206-095 (SW19) and J2217+015 (SW42); if these two are
+fraction declines sharply as lensing mass increases.  The highest-mass
+system with a convincing model is J1434+522 (\sw{05}).  The two low-mass
+outliers are J0206-095 (\sw{19}) and J2217+015 (\sw{42}); if these two are
 indeed lenses, they are probing an interesting regime of very low
 star-formation efficiency.
-
 Some improvements to the modelling software used (SpaghettiLens), and

### 2017-08-30 parts/figures.tex
big table update
overhaul

@@
   stellar population and the oldest possible population at the given
-  redshift.  The vertical extent indicates the spread of masses in
+  redshift.  The vertical extent indicates the spread of masses in the
   lens-model ensemble.  The lower-right shaded region is unphysical
@@
   \caption{Diagnostics of a selected model for each Space Warps candidate
-    (see Section~\ref{sec:summary}).}
+    (see Section~\ref{sec:summary}). Machine readable version in online supplement.}
   \label{tab:models}

### 2017-08-30 parts/intro.tex
overhaul

@@
 lens-candidates discovered through Space~Warps.  We present results
-from modelling of 56 of the 59 lens candidates reported by
+from modelling of 58 of the 59 lens candidates reported by
 \cite{2016MNRAS.455.1191M}.  Each lens candidate was modelled in a
@@
 
-TODO: very short summary of the following sections
-
-The online supplement gives results for all the modelled systems generated
-for all the lensing candidates.
-
-\section{The candidates and models}
-
-TODO: About SW sample
-
-TODO: about SpL
+This paper is organized as follows:
+Section~\ref{sec:candidates_models} introduces the candidates, the models and the diagnostics applied to them.
+The following sections elaborate on the diagnostics.
+Image morphology diagnostics are explained in Section~\ref{sec:morph} and
+diagnostics based on the mass models in Section~\ref{sec:massmodels}.
+Stellar masses are calculated in Section~\ref{sec:stellar-mass} to compare stellar to lensing masses of the lensing candidates.
+Section~\ref{sec:summary} gives our summary and conclusions.
 
@@
 
+The online supplement gives results for all the modelled systems generated
+for all the lensing candidates.
+
+\section{The candidates and models}
+\label{sec:candidates_models}
+
+\SW is a citizen science gravitational lens search \citep{2016MNRAS.455.1171M}.
+Its first run searched the CFHT Legacy Survey, a survey carried out in five optical bands ($u^*$,$g'$,$r'$,$i'$,$z'$) covering a total area of 160 \sqdeg, divided up into four fields.
+It has a field of view of 1 \sqdeg, a pixel size of 0.186'' and the deepest limiting magnitude is 25.47 in the $g$ band\citep{2012AJ....143...38G}.
+The cutouts shown to the volunteers were colour composites of the $g$, $r$ and $i$ band of randomly chosen regions.
+It resulted in 59 new (of which 29 promising) lens candidates that have not been found by other searches already and in the rediscovery of 82 previously known lens candidates.
+The candidates have broadly similar redshifts (0.2 -- 1.0), Einstein radii (0.7\arcsec -- 5\arcsec) and arc magnitudes (22 -- 26) as previous robotic robotic searches by ArcFinder and RingFinder \citep{2016MNRAS.455.1191M}.
+
 \begin{figure}
@@
 
-The volunteers were encouraged to create models of objects found in \SW before they were classified as plausible candidates.
+While \SW was running, volunteers started working with \SpL to create models of possible lensing candidates found in \SW that were debated on the \SW discussion forums, before they were classified as plausible candidates.
 Figure~\ref{fig:time} shows the total number of models generated over time, models created for systems that turned out to be non candidates were not included.
-The first beta version of \SpL was launched around day 140 and additional features were implemented on the fly.
+The first beta version of \SpL was launched in May 2013 and additional features were implemented on the fly.
 The system was tested by eight major contributors, volunteers that at least generated five models.
-Around day 200 (Aug. 2013) a modelling challenge for the candidate later to be identified as \sw{01} was launched.
-A group of five volunteers converged to a set of favorite models that they presented in an online letter after about 65 days and 30 models have been created for this particular system.
-Around day 820 (Apr.
-2015) the first full version of \SpL was presented for testing, around the same time the list of identified candidates was available \citep[as a preprint of the later work][]{2016MNRAS.455.1191M}.
-At this stage, after a call to model candidates that have been neglected up to that date, candidate \sw{29} shows that the volunteers converged to a favorable model after 15 models generated in 30 days.
+In the beginning of August 2013 (day 70) a modelling challenge for the candidate later to be identified as \sw{01} was launched.
+A group of five volunteers converged to a set of favourite models that they presented in an online letter after about 65 days and 30 models have been created for this particular system.
+In April 2015 (day 700) the first full version of \SpL was presented for testing.
+In the same time the list of identified candidates was made available \citep[as a preprint of the later work][]{2016MNRAS.455.1191M}.
+At this stage, the volunteers were asked to complete the sample and to create models for all the lens candidates that were still missing.
+The generated models for candidate \sw{29} show that the volunteers converged to a favorable model much faster, after 15 models generated in 30 days.
+This modelling effort resulted in a set of 356 \SpL models for all but one of the \SW 59 lens candidates; candidate \sw{39} was not modelled.
 

### 2017-08-31 parts/intro.tex
added auto-modelling refs

@@
 The expected flood of new lens discoveries will need a similarly huge
-modelling effort to reconstruct their mass distributions.  To prepare
-for the challenge of massive-sample lens modelling,
-\cite{2015MNRAS.447.2170K} developed a new modelling strategy,
-implemented as the SpaghettiLens system.  The idea is to collaborate
-with experienced members of the citizen-science community, who have
-already participated in lens discovery through \SW, as well as several
-other projects involving astronomical data.  The system was tested on
-a sample of simulated lenses, which were part of the training and
-testing set in \SW.
+modelling effort to reconstruct their mass distributions.
+Lens-modelling robots have started to be developed
+\citep{2017arXiv170807377N,2017arXiv170808842H} but so far are able to
+handle only very clean systems.  For typical lenses, human input is
+still needed.  With that in mind \cite{2015MNRAS.447.2170K} developed
+a new modelling strategy, implemented as the SpaghettiLens system.
+The idea is to collaborate with experienced members of the
+citizen-science community, who have already participated in lens
+discovery through \SW, as well as several other projects involving
+astronomical data.  The system was tested on a sample of simulated
+lenses, which were part of the training and testing set in \SW.
 

### 2017-08-31 paper2.tex
cleaning up appendix mention

@@
 Legacy Survey. Lens modelling was done by a small group of
-specially-interested volunteers from the \SW\ citizen-science community
+specially-interested volunteers from the \SW citizen-science community
 who originally found the candidate lenses.  Models are categorised

### 2017-08-31 parts/intro.tex
cleaning up appendix mention

--- 2017-08-30 parts/intro.tex
@@
 Stellar masses are calculated in Section~\ref{sec:stellar-mass} to compare stellar to lensing masses of the lensing candidates.
-Section~\ref{sec:summary} gives our summary and conclusions.
+Section~\ref{sec:summary} summarises and tabulates the diagnostics in
+Table~\ref{tab:models}.
 
 There are three appendices devoted to various technical issues
-relating to modelling.  \cite{2015MNRAS.447.2170K} tested the system
-on simulated lenses and identified some areas for improvement.  In
-\S~\ref{subsec:sourcefit} we introduce fitting of the brightness
-profiles of the source.  This feature has not yet been included in
-SpaghettiLens, but has been carried out in post-processing for a few
-especially interesting candidates.  In \S~\ref{subsec:hires} we show
-that making mass maps fine-grained in the central region relieves a
-tendency in the earlier work for mass profile to be too shallow. Then in
-\S~\ref{subsec:parameter} we consider the possibility of fitting a
-parametric lens model to the model ensemble; so far we have only been
-successful at extracting an Einstein radius.
-
+relating to modelling.
 The online supplement gives results for all the modelled systems generated
@@
 The generated models for candidate \sw{29} show that the volunteers converged to a favorable model much faster, after 15 models generated in 30 days.
-This modelling effort resulted in a set of 356 \SpL models for all but one of the \SW 59 lens candidates; candidate \sw{39} was not modelled.
+This modelling effort resulted in a set of 377 \SpL models for all but one of the \SW 59 lens candidates; candidate \sw{39} was not modelled.
+
+\cite{2015MNRAS.447.2170K} tested the system
+on simulated lenses and identified some areas for improvement.  In
+\S~\ref{subsec:sourcefit} we introduce fitting of the brightness
+profiles of the source.  This feature has not yet been included in
+SpaghettiLens, but has been carried out in post-processing for a few
+especially interesting candidates.  In \S~\ref{subsec:hires} we show
+that making mass maps fine-grained in the central region relieves a
+tendency in the earlier work for mass profile to be too shallow. Then in
+\S~\ref{subsec:parameter} we consider the possibility of fitting a
+parametric lens model to the model ensemble; so far we have only been
+successful at extracting an Einstein radius.
 
@@
 \end{itemize}
-
-Section~\ref{sec:summary} summarises and tabulates the diagnostics in
-Table~\ref{tab:models}.

### 2017-08-31 parts/intro.tex
some changes

@@
 diagnostics based on the mass models in Section~\ref{sec:massmodels}.
-Stellar masses are calculated in Section~\ref{sec:stellar-mass} to compare stellar to lensing masses of the lensing candidates.
+Stellar masses are calculated in Section~\ref{sec:stellar-mass} to compare stellar to lensing masses of the candidates.
 Section~\ref{sec:summary} summarises and tabulates the diagnostics in
@@
 \SW is a citizen science gravitational lens search \citep{2016MNRAS.455.1171M}.
-Its first run searched the CFHT Legacy Survey, a survey carried out in five optical bands ($u^*$,$g'$,$r'$,$i'$,$z'$) covering a total area of 160 \sqdeg, divided up into four fields.
-It has a field of view of 1 \sqdeg, a pixel size of 0.186'' and the deepest limiting magnitude is 25.47 in the $g$ band\citep{2012AJ....143...38G}.
+Its first run searched the CFHT Legacy Survey, a survey carried out in five optical bands ($u^*$,$g'$,$r'$,$i'$,$z'$) covering a total area of 160 \sqdeg divided up into four fields W1 -- W4.
+It has a field of view of 1 \sqdeg, a pixel size of 0.186'' and the deepest limiting magnitude is 25.47 in the $g$ band \citep{2012AJ....143...38G}.
 The cutouts shown to the volunteers were colour composites of the $g$, $r$ and $i$ band of randomly chosen regions.
 It resulted in 59 new (of which 29 promising) lens candidates that have not been found by other searches already and in the rediscovery of 82 previously known lens candidates.
-The candidates have broadly similar redshifts (0.2 -- 1.0), Einstein radii (0.7\arcsec -- 5\arcsec) and arc magnitudes (22 -- 26) as previous robotic robotic searches by ArcFinder and RingFinder \citep{2016MNRAS.455.1191M}.
+The candidates have broadly similar redshifts (0.2 -- 1.0), Einstein radii (0.7\arcsec -- 5\arcsec) and arc magnitudes (22 -- 26) as those found by previous robotic searches like ArcFinder and RingFinder \citep{2016MNRAS.455.1191M}.
 
@@
   \includegraphics[width=\linewidth]{img/timelapse3}
-  \caption{ Number of models generated over time in days since an arbitrary starting point; black line shows all models, colored lines show five most active candidates.
-Total of 365 models were generated for 56 lens candidates, eight users contributed more than five models per person.
+  \caption{ Number of models generated over time in days since the launch of \SpL; the black line shows all models, the coloured lines show the five most active candidates.
+A total of 377 models were generated for 58 lens candidates, eight users contributed more than five models per person.
 }
@@
 
-While \SW was running, volunteers started working with \SpL to create models of possible lensing candidates found in \SW that were debated on the \SW discussion forums, before they were classified as plausible candidates.
-Figure~\ref{fig:time} shows the total number of models generated over time, models created for systems that turned out to be non candidates were not included.
-The first beta version of \SpL was launched in May 2013 and additional features were implemented on the fly.
-The system was tested by eight major contributors, volunteers that at least generated five models.
-In the beginning of August 2013 (day 70) a modelling challenge for the candidate later to be identified as \sw{01} was launched.
-A group of five volunteers converged to a set of favourite models that they presented in an online letter after about 65 days and 30 models have been created for this particular system.
-In April 2015 (day 700) the first full version of \SpL was presented for testing.
-In the same time the list of identified candidates was made available \citep[as a preprint of the later work][]{2016MNRAS.455.1191M}.
-At this stage, the volunteers were asked to complete the sample and to create models for all the lens candidates that were still missing.
-The generated models for candidate \sw{29} show that the volunteers converged to a favorable model much faster, after 15 models generated in 30 days.
-This modelling effort resulted in a set of 377 \SpL models for all but one of the \SW 59 lens candidates; candidate \sw{39} was not modelled.
+A first version of \SpL was launched in May 2013, while the first run of \SW was ongoing.
+Figure~\ref{fig:time} shows the total number of models generated since launch, but only includes models for the lens candidates.
+A small number of volunteers started to work with \SpL to create models of possible lens candidates found in \SW that were debated on in the \SW discussion forums.
+In the beginning of August 2013 (around day 70) a modelling challenge for the candidate later to be identified as \sw{01} was launched.
+A group of five volunteers converged to a set of favourite models that they presented in an online letter after about 65 days passed and 30 models have been created for this particular system.
+In April 2015 (day 700) the first major release of \SpL was presented.
+In the same time the list of identified candidates was made available \citep[as a preprint of][]{2016MNRAS.455.1191M}.
+At this stage, the volunteers were asked to create models for all the lens candidates that were still missing.
+The generated models for candidate \sw{29} show that the volunteers converged to a favourable model much faster, after 15 models generated in 30 days.
 
-\cite{2015MNRAS.447.2170K} tested the system
+This modelling effort resulted in a total set of 377 \SpL models for all but one of the 59 \SW lens candidates; candidate \sw{39} was not modelled by any volunteer.
+Over its runtime the system saw eight major contributors (volunteers that at least generated five models each).
+
+In parallel \cite{2015MNRAS.447.2170K} tested the system
 on simulated lenses and identified some areas for improvement.  In

### 2017-09-05 paper2.tex
feedback from IF

@@
 lensed image appear to be plausible, and (c)~how the lens-model mass
-compares with compares with the abundance-matched halo mass derived
-from photometry of the lensing galaxy.
-The lens-model masses range from $\sim10^{11}M_\odot$ to
-$>10^{13}M_\odot$.  Preliminary estimates of the stellar masses show
-(with two outliers) a smaller spread in stellar mass: a factor of a
-few below or above $\sim10^{11}M_\odot$.  That is, the stellar-mass
-fraction declines sharply as lensing mass increases.  The highest-mass
-system with a convincing model is J1434+522 (\sw{05}).  The two low-mass
-outliers are J0206-095 (\sw{19}) and J2217+015 (\sw{42}); if these two are
-indeed lenses, they are probing an interesting regime of very low
-star-formation efficiency.
-Some improvements to the modelling software used (SpaghettiLens), and
-discussion of strategies for scaling to future surveys with more and
-frequent discoveries, are also included.
+compares with the stellar mass and the abundance-matched halo mass.
+The lensing masses range from $\sim10^{11}M_\odot$ to
+$>10^{13}M_\odot$. Preliminary estimates of the stellar masses show a
+smaller spread in stellar mass (except for two lenses): a factor of a
+few below or above $\sim10^{11}M_\odot$.  Therefore, we expect the
+stellar-to-total mass fraction to decline sharply as lensing mass
+increases.  The most massive system with a convincing model is
+J1434+522 (\sw{05}).  The two low-mass outliers are J0206-095
+(\sw{19}) and J2217+015 (\sw{42}); if these two are indeed lenses,
+they probe an interesting regime of very low star-formation
+efficiency.  Some improvements to the modelling software
+(SpaghettiLens), and discussion of strategies regarding scaling to
+future surveys with more and frequent discoveries, are included.
 \end{abstract}
@@
 gravitational lensing: strong -- galaxies: general
+-- galaxies: stellar content -- dark matter.
 \end{keywords}

### 2017-09-05 parts/intro.tex
feedback from IF

--- 2017-08-31 parts/intro.tex
@@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
 
-By a curious coincidence, the typical escape velocity of massive galaxies is
-such that $v_{\rm esc}^2/c^2$ is comparable to the apparent sizes of a
-galaxies at cosmological distances.  This coincidence is fortunate,
-because it makes the lensing deflection angle (which is $2v_{\rm
-  esc}^2/c^2$) of distant galaxies comparable to their size on the
-sky, and as a result, strong lensing by galaxies tends to produce
-images that probe the dark halos of those galaxies.  This is
-important, because while there is a general consensus that basic
-mechanism of galaxy formation involves gravitational collapse,
-fragmentation, and mergers of dark-matter clumps, into which gas fell,
-cooling through radiative processes to form dense clouds and
-eventually stars, there is much debate about the details \citep[for a
-  summary, see][]{2012RAA....12..917S}.  In particular, the nature of
-dark matter remains mysterious: most researchers take it to be a
-collisionless non-relativistic fluid (cold dark matter or CDM) readily
-studied by simulations \citep[for example, the influential millenium
-  simulation by][]{2005Natur.435..629S}.  But other scenarios, where
-dark matter has exotic dynamical properties
+By a curious coincidence, the typical escape velocity of massive
+galaxies -- of order a few hundred km/s -- is such that $v_{\rm
+  esc}^2/c^2$, expressed as an angular distance, is comparable to the
+apparent sizes of galaxies at cosmological distances.  This
+coincidence is fortunate, because it makes the gravitational lensing
+deflection angle of distant galaxies ($\alpha\sim 2v_{\rm esc}^2/c^2$)
+comparable to their size on the sky. As a result, strong lensing by
+galaxies produces images that probe their host dark matter halos,
+providing a useful tool to understand galaxy formation.  While there
+is a general consensus about the basic mechanisms at play, involving
+gravitational collapse, fragmentation, and mergers of dark-matter
+clumps, into which gas fell, cooling through radiative processes to
+form dense clouds and eventually stars, there is much debate about the
+details \citep[for a summary, see][]{2012RAA....12..917S}.  In
+particular, the nature of dark matter remains mysterious: most
+researchers take it to be a collisionless non-relativistic fluid (cold
+dark matter or CDM) readily studied by simulations \citep[for example,
+  the influential Millennium
+  simulation,][]{2005Natur.435..629S}. However, alternative scenarios,
+where dark matter has exotic dynamical properties
 \citep{2010MNRAS.405...77S,2016ApJ...818...89S}, or is not really
-matter at all but a modification of gravity
+matter at all, but a modification of gravity
 \citep{2016PhRvL.117t1101M}, have also been considered.
 
-All this motivates using galaxy lenses to study the mutual dynamics of
-dark matter, gas and stars in galaxies.  Several studies in recent
-years have done so
-\citep{2009ApJ...703L..51K,2011ApJ...740...97L,2012MNRAS.424..104L,
+All this motivates the use of strong gravitational lensing over galaxy
+scales to study the mutual dynamics of dark matter, gas and stars.
+Several studies in recent years have done so \citep[see,
+  e.g.,][]{2009ApJ...703L..51K,2011ApJ...740...97L,2012MNRAS.424..104L,
   2016MNRAS.459.3677L,2016MNRAS.456..870B} but it is desirable to
 enlarge the samples from tens of lensing galaxies to thousands.  Doing
-so requires both finding more lenses and also modelling their masses.
-Recent searches through the CFHTLS \citep{2012SPIE.8448E..0MC} using
-arc-finders
+so requires both finding more lenses and also modelling their mass
+distribution.  Recent searches through the CFHT Lens Survey
+\citep[CFHTLS,][]{2012MNRAS.427..146H} using arc-finders
 \citep[e.g.,][]{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G,2017arXiv170401585S}
-by machine learning
-\citep[e.g.,][]{2016A&A...592A..75P,2017arXiv170302642L} and by visual
-inspection by citizen-science volunteers in Space~Warps
+by either machine learning methods 
+\citep[e.g.,][]{2016A&A...592A..75P,2017arXiv170302642L} or visual
+inspection by citizen-science volunteers through the \SW project 
 \citep{2016MNRAS.455.1191M} have, between them, discovered an average
@@
 finding many thousands of lenses in the next generation of wide-field
-surveys, from the LSST in optical and the SKA in radio on the ground,
-and Euclid and WFIRST in orbit.
+surveys, from ground-based surveys such as LSST in the optical window
+and SKA in radio, to space-based missions such as Euclid and WFIRST.
 
-The expected flood of new lens discoveries will need a similarly huge
+The expected flood of new lens discoveries will need a equally large
 modelling effort to reconstruct their mass distributions.  To prepare
@@
 with experienced members of the citizen-science community, who have
-already participated in lens discovery through \SW, as well as several
-other projects involving astronomical data.  The system was tested on
-a sample of simulated lenses, which were part of the training and
-testing set in \SW.
+already participated in the discovery of gravitational lenses through
+\SW, as well as in several other projects involving astronomical data.
+The system was tested on a sample of simulated lenses, that were part
+of the training and testing set in \SW.
 
-This paper continues that study by applying SpaghettiLens to
-lens-candidates discovered through Space~Warps.  We present results
-from modelling of 58 of the 59 lens candidates reported by
-\cite{2016MNRAS.455.1191M}.  Each lens candidate was modelled in a
-collaborative refinement process, where anyone interested can create a
-new model or modify an existing model to try and make it
-better.\footnote{This is in contrast to the main Space~Warps project
-  for discovering lenses, where volunteers in a crowd of $\gtrsim10^4$
-  make independent contributions.  Each person is presented with a
-  random selection of survey-patches and invited to (in effect) vote
-  on each.  The system estimates each volunteer's skill level
-  according to test-patches interspersed with the real data, and
-  weights their votes accordingly \citep{2016MNRAS.455.1171M}.  There
-  is an active forum for volunteers, but since everyone is seeing
-  different data samples with minimal overlap, the forum has little if
-  any influence on votes.}  The resulting model represents a consensus
-among contributors, as to the best that could be achieved with the
-available data and software.
+This paper follows up that study by applying SpaghettiLens to
+candidates discovered through \SW.  We present results from
+the modelling of 58 of the 59 lens candidates reported by
+\cite{2016MNRAS.455.1191M}.  Each lens candidate was modelled
+following a collaborative refinement process, where anyone interested
+could improve the analysis by modifying an existing model or creating
+a new one. Note the difference with respect to the main \SW 
+project, where volunteers from a group of $\gtrsim10^4$ people make
+independent contributions.  Each person is presented with a random
+selection of survey-patches and invited to (in effect) vote on each.
+The system estimates the skill level of each volunteer according to
+test-patches interspersed with the real data, and weights their votes
+accordingly \citep{2016MNRAS.455.1171M}.  There is an active forum for
+volunteers, but since everyone is seeing different data samples with
+minimal overlap, the forum has little if any influence on the votes.
+\textcolor{red}{\bf IF: Please make sure the following is correct:}
+In SpaghettiLens, the number of volunteers is significantly lower, but
+the level of interaction is higher.  The resulting model represents a
+consensus among contributors, as to the best that could be achieved
+with the available data and software.
 
-Interpretation of the results is tentative,
-because the systems are lens candidates at this stage, not secure lenses.
-Moreover the candidate-lens redshifts have large uncertainties, while
-the candidate-source redshifts can only be guessed at present.
-Nevertheless it is interesting to see what trends we can observe with
-the already-available data.
+We emphasize that the interpretation of the results presnted here is
+tentative, because the systems are lens candidates at this stage, not
+secure lenses.  Moreover the candidate-lens redshifts have large
+uncertainties, while the candidate-source redshifts can only be
+guessed at present.  Nevertheless it is interesting to explore the
+trends observed with the already available data.
 %TODO there is more info about uncertainies here:
@@
 This paper is organized as follows:
-Section~\ref{sec:candidates_models} introduces the candidates, the models and the diagnostics applied to them.
-The following sections elaborate on the diagnostics.
-Image morphology diagnostics are explained in Section~\ref{sec:morph} and
-diagnostics based on the mass models in Section~\ref{sec:massmodels}.
-Stellar masses are calculated in Section~\ref{sec:stellar-mass} to compare stellar to lensing masses of the candidates.
-Section~\ref{sec:summary} summarises and tabulates the diagnostics in
-Table~\ref{tab:models}.
+Section~\ref{sec:candidates_models} introduces the candidate lenses,
+their models and the diagnostics applied to them.  The following
+sections elaborate on the diagnostics.  Image morphology diagnostics
+are explained in Section~\ref{sec:morph} and diagnostics based on the
+mass models are discussed in Section~\ref{sec:massmodels}.  Stellar masses are
+presented in Section~\ref{sec:stellar-mass}, to compare stellar and
+lensing masses.  Finally, section~\ref{sec:summary}
+summarises and tabulates the diagnostics in Table~\ref{tab:models}.
 
-There are three appendices devoted to various technical issues
-relating to modelling.
-The online supplement gives results for all the modelled systems generated
-for all the lensing candidates.
+We include three appendices devoted to various technical issues
+relating to the modelling.  The online supplement gives the results
+from all the modelled systems generated for all the lensing
+candidates.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{The candidates and models}
@@
 
-\SW is a citizen science gravitational lens search \citep{2016MNRAS.455.1171M}.
-Its first run searched the CFHT Legacy Survey, a survey carried out in five optical bands ($u^*$,$g'$,$r'$,$i'$,$z'$) covering a total area of 160 \sqdeg divided up into four fields W1 -- W4.
-It has a field of view of 1 \sqdeg, a pixel size of 0.186'' and the deepest limiting magnitude is 25.47 in the $g$ band \citep{2012AJ....143...38G}.
-The cutouts shown to the volunteers were colour composites of the $g$, $r$ and $i$ band of randomly chosen regions.
-It resulted in 59 new (of which 29 promising) lens candidates that have not been found by other searches already and in the rediscovery of 82 previously known lens candidates.
-The candidates have broadly similar redshifts (0.2 -- 1.0), Einstein radii (0.7\arcsec -- 5\arcsec) and arc magnitudes (22 -- 26) as those found by previous robotic searches like ArcFinder and RingFinder \citep{2016MNRAS.455.1191M}.
+\SW is a citizen science gravitational lens search
+\citep{2016MNRAS.455.1171M}.  Its first run searched the CFHT Legacy
+Survey, a survey carried out in five optical bands
+($u^*$,$g^\prime$,$r^\prime$,$i^\prime$,$z^\prime$) covering a total
+area of 160\,\sqdeg divided up into four fields W1 -- W4.  The
+MegaPrime camera, used for the survey, has a field of view of
+1\,\sqdeg, with 0.186$^{\prime\prime}$ pixels. The flux limit of the
+survey is $g^\prime<$25.6AB (5\,$\sigma$) with a typical seeing
+FWHM$\sim 0.7^{\prime\prime}$ \citep{2013MNRAS.433.2545E}. The cutouts
+shown to the volunteers were colour composites of the $g^\prime$,
+$r^\prime$ and $i^\prime$ bands from randomly chosen regions.
+The programme \citep{2016MNRAS.455.1191M} resulted in 59 new lens candidates (of which 29 are
+promising  \textcolor{red}{\bf IF: why are
+  they promising? explain this here).}  Moreover, 82 previously known
+lens candidates were ``rediscovered''.  The candidates have broadly
+similar redshifts (0.2$<$z$<$1.0), Einstein radii between 0.7 and
+5\,\arcsec, and arc magnitudes between 22 and 26 \textcolor{red}{\bf
+  IF: in the $g^\prime$ band?}. These properties are similar to those
+found by previous robotic searches like ArcFinder and RingFinder.
 
@@
   \includegraphics[width=\linewidth]{img/timelapse3}
-  \caption{ Number of models generated over time in days since the launch of \SpL; the black line shows all models, the coloured lines show the five most active candidates.
-A total of 377 models were generated for 58 lens candidates, eight users contributed more than five models per person.
-}
+  \caption{ Number of models generated over time in days since the
+    launch of \SpL; the black line shows all models, the coloured
+    lines show the five most active candidates. A total of 377 models
+    were generated for 58 lens candidates, eight users contributed
+    more than five models per person. }
   \label{fig:time}
@@
 
-A first version of \SpL was launched in May 2013, while the first run of \SW was ongoing.
-Figure~\ref{fig:time} shows the total number of models generated since launch, but only includes models for the lens candidates.
-A small number of volunteers started to work with \SpL to create models of possible lens candidates found in \SW that were debated on in the \SW discussion forums.
-In the beginning of August 2013 (around day 70) a modelling challenge for the candidate later to be identified as \sw{01} was launched.
-A group of five volunteers converged to a set of favourite models that they presented in an online letter after about 65 days passed and 30 models have been created for this particular system.
-In April 2015 (day 700) the first major release of \SpL was presented.
-In the same time the list of identified candidates was made available \citep[as a preprint of][]{2016MNRAS.455.1191M}.
-At this stage, the volunteers were asked to create models for all the lens candidates that were still missing.
-The generated models for candidate \sw{29} show that the volunteers converged to a favourable model much faster, after 15 models generated in 30 days.
+A first version of \SpL\footnote{\textcolor{red}{\bf IF include web
+    link: {\tt http://xxx.yyy.ch}}} was launched in May 2013, while
+the first run of \SW was ongoing.  Fig.~\ref{fig:time} shows the
+total number of models generated since launch for our lens candidates.
+A small number of volunteers started creating models of possible lens
+candidates from \SW that were debated in the discussion forum.  In the
+beginning of August 2013 (around day 70 since release) a modelling
+challenge for the candidate later to be identified as \sw{01} was
+launched.  A group of five volunteers presented their results in an
+online letter \textcolor{red}{\bf REFERENCE?} about 65 days later,
+converging on a set of 30 models. In April 2015 (day 700),
+the first major version of \SpL was released. At the same time,
+the list of identified candidates was made available \citep[as a preprint
+  of][]{2016MNRAS.455.1191M}.  At this stage, the volunteers were
+asked to create models for all the lens candidates that were still
+missing.  The work done for candidate \sw{29} show that the
+volunteers converged on a favourable model much faster, after 15
+models, generated in 30 days.  The total modelling effort resulted in
+a set of 377 \SpL models for all but one of the 59 \SW lens
+candidates; candidate \sw{39} was not modelled by any volunteer.  Over
+its runtime, the system logged eight major contributors (defined as
+volunteers that generated, at least, five models).
 
-This modelling effort resulted in a total set of 377 \SpL models for all but one of the 59 \SW lens candidates; candidate \sw{39} was not modelled by any volunteer.
-Over its runtime the system saw eight major contributors (volunteers that at least generated five models each).
-
-In parallel \cite{2015MNRAS.447.2170K} tested the system
-on simulated lenses and identified some areas for improvement.  In
-\S~\ref{subsec:sourcefit} we introduce fitting of the brightness
-profiles of the source.  This feature has not yet been included in
-SpaghettiLens, but has been carried out in post-processing for a few
-especially interesting candidates.  In \S~\ref{subsec:hires} we show
-that making mass maps fine-grained in the central region relieves a
-tendency in the earlier work for mass profile to be too shallow. Then in
-\S~\ref{subsec:parameter} we consider the possibility of fitting a
-parametric lens model to the model ensemble; so far we have only been
-successful at extracting an Einstein radius.
+In parallel, \citet{2015MNRAS.447.2170K} tested the system on
+simulated lenses and identified some areas for improvement.  In
+\S~\ref{subsec:sourcefit} we introduce fitting of the surface
+brightness profile of the source.  This feature has not been included
+yet in SpaghettiLens, but we carried the analysis during
+post-processing for a few interesting cases.  In \S~\ref{subsec:hires}
+we show that fine-grained mass maps within the central region
+relieves a tendency in the earlier work for mass profiles to be too
+shallow. In \S~\ref{subsec:parameter} we consider the possibility
+of fitting a parametric lens model to the ensemble.
+%; so far we have only been successful at extracting an Einstein radius.
 
 We characterise each model with seven diagnostics, grouped into three
-categories, whose purpose is to help identify which systems are most probably 
-lenses, and which ones are likely to be most rewarding for future follow-up 
-observations. The diagnostics are as follows.
+categories, whose purpose is to help identify the most likely cases of
+a gravitational lens, as well as flag the most interesting candidates
+for future follow-up observations. The diagnostics are as follows.
 
 \begin{itemize}
-\item First we have diagnostics based on morphology of the
-  system.
-  Section~\ref{sec:morph} and Figure~\ref{fig:splinput} explain.
+\item Firstly we have diagnostics based on morphology.
+  Section~\ref{sec:morph} and Fig.~\ref{fig:splinput} explain
+  this diagnostic in more detail. We consider:
 \begin{enumerate}
-\item Whether the images are unblended.  Distinct unblended images are
-  an advantage in modelling, but not essential.
+\item Whether the images are unblended:  Distinct, unblended images are
+  an advantage in modelling, although not essential.
 \item Whether all images are discernible.  The topography of an
@@
   insert conjectural image positions.
-\item Whether the lens is fairly isolated.
+\item Whether the lens is isolated.
 \item The image morphology concisely described: double or quads,
@@
 \end{enumerate}
-\item Second we have mass models, covered in Section~\ref{sec:massmodels}.
+\item Secondly we have mass models, covered in Section~\ref{sec:massmodels}.
+  We assess the following points:
 \begin{enumerate}
 \setcounter{enumi}{4}
-\item Whether the mass map is reasonable. Figure~\ref{fig:kappa}.
+\item Whether the mass map is reasonable (see Fig.~\ref{fig:kappa}).
 \item Whether the arrival-time surface and synthetic image are
-  plausible.  In particular, additional images are implied in regions
-  where they are not observed signal an unsatisfactory model.
-  Figures~\ref{fig:arriv} and \ref{fig:synth} and \ref{fig:encl}.
+  plausible. In particular, an unsatisfactory model is flagged when 
+  additional images are implied in regions
+  where they are not observed (see Figs.~\ref{fig:arriv}, \ref{fig:synth} \ref{fig:encl}).
 \end{enumerate}
-\item Third, whether the total implied lensing mass
-  determined from the lens model is plausible, given the
-  photometry of the lensing galaxy.
-  In this work we define lensing mass as the sum of all mass tiles
-  needed to model a lens. These mass tiles reach out to typically twice
-  the radius of the the outermost image.
-  Section~\ref{sec:stellar-mass}
-  explains how we compare the lensing mass with the mass in stars in
-  the lensing galaxy.  We estimate the stellar mass by comparing
-  galaxy magnitudes from the CFHTLS pipeline with the well-known
-  stellar-population models of \cite{2003MNRAS.344.1000B}.  We then
-  extrapolate the stellar mass to a halo mass using the
-  abundance-matching prescription of \cite{2010ApJ...710..903M}.
-  Naturally, the lensing mass must be more than the stellar mass but
-  no more than the total halo mass.
+\item Thirdly, whether the total implied lensing mass determined from
+  the lens model is plausible, given the photometry of the lensing
+  galaxy.  In this work we define the lensing mass as the sum of all
+  mass tiles in the model.  These mass tiles reach out to typically
+  twice the radius of the outermost image.
+  Section~\ref{sec:stellar-mass} explains how we compare the lensing
+  (i.e. total) mass with the stellar mass. Naturally, the lensing
+  mass should be somewhere between the stellar mass (lower bound)
+  and the total halo mass (upper bound).
 \begin{enumerate}
 \setcounter{enumi}{6}
-\item We then introduce what we call a halo index ($\haloindex$) which
-  gives an idea of how the lensing mass compares with these two
-  constraints.  Figure~\ref{fig:stelmass}.
+\item We then introduce a so-called halo index ($\haloindex$), that
+  quantifies how the lensing mass compares with these two
+  constraints (see Fig.~\ref{fig:stelmass}).
 \end{enumerate}

### 2017-09-05 parts/massmodel.tex
z errors
feedback from IF

--- 2017-07-18 parts/massmodel.tex
@@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Mass models}\label{sec:massmodels}
@@
 forwarded to a server-side numerical framework, which searches for
-mass maps consistent with the given image locations, parities and time
-ordering.  The mass maps are made up of mass tiles and are free-form,
-but are required to be concentrated around the identified lens centre
-\citep[see][for the precise formulation of the search
-  problem.]{2014MNRAS.445.2181C} Assuming such mass distributions can
-be found (which in practice is usually the case) a statistical
-ensemble of two-dimensional mass maps is returned.  This ensemble,
-along with derived quantities and uncertainties, makes up one
-SpaghettiLens model.
+mass maps consistent with the image locations, parities and time
+ordering, given by the modeller.  The mass maps are made up of mass
+tiles and are free-form, but are required to be concentrated around
+the identified lens centre \citep[see][for the precise formulation of
+  the search problem]{2014MNRAS.445.2181C}. Assuming such mass
+distributions can be found -- which in practice is usually the case --
+a statistical ensemble of two-dimensional mass maps is returned.  This
+ensemble, along with derived quantities and uncertainties, makes up
+one SpaghettiLens model.
 
 The mass will naturally depend on the lens and source redshifts, which
-are unknown when a lens candidate is first identified.  But this is
-not a problem, because a model can be trivially rescaled to use better
-redshift values, as and when they become available.  This work applies
-photometric redshifts from the CFHTLS pipeline to the candidate
-lensing galaxies; the values range from $z=0.2$ to $z=1$ (see
-Table~\ref{tab:models}).  As the mass normalisation depends only weakly
-on source redshift, provided it is larger than the lens redshift,
-we assumed all sources to lie at $z=2$ unless an unambiguous photometric
-redshift is available.
+are unknown when a lens candidate is first identified.  However, this
+is not a problem, because a model can be trivially rescaled to use
+better redshift values, as they become available.  This work applies
+photometric redshifts from the CFHTLS pipeline
+\citep{2009A&A...500..981C} to the candidate lensing galaxies; the
+values range from z=0.2 to 1 (see Table~\ref{tab:models}).
+These redshifts entail rather big uncertainties, up to a few ten
+percent.  Since, however, the angular critical density is proportional
+to $d_l d_s d_{ls}^{-1}$ \citep[consult Equation~A1
+  in][]{2015MNRAS.447.2170K} it is negligible for this tentative
+analysis. \textcolor{red}{\bf IF: I would not say this is
+  ``negligible'' but, rather, that the error in the redshift would lead to
+  surface mass density uncertainties of XX\%, which, for the
+  aim of the tentative analysis presented here, is an acceptable
+  result. You should also check and quantify properly the
+  uncertainty in the photo-z. What is the value claimed by the
+  CFHTLS group? I would say 5-10\% is a decent level, but you
+are mentioning 10s of \% which is rather extreme!}.
+As the mass normalisation depends only weakly on the source redshift,
+provided it is higher than the lens redshift, we adopted a redshift
+z=2 for all sources, unless an unambiguous photometric redshift is
+available. \textcolor{red}{\bf IF: Again, a simple quantification of the
+change you expect, for instance, if the source is at z=3 would be good.}
 
@@
 
-Figure~\ref{fig:arriv} shows arrival-time surfaces corresponding to
-the spaghetti diagrams in Figure~\ref{fig:splinput}.  The arrival-time
+Fig.~\ref{fig:arriv} shows the arrival-time surfaces corresponding to
+the spaghetti diagrams of Fig.~\ref{fig:splinput}.  The arrival-time
 contours look like machine-made elaborations of the input spaghetti
@@
 unexpected features are far from identified lens images, that signals
-a doubtful model.  Figure~\ref{fig:synth} shows what we call synthetic
+an improbable model.  Fig.~\ref{fig:synth} shows what we call synthetic
 images, meaning reconstructions of the extended lensed features by
 fitting for a source.  These were generated by a new method, explained
-in Appendix~\ref{subsec:sourcefit}, implemented in offline
+in Appendix~\ref{subsec:sourcefit}, implemented during the offline
 post-processing after the modelling process was complete.  The
 synthetic images provided by SpaghettiLens during the collaborative
-modelling and discussion were more crude; these are included in the
+modelling and discussion were more crude; those are included in the
 online supplement.
@@
 image is consistent with the data would need to allow for PSF
-dependence and unmodelled substructure ---otherwise all models would
-be summarily rejected--- and it is not clear how to do this.
+dependence and unmodelled substructure -- otherwise all models would
+be summarily rejected, something left for a future implementation
+in SpaghettiLens.
 
-Figure~\ref{fig:kappa} shows projected mass maps of the example
-systems.  Actually, this figure only shows the ensemble-average mass
-maps, and not the variation within the ensemble, from which
-uncertainties can be inferred.  (The same applies to the arrival-time
-surfaces and synthetic images in the two previous figures.
-Uncertainties will be shown in a concise form later, with
-Figure~\ref{fig:encl}.)  Figure~\ref{fig:kappa} makes evident the
-tiled nature of the mass model.  The tiles can be smoothed over by
-interpolating, and this was actually done in the mass maps shown
-online during the modelling process.  It is interesting, however, to
-see the tiling artifacts, if only as a reminder that the substructure
-in the mass distribution are very uncertain, even if some integrated
-quantities are very well constrained.  How the free-form mass maps
-relate to parameterised lens models is discussed in
-Appendix~\ref{subsec:parameter}.  Note that the arrival-time surface
-does not have discontinuous jumps, because the modelling numerics uses
-an analytical integral over square tiles; likewise the lens equation.
+Fig.~\ref{fig:kappa} shows the projected mass maps of the sample.  In
+fact, this figure only shows the ensemble-average mass maps, and not
+the variation within the ensemble, from which uncertainties can be
+inferred. The same applies to the arrival-time surfaces and synthetic
+images in the previous two figures. The uncertainties will be shown in
+a concise form in Fig.~\ref{fig:encl}.  Fig.~\ref{fig:kappa} makes
+evident the tiled nature of the mass model.  The tiles can be smoothed
+over by interpolation, and this was done in the mass maps during the
+modelling process, available in the online version.  It is
+interesting, however, to note the tiling artifacts, if only as a
+reminder that the substructure in the mass distribution is very
+uncertain, even if some integrated quantities are  well
+constrained.  How the free-form mass maps relate to parameterised lens
+models is discussed in Appendix~\ref{subsec:parameter}.
+\textcolor{red}{{\bf IF: This sentence is confusing and needs some
+    clarification:} Note that the arrival-time surface does not have
+  discontinuous jumps, because the modelling numerics uses an
+  analytical integral over square tiles; likewise the lens equation.}
 
-Figure~\ref{fig:encl} shows the enclosed-mass profiles,
-expressed as the average convergence $\kappa$ within circles of given
-projected radius.  This time, uncertainties are included.
-Appendix~\ref{subsec:hires} describes improvements made since our
-earlier work \citep{2015MNRAS.447.2170K}, to allow for steeper
-profiles in the inner regions.  The enclosed mass is typically best
-constrained at the notional Einstein radius, becoming more uncertain
-at larger and smaller radii.
+Fig.~\ref{fig:encl} shows the enclosed-mass profiles, expressed as the
+average convergence, $\kappa$, within circles of given projected
+radius.  The uncertainties \textcolor{red}{\bf IF: at the BLAH level}
+are included.  Appendix~\ref{subsec:hires} describes the improvements made
+since our earlier work \citep{2015MNRAS.447.2170K}, to allow for
+steeper profiles in the inner regions.  The enclosed mass is typically
+best constrained at the notional Einstein radius, becoming more
+uncertain at larger and smaller radii.
 
 The mass maps and mass profiles are the basis of a further diagnostic:
-are the mass distributions plausible?
+are the mass distributions plausible? This is also a judgment call
+made by modellers, but it showed to be a powerful diagnostic,
+summarizing three aspects. The overall shape is forced to be
+$180^\circ$-rotation symmetric, usually a plausible assumption, but
+volunteers can deactivate this constraint. The profile slope turned
+out to be a good indicator of plausible models, as can seen by
+contrasting model \sw{57} with the rest of the sample:  The missing
+core in Fig.~\ref{fig:kappa} and the flat profile in
+Fig.~\ref{fig:encl} disqualify this model. The clumpiness of the
+mass map is another useful indicator. Flat profile slopes can often be
+identified directly in the mass map, where the mass tiles form a
+checkerboard pattern.

### 2017-09-05 parts/stelmass.tex
feedback from IF

@@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Stellar and halo mass estimates}
@@
 The stellar masses of the lens galaxies are derived by comparison of
-the photometric data with M/L estimates from population synthesis
-models.  In principle, a detailed analysis of the spectral energy
-distribution is needed to derive accurate stellar masses
+the photometric data with stellar M/L estimates from population
+synthesis models.  In principle, a detailed analysis of the spectral
+energy distribution is needed to derive accurate stellar masses
 \citep[e.g.][]{2009ApJS..185..253G,2011MNRAS.418.1587T}.  However,
-estimates to within 0.3\,dex in $\log(\Mstel/\Msun)$ can be derived
+estimates to within $\sim$0.3\,dex in $\log(\Mstel/\Msun)$ can be derived
 with a single colour, preferably tracing a rest-frame colour similar
-to $U-V$ \citep[see Fig.~1 of][]{2008MNRAS.383..857F}.  There is some
-evidence from spectral lines that massive galaxies tend to have a more
-bottom-heavy IMF than the Milky Way, but a much higher stellar
-mass-to-light would over-predict the mass in some lensing systems
-\citep{2015MNRAS.454L..71S}.
+to $U-V$ \citep[see Fig.~1 of][]{2008MNRAS.383..857F}, assuming
+a universal initial mass function (IMF). There is
+evidence from detailed absorption line strength analysis that massive
+galaxies can feature a non-standard IMF 
+\citep[e.g.][]{2013MNRAS.429L..15F}. However, these variations --
+towards a bottom-heavy distribution -- are typically found in the
+cores of massive early-type galaxies \citep{2016MNRAS.457.1468L}. The
+effect of these variations on the stellar M/L of lensing systems is
+still rather controversial
+\citep{2015MNRAS.449.3441S,2016MNRAS.459.3677L}.
 
@@
 the redshift of the lens.  For typical stellar-population parameters,
-the variation of this relation is at most 1\,dex.  A further possible
-systematic error is contamination of the light of the lensing galaxy
-by the lensed background galaxy.  Reducing or eliminating the latter
-would require detailed fitting of light distributions for each
-candidate \citep[see][]{2011ApJ...740...97L}, which we have not yet
-attempted.  Nonetheless, because the lensing masses range over two
-order of magnitude, it is still interesting to compare with very rough
-stellar masses.
+the variation of this relation is at most $\Delta\log$M$_s\sim$1\,dex.
+A further potential systematic can arise from contamination of the
+light of the lensing galaxy by the lensed background source.  Reducing
+or eliminating the latter would require detailed fitting of light
+distributions for each candidate \citep[see][]{2011ApJ...740...97L},
+which we have not yet attempted.  Nonetheless, because the lensing
+masses range over two orders of magnitude, it is still interesting to
+compare them with rough estimates of stellar mass.
 
 We make use of the \citet{2003MNRAS.344.1000B} models to derive two
-functional forms of the stellar mass with respect to SDSS-$i$ band
+functional forms of the stellar mass with respect to the $i^{\prime}$-band
 magnitudes. The models have solar metallicity, with a Chabrier IMF,
@@
 
-Figure~\ref{fig:stelmass} shows a comparison of stellar and lensing
-masses.  The comparatively large span in the stellar mass shows the range 
-between the masses derived using the two age trends respectively
-and lies between 0.4 and 0.8~dex.
-It will be improved in future work by using available optical and NIR 
-magnitudes to derive more accurate constraints on the stellar populations.
-In addition, we also derive halo masses for the lenses using an
-abundance-matching formula.  This technique matches the distribution
-function of observed stellar mass in galaxies with that of dark-halo
-masses in $N$-body simulations to derive a simple relation between
-stellar mass and halo mass.  We emphasize that a halo mass from
-abundance matching should be considered an ``average'' estimate, and a
-significant scatter can be expected as galaxies with the same stellar
-mass can be found in different environments. We refer the reader to
-\cite{2012MNRAS.424..104L} for an assessment of the effect of
-abundance matching on the derivation of dark matter halo properties in
-lensing galaxies. We follow the prescription of
+Fig.~\ref{fig:stelmass} shows a comparison of stellar and lensing mass
+in our sample.  The comparatively large span of the error bars in
+stellar mass (horizontal axis) shows the range between the masses
+derived using the two age trends respectively, and lies between 0.4 and
+0.8\,dex.  It will be improved in future work by the use of available
+optical and NIR magnitudes to derive more accurate constraints on the
+stellar populations.  In addition, we also derive halo masses for the
+lenses using an abundance-matching formula.  This technique matches
+the distribution function of observed stellar mass in galaxies with
+that of dark-halo masses from $N$-body simulations, to define  a simple
+relation between stellar mass and halo mass.  We emphasize that a halo
+mass from abundance matching should be considered an ``average''
+estimate, and a significant scatter can be expected as galaxies with
+the same stellar mass can be found in different environments. We refer
+the reader to \cite{2012MNRAS.424..104L} for an assessment of the
+effect of abundance matching on the derivation of dark matter halo
+properties in lensing galaxies. We follow the prescription of
 \citet{2010ApJ...710..903M}, namely:
 \begin{equation}
+  \left.
   \begin{aligned}
@@
 \end{aligned}
+  \right\}
 \end{equation}
-Figure~\ref{fig:stelmass} may be compared with Figure~4 in
+Fig.~\ref{fig:stelmass} may be compared with fig.~4 in
 \cite{2011ApJ...734...69M}.
-
-The comparison of lensing and stellar masses provides us with the last
-of our model diagnostics.  This is a halo-matching index:
+The comparison of lensing and stellar mass produces the last 
+of our model diagnostics, defined as a halo-matching index:
 \begin{equation}
-\haloindex = \frac{\ln(M/\Mstel)}{\ln(\Mhalo/\Mstel)}
+\haloindex \equiv \frac{\ln(M/\Mstel)}{\ln(\Mhalo/\Mstel)}
 \end{equation}
@@
 \item $\haloindex < 0$ is unphysical because $M<\Mstel$.
-\item $\haloindex = 0$ is when the stellar mass exactly accounts for the
-  lensing mass.
+\item $\haloindex = 0$ means the stellar mass exactly accounts for the
+  lensing mass (i.e. no dark matter affects the lensing model).
 \item $0 < \haloindex < 1$ is the typical situation, where the lens
@@
 The halo-matching index expresses whether the lensing mass is
-plausible given the light from the candidate lensing galaxy.
+plausible given the flux received from the candidate lensing galaxy.
 
-Figure~\ref{fig:stelmass} and Table~\ref{tab:models} show most of the
-candidates having stellar
-and lensing mass typical of massive ellipticals\footnote{
+Fig.~\ref{fig:stelmass} and Table~\ref{tab:models} show that most of the
+candidates have stellar
+and lensing masses typical of massive ellipticals\footnote{
   Exact values can be found in the online version of Table~\ref{tab:models}}.
-SW05 is one of the
-most massive of all the candidates, with a mass of galaxy-group scale.
-It is a particularly attractive system for follow-up observations at
-higher resolution, as it is a large system with clear multiple-image
-features, and modelling leaves little doubt that it is a lens.  SW04
-seems to be even more massive, but the diagnostics leave some doubts
-about this model.  The two lowest-mass systems, SW19 and SW42, are
-important if they are indeed lenses, as they would be low-mass lenses
-dominated by dark matter.  All the modelled systems have reasonable
-stellar-mass fractions, except for two cases where the stellar-mass
-fraction is too low ($\haloindex > 1$): these are SW42 and
-SW57.  In the case of SW57, the model has poor diagnostics and should
-be discounted.  The model for SW42, on the other hand, is quite
-convincing --- except for the high halo-matching index.  If SW42 turns
-out not to be a lens, that would support the halo-matching index as an
-effective criterion for filtering models.
+SW05 is one of the most massive of all the candidates, corresponding
+to a galaxy-group mass scale.  It is a particularly attractive system
+for follow-up observations at higher resolution, as it is a large
+system with clear multiple-image features. Modelling leaves little
+doubt that it is a lens.  SW04 seems to be even more massive, but the
+diagnostics leave some doubts about the validity of this model.  The
+two lowest-mass systems, SW19 and SW42, are important if they are
+indeed lenses, as they would be low-mass lenses dominated by dark
+matter.  All the modelled systems have reasonable stellar-mass
+fractions, except for two cases where the stellar-mass fraction is too
+low ($\haloindex > 1$): these are SW42 and SW57.  In the case of SW57,
+the model has poor diagnostics and should be discarded.  The model
+for SW42, on the other hand, is quite convincing -- except for the
+high halo-matching index.  If SW42 turned out not to be a lens, that
+would support the halo-matching index as an effective criterion to
+discriminate models.

### 2017-09-05 parts/app.tex
cleanup

--- 2017-08-23 parts/app.tex
@@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Developments in SpaghettiLens}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Improved synthetic images}\label{subsec:sourcefit}
 
-The mass maps produced by the current implementation of SpaghettiLens are
-based on images of point-like features.  No information about extended
-images is used, except in so far as they help the user identify images
-of point-like features.  The synthetic images offered to users are
-rudimentary, corresponding to conical light profiles (that is,
-circular light profiles with brightness decreasing linearly with radius).
+The mass maps produced by the current implementation of SpaghettiLens
+are based on images of point-like features.  No information about
+extended images is used, except in so far as they help the user
+identify images of point-like features.  The synthetic images offered
+to users are rudimentary, corresponding to conical light profiles
+(i.e.  circular light profiles with brightness decreasing linearly
+with radius).
 
-We have now developed a prototype to improve the generation of synthetic
-images.  Figure~\figref{synthimg} illustrates.  First, areas
+We have now developed a prototype to improve the generation of
+synthetic images, as illustrated in Fig.~\figref{synthimg}. Areas
 containing lensed images are selected (green frames in the figure).
-The selected areas should be as free as possible from of light from
-the lensing galaxy or from extraneous objects.  Pixels within the
+The selected areas should be as free as possible from other
+sources, including the lensing galaxy. Pixels within the
 selected areas are mapped to a grid on the source plane, using bending
@@
 and magnification.  The brightness of each source-plane pixel is set
-to the mean of all the lens-plane pixels mapping to it.  Finally, the
+to the mean of all the lens-plane pixels mapped to it.  Finally, the
 mapping is run back to the lens plane.  The result is a synthetic
@@
 The procedure is not yet implemented in SpaghettiLens but can be
-applied in post-processing.  The new synthetic images could be used to
-improve the mass reconstruction, by weighting the ensemble of maps
-according to how good the synthetic images are, but we have not
-attempted to do so as yet.
+applied during post-processing.  The new synthetic images could be used to
+improve the mass reconstruction, by weighing the ensemble of maps
+according to how good the synthetic images are.
 
@@
 
-\subsection{Sub-sampling of central region}\label{subsec:hires}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Sub-sampling of the central region}\label{subsec:hires}
 
-The models of simulated lenses in \cite{2015MNRAS.447.2170K} showed a tendency 
-to produce density profiles which were too shallow, resulting typically
-in overestimates of the Einstein radius.
-Allowing smaller mass tiles in the
-central region, thus allowing the mass profile to rise more steeply
-near the centre, was suggested as a possible cure.
+The models of simulated lenses in \cite{2015MNRAS.447.2170K} showed a
+tendency to produce density profiles which were too shallow, resulting
+typically in overestimates of the Einstein radius. Volunteers could
+already set the size of the pixels by defining the radius of the lens
+in pixels, with typical values between 8 and 12 pixels. Additionally,
+it was possible to select smaller mass tiles in the central region,
+thus allowing the mass profile to rise more steeply near the centre.
+These options were was suggested as a possible cure.
+\textcolor{red}{\bf IF: I don't even know what you mean by the last
+  sentence: were those measures already implemented in the work
+  described in that paper, or were these things considered a solution
+  to the shallow profiles? Please clarify.}
 
-Figure~\figref{subsampling} shows an experiment with smaller mass
+Fig.~\figref{subsampling} shows an experiment with smaller mass
 tiles in the inner region.  Replacing the very central mass tile with
 9 smaller tiles allows for steeper central profiles.  Doing the same
-for the 25 innermost mass tiles allows for still steeper central
-profiles, eliminating the systematic shallowness.  This is, however,
-still not a completely satisfactory solution, because (a)~it increases
+for the 25 innermost mass tiles allows for even steeper central
+profiles, eliminating the systematic shallow profiles.  However, 
+it does not provide a completely satisfactory solution, because (a)~it increases
 the number of mass tiles by 40\% and significantly increases the
-computational time, and (b)~the square boundary between area with
+computational time, and (b)~the square boundary between areas with
 different tile sizes is rather undesirable.
@@
 presented in this paper apply the intermediate option (corresponding
-to the middle panel in Figure~\figref{subsampling}) while others use
-the old system.  The results in this paper, however, mainly concern
-the enclosed mass in the outer regions, so shallowness in the central
-region should be inconsequential.
+to the middle panel in Fig.~\figref{subsampling}) while others use
+the old system.  We note this paper mainly concerns the enclosed mass
+in the outer regions, so shallowness in the central region should not be
+an issue.
 
@@
 \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_33_hires_comparison}
-  \caption{Model improvement resulting from using smaller mass tiles
+  \caption{Model improvement resulting from the use of smaller mass tiles
     in the inner region of the mass model.  Shown here are the average
@@
     answer.  The orange band represents the statistical ensemble from
-    SpaghettiLens, the orange line being the ensemble mean.  Locations of
+    SpaghettiLens, the orange line shows the ensemble mean.  Locations of
     images (maximum, saddle point, minimum) are marked with vertical
-    arrows.  Crossing the horizontal $\kappa=1$ line is the effective
-    Einstein radius \ER. The upper panel is from
-    K\"ung et al., (2015) (see Figure~3 of that paper).  The middle
+    arrows.  The radial value at $\kappa=1$ is the effective
+    Einstein radius, \ER. The upper panel is taken from
+    \citet{2015MNRAS.447.2170K}, see fig.~3 of that paper.  The middle
     panel is the result when the innermost mass tile is replaced by 9
-    smaller tiles.  The lower panel results from replacing each of the
-    innermost 5 by 5 tiles each with 9 smaller tiles.}
+    smaller tiles.  The lower panel results from replacing the
+    innermost 5$\times$5 tiles with 9 smaller tiles each.}
   \label{fig:subsampling}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Parametrization of pixel models} \label{subsec:parameter}
 
-In order to fit the set of pixelated models to a single parametrized model, a 
-program was written that took a parametrized function and subtracted from it 
-the mean and the principal components of the data, which were calculated using 
-classical Principal Component Analysis.
-This created the residuals function.
-The number of components used in the analysis was varied, to test how this 
-affected the output, and it was found that using 5 principal components tended 
-to give a reasonable approximation.
-A masking function was added which selected only the data points that fell 
-inside the image of the lens, and the principal components were clipped in 
-order to keep the values inside the region of the ensemble of models.
-Any value higher than the clip was set to be the clip value.
-This was chosen to be 2.5 because, assuming that the data follows a Gaussian error 
-distribution, almost all the values for the variance should lie between 2 and 3 
-standard deviations from the mean.
-Minimising the residuals function produces the set of parameters that fit the 
-parametrized function to the original pixelated ensemble most closely.
-A least squares fit was used to perform this minimisation.
-The parametrized model function was obtained from the gravitational potential 
-of an isothermal ellipsoid mass distribution \citep{2001astro.ph..2341K}.
-This model is frequently used to describe gravitational lenses as it tends to 
-fit well with observations.
-The isothermal ellipsoid model outputs three useful parameters: the radius of 
-the Einstein ring, the ellipticity of the model and the angle of the 
-ellipticity from the vertical, giving the orientation of the galaxy.
-By applying this model to simulated lenses for which the values of these 
-parameters were already known, it was possible to gain an estimate of the 
-projected accuracy of the results, before applying the model to the candidate 
-lensing galaxies.
-
-Preliminary results on recovery of Einstein radii are shown in
-Figure~\ref{fig:parameter}.
+In order to fit the set of pixelated models to a single parametrized
+model, a programme was written that took a parametrized function and
+subtracted from it the mean and the principal components (PCs) of the
+data. This created the residual function.  The number of principal
+components in the analysis was varied, to test how this affected the
+output. It was found that 5 PCs gave a reasonable approximation. A
+masking function was added, selecting only the data points that fell
+inside the image of the lens, and the PCs were clipped in order to
+keep the values inside the region of the ensemble. Any value higher
+than the clip was set to be the clip value. This was chosen to 2.5
+because, assuming that the data follows a Gaussian error distribution,
+almost all the values for the variance should lie between 2 and 3
+standard deviations from the mean. Minimising the residuals function
+produces the set of parameters that fit the parametrized function to
+the original pixelated ensemble most closely.  A least squares fit was
+used to perform this minimisation.  The parametrized model function
+was obtained from the gravitational potential of an isothermal
+ellipsoid mass distribution \citep{2001astro.ph..2341K}.  This model
+is frequently used to describe gravitational lenses, giving good fits
+to the observations.  The isothermal ellipsoid model outputs three
+useful parameters: the radius of the Einstein ring, the ellipticity of
+the model and the angle of the ellipticity from the vertical, giving
+the orientation of the galaxy.  By applying this model to simulated
+lenses for which the values of these parameters were already known, it
+was possible to assess the accuracy of the methodology, before
+applying the model to the candidate lensing galaxies.  Preliminary
+results on the recovery of Einstein radii are shown in
+Fig.~\ref{fig:parameter}.
 
@@
   \includegraphics[width=\linewidth]{img/rE_comp/rE_comp.png}
-  \caption{
-    Comparison of Einstein radii \ER\ obtained from mass tiles directly to 
-    those obtained from a parameterized model to test the performance of the 
-    parametrization algorithm.  The parameterized model was generated using 
-    principal component analysis on the ensemble of models.  The blue dashed
-    line represents a perfect recovery of \ER.
-    }
+  \caption{ Comparison of Einstein radii \ER\ obtained from mass tiles
+    to the results from a parameterized model to test the performance
+    of the algorithm.  The parameterized model was generated using
+    principal component analysis on the ensemble of models.  The blue
+    dashed line represents a perfect recovery of \ER.  }
   \label{fig:parameter}

### 2017-09-05 parts/intro.tex

@@
 
-The expected flood of new lens discoveries will need a equally large
-modelling effort to reconstruct their mass distributions.  To prepare
-for the challenge of massive-sample lens modelling,
-\cite{2015MNRAS.447.2170K} developed a new modelling strategy,
-implemented as the SpaghettiLens system.  The idea is to collaborate
-with experienced members of the citizen-science community, who have
-already participated in the discovery of gravitational lenses through
-\SW, as well as in several other projects involving astronomical data.
-The system was tested on a sample of simulated lenses, that were part
-of the training and testing set in \SW.
+The expected flood of new lens discoveries will need a similarly large
+modelling effort to reconstruct their mass distributions.
+Lens-modelling robots have started to be developed
+\citep{2017arXiv170807377N,2017arXiv170808842H} but so far are able to
+handle only very clean systems.  For typical lenses, human input is
+still needed.  With that in mind \cite{2015MNRAS.447.2170K} developed
+a new modelling strategy, implemented as the SpaghettiLens system.
+The idea is to collaborate with experienced members of the
+citizen-science community, who have already participated in lens
+discovery through \SW, as well as several other projects involving
+astronomical data.  The system was tested on a sample of simulated
+lenses, which were part of the training and testing set in \SW.
 

### 2017-09-05 parts/morph.tex
bugfix
about mass map diagnostic

--- 2017-06-15 parts/morph.tex
@@
-\section{Image morphology}\label{sec:morph}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Image morphology}
+\label{sec:morph}
 
-A modeller's main input to the lens-modelling process is a markup of
-the candidate lens system, which we call a spaghetti diagram.
-This is a sketch of the arrival-time surface from a point-like source,
-with proposed locations of maxima, minima and saddle points, and an
-implied time-ordering of the images.  Such information encodes a
-starting proposal for the mass distribution.  A spaghetti diagram is
-thus a completely abstract construction, and moreover it refers to a
+The main input of a modeller to the process is a markup of the
+candidate lens system, which we call a spaghetti diagram.  This is a
+sketch of the arrival-time surface from a point-like source, with
+proposed locations of maxima, minima and saddle points, and an implied
+time-ordering of the images.  Such information encodes a starting
+proposal for the mass distribution.  A spaghetti diagram is thus a
+completely abstract construction, and moreover it refers to a
 simplified system with a point source.  However, spaghetti diagrams
-are intuitive because they tend to resemble the form of lensed arcs,
-and of course they are simple to draw, and easy to vary and refine in
-an open collaborative environment.  This makes them very practical for
-non-professional lens enthusiasts in the citizen-science community.
-Details and tests are given in \cite{2015MNRAS.447.2170K}.
+are intuitive because they tend to resemble the form of lensed arcs
+\citep[see fig.3 of][]{2008MNRAS.383..857F}, and of course they are
+simple to draw, and easy to vary and refine in an open collaborative
+environment. This makes them very practical for non-professional lens
+enthusiasts in the citizen-science community.  Details and tests are
+given in \citet{2015MNRAS.447.2170K}.
 
@@
 drawing the spaghetti diagram, even before detailed mass-modelling
-takes place.  Figure~\ref{fig:splinput} shows nine examples, each
-consisting of a cutout of the Space~Warps image of a lens candidate,
+takes place.  Fig.~\ref{fig:splinput} shows nine examples, each
+consisting of a cutout of the \SW  image of a lens candidate,
 marked up with a spaghetti diagram.
+The volunteers are initially presented a square image with side
+82\arcsec (440~pixels) in full size, but they have the
+ability to zoom in individually.
+The cutouts presented in Figs.~\ref{fig:splinput} to \ref{fig:kappa}
+are rescaled during post-processing, relative to the outermost image.
+% it's a factor L/(L-4) with L=pixradius, for L=12 -> 1.5
+% maprad = rmax * L / (L-4)
 
-All the examples in Figure~\ref{fig:splinput} identify five locations:
+All the examples shown in Fig.~\ref{fig:splinput} identify five locations:
 the centre of the main lensing galaxy, which is also a maximum of the
@@
 examples, an arc is interpreted as a blend of three or four images.
-This gives the `unblended images' diagnostic.  Note that this
-characterisation could be different if the spaghetti diagram is
+This defines the `unblended images' diagnostic.  Note that this
+characterisation could be different if the spaghetti diagram were 
 different.  For example, SW28 has also been modelled with the arc on
 the right interpreted as a single image, rather than as three images
-as shown in the figure; for such a model, `unblended images'
+as shown in the figure; for such a model, the `unblended images'
 diagnostic would be true.
 
-The second diagnostic is whether all images are visible.  For example,
-we see in SW58 at the top left of Figure~\ref{fig:splinput} that an
+The second diagnostic checks whether all images are visible.  For example,
+we see in SW58 at the top left of Fig.~\ref{fig:splinput} that an
 image at the second minimum is conjectural and does not correspond to
@@
 
-The third diagnostic is whether the lens is fairly isolated, or
-whether there are other galaxies in the field that probably contribute
-significantly to the lensing.  For this, we do not consider stars or
-other clearly foregound objects.  Additional galaxies contributing to
-the lensing mass can be
-marked by the volunteer alongside the spaghetti diagrams.  An example
-can be seen as the grey dot and circle in the cutout with SW57 at the
-top right of Figure~\ref{fig:splinput}.  Objects marked in this way
-are modelled as point masses.  Other possible contributors to lensing
-are galaxies or groups that are not in the immediate vicinity of
-the lensed images, yet massive enough to have an effect.  These are
-accounted for by allowing a constant but adjustable external shear.
+The third diagnostic tests whether the lens is isolated, or whether
+other galaxies could contribute to the lensing.  For this, we do not
+consider stars or other clearly foregound objects.  Additional
+galaxies contributing to the lensing mass can be marked by the
+volunteer alongside the spaghetti diagrams.  An example can be seen as
+the grey dot and circle in the cutout with SW57 at the top right of
+Fig.~\ref{fig:splinput}.  Objects marked in this way are modelled as
+point masses.  Other possible contributors to lensing are galaxies or
+groups that are not in the immediate vicinity of the lensed images,
+yet massive enough to exert an influence. These are accounted for by
+allowing a constant but adjustable external shear.
 
-We remark that blended images or missing images or perturbing galaxies
-do not imply that a given candidate is unlikely to be a lens.  They
-mean, rather, that the models are more uncertain and perhaps could be
-more easily improved by trying further variations in the markup.
+We remark that the lack of expected lensed images, or the presence of
+blended images or perturbing galaxies do not imply that a given
+candidate is unlikely to be a lens.  This means, rather, that the
+models are more uncertain and perhaps could be more easily improved by
+trying further variations in the markup.
 
@@
 distribution.  Sources close to being dead-centre behind a lens tend
-to produce quads, sources at larger transverse distance tend to
-produce doubles.  We denote these as Q and D respectively, and add a
+to produce quads; sources at larger transverse distance tend to
+produce doubles.  We denote these as Q and D, respectively, and add a
 prefix to the Q systems, as follows: we write LQ if the source is
 inferred as displaced along the long axis of the lens, SQ if displaced
-along the short axis, IQ if inclined to both axes, CQ if only very little to
-no displacement.  Although the
+along the short axis, IQ if inclined to both axes, CQ if only very little or
+no displacement is evident.  Although the
 unlensed source and its location are obviously not seen, the LQ, SQ, IQ and CQ
@@
   minima in an arc, with the second saddle point on the other side of
-  the lensing galaxy, and closer to the galaxy than the arc is.  SW58
-  and SW28 in the upper row of Figure~\ref{fig:splinput} are typical
-  examples of SQ.  If the source would move outwards along the short
-  axis, the minimum-saddle-minimum would merge into a single minimum,
-  leaving a D system; the transition is known as cusp catastrophe.
-\item The middle row of Figure~\ref{fig:splinput} shows three IQ
-  systems, SW05, SW42 and SW19.  This type has a characteristic
+  the lensing galaxy, at a closer to the galaxy than the arc.  SW58
+  and SW28 in the upper row of Fig.~\ref{fig:splinput} are typical
+  examples of SQ.  If the source were moved outwards along the short
+  axis, the minimum-saddle-minimum set would merge into a single minimum,
+  leaving a D system; the transition is known as a cusp catastrophe.
+\item The middle row of Fig.~\ref{fig:splinput} shows three IQ
+  systems: SW05, SW42 and SW19.  This type has a characteristic
   asymmetry, often with two images close together.  If the source
-  would move outwards, the minimum-saddle pair would merge and
-  mutually cancel, again leaving a D system; the transition is known
+  were moved outwards, the minimum-saddle pair would merge and
+  mutually cancel, leaving again a D system. This transition is known
   as a fold catastrophe.
-\item The lower row of Figure~\ref{fig:splinput} shows three LQ
-  systems, SW09, SW29 and SW02, and the failed model SW57 at top right
-  also possibly belonging to this category.  Here the images have a
+\item The lower row of Fig.~\ref{fig:splinput} shows three LQ
+  systems: SW09, SW29 and SW02. The failed model, SW57, at top right
+  may also belong to this category.  Here the images have a
   fairly symmetric arrangement with an arc and a counter-image on the
   other side, but the spaghetti diagram is completely asymmetric.  If
-  the source would move outwards along the long axis, the
-  saddle-minimum-saddle would merge into a single saddle --- another
+  the source were moved outwards along the long axis, the
+  saddle-minimum-saddle set  would merge into a single saddle --- another
   form of cusp catastrophe.  LQ can be visually distinguished from SQ
-  from the relative distances of the arc and the counter-image.  For
+  by the relative distances of the arc and the counter-image.  For
   LQ the arc is closer, for SQ the counter-image is closer.

### 2017-09-05 parts/summary.tex
z errors

--- 2017-08-24 parts/summary.tex
@@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Summary and conclusions}\label{sec:summary}
 
-We report on a first set of mass distributions and follow up diagnostics for 
-the {\SW} lens candidates created with a novel approach that aims to be scalable 
-by orders of magnitudes to prepare for the many thousands of lenses the next 
-generation of wide field surveys will yield.
+We report on a first set of mass distributions and follow-up
+diagnostics for the {\SW} lens candidates created with a novel
+approach that aims to be scalable by {\sl orders of magnitude} to
+prepare for the many thousands of lenses the next generation of wide
+field surveys will yield (e.g. Euclid, WFIRST).
 
-The way of discovering lenses is changing with the introduction of
-machine learning and citizen science, combined with the coverage of
-huge areas by modern surveys.  The way mass models are constructed also needs to
-change, in order to be prepared for the increasing influx of lenses to
-be modelled.  This work is a hybrid of the classical style, where a
-small team of experts invest many hours into the creation of a single
-model, with the approach of citizen science, where a crowd of amateur
-volunteers make independent contributions.  We are a collaboration of
-professionals and experienced citizen-science volunteers, aiming to
-create early-stage lens models as soon as a lens candidate is found.
+Over the past few years, the way of discovering lenses has changed
+with the introduction of machine learning and citizen science methods,
+combined with the coverage of large areas of the sky by modern
+surveys.  The way lensing mass models are constructed also needs to
+change, in order to be prepared for the increasing influx of lens
+candidates.  The work in this paper represents a hybrid approach
+between the classical style -- where a small team of experts invest
+many hours into the creation of a single model -- and a citizen
+science project -- where a crowd of amateur volunteers make
+independent contributions.  The authors of this paper are a
+collaboration of professional and experienced citizen-science
+volunteers, aiming to create early-stage lens models as soon as a lens
+candidate is found.
 
-To assists volunteer modellers assessing their models, we introduce a
-set of diagnostics allowing the qualification of the lenses and the
-generated models and present them alongside the generated models. At a
-later stage, we encourage modellers to apply those diagnostics
-themselves to get a preliminary feedback on the plausibility of their
-models.
+To assist volunteers in constraining lensing models, we introduce a
+set of diagnostics that help asses the validity of the models. At a
+later stage, we encourage modellers to apply those diagnostics as
+feedback on the plausibility of their assumptions, and to suggest
+additional diagnostics.
+
+The diagnostics (i) -- (iv) (see Section.~\ref{sec:candidates_models})
+turned out to be useful measures of the difficulty in modelling a
+system, but they did not constitute necessary conditions for a
+promising model.  They can help select systems to introduce novice
+volunteers to the modelling process. In contrast, diagnostics (v) and
+(vi) can be considered as necessary criteria for a good model.
+Volunteers employed those ones to evaluate their models, and turned out
+to be easy enough to grasp by new volunteers.  The halo-matching
+index diagnostic (vii, $\haloindex$), is an interesting criterion that
+might be useful for the modellers, but needs further investigation.
 
@@
 model mass compares with the estimated stellar and full-halo masses.
-Missing entries are due to photometry data not being available, whereas
-missing rows are due to models not having been created for this particular
+Missing entries are due unavailable imaging data, whereas 
+missing rows are due to models that were not created for this particular
 candidate.
 
-The trend in Figure~\ref{fig:stelmass}, that higher-mass galaxies get 
-progressively more dark-matter dominated, is expected, e.g. see 
-\cite{2005ApJ...623L...5F}, as is the span of about one order of magnitude for 
-the stellar mass and the two order of magnitudes for the lensing mass. With 
-future data, it would be interesting to compare enclosed stellar and lensing 
-mass as a function of radius, going from star-dominated inner regions to dark 
-halos. \cite{2011ApJ...740...97L} illustrate this behaviour in their Figure~5, 
-but the present sample could go an order of magnitude higher in mass.
+The trend in Fig.~\ref{fig:stelmass}, where higher-mass galaxies get
+progressively more dark-matter dominated, is expected
+\citep[see, e.g.][]{2005ApJ...623L...5F}, as is the span of about one
+order of magnitude for the stellar mass and the two orders of
+magnitude in lensing mass. With future data, it will be interesting to
+compare the enclosed stellar and lensing mass as a function of radius,
+going from the star-dominated inner regions to the outer dark
+halos. \citet{2011ApJ...740...97L} illustrate this behaviour in their
+fig.~5, but the present sample could go an order of magnitude higher
+in mass.
 
-The quick creation of many models for the {\SW} candidates successfully showed 
-that a subset of citizen scientists are interested in being involved in more 
-challenging tasks that take some time to learn. A next steps involves 
-recruiting more lensing enthusiasts, as soon as the next round of {\SW} is 
-started. In the meantime, the improvements shown in the Appendix have to been 
-integrated into regular {\SpL} usage. Additionally, photometric fitting could 
-be integrated into {\SpL}. This would allow experienced citizen scientists to 
-generate photometric redshifts and stellar masses, and thus generate 
-preliminary dark-matter maps as soon as a lens-candidate is identified.
+The quick creation of many models for the {\SW} candidates
+successfully showed that a subset of citizen scientists are interested
+in being involved in more challenging tasks that take some time to
+learn. The next step involves recruiting more lensing enthusiasts, as
+soon as the next round of {\SW} is started. In the meantime, the
+improvements shown in the Appendix will be integrated in the standard
+version of {\SpL}. Photometric fitting could also be
+integrated into {\SpL}. This would allow experienced citizen
+scientists to generate photometric redshifts and stellar masses, and
+thus generate preliminary dark-matter maps as soon as a lens-candidate
+is identified.

### 2017-09-05 parts/massmodel.tex

@@
 models is discussed in Appendix~\ref{subsec:parameter}.
-\textcolor{red}{{\bf IF: This sentence is confusing and needs some
-    clarification:} Note that the arrival-time surface does not have
-  discontinuous jumps, because the modelling numerics uses an
-  analytical integral over square tiles; likewise the lens equation.}
+Note that although the mass distribution can have discontinuous jumps,
+the lens equation and arrival-time surface are continuous.
 

### 2017-09-06 parts/intro.tex
edited points flagged by IF

@@
 minimal overlap, the forum has little if any influence on the votes.
-\textcolor{red}{\bf IF: Please make sure the following is correct:}
+%\textcolor{red}{\bf IF: Please make sure the following is correct:}
+% OK
 In SpaghettiLens, the number of volunteers is significantly lower, but
@@
 $r^\prime$ and $i^\prime$ bands from randomly chosen regions.
-The programme \citep{2016MNRAS.455.1191M} resulted in 59 new lens candidates (of which 29 are
-promising  \textcolor{red}{\bf IF: why are
-  they promising? explain this here).}  Moreover, 82 previously known
-lens candidates were ``rediscovered''.  The candidates have broadly
-similar redshifts (0.2$<$z$<$1.0), Einstein radii between 0.7 and
-5\,\arcsec, and arc magnitudes between 22 and 26 \textcolor{red}{\bf
-  IF: in the $g^\prime$ band?}. These properties are similar to those
-found by previous robotic searches like ArcFinder and RingFinder.
+The programme resulted in 59 new lens candidates, of which 29 are
+considered high quality \citep{2016MNRAS.455.1191M}.
+% \textcolor{red}{\bf IF: why are they promising? explain this here).}
+Moreover, 82 previously known lens candidates were ``rediscovered''.
+The candidates have broadly similar redshifts ($0.2<z<1.0$), Einstein
+radii between 0.7 and 5\,\arcsec, and arc magnitudes between 22 and 26
+\textcolor{red}{\bf IF: in the $g^\prime$ band?}. These properties are
+similar to those found by previous robotic searches like ArcFinder and
+RingFinder.
 
@@
 
-A first version of \SpL\footnote{\textcolor{red}{\bf IF include web
-    link: {\tt http://xxx.yyy.ch}}} was launched in May 2013, while
+A first version of \SpL
+% \footnote{\textcolor{red}{\bf IF include web
+%  link: {\tt http://xxx.yyy.ch}}}
+% Not currently online
+was launched in May 2013, while
 the first run of \SW was ongoing.  Fig.~\ref{fig:time} shows the
@@
 launched.  A group of five volunteers presented their results in an
-online letter \textcolor{red}{\bf REFERENCE?} about 65 days later,
+online letter
+% \textcolor{red}{\bf REFERENCE?} about 65 days later,
+% Not available any more.
 converging on a set of 30 models. In April 2015 (day 700),

### 2017-09-06 parts/massmodel.tex
edited points flagged by IF

@@
 the identified lens centre \citep[see][for the precise formulation of
-  the search problem]{2014MNRAS.445.2181C}. Assuming such mass
-distributions can be found -- which in practice is usually the case --
-a statistical ensemble of two-dimensional mass maps is returned.  This
-ensemble, along with derived quantities and uncertainties, makes up
-one SpaghettiLens model.
+  the search problem]{2014MNRAS.445.2181C}.  The modeller can also set
+various options for the search, such as the number of mass tiles and
+the extent of the mass map; all options have defaults.  Typically,
+there are $\sim500$ mass tiles arranged in a disc, centred on the
+lensing galaxy and extending to twice the radius of the outermost
+image.  By default, the mass distributed is required to have
+$180^\circ$ rotation symmetry, but this option can be unset.  Assuming
+mass distributions can be found -- which in practice is usually the
+case -- a statistical ensemble of two-dimensional mass maps is
+returned.  This ensemble, along with derived quantities and
+uncertainties, makes up one SpaghettiLens model.
 
@@
 is not a problem, because a model can be trivially rescaled to use
-better redshift values, as they become available.  This work applies
-photometric redshifts from the CFHTLS pipeline
-\citep{2009A&A...500..981C} to the candidate lensing galaxies; the
-values range from z=0.2 to 1 (see Table~\ref{tab:models}).
-These redshifts entail rather big uncertainties, up to a few ten
-percent.  Since, however, the angular critical density is proportional
-to $d_l d_s d_{ls}^{-1}$ \citep[consult Equation~A1
-  in][]{2015MNRAS.447.2170K} it is negligible for this tentative
-analysis. \textcolor{red}{\bf IF: I would not say this is
-  ``negligible'' but, rather, that the error in the redshift would lead to
-  surface mass density uncertainties of XX\%, which, for the
-  aim of the tentative analysis presented here, is an acceptable
-  result. You should also check and quantify properly the
-  uncertainty in the photo-z. What is the value claimed by the
-  CFHTLS group? I would say 5-10\% is a decent level, but you
-are mentioning 10s of \% which is rather extreme!}.
-As the mass normalisation depends only weakly on the source redshift,
-provided it is higher than the lens redshift, we adopted a redshift
-z=2 for all sources, unless an unambiguous photometric redshift is
-available. \textcolor{red}{\bf IF: Again, a simple quantification of the
-change you expect, for instance, if the source is at z=3 would be good.}
+better redshift values, as they become available.  The mass
+normalisation of the models is proportional, through the angular
+critical density, to the factor $d_L\, d_S\, d_{LS}^{-1}$, where
+$d_L,d_S$ and $d_{LS}$ are the usual angular-diameter distances.  In
+the redshift ranges typical of galaxy lensing, the normalisation
+factor is roughly proportional to the lens redshift, and weakly
+dependent on the source redshift.  This work applies photometric
+redshifts from the CFHTLS pipeline \citep{2009A&A...500..981C} to the
+candidate lensing galaxies; the values range from $z=0.2$ to 1 (see
+Table~\ref{tab:models}).  The source redshifts are assumed as $z=2$,
+unless an unambiguous photometric redshift is available.  The lens
+redshifts redshifts entail rather big uncertainties, up to a few tens
+of percent.  The lensing masses are uncertain at the same level.  On
+the other hand, the lensing masses in the sample range from
+$10^{11}M_\odot$ to $10^{13}M_\odot$, hence the redshift uncertainty
+is not so important in this preliminary analysis.
+% \textcolor{red}{\bf IF: I would not say this is
+% ``negligible'' but, rather, that the error in the redshift would lead to
+%  surface mass density uncertainties of XX\%, which, for the
+%  aim of the tentative analysis presented here, is an acceptable
+%  result. You should also check and quantify properly the
+%  uncertainty in the photo-z. What is the value claimed by the
+%  CFHTLS group? I would say 5-10\% is a decent level, but you
+%  are mentioning 10s of \% which is rather extreme!}.
+% \textcolor{red}{\bf IF: Again, a simple quantification of the
+% change you expect, for instance, if the source is at z=3 would be good.}
 
@@
 average convergence, $\kappa$, within circles of given projected
-radius.  The uncertainties \textcolor{red}{\bf IF: at the BLAH level}
-are included.  Appendix~\ref{subsec:hires} describes the improvements made
+radius.  Uncertainties are included (see the figure caption for
+details).
+% \textcolor{red}{\bf IF: at the BLAH level}
+% Explained in the caption.
+Appendix~\ref{subsec:hires} describes the improvements made
 since our earlier work \citep{2015MNRAS.447.2170K}, to allow for

### 2017-09-06 parts/app.tex

@@
 tendency to produce density profiles which were too shallow, resulting
-typically in overestimates of the Einstein radius. Volunteers could
-already set the size of the pixels by defining the radius of the lens
-in pixels, with typical values between 8 and 12 pixels. Additionally,
-it was possible to select smaller mass tiles in the central region,
-thus allowing the mass profile to rise more steeply near the centre.
-These options were was suggested as a possible cure.
-\textcolor{red}{\bf IF: I don't even know what you mean by the last
-  sentence: were those measures already implemented in the work
-  described in that paper, or were these things considered a solution
-  to the shallow profiles? Please clarify.}
+typically in overestimates of the Einstein radius. Allowing some extra
+mass tiles in central region, thus allowing the mass profile to rise
+more steeply near the centre, was suggested as a possible cure.
+%\textcolor{red}{\bf IF: I don't even know what you mean by the last
+%  sentence: were those measures already implemented in the work
+%  described in that paper, or were these things considered a solution
+%  to the shallow profiles? Please clarify.}
 

### 2017-09-06 parts/figures.tex
update all images
feedback from IF
last changes

@@
   This selection includes the
-  best-modelled systems, but also one case (SW57 at upper right) of
+  best-modelled systems, but also one case (\sw{57} at upper right) of
   unsuccessful modelling.  Since the modelling process is
@@
   $180^\circ$-rotation symmetry, which is imposed by default.  For
-  SW02 and SW57, where the lensing mass is clearly asymmetric, the
+  \sw{02} and \sw{57}, where the lensing mass is clearly asymmetric, the
   modeller chose to turn off the symmetry.
@@
 \begin{figure*}
-\includegraphics[width=\linewidth]{img/mlens_vs_mstel_one/mstel_vs_mtot_one}
+\includegraphics[width=\linewidth]{img/mlens_vs_mstel/mlens_vs_mstel}
 \caption{Total mass in the model against the estimated stellar mass,
@@
 \begin{table*}
-  \caption{Diagnostics of a selected model for each Space Warps candidate
-    (see Section~\ref{sec:summary}). Machine readable version in online supplement.}
+  \caption{Diagnostics of the selected models for each \SW
+    candidate (see Section~\ref{sec:summary}).
+    %A machine-readable version is available in the online supplement.
+    }
   \label{tab:models}

### 2017-09-06 parts/intro.tex
last changes

@@
 still needed.  With that in mind \cite{2015MNRAS.447.2170K} developed
-a new modelling strategy, implemented as the SpaghettiLens system.
+a new modelling strategy, implemented as the SpaghettiLens\footnote{\url{http://labs.spacewarps.org/spaghetti/}}
+system.
 The idea is to collaborate with experienced members of the
@@
 ($u^*$,$g^\prime$,$r^\prime$,$i^\prime$,$z^\prime$) covering a total
-area of 160\,\sqdeg divided up into four fields W1 -- W4.  The
+area of 160\sqdeg divided up into four fields W1 -- W4.  The
 MegaPrime camera, used for the survey, has a field of view of
-1\,\sqdeg, with 0.186$^{\prime\prime}$ pixels. The flux limit of the
-survey is $g^\prime<$25.6AB (5\,$\sigma$) with a typical seeing
-FWHM$\sim 0.7^{\prime\prime}$ \citep{2013MNRAS.433.2545E}. The cutouts
+1\sqdeg, with $0.186\arcsec$ pixels. The flux limit of the
+survey is $g^\prime<25.6\,\text{AB}$ ($5 \sigma$) with a typical seeing
+FWHM $\sim 0.7\arcsec$ \citep{2013MNRAS.433.2545E}. The cutouts
 shown to the volunteers were colour composites of the $g^\prime$,
@@
 The programme resulted in 59 new lens candidates, of which 29 are
-considered high quality \citep{2016MNRAS.455.1191M}.
+considered high quality.
 % \textcolor{red}{\bf IF: why are they promising? explain this here).}
@@
 The candidates have broadly similar redshifts ($0.2<z<1.0$), Einstein
-radii between 0.7 and 5\,\arcsec, and arc magnitudes between 22 and 26
-\textcolor{red}{\bf IF: in the $g^\prime$ band?}. These properties are
+radii between 0.7 and 5\arcsec, and arc fluxes in $g$-band AB
+magnitudes between 22 and 26. These properties are
 similar to those found by previous robotic searches like ArcFinder and
-RingFinder.
+RingFinder \citep{2016MNRAS.455.1191M}.
 
@@
 
-A first version of \SpL
-% \footnote{\textcolor{red}{\bf IF include web
-%  link: {\tt http://xxx.yyy.ch}}}
-% Not currently online
-was launched in May 2013, while
+A first version of \SpL was launched in May 2013, while
 the first run of \SW was ongoing.  Fig.~\ref{fig:time} shows the

### 2017-09-06 parts/morph.tex
last changes

@@
 saddle points (green dots and also self-intersections of the curves).
-Only two (SW05 and SW42) of the nine systems, however, have five
+Only two (\sw{05} and \sw{42}) of the nine systems, however, have five
 distinct features in plausible locations.  In the other seven
@@
 characterisation could be different if the spaghetti diagram were 
-different.  For example, SW28 has also been modelled with the arc on
+different.  For example, \sw{28} has also been modelled with the arc on
 the right interpreted as a single image, rather than as three images
@@
 The second diagnostic checks whether all images are visible.  For example,
-we see in SW58 at the top left of Fig.~\ref{fig:splinput} that an
+we see in \sw{58} at the top left of Fig.~\ref{fig:splinput} that an
 image at the second minimum is conjectural and does not correspond to
@@
 volunteer alongside the spaghetti diagrams.  An example can be seen as
-the grey dot and circle in the cutout with SW57 at the top right of
+the grey dot and circle in the cutout with \sw{57} at the top right of
 Fig.~\ref{fig:splinput}.  Objects marked in this way are modelled as
@@
   minima in an arc, with the second saddle point on the other side of
-  the lensing galaxy, at a closer to the galaxy than the arc.  SW58
-  and SW28 in the upper row of Fig.~\ref{fig:splinput} are typical
+  the lensing galaxy, at a closer to the galaxy than the arc.  \sw{58}
+  and \sw{28} in the upper row of Fig.~\ref{fig:splinput} are typical
   examples of SQ.  If the source were moved outwards along the short
@@
 \item The middle row of Fig.~\ref{fig:splinput} shows three IQ
-  systems: SW05, SW42 and SW19.  This type has a characteristic
+  systems: \sw{05}, \sw{42} and \sw{19}.  This type has a characteristic
   asymmetry, often with two images close together.  If the source
@@
 \item The lower row of Fig.~\ref{fig:splinput} shows three LQ
-  systems: SW09, SW29 and SW02. The failed model, SW57, at top right
+  systems: \sw{09}, \sw{29} and \sw{02}. The failed model, \sw{57}, at top right
   may also belong to this category.  Here the images have a

### 2017-09-06 parts/stelmass.tex
diff fix
last changes

@@
 \begin{equation}
-  \left.
-  \begin{aligned}
-\frac{\Mstel}{\Mhalo} &= \frac{2C_0}{(\Mhalo/M_1)^{-\beta} +
-                                     (\Mhalo/M_1)^\gamma} \\
-C_0 &= 0.02820, \quad M_1 = 10^{11.884} M_\odot \\
-\beta &= 1.057, \quad \gamma = 0.556.
-\end{aligned}
-  \right\}
+    \frac{\Mstel}{\Mhalo} = \frac{2C_0}{(\Mhalo/M_1)^{-\beta} +
+                                     (\Mhalo/M_1)^\gamma}
 \end{equation}
+\begin{align*}
+    C_0 &= 0.02820, & M_1 &= 10^{11.884} M_\odot \\
+    \beta &= 1.057, & \gamma &= 0.556.
+\end{align*}
 Fig.~\ref{fig:stelmass} may be compared with fig.~4 in
@@
   Exact values can be found in the online version of Table~\ref{tab:models}}.
-SW05 is one of the most massive of all the candidates, corresponding
+\sw{05} is one of the most massive of all the candidates, corresponding
 to a galaxy-group mass scale.  It is a particularly attractive system
@@
 system with clear multiple-image features. Modelling leaves little
-doubt that it is a lens.  SW04 seems to be even more massive, but the
+doubt that it is a lens.  \sw{04} seems to be even more massive, but the
 diagnostics leave some doubts about the validity of this model.  The
-two lowest-mass systems, SW19 and SW42, are important if they are
+two lowest-mass systems, \sw{19} and \sw{42}, are important if they are
 indeed lenses, as they would be low-mass lenses dominated by dark
@@
 fractions, except for two cases where the stellar-mass fraction is too
-low ($\haloindex > 1$): these are SW42 and SW57.  In the case of SW57,
+low ($\haloindex > 1$): these are \sw{42} and \sw{57}.  In the case of \sw{57},
 the model has poor diagnostics and should be discarded.  The model
-for SW42, on the other hand, is quite convincing -- except for the
-high halo-matching index.  If SW42 turned out not to be a lens, that
+for \sw{42}, on the other hand, is quite convincing -- except for the
+high halo-matching index.  If \sw{42} turned out not to be a lens, that
 would support the halo-matching index as an effective criterion to

### 2017-09-06 parts/morph.tex
clean up

@@
   minima in an arc, with the second saddle point on the other side of
-  the lensing galaxy, at a closer to the galaxy than the arc.  \sw{58}
+  the lensing galaxy, closer to the galaxy than the arc.  \sw{58}
   and \sw{28} in the upper row of Fig.~\ref{fig:splinput} are typical

### 2017-09-06 parts/summary.tex
make fig uniform

@@
 independent contributions.  The authors of this paper are a
-collaboration of professional and experienced citizen-science
+collaboration of professionals and experienced citizen-science
 volunteers, aiming to create early-stage lens models as soon as a lens
@@
 halos. \citet{2011ApJ...740...97L} illustrate this behaviour in their
-fig.~5, but the present sample could go an order of magnitude higher
+Fig.~5, but the present sample could go an order of magnitude higher
 in mass.

### 2017-09-07 parts/morph.tex
make fig uniform
my hands are typing words

@@
 are intuitive because they tend to resemble the form of lensed arcs
-\citep[see fig.3 of][]{2008MNRAS.383..857F}, and of course they are
+\citep[see Fig.3 of][]{2008MNRAS.383..857F}, and of course they are
 simple to draw, and easy to vary and refine in an open collaborative
@@
 \begin{itemize}
-\item The simplest is the SQ case: this creates a saddle point and two
+\item The simplest is the LQ case: this creates a saddle point and two
   minima in an arc, with the second saddle point on the other side of
@@
   and \sw{28} in the upper row of Fig.~\ref{fig:splinput} are typical
-  examples of SQ.  If the source were moved outwards along the short
+  examples of LQ.  If the source were moved outwards along the short
   axis, the minimum-saddle-minimum set would merge into a single minimum,
@@
   as a fold catastrophe.
-\item The lower row of Fig.~\ref{fig:splinput} shows three LQ
+\item The lower row of Fig.~\ref{fig:splinput} shows three SQ
   systems: \sw{09}, \sw{29} and \sw{02}. The failed model, \sw{57}, at top right
@@
   saddle-minimum-saddle set  would merge into a single saddle --- another
-  form of cusp catastrophe.  LQ can be visually distinguished from SQ
+  form of cusp catastrophe.  SQ can be visually distinguished from LQ
   by the relative distances of the arc and the counter-image.  For
-  LQ the arc is closer, for SQ the counter-image is closer.
+  SQ the arc is closer, for LQ the counter-image is closer.
 \end{itemize}

### 2017-09-07 parts/massmodel.tex
typo fix

@@
 unless an unambiguous photometric redshift is available.  The lens
-redshifts redshifts entail rather big uncertainties, up to a few tens
-of percent.  The lensing masses are uncertain at the same level.  On
-the other hand, the lensing masses in the sample range from
-$10^{11}M_\odot$ to $10^{13}M_\odot$, hence the redshift uncertainty
-is not so important in this preliminary analysis.
+redshifts entail rather big uncertainties, up to a few tens of
+percent.  The lensing masses are uncertain at the same level.  On the
+other hand, the lensing masses in the sample range from
+$10^{11}M_\odot$ to $10^{13}M_\odot$; in comparison, the redshift
+uncertainty is not so important in this preliminary analysis.
 % \textcolor{red}{\bf IF: I would not say this is

### 2017-10-10 parts/intro.tex
CLEAN UP code, removing comments
working on report/letter2

@@
 surveys, from ground-based surveys such as LSST in the optical window
-and SKA in radio, to space-based missions such as Euclid and WFIRST.
+and SKA in radio, to space-based missions such as Euclid and WFIRST 
+\citep{2010MNRAS.405.2579O,2015ApJ...811...20C}.
 
@@
 minimal overlap, the forum has little if any influence on the votes.
-%\textcolor{red}{\bf IF: Please make sure the following is correct:}
-% OK
 In SpaghettiLens, the number of volunteers is significantly lower, but
@@
 
-We emphasize that the interpretation of the results presnted here is
+We emphasize that the interpretation of the results presented here is
 tentative, because the systems are lens candidates at this stage, not
@@
 guessed at present.  Nevertheless it is interesting to explore the
-trends observed with the already available data.
-%TODO there is more info about uncertainies here:
-% https://arxiv.org/pdf/0811.3326.pdf
+trends observed with the already available data, based on some 300 models
+created by 8 volunteers for 58 candidate lenses found in the 150\sqdeg
+CFHTLS.  The availability of the recently published year 1 result of the
+Dark Energy Survey \citep{2017arXiv170801531D},
+which covered 1800\sqdeg, suggests that
+these numbers have the possibility to grow by at least an order of
+magnitude within a very short time period.
+Moreover, ongoing work by Denzel et al. (in prep) will provide much more
+strict bounds on the uncertainties presented in this work.
 
@@
 considered high quality.
-% \textcolor{red}{\bf IF: why are they promising? explain this here).}
 Moreover, 82 previously known lens candidates were ``rediscovered''.
@@
 online letter
-% \textcolor{red}{\bf REFERENCE?} about 65 days later,
-% Not available any more.
 converging on a set of 30 models. In April 2015 (day 700),
@@
 of fitting a parametric lens model to the ensemble.
-%; so far we have only been successful at extracting an Einstein radius.
 

### 2017-10-10 parts/massmodel.tex
redshift-uncertainty ref
CLEAN UP code, removing comments
working on report/letter2

@@
 the extent of the mass map; all options have defaults.  Typically,
-there are $\sim500$ mass tiles arranged in a disc, centred on the
+there are $\sim$ 500 mass tiles arranged in a disc, centred on the
 lensing galaxy and extending to twice the radius of the outermost
@@
 case -- a statistical ensemble of two-dimensional mass maps is
-returned.  This ensemble, along with derived quantities and
-uncertainties, makes up one SpaghettiLens model.
+returned.  
+This ensemble of typically 200 models, along with derived quantities and uncertainties, makes up one SpaghettiLens model.
+Each of these ensemble of models is usually represented using tile-by-tile mean values and uncertainties derived from tile-by-tile minima and maxima.
 
@@
 unless an unambiguous photometric redshift is available.  The lens
-redshifts entail rather big uncertainties, up to a few tens of
-percent.  The lensing masses are uncertain at the same level.  On the
-other hand, the lensing masses in the sample range from
-$10^{11}M_\odot$ to $10^{13}M_\odot$; in comparison, the redshift
-uncertainty is not so important in this preliminary analysis.
-% \textcolor{red}{\bf IF: I would not say this is
-% ``negligible'' but, rather, that the error in the redshift would lead to
-%  surface mass density uncertainties of XX\%, which, for the
-%  aim of the tentative analysis presented here, is an acceptable
-%  result. You should also check and quantify properly the
-%  uncertainty in the photo-z. What is the value claimed by the
-%  CFHTLS group? I would say 5-10\% is a decent level, but you
-%  are mentioning 10s of \% which is rather extreme!}.
-% \textcolor{red}{\bf IF: Again, a simple quantification of the
-% change you expect, for instance, if the source is at z=3 would be good.}
+redshifts entail rather big uncertainties, up to a few tens of percent
+\citep[see Fig.~5 in][]{2009A&A...500..981C}. The lensing masses would
+be uncertain at the same level.  On the other hand, the lensing masses
+in the sample range from $10^{11}M_\odot$ to $10^{13}M_\odot$; in
+comparison, the redshift uncertainty is not so important in this
+preliminary analysis.
 
@@
 details).
-% \textcolor{red}{\bf IF: at the BLAH level}
-% Explained in the caption.
 Appendix~\ref{subsec:hires} describes the improvements made
@@
 out to be a good indicator of plausible models, as can seen by
-contrasting model \sw{57} with the rest of the sample:  The missing
+contrasting the model for \sw{57} with the rest of the sample:  The missing
 core in Fig.~\ref{fig:kappa} and the flat profile in
@@
 checkerboard pattern.
+
+More experienced volunteers applied these diagnostics already during the process of creating models as a criteria of a successful model, the evaluation presented in this work however was generated by the authors during post processing.

### 2017-10-12 parts/intro.tex
working on letter2

@@
   twice the radius of the outermost image.
+  We note that even though this definition of the lensing mass encloses
+  most of the total galaxy mass, since the halos extend well beyond this, it
+  creates a bias toward low lensing masses, compared to their total mass.
+  One solution would be to extrapolate as done in \citet{2012MNRAS.424..104L},
+  but this has not been tried yet.
   Section~\ref{sec:stellar-mass} explains how we compare the lensing

### 2017-10-13 parts/massmodel.tex
working on letter2
small edits

@@
 the extent of the mass map; all options have defaults.  Typically,
-there are $\sim$ 500 mass tiles arranged in a disc, centred on the
+there are $\sim500$ mass tiles arranged in a disc, centred on the
 lensing galaxy and extending to twice the radius of the outermost
@@
 mass distributions can be found -- which in practice is usually the
-case -- a statistical ensemble of two-dimensional mass maps is
-returned.  
-This ensemble of typically 200 models, along with derived quantities and uncertainties, makes up one SpaghettiLens model.
-Each of these ensemble of models is usually represented using tile-by-tile mean values and uncertainties derived from tile-by-tile minima and maxima.
+case -- a statistical ensemble of 200 two-dimensional mass maps is
+returned.  From each mass map, further quantities such as lens
+potentials or enclosed masses can be derived.  Thus, there are
+ensembles of 200 values for the surface density at any point, for the
+enclosed mass within a given radius and so on.  In this paper we
+present the averages and ranges of different quantities, but other
+quantities such as 90\% confidence ranges could also be computed.  The
+whole ensemble of mass maps, along with derived quantities and
+uncertainties, makes up one SpaghettiLens model.
 
@@
 
-More experienced volunteers applied these diagnostics already during the process of creating models as a criteria of a successful model, the evaluation presented in this work however was generated by the authors during post processing.
+More experienced volunteers applied these diagnostics already during the 
+process of creating models as a criteria of a successful model, the evaluation 
+presented in this work however was generated by the authors during post 
+processing.

### 2017-10-16 parts/intro.tex
editing

--- 2017-10-10 parts/intro.tex
@@
   Section~\ref{sec:stellar-mass} explains how we compare the lensing
-  (i.e. total) mass with the stellar mass. Naturally, the lensing
-  mass should be somewhere between the stellar mass (lower bound)
-  and the total halo mass (upper bound).
+  mass with the stellar mass.  Galaxies may have halos extending well
+  beyond the mass maps in the models, so the calculated lensing mass
+  is only a lower bound on the total galaxy mass.  Hence, the lensing
+  mass should be somewhere between the stellar mass (lower bound) and
+  the total halo mass (upper bound).  Extrapolation of the lens model
+  to estimate the full virial mass may be possible
+  \citep[cf.][]{2012MNRAS.424..104L}, but is not attempted in this
+  work.
 \begin{enumerate}

### 2017-10-16 parts/stelmass.tex
make fig uniform
edit

@@
 \end{align*}
-Fig.~\ref{fig:stelmass} may be compared with fig.~4 in
+Fig.~\ref{fig:stelmass} may be compared with Fig.~4 in
 \cite{2011ApJ...734...69M}.
@@
 candidates have stellar
-and lensing masses typical of massive ellipticals\footnote{
-  Exact values can be found in the online version of Table~\ref{tab:models}}.
+and lensing masses typical of massive ellipticals\footnote{The mass values
+themselves are given in the online version of Table~\ref{tab:models}}.
 \sw{05} is one of the most massive of all the candidates, corresponding

### 2017-10-17 parts/intro.tex
edits

@@
 and SKA in radio, to space-based missions such as Euclid and WFIRST
-\citep{2010MNRAS.405.2579O,2015ApJ...811...20C}.
+\citep{2010MNRAS.405.2579O,2015ApJ...811...20C}.  The availability of
+the recently published year~1 result of the Dark Energy Survey
+\citep{2017arXiv170801531D}, which covered 1800\sqdeg, suggests that
+the number of lenses could grow by at least an order of magnitude
+within a very short time period.
+% Moreover, ongoing work by Denzel et al. (in prep) will provide much more
+% strict bounds on the uncertainties presented in this work.
 
@@
 created by 8 volunteers for 58 candidate lenses found in the 150\sqdeg
-CFHTLS.  The availability of the recently published year 1 result of the
-Dark Energy Survey \citep{2017arXiv170801531D},
-which covered 1800\sqdeg, suggests that
-these numbers have the possibility to grow by at least an order of
-magnitude within a very short time period.
-Moreover, ongoing work by Denzel et al. (in prep) will provide much more
-strict bounds on the uncertainties presented in this work.
+CFHTLS.
 

### 2017-11-14 parts/stelmass.tex
draft response3

@@
 energy distribution is needed to derive accurate stellar masses
-\citep[e.g.][]{2009ApJS..185..253G,2011MNRAS.418.1587T}.  However,
+\citep[e.g.][]{2009ApJS..185..253G,2011MNRAS.418.1587T}.
+Fortunately, however, the 4000\thinspace\AA~break in stellar spectra
+makes things considerably easier, as this spectral feature is (a)~very
+sensitive to the age of a stellar population, and (b)~possible to
+constrain even with just two broad-band flux measurements on either
+side of it.  As a result,
 estimates to within $\sim$0.3\,dex in $\log(\Mstel/\Msun)$ can be derived

### 2017-11-16 parts/stelmass.tex
further small edits

--- 2017-10-16 parts/stelmass.tex
@@
 energy distribution is needed to derive accurate stellar masses
-\citep[e.g.][]{2009ApJS..185..253G,2011MNRAS.418.1587T}.  However,
+\citep[e.g.][]{2009ApJS..185..253G,2011MNRAS.418.1587T}.
+However, useful constrain can be obtained even with just two
+broad-band flux measurements on either side of the
+4000\thinspace\AA~break in stellar spectra, because this feature is
+very sensitive to age for young stellar population, and hence to the
+stellar mass-to-light ratio.  Tests indicate that
 estimates to within $\sim$0.3\,dex in $\log(\Mstel/\Msun)$ can be derived

### 2017-11-16 parts/stelmass.tex
typo fix

@@
 \citep[e.g.][]{2009ApJS..185..253G,2011MNRAS.418.1587T}.
-However, useful constrain can be obtained even with just two
+However, useful constraints can be obtained even with just two
 broad-band flux measurements on either side of the

### 2017-11-17 parts/stelmass.tex

--- 2017-11-16 parts/stelmass.tex
@@
 The stellar masses of the lens galaxies are derived by comparison of
-the photometric data with stellar M/L estimates from population
+the photometric data with stellar $M/L$ estimates from population
 synthesis models.  In principle, a detailed analysis of the spectral
 energy distribution is needed to derive accurate stellar masses
-\citep[e.g.][]{2009ApJS..185..253G,2011MNRAS.418.1587T}.
-However, useful constrain can be obtained even with just two
-broad-band flux measurements on either side of the
-4000\thinspace\AA~break in stellar spectra, because this feature is
-very sensitive to age for young stellar population, and hence to the
-stellar mass-to-light ratio.  Tests indicate that
+\citep[e.g.][]{2009ApJS..185..253G,2011MNRAS.418.1587T}.  However,
+at the redshifts probed, the photometric data mainly
+constrain the information-rich 4000\thinspace\AA~break region, whose
+strength depends sensitively on age and metallicity, thereby
+providing a strong constraint on the stellar $M/L$.  Hence,
 estimates to within $\sim$0.3\,dex in $\log(\Mstel/\Msun)$ can be derived
@@
 cores of massive early-type galaxies \citep{2016MNRAS.457.1468L}. The
-effect of these variations on the stellar M/L of lensing systems is
+effect of these variations on the stellar $M/L$ of lensing systems is
 still rather controversial

### 2017-11-21 KuengR__Lens_models.tex
cleanup: names

--- 2017-09-05 paper2.tex
@@
 \documentclass[fleqn,usenatbib]{template/mnras}
-
-%%% DEBUG SETTINGS - remove at the end %%%%%%%%%%%%%%%
-
-%\usepackage{silence} % silence error warinings
-%\WarningFilter{caption}{Unsupported document class} % caption doesn't know mnras..
-%\hbadness = 10000
-%\vbadness = 10000
-
-% \usepackage{}
-
-% MNRAS is set in Times font. If you don't have this installed (most LaTeX
-% installations will be fine) or prefer the old Computer Modern fonts, comment
-% out the following line
-%\usepackage{newtxtext,newtxmath} % not yet supported on arxiv and uni computer
-%\usepackage{txfonts}
-
-% Depending on your LaTeX fonts installation, you might get better results with one of these:
-%\usepackage{mathptmx}
-%\usepackage{txfonts}
 
@@
 \usepackage[T1]{fontenc}      % make sure font is supported
-% \usepackage{ae,aecompl} %obsolete when using modern fonts
 \usepackage[final]{microtype} % make sure font is supported
-% and a suitable font
 \usepackage{lmodern}          % use a modern font with T1 support
-%\usepackage{cm-super} % use a modern font with T1 support
-
-%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
 
 % Only include extra packages if you really need them. Common packages are:
-%\usepackage[dvipdfmx]{graphicx}	% Including figure files
 \usepackage{graphicx} % Including figure files
-%\usepackage[skip=0pt]{subcaption}
 \usepackage{amsmath}  % Advanced maths commands
@@
 \usepackage{pifont}   % Extra maths symbols
-%\usepackage{bmpsize}  % PS still needs this for correct bounding boxes?
 \usepackage{xspace}   % handling of spaces after shortcuts
 
-% TODO stuff, comment out for final submit
-\usepackage{todonotes} % as long as we are editing...
-%\usepackage{showframe} % for debug
-\overfullrule=5pt      % show overfull boxes
+%%% DEBUG SETTINGS - remove at the end %%%%%%%%%%%%%%%
+% \usepackage{todonotes} % as long as we are editing...
+% \usepackage{showframe} % for debug
+% \overfullrule=5pt      % show overfull boxes
 
@@
 
-%\newcommand{\lenstitle}[1]{\noindent\textbf{#1} --}
-%\newcommand{\params}[3]{(\(\Theta_\text{E}:#1\), $\varepsilon:#2$, $\alpha_\varepsilon:#3$ )}
-
 \newcommand{\SW}{Space\,Warps\xspace}
 \newcommand{\SpL}{SpaghettiLens\xspace}
-\newcommand{\asw}[1]{ASW000#1\xspace}
+\newcommand{\asw}[1]{ASW000\,#1\xspace}
 \newcommand{\sw}[1]{SW\,#1\xspace}
@@
 
-%\newcommand{\Mstel}{\ensuremath{M_{\rm stel}}}
-%\newcommand{\Mhalo}{\ensuremath{M_{\rm h}}}
 \newcommand{\Mstel}{\ensuremath{M_\text{stel}}}
@@
 %\newcommand{\ER}{$\Theta_{\text{E}}$} % einstein radius
-\newcommand{\ER}{\ensuremath{r_\text{E}}} % einstein radius
+\newcommand{\ER}{\ensuremath{r_\text{E}}\xspace} % einstein radius
 
-\newcommand{\sqdeg}{\ensuremath{\text{deg}^2}}
+\newcommand{\sqdeg}{\ensuremath{\,\text{deg}^2}\xspace}
+\renewcommand{\arcsec}{\ensuremath{\,^{\prime\prime}}\xspace}
 
@@
 
-\title[Lens models for Space Warps CFHTLS]{Models of gravitational lens candidates from
-  Space Warps CFHTLS}
+\title[Lens models for Space Warps CFHTLS]{Models of gravitational
+    lens candidates from Space Warps CFHTLS}
 
@@
 increases.  The most massive system with a convincing model is
-J1434+522 (\sw{05}).  The two low-mass outliers are J0206-095
+J1434+522 (\sw{05}).  The two low-mass outliers are J0206$-$095
 (\sw{19}) and J2217+015 (\sw{42}); if these two are indeed lenses,
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \bibliographystyle{template/mnras}
 \bibliography{bib/bibli}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%\section{TODO}
-%\listoftodos
-
 % Don't change these lines

### 2017-11-21 KuengR__Lens_models.tex
cleanup: backport arxiv modifications
cleanup: enter acceptance date

@@
 \documentclass[fleqn,usenatbib]{template/mnras}
+
+\pdfoutput=1
+% pdfoutput is used for arxiv, should be somewhere in lines 1-5
 
@@
 \usepackage{hyperref}   % Hyperlinks
-\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,filecolor=blue,urlcolor=blue}
+\hypersetup{
+  colorlinks=true,
+  linkcolor=blue,
+  citecolor=blue,
+  filecolor=blue,
+  urlcolor=blue,
+  pdfauthor={Kueng, Rafael et al.},
+  pdftitle={Models of gravitational lens candidates from Space Warps CFHTLS}
+}
 
@@
 % These dates will be filled out by the publisher
-\date{Accepted XXX. Received YYY; in original form ZZZ}
+\date{Accepted 2017 November 19 . Received 2017 November 19 ; in original form 2017 May 02}
 

### 2017-12-04 KuengR__Lens_models.tex
editors corrections

@@
 \usepackage{xspace}   % handling of spaces after shortcuts
+\usepackage{siunitx}
 
@@
 \newcommand{\sqdeg}{\ensuremath{\,\text{deg}^2}\xspace}
-\renewcommand{\arcsec}{\ensuremath{\,^{\prime\prime}}\xspace}
+\renewcommand{\arcsec}{\ensuremath{\text{arcsec}}\xspace}
 
@@
 % These dates will be filled out by the publisher
-\date{Accepted 2017 November 19 . Received 2017 November 19 ; in original form 2017 May 02}
+\date{Accepted 2017 November 19. Received 2017 November 19; in original form 2017 May 02}
 
@@
 \begin{abstract}
-We report modelling follow-up of recently-discovered
+We report modelling follow-up of recently discovered
 gravitational-lens candidates in the Canada France Hawaii Telescope
 Legacy Survey. Lens modelling was done by a small group of
-specially-interested volunteers from the \SW citizen-science community
-who originally found the candidate lenses.  Models are categorised
+specially interested volunteers from the \SW citizen-science community
+who originally found the candidate lenses.  Models are categorized
 according to seven diagnostics indicating (a)~the image morphology and
@@
 (\sw{19}) and J2217+015 (\sw{42}); if these two are indeed lenses,
-they probe an interesting regime of very low star-formation
+they probe an interesting regime of very low star formation
 efficiency.  Some improvements to the modelling software

### 2017-12-04 parts/app.tex
make fig uniform
CLEAN UP code, removing comments
editors corrections

@@
 image.  In effect, one is reconstructing a source-plane brightness map
-by least-squares.
+by least squares.
 
@@
     synthetic image (coloured arcs) with lensing galaxy and unrelated
-    objects in greyscale.  Bottom from left to right: reconstructed
-    source in colour, intensity (greyscale), count of lens plane
-    pixels per source plane pixel, residual of original image to
+    objects in grey-scale.  Bottom from left to right: reconstructed
+    source in colour, intensity (grey-scale), count of lens-plane
+    pixels per source-plane pixel, and residual of original image to
     synthetic image.}
@@
 more steeply near the centre, was suggested as a possible cure.
-%\textcolor{red}{\bf IF: I don't even know what you mean by the last
-%  sentence: were those measures already implemented in the work
-%  described in that paper, or were these things considered a solution
-%  to the shallow profiles? Please clarify.}
 
@@
 tiles in the inner region.  Replacing the very central mass tile with
-9 smaller tiles allows for steeper central profiles.  Doing the same
+nine smaller tiles allows for steeper central profiles.  Doing the same
 for the 25 innermost mass tiles allows for even steeper central
@@
 it does not provide a completely satisfactory solution, because (a)~it increases
-the number of mass tiles by 40\% and significantly increases the
+the number of mass tiles by \SI{40}{\%} and significantly increases the
 computational time, and (b)~the square boundary between areas with
 different tile sizes is rather undesirable.
-% 689 / 489 = 1.40899; in practice, runtime is more like x4 - x5!
-% runtimes from logfiles: 87/22, 86/21, 85/16
 The main modelling work in this paper was, however, done before the
-experiments with smaller mass tiles was complete.  Some of the models
+experiment with smaller mass tiles was complete.  Some of the models
 presented in this paper apply the intermediate option (corresponding
@@
     answer.  The orange band represents the statistical ensemble from
-    SpaghettiLens, the orange line shows the ensemble mean.  Locations of
+    \SpL, and the orange line shows the ensemble mean.  Locations of
     images (maximum, saddle point, minimum) are marked with vertical
@@
     \citet{2015MNRAS.447.2170K}, see fig.~3 of that paper.  The middle
-    panel is the result when the innermost mass tile is replaced by 9
+    panel is the result when the innermost mass tile is replaced by nine
     smaller tiles.  The lower panel results from replacing the
-    innermost 5$\times$5 tiles with 9 smaller tiles each.}
+    innermost 5$\times$5 tiles with nine smaller tiles each.}
   \label{fig:subsampling}
@@
 In order to fit the set of pixelated models to a single parametrized
-model, a programme was written that took a parametrized function and
+model, a program was written that took a parametrized function and
 subtracted from it the mean and the principal components (PCs) of the
-data. This created the residual function.  The number of principal
-components in the analysis was varied, to test how this affected the
-output. It was found that 5 PCs gave a reasonable approximation. A
+data. This created the residual function.  The number of PCs in
+the analysis was varied, to test how this affected the
+output. It was found that five PCs gave a reasonable approximation. A
 masking function was added, selecting only the data points that fell
@@
 than the clip was set to be the clip value. This was chosen to 2.5
-because, assuming that the data follows a Gaussian error distribution,
+because, assuming that the data follow a Gaussian error distribution,
 almost all the values for the variance should lie between 2 and 3
-standard deviations from the mean. Minimising the residuals function
+standard deviations from the mean. Minimizing the residuals function
 produces the set of parameters that fit the parametrized function to
 the original pixelated ensemble most closely.  A least squares fit was
-used to perform this minimisation.  The parametrized model function
+used to perform this minimization.  The parametrized model function
 was obtained from the gravitational potential of an isothermal
@@
   \caption{ Comparison of Einstein radii \ER\ obtained from mass tiles
-    to the results from a parameterized model to test the performance
-    of the algorithm.  The parameterized model was generated using
+    to the results from a parametrized model to test the performance
+    of the algorithm.  The parametrized model was generated using
     principal component analysis on the ensemble of models.  The blue

### 2017-12-04 parts/figures.tex
editors corrections

@@
   The curves help guide the placement of the dots, but their precise
-  appearance has no significance.  This images are screenshots from the 
+  appearance has no significance.  These images are screenshots from the 
   SpaghettiLens user interface, which applies interpolation to background
@@
 \caption{Arrival-time surfaces for models of the systems from
-  Figure~\ref{fig:splinput}.  The registration differs slightly from
-  Figure~\ref{fig:splinput}, but the coloured dots represent exactly
+  Fig.~\ref{fig:splinput}.  The registration differs slightly from
+  Fig.~\ref{fig:splinput}, but the coloured dots represent exactly
   the sky positions specified in the earlier figure.  The orange
@@
 \caption{Synthetic images of the systems from
-  Figure~\ref{fig:splinput}, derived from the lens models.  The
-  reconstructed lensed features keep the Space~Warps false-colour
-  scheme from Figures~\ref{fig:splinput}.  The rest has been changed
-  to black-and-white. 
+  Fig.~\ref{fig:splinput}, derived from the lens models.  The
+  reconstructed lensed features keep the \SW false-colour
+  scheme from Fig~\ref{fig:splinput}.  The rest has been changed
+  to black and white.
   \label{fig:synth}}
@@
 \caption{Ensemble-average mass distribution $\kappa$ for which the
-  results Figures~\ref{fig:arriv}--\ref{fig:synth} were derived.  The
+  results Figs~\ref{fig:arriv}--\ref{fig:synth} were derived.  The
   dashed curves denote $\kappa=1$.  Most of the mass maps have a
-  $180^\circ$-rotation symmetry, which is imposed by default.  For
+  \SI{180}{\degree}-rotation symmetry, which is imposed by default.  For
   \sw{02} and \sw{57}, where the lensing mass is clearly asymmetric, the
@@
 \caption{Cumulative circular-averages of the mass maps from
-  Figure~\ref{fig:kappa}, with uncertainties.  More precisely, we show
+  Fig.~\ref{fig:kappa}, with uncertainties.  More precisely, we show
   the enclosed mass within a given projected radius, expressed as the
@@
   radius, or where the mean enclosed $\kappa$ is unity.  The short
-  vertical arrows marks the positions of the images (maxima, saddle
+  vertical arrows mark the positions of the images (maxima, saddle
   points and minima).
@@
   bars are the systems shown in detail in
-  Figures~\ref{fig:splinput}--\ref{fig:encl}.)  The horizontal extent
-  of each bar indicates the extreme cases of a young (0.5~Gyr-old)
+  Figs~\ref{fig:splinput}--\ref{fig:encl}.)  The horizontal extent
+  of each bar indicates the extreme cases of a young (\SI{0.5}{Gyr}-old)
   stellar population and the oldest possible population at the given

### 2017-12-04 parts/intro.tex
corrected typo...
editors corrections

@@
 By a curious coincidence, the typical escape velocity of massive
-galaxies -- of order a few hundred km/s -- is such that $v_{\rm
+galaxies -- of the order of a few hundred km/s -- is such that $v_{\rm
   esc}^2/c^2$, expressed as an angular distance, is comparable to the
@@
 comparable to their size on the sky. As a result, strong lensing by
-galaxies produces images that probe their host dark matter halos,
+galaxies produces images that probe their host dark matter haloes,
 providing a useful tool to understand galaxy formation.  While there
@@
 distribution.  Recent searches through the CFHT Lens Survey
-\citep[CFHTLS,][]{2012MNRAS.427..146H} using arc-finders
-\citep[e.g.,][]{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G,2017arXiv170401585S}
+\citep[CFHTLS;][]{2012MNRAS.427..146H} using arc-finders
+\citep[e.g.][]{2012ApJ...749...38M,2014A&A...567A.111M,2014ApJ...785..144G,2017arXiv170401585S}
 by either machine learning methods
@@
 The idea is to collaborate with experienced members of the
-citizen-science community, who have already participated in lens
+citizen-science community who have already participated in lens
 discovery through \SW, as well as several other projects involving
@@
 trends observed with the already available data, based on some 300 models
-created by 8 volunteers for 58 candidate lenses found in the 150\sqdeg
+created by eight volunteers for 58 candidate lenses found in the 150\sqdeg
 CFHTLS.
 
-This paper is organized as follows:
+This paper is organized as follows.
 Section~\ref{sec:candidates_models} introduces the candidate lenses,
@@
 presented in Section~\ref{sec:stellar-mass}, to compare stellar and
-lensing masses.  Finally, section~\ref{sec:summary}
-summarises and tabulates the diagnostics in Table~\ref{tab:models}.
+lensing masses.  Finally, Section~\ref{sec:summary}
+summarizes and tabulates the diagnostics in Table~\ref{tab:models}.
 
@@
 
-\SW is a citizen science gravitational lens search
+\SW is a citizen-science gravitational lens search
 \citep{2016MNRAS.455.1171M}.  Its first run searched the CFHT Legacy
@@
 ($u^*$,$g^\prime$,$r^\prime$,$i^\prime$,$z^\prime$) covering a total
-area of 160\sqdeg divided up into four fields W1 -- W4.  The
+area of \SI{160}{\sqdeg} divided up into four fields W1--W4.  The
 MegaPrime camera, used for the survey, has a field of view of
-1\sqdeg, with $0.186\arcsec$ pixels. The flux limit of the
+\SI{1}{\sqdeg}, with \SI{0.186}{\arcsec} pixels. The flux limit of the
 survey is $g^\prime<25.6\,\text{AB}$ ($5 \sigma$) with a typical seeing
-FWHM $\sim 0.7\arcsec$ \citep{2013MNRAS.433.2545E}. The cutouts
+FWHM $\sim \SI{0.7}{\arcsec}$ \citep{2013MNRAS.433.2545E}. The cutouts
 shown to the volunteers were colour composites of the $g^\prime$,
@@
 considered high quality.
-Moreover, 82 previously known lens candidates were ``rediscovered''.
+Moreover, 82 previously known lens candidates were `rediscovered'.
 The candidates have broadly similar redshifts ($0.2<z<1.0$), Einstein
-radii between 0.7 and 5\arcsec, and arc fluxes in $g$-band AB
+radii between 0.7 and \SI{5}{\arcsec}, and arc fluxes in $g$-band AB
 magnitudes between 22 and 26. These properties are
@@
   \caption{ Number of models generated over time in days since the
-    launch of \SpL; the black line shows all models, the coloured
+    launch of \SpL; the black line shows all models, and the coloured
     lines show the five most active candidates. A total of 377 models
@@
 
-A first version of \SpL was launched in May 2013, while
+A first version of \SpL was launched in 2013 May, while
 the first run of \SW was ongoing.  Fig.~\ref{fig:time} shows the
@@
 candidates from \SW that were debated in the discussion forum.  In the
-beginning of August 2013 (around day 70 since release) a modelling
+beginning of 2013 August (around day 70 since release), a modelling
 challenge for the candidate later to be identified as \sw{01} was
@@
 online letter
-converging on a set of 30 models. In April 2015 (day 700),
+converging on a set of 30 models. In 2015 April (day 700),
 the first major version of \SpL was released. At the same time,
@@
 asked to create models for all the lens candidates that were still
-missing.  The work done for candidate \sw{29} show that the
+missing.  The work done for candidate \sw{29} shows that the
 volunteers converged on a favourable model much faster, after 15
@@
 
-We characterise each model with seven diagnostics, grouped into three
+We characterize each model with seven diagnostics, grouped into three
 categories, whose purpose is to help identify the most likely cases of
@@
 \begin{itemize}
-\item Firstly we have diagnostics based on morphology.
+\item First, we have diagnostics based on morphology.
   Section~\ref{sec:morph} and Fig.~\ref{fig:splinput} explain
@@
 \item The image morphology concisely described: double or quads,
-  further sub-categorised to indicate the elongation direction of the
+  further sub-categorized to indicate the elongation direction of the
   lensing mass.
 \end{enumerate}
-\item Secondly we have mass models, covered in Section~\ref{sec:massmodels}.
+\item Secondly, we have mass models, covered in Section~\ref{sec:massmodels}.
   We assess the following points:
@@
   additional images are implied in regions
-  where they are not observed (see Figs.~\ref{fig:arriv}, \ref{fig:synth} \ref{fig:encl}).
+  where they are not observed (see Figs.~\ref{fig:arriv}, \ref{fig:synth} and \ref{fig:encl}).
 \end{enumerate}
@@
   Section~\ref{sec:stellar-mass} explains how we compare the lensing
-  mass with the stellar mass.  Galaxies may have halos extending well
+  mass with the stellar mass.  Galaxies may have haloes extending well
   beyond the mass maps in the models, so the calculated lensing mass
@@
 \setcounter{enumi}{6}
-\item We then introduce a so-called halo index ($\haloindex$), that
+\item We then introduce a so-called halo index ($\haloindex$), which
   quantifies how the lensing mass compares with these two

### 2017-12-04 parts/massmodel.tex
editors corrections

@@
 lensing galaxy and extending to twice the radius of the outermost
-image.  By default, the mass distributed is required to have
-$180^\circ$ rotation symmetry, but this option can be unset.  Assuming
-mass distributions can be found -- which in practice is usually the
-case -- a statistical ensemble of 200 two-dimensional mass maps is
+image.  By default, the mass distributed is required to have a
+\SI{180}{\degree}-rotation symmetry, but this option can be unset.  Assuming
+mass distributions can be found, which in practice is usually the
+case, a statistical ensemble of 200 two-dimensional mass maps is
 returned.  From each mass map, further quantities such as lens
@@
 ensembles of 200 values for the surface density at any point, for the
-enclosed mass within a given radius and so on.  In this paper we
+enclosed mass within a given radius and so on.  In this paper, we
 present the averages and ranges of different quantities, but other
-quantities such as 90\% confidence ranges could also be computed.  The
+quantities such as \SI{90}{\%} confidence ranges could also be computed.  The
 whole ensemble of mass maps, along with derived quantities and
@@
 better redshift values, as they become available.  The mass
-normalisation of the models is proportional, through the angular
+normalization of the models is proportional, through the angular
 critical density, to the factor $d_L\, d_S\, d_{LS}^{-1}$, where
 $d_L,d_S$ and $d_{LS}$ are the usual angular-diameter distances.  In
-the redshift ranges typical of galaxy lensing, the normalisation
+the redshift ranges typical of galaxy lensing, the normalization
 factor is roughly proportional to the lens redshift, and weakly
@@
 
-The arrival-time surface and synthetic image are summarised by one
+The arrival-time surface and synthetic image are summarized by one
 diagnostic, the most important of all: are the lensed features
@@
 modelling process, available in the online version.  It is
-interesting, however, to note the tiling artifacts, if only as a
+interesting, however, to note the tiling artefacts, if only as a
 reminder that the substructure in the mass distribution is very
 uncertain, even if some integrated quantities are  well
-constrained.  How the free-form mass maps relate to parameterised lens
+constrained.  How the free-form mass maps relate to parametrized lens
 models is discussed in Appendix~\ref{subsec:parameter}.
@@
 Fig.~\ref{fig:encl} shows the enclosed-mass profiles, expressed as the
-average convergence, $\kappa$, within circles of given projected
+average convergence, $\kappa$, within circles of a given projected
 radius.  Uncertainties are included (see the figure caption for
@@
 process of creating models as a criteria of a successful model, the evaluation 
-presented in this work however was generated by the authors during post 
-processing.
+presented in this work however was generated by the authors during
+post-processing.

### 2017-12-04 parts/morph.tex
CLEAN UP code, removing comments
working on report/letter2
editors corrections

@@
 are intuitive because they tend to resemble the form of lensed arcs
-\citep[see Fig.3 of][]{2008MNRAS.383..857F}, and of course they are
+\citep[see Fig.~3 of][]{2008MNRAS.383..857F}, and of course they are
 simple to draw, and easy to vary and refine in an open collaborative
@@
 The volunteers are initially presented a square image with side
-82\arcsec (440~pixels) in full size, but they have the
+\SI{82}{\arcsec} (\SI{440}{pixels}) in full size, but they have the
 ability to zoom in individually.
-The cutouts presented in Figs.~\ref{fig:splinput} to \ref{fig:kappa}
+The cutouts presented in Figs.~\ref{fig:splinput}--\ref{fig:kappa}
 are rescaled during post-processing, relative to the outermost image.
-% it's a factor L/(L-4) with L=pixradius, for L=12 -> 1.5
-% maprad = rmax * L / (L-4)
 
@@
 The third diagnostic tests whether the lens is isolated, or whether
-other galaxies could contribute to the lensing.  For this, we do not
-consider stars or other clearly foregound objects.  Additional
+other galaxies could contribute to the lensing, based on visual inspection 
+of the field.
+For this, we do not
+consider stars or other clearly foreground objects.  Additional
 galaxies contributing to the lensing mass can be marked by the
@@
 We remark that the lack of expected lensed images, or the presence of
-blended images or perturbing galaxies do not imply that a given
+blended images or perturbing galaxies, does not imply that a given
 candidate is unlikely to be a lens.  This means, rather, that the
@@
 The fourth diagnostic is based on the fact that the arrangement of
-lensed images of a pointlike source through a non-circular
+lensed images of a point-like source through a non-circular
 gravitational lens depends on the location of the source relative to
@@
 produce doubles.  We denote these as Q and D, respectively, and add a
-prefix to the Q systems, as follows: we write LQ if the source is
+prefix to the Q systems as follows: we write LQ if the source is
 inferred as displaced along the long axis of the lens, SQ if displaced
-along the short axis, IQ if inclined to both axes, CQ if only very little or
+along the short axis, IQ if inclined to both axes, and CQ if only very little or
 no displacement is evident.  Although the
 unlensed source and its location are obviously not seen, the LQ, SQ, IQ and CQ
-cases correspond to easily-seen image morphologies \citep[see,
+cases correspond to easily seen image morphologies \citep[see,
   e.g.,][]{2003AJ....125.2769S}.
+
 \begin{itemize}
@@
   systems: \sw{09}, \sw{29} and \sw{02}. The failed model, \sw{57}, at top right
-  may also belong to this category.  Here the images have a
+  may also belong to this category.  Here, the images have a
   fairly symmetric arrangement with an arc and a counter-image on the
@@
   the source were moved outwards along the long axis, the
-  saddle-minimum-saddle set  would merge into a single saddle --- another
+  saddle-minimum-saddle set  would merge into a single saddle -- another
   form of cusp catastrophe.  SQ can be visually distinguished from LQ
   by the relative distances of the arc and the counter-image.  For
-  SQ the arc is closer, for LQ the counter-image is closer.
+  SQ, the arc is closer, and for LQ the counter-image is closer.
 \end{itemize}
@@
 standard in the literature, but the morphological classification they
-express is familiar to experienced modellers.  Hence they can be
+express is familiar to experienced modellers.  Hence, they can be
 useful to researchers wishing to apply other modelling methods to the

### 2017-12-04 parts/stelmass.tex
editors corrections

@@
 
-The stellar masses of the lens galaxies are derived by comparison of
+The stellar masses of the lens galaxies are derived by a comparison of
 the photometric data with stellar $M/L$ estimates from population
@@
 at the redshifts probed, the photometric data mainly
-constrain the information-rich 4000\thinspace\AA~break region, whose
+constrain the information-rich \SI{4000}{\angstrom} break region, whose
 strength depends sensitively on age and metallicity, thereby
 providing a strong constraint on the stellar $M/L$.  Hence,
-estimates to within $\sim$0.3\,dex in $\log(\Mstel/\Msun)$ can be derived
+estimates to within $\sim \SI{0.3}{dex}$ in $\log(\Mstel/\Msun)$ can be derived
 with a single colour, preferably tracing a rest-frame colour similar
@@
 galaxies can feature a non-standard IMF 
-\citep[e.g.][]{2013MNRAS.429L..15F}. However, these variations --
-towards a bottom-heavy distribution -- are typically found in the
+\citep[e.g.][]{2013MNRAS.429L..15F}. However, these variations,
+towards a bottom-heavy distribution, are typically found in the
 cores of massive early-type galaxies \citep{2016MNRAS.457.1468L}. The
@@
 
-In this paper we further simplify the analysis by assuming a
+In this paper, we further simplify the analysis by assuming a
 relationship between the apparent total magnitude and stellar mass, at
 the redshift of the lens.  For typical stellar-population parameters,
-the variation of this relation is at most $\Delta\log$M$_s\sim$1\,dex.
+the variation of this relation is at most
+$\Delta \log \Mstel \sim \SI{1}{dex}$.
 A further potential systematic can arise from contamination of the
@@
 magnitudes. The models have solar metallicity, with a Chabrier IMF,
-and assume two different age trends: a ``young'' model, with a
-constant 500\,Myr age at all redshifts, and an ``old'' model where the
+and assume two different age trends: a `young' model, with a
+constant $\SI{500}{Myr}$ age at all redshifts, and an `old' model where the
 age is the oldest one possible at each redshift, adopting a standard
-$\Lambda$CDM model with $H_0=70$\,km\,s$^{-1}$\,Mpc$^{-1}$ and
+$\Lambda$CDM model with $H_0 = \SI{70}{km.s^{-1}.Mpc^{-1}}$ and
 $\Omega_m=0.3$.
@@
 stellar mass (horizontal axis) shows the range between the masses
-derived using the two age trends respectively, and lies between 0.4 and
-0.8\,dex.  It will be improved in future work by the use of available
+derived using the two age trends, respectively, and lies between 0.4 and
+\SI{0.8}{dex}.  It will be improved in future work by the use of available
 optical and NIR magnitudes to derive more accurate constraints on the
@@
 relation between stellar mass and halo mass.  We emphasize that a halo
-mass from abundance matching should be considered an ``average''
+mass from abundance matching should be considered an `average'
 estimate, and a significant scatter can be expected as galaxies with
@@
 \begin{align*}
-    C_0 &= 0.02820, & M_1 &= 10^{11.884} M_\odot \\
+    C_0 &= 0.02820, & M_1 &= \SI{e11.884}{\Msun} \\
     \beta &= 1.057, & \gamma &= 0.556.
@@
 \item $\haloindex = 1$ means that the lens consists of the entire halo.
-\item $\haloindex > 1$ is in tension with abundance-matching, because the
+\item $\haloindex > 1$ is in tension with abundance matching, because the
   lensing mass exceeds the expected halo mass.
@@
 diagnostics leave some doubts about the validity of this model.  The
-two lowest-mass systems, \sw{19} and \sw{42}, are important if they are
+two lowest mass systems, \sw{19} and \sw{42}, are important if they are
 indeed lenses, as they would be low-mass lenses dominated by dark

### 2017-12-04 parts/summary.tex
working on letter2
editors corrections

@@
 approach that aims to be scalable by {\sl orders of magnitude} to
-prepare for the many thousands of lenses the next generation of wide
-field surveys will yield (e.g. Euclid, WFIRST).
+prepare for the many thousands of lenses the next generation of
+wide-field surveys will yield (e.g. Euclid and WFIRST).
 
 Over the past few years, the way of discovering lenses has changed
-with the introduction of machine learning and citizen science methods,
+with the introduction of machine learning and citizen-science methods,
 combined with the coverage of large areas of the sky by modern
@@
 candidates.  The work in this paper represents a hybrid approach
-between the classical style -- where a small team of experts invest
-many hours into the creation of a single model -- and a citizen
-science project -- where a crowd of amateur volunteers make
+between the classical style, where a small team of experts invests
+many hours into the creation of a single model, and a citizen-science
+project, where a crowd of amateur volunteers makes
 independent contributions.  The authors of this paper are a
@@
 To assist volunteers in constraining lensing models, we introduce a
-set of diagnostics that help asses the validity of the models. At a
+set of diagnostics that helps us to assess the validity of the models. At a
 later stage, we encourage modellers to apply those diagnostics as
@@
 
-The diagnostics (i) -- (iv) (see Section.~\ref{sec:candidates_models})
+The diagnostics (i)--(iv) (see Section.~\ref{sec:candidates_models})
 turned out to be useful measures of the difficulty in modelling a
@@
 to be easy enough to grasp by new volunteers.  The halo-matching
-index diagnostic (vii, $\haloindex$), is an interesting criterion that
+index diagnostic (vii, $\haloindex$) is an interesting criterion that
 might be useful for the modellers, but needs further investigation.
 
-Table~\ref{tab:models} is a summary of our results.  It characterises
+Table~\ref{tab:models} is a summary of our results.  It characterizes
 each modelled system with seven diagnostics, indicating (a)~the image
@@
 progressively more dark-matter dominated, is expected
-\citep[see, e.g.][]{2005ApJ...623L...5F}, as is the span of about one
+\citep[see e.g.][]{2005ApJ...623L...5F}, as is the span of about one
 order of magnitude for the stellar mass and the two orders of
@@
 going from the star-dominated inner regions to the outer dark
-halos. \citet{2011ApJ...740...97L} illustrate this behaviour in their
-Fig.~5, but the present sample could go an order of magnitude higher
+haloes. \citet{2011ApJ...740...97L} illustrate this behaviour in their
+fig.~5, but the present sample could go an order of magnitude higher
 in mass.
@@
 The quick creation of many models for the {\SW} candidates
-successfully showed that a subset of citizen scientists are interested
+successfully showed that a subset of citizen-scientists is interested
 in being involved in more challenging tasks that take some time to
@@
 soon as the next round of {\SW} is started. In the meantime, the
-improvements shown in the Appendix will be integrated in the standard
+improvements shown in the appendix will be integrated in the standard
 version of {\SpL}. Photometric fitting could also be
@@
 scientists to generate photometric redshifts and stellar masses, and
-thus generate preliminary dark-matter maps as soon as a lens-candidate
+thus generate preliminary dark-matter maps as soon as a lens candidate
 is identified.
+
+\section{Acknowledgements}\label{sec:ack}
+This work was supported by the University of Zurich
+Candoc reseach grant (Forschungskredit Candoc; FK-14-
+081 and FK-15-087).
